### 2021-06-18 Methods and Results.Rmd
Update

---
title: "Methods and Results"
author: "L Heron"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

###############################################################
# Question 1: results output                         ##########
# Proportion of asymptomatic cases                   ##########
###############################################################

#load the libraries
library(meta)
library(readxl)
library(tidyverse)
library(httr) 
library(RCurl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(metafor)
library(kableExtra)

# Prepare the data
# get the data directly from redcap:
# report #155 is Q1:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='155',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response <- httr::POST(url, body = formData, encode = "form")
asymptomaticQ1 <- httr::content(response)

settings=c("Contact investigation",
           "Contact investigation, aggregated",
           "Outbreak investigation",
           "Statistical model",
           "Screening",
           "Hospitalised adults",
           "Hospitalised children",
           "Hospitalised adults & children")

asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:8, labels=settings)

# minor cleaning
asymptomaticQ1[asymptomaticQ1==9999]=NA

asymptomaticQ1$setting=asymptomaticQ1$setting2

data_long1 <- gather(asymptomaticQ1, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
  mutate(id=1:nrow(.)) %>%
  select(record_id, author_1, setting, total, id, cluster)
data_long2 <-gather(asymptomaticQ1, cluster, events, c(q1_c1_event,q1_c2_event,q1_c3_event), factor_key=TRUE) %>% 
  mutate(id=1:nrow(.)) %>%
  select(events, id)

data_Q1 = merge(data_long1, data_long2, by="id")
data_Q1 = data_Q1[!is.na(data_Q1$total),]
data_Q1$cluster=factor(data_Q1$cluster,labels=c("1","2","3"),levels=c("q1_c1_total","q1_c2_total","q1_c3_total"))

data_Q1[data_Q1$record_id %in% asymptomaticQ1[is.na(asymptomaticQ1$q1_c2_event),]$record_id,]$cluster=NA

asymptomaticQ1=data_Q1

asymptomaticQ1$label=paste0("#", asymptomaticQ1$record_id, " ", asymptomaticQ1$author_1, " (2020)",ifelse(!is.na(asymptomaticQ1$cluster),paste0(" cluster:",asymptomaticQ1$cluster),"")) # [FU: ",asymptomaticQ1$fup_median,"]")

asymptomaticQ1$label=paste0("#", asymptomaticQ1$record_id, " ", asymptomaticQ1$author_1,ifelse(!is.na(asymptomaticQ1$cluster),paste0(" [cluster:",asymptomaticQ1$cluster,"]"),"")) # [FU: ",asymptomaticQ1$fup_median,"]")

data=asymptomaticQ1[order(asymptomaticQ1$setting,1/(1/asymptomaticQ1$events+1/(asymptomaticQ1$total-asymptomaticQ1$events))),]

data[is.na(data$setting),]$record_id
data=data[!is.na(data$setting),]

asym_plot<-metaprop(events,total,data=data,sm = "PLOGIT", studlab=label, 
                    byvar=setting,# tau.common =TRUE,
                    control=list(stepadj=0.05, maxiter=10000))#, method ="INV") #, verbose=TRUE, digits=5, control=list(stepadj=0.5))

png(file = 'forest_meta_Q1.png',width=25,height=65, res=600, units="cm")

forest(asym_plot,  col.square=data$setting,
       #squaresize = 1/(1/data$events+1/(data$total-data$events)),
       #sortvar = 1/(1/events+1/(total-events)), 
       subgroup=TRUE, 
       just.studlab="left", colgap.studlab="2cm",
       #leftcols = c("label", "setting", "age", "design", "asym_denom"),
       #leftcols=c("studlab", "record_id", "event", "n"),
       xlab = "",just="left",comb.random=TRUE,test.subgroup.random=FALSE,
       comb.fixed=FALSE,test.subgroup.fixed=FALSE, predict=T)#, study.results=TRUE,test.subgroup=TRUE)
dev.off()

q1_nstudies <- nrow(asym_plot$data) #total number of studies included in q1
q1_nppl <- prettyNum(sum(asymptomaticQ1$total), big.mark = ",") #total number of people included in q1
q1_nasymp <-  prettyNum(sum(asymptomaticQ1$events), big.mark = ",") #number of people asymptomatic included in q1

###############################################################
# Question 2.1: results output ################################
# Secondary attack rate from asymp or pre-symp cases ##########
###############################################################

# get the data directly from redcap: 
# report #172 is Q2.1 SAR:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData2_1 <- list("token"=token,
                    content='report',
                    format='csv',
                    report_id='172',
                    csvDelimiter='',
                    rawOrLabel='raw',
                    rawOrLabelHeaders='raw',
                    exportCheckboxLabel='false',
                    returnFormat='json'
)
response2_1 <- httr::POST(url, body = formData2_1, encode = "form")
asymptomaticQ2_1 <- httr::content(response2_1)

#clean data
asymptomaticQ2_1[asymptomaticQ2_1=="9999;9999"]=NA #indicate as missing
asymptomaticQ2_1[asymptomaticQ2_1=="9999"]=NA #indicate as missing
asymptomaticQ2_1=asymptomaticQ2_1%>% #separate symp SAR into 2 variables
  separate(q3_sar_s, c("Ec","Nc"), ";", remove=FALSE) 
asymptomaticQ2_1=asymptomaticQ2_1%>% #separate asymp SAR into 2 variables
  separate(q3_sar_a, c("Ee_a","Ne_a"), ";", remove=FALSE) 
asymptomaticQ2_1=asymptomaticQ2_1%>% #separate presymp SAR into 2 variables
  separate(q3_sar_p, c("Ee_p","Ne_p"), ";", remove=FALSE)

asymptomaticQ2_1=asymptomaticQ2_1 %>% #change values to numeric
  mutate(Ec=as.numeric(Ec),
         Nc=as.numeric(Nc),
         Ee_a=as.numeric(Ee_a),
         Ne_a=as.numeric(Ne_a),
         Ee_p=as.numeric(Ee_p),
         Ne_p=as.numeric(Ne_p))

#metaanalysis for asymptomatic transmission

q2_1_asymp <- metabin(event.e = Ee_a,
                      n.e = Ne_a,
                      event.c = Ec,
                      n.c = Nc, 
                      data = asymptomaticQ2_1[!is.na(asymptomaticQ2_1$Ee_a),],
                      studlab = author_1,
                      prediction = TRUE,
                      sm = "RR",
                      method = "MH",
                      MH.exact = TRUE)
q2_1_asymp

png(file = 'forest_meta_Q2_1_asymp.png',width=750,height=250)

forest(q2_1_asymp)

dev.off()

#metaanalysis for presymptomatic transmission

q2_1_presymp <- metabin(event.e = Ee_p,
                        n.e = Ne_p,
                        event.c = Ec,
                        n.c = Nc, 
                        data = asymptomaticQ2_1[!is.na(asymptomaticQ2_1$Ee_p),],
                        studlab = author_1,
                        prediction = TRUE,
                        sm = "RR",
                        method = "MH",
                        MH.exact = TRUE)

q2_1_presymp

png(file = 'forest_meta_Q2_1_presymp.png',width=750,height=190)

forest(q2_1_presymp)

dev.off()

###############################################################
# Question 2.2: results output ################################
# Proportion of transmission from asymp or pre-symp ###########
###############################################################

# get the data directly from REDCap: 
# report #157 is Q2.2:

url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData2_2 <- list("token"=token,
                    content='report',
                    format='csv',
                    report_id='157',
                    csvDelimiter='',
                    rawOrLabel='raw',
                    rawOrLabelHeaders='raw',
                    exportCheckboxLabel='false',
                    returnFormat='csv'
)
response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
asymptomaticQ2_2 <- httr::content(response2_2)

#clean data
asymptomaticQ2_2[asymptomaticQ2_2=="9999;9999"]=NA #indicate as missing
asymptomaticQ2_2[asymptomaticQ2_2 == "9999"] = NA #indicate as missing

#create a separate dataset for the records with >1 result
two_models <- asymptomaticQ2_2
#separate into 2 variables
two_models = two_models %>% 
  separate(q3_pp_m, c("q3_pp_m_1","q3_pp_m_2"), ";")
two_models = two_models %>% 
  separate(q3_pp_l, c("q3_pp_l_1","q3_pp_l_2"), ";") 
two_models = two_models %>%
  separate(q3_pp_u, c("q3_pp_u_1","q3_pp_u_2"), ";")
two_models = two_models %>% 
  separate(q3_setting, c("q3_setting_1","q3_setting_2"), ";")

two_models <- two_models %>% #change values to numeric
  mutate(q3_pp_m_1=as.numeric(q3_pp_m_1),
         q3_pp_m_2=as.numeric(q3_pp_m_2),
         q3_pp_l_1=as.numeric(q3_pp_l_1),
         q3_pp_l_2=as.numeric(q3_pp_l_2),
         q3_pp_u_1=as.numeric(q3_pp_u_1),
         q3_pp_u_2=as.numeric(q3_pp_u_2))

two_models <- two_models[!is.na(two_models$q3_pp_m_2),]

substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

L1 <- two_models %>%
  pivot_longer(cols = c(6:7),
               names_to = "model",
               values_to = "q3_pp_m") 
L1$label <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")
L2 <- two_models %>%
  pivot_longer(cols = c(8:9),
               names_to = "model",
               values_to = "q3_pp_l") %>%
  select("record_id", "model", "q3_pp_l", "author_1")
L2$label <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
L2 <- L2 %>% select("q3_pp_l", "label")
L3 <- two_models %>%
  pivot_longer(cols = c(10:11),
               names_to = "model",
               values_to = "q3_pp_u") %>%
  select("record_id", "model", "q3_pp_u", "author_1")
L3$label <- paste(L3$author_1, " [", substrRight(L3$model, 1), "]", sep = "")
L3 <- L3 %>% select("q3_pp_u", "label")
L4 <- two_models %>%
  pivot_longer(cols = c(13:14),
               names_to = "model",
               values_to = "setting") %>%
  select("record_id", "model", "setting", "author_1")
L4$label <- paste(L4$author_1, " [", substrRight(L4$model, 1), "]", sep = "")
L4 <- L4 %>% select("setting", "label")
#merge together
Lall <- merge(L2, L3, by = "label")   
Lall <- merge(Lall, L4, by = "label") 
Lall <- merge(Lall, L1, by = "label")
Lall <- Lall %>%
  select("record_id", "author_1", "q3_pa_m", "q3_pa_l", "q3_pa_u", 
         "q3_pp_m", "q3_pp_l", "q3_pp_u", "question_3_complete", "setting", 
         "label")

#clean original dataset
asymptomaticQ2_2$label <- asymptomaticQ2_2$author_1
asymptomaticQ2_2 <- asymptomaticQ2_2 %>%
  mutate(setting = q3_setting)
asymptomaticQ2_2$q3_setting <- NULL
asymptomaticQ2_2 <- as.data.frame(asymptomaticQ2_2)
attr(asymptomaticQ2_2, 'spec') <- NULL
str(asymptomaticQ2_2)
asymptomaticQ2_2$q3_pp_m <- as.numeric(asymptomaticQ2_2$q3_pp_m)
asymptomaticQ2_2$q3_pp_l <- as.numeric(asymptomaticQ2_2$q3_pp_l)
asymptomaticQ2_2$q3_pp_u <- as.numeric(asymptomaticQ2_2$q3_pp_u)

#add extra rows to original dataset
Q2_2 <- bind_rows(asymptomaticQ2_2, Lall)
#if q3_pp_m and q3_pa_m both NA then delete
Q2_2 <- Q2_2[!is.na(Q2_2$q3_pa_m) | !is.na(Q2_2$q3_pp_m),]

#create new variable for all estimates and indicate asymp/presymp with new variable
#fill Q2_2 first with estimates from q3_pp_m then q3_pa_m
Q2_2 <- Q2_2 %>%
  mutate(estimate = ifelse(!is.na(q3_pp_m),
                           q3_pp_m,
                           q3_pa_m),
         lower_bound = ifelse(!is.na(q3_pp_m),
                                 q3_pp_l,
                                 q3_pa_l),
         upper_bound = ifelse(!is.na(q3_pp_m),
                                 q3_pp_u,
                                 q3_pa_u),
         subgroup = ifelse(!is.na(q3_pp_m),
                           "presymp",
                           "asymp"))
#some records have presymp estimates in estimate now - must make new observation
both <- Q2_2 %>%
  filter(!is.na(Q2_2$q3_pa_m) & !is.na(Q2_2$q3_pp_m)) %>%
  mutate(estimate = q3_pa_m,
         lower_bound = q3_pa_l,
         upper_bound = q3_pa_u,
         subgroup = "asymp")
Q2_2 <- bind_rows(Q2_2, both)
#remove unnecessary cols
Q2_2 <- Q2_2 %>%
  select(c("record_id", "label", "setting", "estimate", "lower_bound", "upper_bound", "subgroup"))
#round numbers to 2 decimal points
Q2_2$estimate <- round(Q2_2$estimate, digits = 2)
Q2_2$lower_bound <- round(Q2_2$lower_bound, digits = 2)
Q2_2$upper_bound <- round(Q2_2$upper_bound, digits = 2)

###############################################################
# forest plot

#prepare data
Q2_2_df <- Q2_2
#create label for proportions
Q2_2_df$prop <- sprintf("%2.2f", Q2_2_df$estimate)
#create label for 95% CIs
Q2_2_df$CI_lower <- sprintf("%2.2f", Q2_2_df$lower_bound)
Q2_2_df$CI_upper <- sprintf("%2.2f", Q2_2_df$upper_bound)
Q2_2_df$CIs <- paste("[", Q2_2_df$CI_lower, #paste together 95% CIs
                     ";", Q2_2_df$CI_upper, "]", 
                     sep = "")
Q2_2_df <- Q2_2_df %>%
  mutate(CI = ifelse(is.na(Q2_2_df$CI_lower), NA, CIs))
Q2_2_df$CI[Q2_2_df$CI == "[NA;NA]"] <- NA
str(Q2_2_df)
#col to indicate headings/studies in plot
Q2_2_df$type <- 2
#new row for asymptomatic label in plot
Asymp_label <- data.frame(NA, "Asymptomatic transmission", NA, NA, NA, NA, NA, 
                          NA, NA, NA, NA, NA, 1)
names(Asymp_label) <- names(Q2_2_df)
#new row for asymptomatic label in plot
Presymp_label <- data.frame(NA, "Presymptomatic transmission", NA, NA, NA, NA, NA, 
                            NA, NA, NA, NA, NA, 1)
names(Presymp_label) <- names(Q2_2_df)
#add to exisiting dataframe
Q2_2_df <- rbind(Q2_2_df, Asymp_label, Presymp_label)
#font indicator
Q2_2_df$fontface = ifelse(Q2_2_df$type == 1, "italic","plain")
str(Q2_2_df$fontface)

#arrange studies by subgroup
asymp_n <- sum(Q2_2_df$subgroup == "asymp", #number of asymp studies
               na.rm = TRUE) 
presymp_n <- sum(Q2_2_df$subgroup == "presymp", #number of presymp studies
                 na.rm = TRUE) 
Q2_2_df$line[Q2_2_df$label == "Asymptomatic transmission"] <- 1
#new row for space in plot
space <- data.frame(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA)
names(space) <- names(Q2_2_df)
#add to exisiting dataframe
Q2_2_df <- rbind(Q2_2_df, space)
Q2_2_df$line[is.na(Q2_2_df$label)] <- 2 + asymp_n
Q2_2_df$line[Q2_2_df$label == "Presymptomatic transmission"] <- 3 + asymp_n
Q2_2_df_a <- Q2_2_df %>% #order the asymp studies
  filter(subgroup == "asymp") %>%
  mutate(line = 2:(asymp_n + 1))
Q2_2_df_p <- Q2_2_df %>% #order the presymp studies
  filter(subgroup == "presymp") %>%
  mutate(line = (asymp_n + 4):(presymp_n + asymp_n + 3))
Q2_2_df <- Q2_2_df[is.na(Q2_2_df$record_id),]
#join all rows again
Q2_2_df <- rbind(Q2_2_df, Q2_2_df_a, Q2_2_df_p)

#create forest plot
p <- ggplot() + 
  geom_point(data = Q2_2_df, #add estimates 
             aes(y = line, 
                 x = estimate),
             fill = "gray", 
             shape = 22, 
             color = "black",
             size = 4) +
  geom_errorbarh(data = Q2_2_df, #add error bars 
                 aes(y = line, 
                     xmin = lower_bound, 
                     xmax = upper_bound), 
                 height=0.3) +
  geom_text(aes(y = c(-1, -1, -1),  #add cols for study, estimates and CIs
                x = c(-0.9, 1.25, 1.75), 
                label=c("Study", "Prop.", "95% CI")), 
            hjust = 0, 
            fontface = "bold") +
  geom_text(data = Q2_2_df, #add estimate labels
            aes(y = line, 
                x = 1.25, 
                label = prop), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add CI labels
            aes(y = line,
                x = 1.75,
                label = CI), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add study labels
            aes(y= line, 
                x=-0.9, 
                label = label,
                hjust = 0,
                fontface = fontface)) +
  theme_void() + #remove background
  scale_y_reverse() +
  geom_segment(data = Q2_2_df, #add line below point estimates
               aes(y = max(line) + 1, x = 0, xend = 1, 
                   yend = max(line) + 1)) +
  geom_segment(data = Q2_2_df, #add dash for 0
               aes(y = max(line) + 1, yend = max(line) + 1.3, 
                   x = 0, xend = 0)) +
  geom_segment(data = Q2_2_df, #add dash for 0.25
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x = 0.25, xend = 0.25)) +
  geom_segment(data = Q2_2_df, #add dash for 0.5
               aes(y = max(line)+1, yend=max(line) + 1.3,
                   x=0.5, xend=0.5)) +
  geom_segment(data = Q2_2_df, #add dash for 0.75
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x=0.75, xend = 0.75)) +
  geom_segment(data = Q2_2_df, #add dash for 1
               aes(y = max(line) + 1, 
                   yend = max(line) + 1.3,
                   x = 1, xend = 1)) +
  geom_text(aes(y = rep(max(Q2_2_df$line) + 2,5), #add numbers to line
                x = 0:4/4, 
                label = c(0.00,0.25,0.5,0.75,1.00)))

p

#create image file
png(file="forest_Q2_2.png", 
    res=300, 
    height=20, width=50, units="cm")
p
dev.off()

```

## Methods   
### Data analysis

## Results
### Q1: Proportion of asymptomatic cases

We included `r q1_nstudies` studies that reported empirical data about `r q1_nppl` people with SARS-CoV-2 infection (`r q1_nasymp` defined as having asymptomatic infection).

![Figure 1. Forest plot of proportion  of people with asymptomatic SARS-CoV-2 infection, stratified by setting](forest_meta_Q1.png)

### Q2.1: Secondary attack rate from asymptomatic and presymptomatic cases

![Figure 2. Forest plot of secondary attack rate comparing infections in contacts of asymptomatic index cases with infections in contacts of symptomatic cases](forest_meta_Q2_1_asymp.png)

![Figure 3. Forest plot of secondary attack rate comparing infections in contacts of presymptomatic index cases with infections in contacts of symptomatic cases](forest_meta_Q2_1_presymp.png)

### Q2.2: Proportion of transmission from asymptomatic or pre-symptomatic infections

![Figure 4. Forest plot of proportion of SARS-CoV-2 infection resulting from asymptomatic or presymptomatic transmission](forest_Q2_2.png)

### 2021-06-18 AsymptomaticAnalysis_Q2_2_Hira.R

@@ -1,0 +1,155 @@
+rm(list = ls())
+
+library(RCurl)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+
+# get the data directly from REDCap: 
+# report #157 is Q2.2:
+
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData2_2 <- list("token"=token,
+                    content='report',
+                    format='csv',
+                    report_id='157',
+                    csvDelimiter='',
+                    rawOrLabel='raw',
+                    rawOrLabelHeaders='raw',
+                    exportCheckboxLabel='false',
+                    returnFormat='csv'
+)
+response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
+asymptomaticQ2_2 <- httr::content(response2_2)
+
+
+library(dplyr)
+
+asymptomaticQ3 = asymptomaticQ2_2 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
+asymptomaticQ3$q3_setting=ifelse(asymptomaticQ3$q3_setting=="",NA,asymptomaticQ3$q3_setting)
+
+asymptomaticQ3 <- asymptomaticQ3[-9,]
+
+#Michel`s codes` - doesn`t work now`
+# s <- strsplit(asymptomaticQ3$q3_setting, split = ";")
+# pp_m <- strsplit(asymptomaticQ3$q3_pp_m, split = ";")
+# pp_l <- strsplit(asymptomaticQ3$q3_pp_l, split = ";")
+# pp_u <- strsplit(asymptomaticQ3$q3_pp_u, split = ";")
+
+#New codes Hira - 06.04.21
+s <- gsub(";"," ",asymptomaticQ3$q3_setting)
+pp_m <- gsub(";"," ",asymptomaticQ3$q3_pp_m)
+pp_l <- gsub(";"," ",asymptomaticQ3$q3_pp_l)
+pp_u <- gsub(";"," ",asymptomaticQ3$q3_pp_u)
+
+
+
+#Michel`s codes` - doesn`t work now`
+# dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ3$author_1), sapply(pp_m, length)),
[…]

### 2021-06-18 MC analysis v3.R

@@ -1,0 +1,70 @@
+dataG=df_Q3SAR
+dig=2
+r<-function(x){format(round(as.numeric(x),2),dig=2)}
+r2<-function(x){format(round(as.numeric(x),4),dig=2)}
+dataG$label=ifelse(dataG$type==2,paste0("   ",dataG$label),dataG$label)
+dataG$fontface=ifelse(dataG$type==1, "italic","plain")
+dataG$fontface=ifelse(dataG$type==3, "bold",dataG$fontface)
+dataG$label_studyCI=ifelse(!is.na(dataG$h), paste0("[",r(dataG$l),";",r2(dataG$h),"]"),NA)
+#dataG$label_studyCI=ifelse(!is.na(dataG$Pl), paste0("[",r(dataG$Pl),";",r(dataG$Ph),"]"),dataG$label_studyCI)
+#dataG$label_studyCI=ifelse(!is.na(dataG$Rl), paste0("[",r(dataG$Rl),";",r(dataG$Rh),"]"),dataG$label_studyCI)
+dataG$label_study=ifelse(!is.na(dataG$p),r(dataG$p),NA)
+dataG$label_studyC=ifelse(!is.na(dataG$nc),paste0(dataG$event.c,"/",dataG$nc),NA)
+dataG$label_studyE=ifelse(!is.na(dataG$ne),paste0(dataG$event.e,"/",dataG$ne),NA)
+
+breaks=c(0.01,0.1,1,10)
+
+
+dataG = dataG %>% mutate(Rp=ifelse(type==3, p, NA),
+                         Rl=ifelse(type==3, l, NA),
+                         Rh=ifelse(type==3, h, NA),
+                         p=ifelse(type!=3, p, NA),
+                         l=ifelse(type!=3, l, NA),
+                         h=ifelse(type!=3, h, NA))
+
+tmp=dataG[!is.na(dataG$Rl),]
+
+p=ggplot()+ 
+  geom_point(data=dataG,aes(y=dataG$line, x=log(dataG$p)),fill="gray", shape=22, color="black",size=4)+
+  geom_errorbarh(data=dataG,aes(y=dataG$line, xmin=log(dataG$l), xmax=log(dataG$h)), height=0.3)+
+  
+  
[…]

### 2021-06-18 Q1.R

@@ -1,0 +1,93 @@
+###############################################################
+# Question 1: results output                         ##########
+# Proportion of asymptomatic cases                   ##########
+###############################################################
+
+#load the libraries
+library(meta)
+library(readxl)
+library(tidyverse)
+library(httr) # use to retrieve data from REDCap
+
+# Prepare the data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+asymptomaticQ1 <- httr::content(response)
+
+
+settings=c("Contact investigation",
+           "Contact investigation, aggregated",
+           "Outbreak investigation",
+           "Statistical model",
+           "Screening",
+           "Hospitalised adults",
+           "Hospitalised children",
+           "Hospitalised adults & children")
+
+
+asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:8, labels=settings)
+#combine contact investigation and contact investigation aggregated
+asymptomaticQ1$setting2[asymptomaticQ1$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"
+
+# minor cleaning
+asymptomaticQ1[asymptomaticQ1==9999]=NA
+
+asymptomaticQ1$setting=asymptomaticQ1$setting2
+
+
+data_long1 <- gather(asymptomaticQ1, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
+  mutate(id=1:nrow(.)) %>%
+  select(record_id, author_1, setting, total, id, cluster)
[…]

### 2021-06-18 Q2_1.R

@@ -1,0 +1,113 @@
+###############################################################
+# Question 2.1: results output ################################
+# Secondary attack rate from asymp or pre-symp cases ##########
+###############################################################
+
+
+#load libraries
+library(RCurl)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(meta)
+library(metafor)
+
+# get the data directly from redcap: 
+# report #172 is Q2.1 SAR:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData2_1 <- list("token"=token,
+                    content='report',
+                    format='csv',
+                    report_id='172',
+                    csvDelimiter='',
+                    rawOrLabel='raw',
+                    rawOrLabelHeaders='raw',
+                    exportCheckboxLabel='false',
+                    returnFormat='json'
+)
+response2_1 <- httr::POST(url, body = formData2_1, encode = "form")
+asymptomaticQ2_1 <- httr::content(response2_1)
+
+#clean data
+asymptomaticQ2_1[asymptomaticQ2_1=="9999;9999"]=NA #indicate as missing
+asymptomaticQ2_1[asymptomaticQ2_1=="9999"]=NA #indicate as missing
+asymptomaticQ2_1=asymptomaticQ2_1%>% #separate symp SAR into 2 variables
+  separate(q3_sar_s, c("Ec","Nc"), ";", remove=FALSE) 
+asymptomaticQ2_1=asymptomaticQ2_1%>% #separate asymp SAR into 2 variables
+  separate(q3_sar_a, c("Ee_a","Ne_a"), ";", remove=FALSE) 
+asymptomaticQ2_1=asymptomaticQ2_1%>% #separate presymp SAR into 2 variables
+  separate(q3_sar_p, c("Ee_p","Ne_p"), ";", remove=FALSE) 
+
+asymptomaticQ2_1=asymptomaticQ2_1 %>% #change values to numeric
+  mutate(Ec=as.numeric(Ec),
+         Nc=as.numeric(Nc),
+         Ee_a=as.numeric(Ee_a),
+         Ne_a=as.numeric(Ne_a),
+         Ee_p=as.numeric(Ee_p),
+         Ne_p=as.numeric(Ne_p))
+
+#metaanalysis for asymptomatic transmission
+
+q2_1_asymp <- metabin(event.e = Ee_a,
+                      n.e = Ne_a,
+                      event.c = Ec,
[…]

### 2021-06-18 Q2_2.R

@@ -1,0 +1,274 @@
+###############################################################
+# Question 2.2: results output ################################
+# Proportion of transmission from asymp or pre-symp ###########
+###############################################################
+
+rm(list = ls())
+
+library(RCurl)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+
+
+# get the data directly from REDCap: 
+# report #157 is Q2.2:
+
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData2_2 <- list("token"=token,
+                    content='report',
+                    format='csv',
+                    report_id='157',
+                    csvDelimiter='',
+                    rawOrLabel='raw',
+                    rawOrLabelHeaders='raw',
+                    exportCheckboxLabel='false',
+                    returnFormat='csv'
+)
+response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
+asymptomaticQ2_2 <- httr::content(response2_2)
+
+#clean data
+asymptomaticQ2_2[asymptomaticQ2_2=="9999;9999"]=NA #indicate as missing
+asymptomaticQ2_2[asymptomaticQ2_2 == "9999"] = NA #indicate as missing
+
+#create a separate dataset for the records with >1 result
+two_models <- asymptomaticQ2_2
+#separate into 2 variables
+two_models = two_models %>% 
+  separate(q3_pp_m, c("q3_pp_m_1","q3_pp_m_2"), ";")
+two_models = two_models %>% 
+  separate(q3_pp_l, c("q3_pp_l_1","q3_pp_l_2"), ";") 
+two_models = two_models %>%
+  separate(q3_pp_u, c("q3_pp_u_1","q3_pp_u_2"), ";")
+two_models = two_models %>% 
+  separate(q3_setting, c("q3_setting_1","q3_setting_2"), ";") 
+
+two_models <- two_models %>% #change values to numeric
+  mutate(q3_pp_m_1=as.numeric(q3_pp_m_1),
+         q3_pp_m_2=as.numeric(q3_pp_m_2),
+         q3_pp_l_1=as.numeric(q3_pp_l_1),
+         q3_pp_l_2=as.numeric(q3_pp_l_2),
[…]

### 2021-08-23 Asymptomatic_LSR_Supplement.Rmd
updated

---
title: "Supporting Information"
author: "Diana Buitrago-Garcia, Aziz Mert Ipekci, Leonie Heron, Stefanie Hossmann, Hira Imeri, Georgia Salanti, Nicola Low"
date: "`r format(Sys.time(), '%d/%m/%y')`"
output: 
  html_document:
  toc: true
  toc_float: true
  theme: united
  highlight: tango
#always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

###############################################################
# Supplementary material                        ##########
###############################################################

###############################################################
# Question 1: results output                         ##########
# Proportion of asymptomatic cases                   ##########
# Supplementary material: preprints removed          ##########
###############################################################

#load the libraries
library(meta)
library(readxl)
library(tidyverse)
library(httr) # use to retrieve data from REDCap
library(kableExtra)
library(flextable)
library(dplyr)
library(Rcpp)

# Prepare the data
# get the data directly from redcap:
# report #155 is Q1:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='155',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response <- httr::POST(url, body = formData, encode = "form")
asymptomaticQ1_pub <- httr::content(response)

settings=c("Contact investigation",
           "Contact investigation, aggregated",
           "Outbreak investigation",
           "Statistical model",
           "Screening",
           "Hospitalised adults",
           "Hospitalised children",
           "Hospitalised adults & children")

asymptomaticQ1_pub$setting2<-factor(asymptomaticQ1_pub$setting2, levels=1:8, labels=settings)
#combine contact investigation and contact investigation aggregated
asymptomaticQ1_pub$setting2[asymptomaticQ1_pub$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"

# minor cleaning
asymptomaticQ1_pub[asymptomaticQ1_pub==9999]=NA

asymptomaticQ1_pub$setting=asymptomaticQ1_pub$setting2

#remove preprints at time of search
asymptomaticQ1_pub <- asymptomaticQ1_pub %>%
  filter(source != 1 & source != 2)

data_long1_pub <- gather(asymptomaticQ1_pub, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
  mutate(id=1:nrow(.)) %>%
  select(record_id, author_1, setting, total, id, cluster)
data_long2_pub <-gather(asymptomaticQ1_pub, cluster, events, c(q1_c1_event,q1_c2_event,q1_c3_event), factor_key=TRUE) %>% 
  mutate(id=1:nrow(.)) %>%
  select(events, id)

data_Q1_pub = merge(data_long1_pub, data_long2_pub, by="id")
data_Q1_pub = data_Q1_pub[!is.na(data_Q1_pub$total),]
data_Q1_pub$cluster=factor(data_Q1_pub$cluster,labels=c("1","2","3"),levels=c("q1_c1_total","q1_c2_total","q1_c3_total"))

data_Q1_pub[data_Q1_pub$record_id %in% asymptomaticQ1_pub[is.na(asymptomaticQ1_pub$q1_c2_event),]$record_id,]$cluster=NA

asymptomaticQ1_pub=data_Q1_pub

asymptomaticQ1_pub$label=paste0("#", asymptomaticQ1_pub$record_id, " ", asymptomaticQ1_pub$author_1, " (2020)",ifelse(!is.na(asymptomaticQ1_pub$cluster),paste0(" cluster:",asymptomaticQ1_pub$cluster),"")) # [FU: ",asymptomaticQ1$fup_median,"]")

asymptomaticQ1_pub$label=paste0("#", asymptomaticQ1_pub$record_id, " ", asymptomaticQ1_pub$author_1,ifelse(!is.na(asymptomaticQ1_pub$cluster),paste0(" [cluster:",asymptomaticQ1_pub$cluster,"]"),"")) # [FU: ",asymptomaticQ1$fup_median,"]")

#change clusters to descriptions
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4479 Harada [cluster:1]"] <- "#4479 Harada [Patients]"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4479 Harada [cluster:2]"] <- "#4479 Harada [Healthcare workers]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor []" #clarify
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor []"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2892 Kennelly [cluster:1]"] <- "#2892 Kennelly [Nursing home residents]"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2802 Bender [cluster:1]"] <- "#2802 Bender [Hospital 1]"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2802 Bender [cluster:2]"] <- "#2802 Bender [Hospital 2]"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4968 van Buul [cluster:2]"] <- "#4968 van Buul [Healthcare workers]"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#5273 Theuring [cluster:1]"] <- "#5273 Theuring [School students and staff]"
asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"

data_pub=asymptomaticQ1_pub[order(asymptomaticQ1_pub$setting,1/(1/asymptomaticQ1_pub$events+1/(asymptomaticQ1_pub$total-asymptomaticQ1_pub$events))),]

data_pub[is.na(data_pub$setting),]$record_id
data_pub=data_pub[!is.na(data_pub$setting),]

asym_plot<-metaprop(events,total,data=data_pub,sm = "PLOGIT", studlab=label, 
                    byvar=setting,# tau.common =TRUE,
                    prediction = TRUE,
                    control=list(stepadj=0.05, maxiter=10000))#, method ="INV") #, verbose=TRUE, digits=5, control=list(stepadj=0.5))

asym_plot

png(file = 'forest_meta_Q1_published.png',width = 30,height = 60, res=600, units="cm")

forest(asym_plot,  col.square=data_pub$setting, sortvar = 1/seTE,
       #squaresize = 1/(1/data$events+1/(data$total-data$events)),
       #sortvar = 1/(1/events+1/(total-events)), 
       subgroup=TRUE, 
       just.studlab="left", colgap.studlab="2cm",
       #leftcols = c("label", "setting", "age", "design", "asym_denom"),
       #leftcols=c("studlab", "record_id", "event", "n"),
       xlab = "",just="left",comb.random=TRUE,test.subgroup.random=FALSE,
       comb.fixed=FALSE,test.subgroup.fixed=FALSE, predict=T)#, study.results=TRUE,test.subgroup=TRUE)
dev.off()

###############################################################
# Countries included in Q1                           ##########
###############################################################

Q1_table_countries <- httr::content(response)

#clean countries
Q1_table_countries <- Q1_table_countries %>%
  mutate(country = ifelse(country == 10, "Australia", country),
         country = ifelse(country == 11, "Austria", country),
         country = ifelse(country == 15, "Bahrain", country),
         country = ifelse(country == 19, "Belgium", country),
         country = ifelse(country == 28, "Brunei", country),
         country = ifelse(country == 34, "Canada", country),
         country = ifelse(country == 40, "China", country),
         country = ifelse(country == 41, "Colombia", country),
         country = ifelse(country == 51, "Denmark", country),
         country = ifelse(country == 62, "France", country),
         country = ifelse(country == 63, "French Guyana", country),
         country = ifelse(country == 67, "Germany", country),
         country = ifelse(country == 69, "Greece", country),
         country = ifelse(country == 78, "Iceland", country),
         country = ifelse(country == 79, "India", country),
         country = ifelse(country == 83, "Ireland", country),
         country = ifelse(country == 85, "Italy", country),
         country = ifelse(country == 87, "Japan", country),
         country = ifelse(country == 92, "Kuwait", country),
         country = ifelse(country == 105, "Malaysia", country),
         country = ifelse(country == 121, "Netherlands", country),
         country = ifelse(country == 128, "Norway", country),
         country = ifelse(country == 888, "Other", country),
         country = ifelse(country == 138, "Portugal", country),
         country = ifelse(country == 146, "Saudi Arabia", country),
         country = ifelse(country == 157, "South Korea", country),
         country = ifelse(country == 160, "Spain", country),
         country = ifelse(country == 174, "Turkey", country),
         country = ifelse(country == 176, "Uganda", country),
         country = ifelse(country == 180, "United Kingdom", country),
         country = ifelse(country == 181, "United States of America", country),
         country = ifelse(country == 185, "Vietnam", country))

#clean case numbers
#total SARS-CoV-2 n
Q1_table_countries$q1_c1_total[is.na(Q1_table_countries$q1_c1_total)] <- 0
Q1_table_countries$q1_c2_total[is.na(Q1_table_countries$q1_c2_total)] <- 0
Q1_table_countries$q1_c1_event[is.na(Q1_table_countries$q1_c1_event)] <- 0
Q1_table_countries$q1_c2_event[is.na(Q1_table_countries$q1_c2_event)] <- 0

Q1_table_countries$total_SARS_n <- Q1_table_countries$q1_c1_total + Q1_table_countries$q1_c2_total
Q1_table_countries$asymp_SARS_n <- Q1_table_countries$q1_c1_event + Q1_table_countries$q1_c2_event

#remove unnecessary cols
Q1_table_countries <- Q1_table_countries %>%
  select(country, total_SARS_n, asymp_SARS_n)

#group by countries to calculate n, total cases, total asymp cases
Q1_table_countries <- Q1_table_countries %>%
  group_by(country) %>%
  summarise(total_SARS = sum(total_SARS_n),
            total_asymp_SARS = sum(asymp_SARS_n),
            n = n())

#arrange by number of studies
Q1_table_countries <- Q1_table_countries %>%
  arrange(desc(n))

```

## PRISMA 2020 Checklist
*Shiny app can be used to complete checklist here:* <https://prisma.shinyapps.io/checklist/>

***

## Search strings

From: Living Evidence on COVID-19 (<https://ispmbern.github.io/covid-19/living-review/collectingdata.html>, accessed 31.01.2021)

We retrieve data from [EMBASE](http://www.embase.com/) via OVID, [MEDLINE](https://www.ncbi.nlm.nih.gov/pubmed/) via PubMed, BioRxiv and MedRxiv.

**Search terms**

When searches are updated, references that are identified that were not in the database before, are inserted by date (**date_entrez**) they were indexed in remote database, the date they are inserted in OUR database is formatted as the ‘**strategydate**’ (raw data is available [here](https://github.com/leonieheron/LSRworkflow>)).

**30.10.2020**

EMBASE:

(exp SARS-related coronavirus/ or severe acute respiratory syndrome/ or coronavirus disease 2019/ or (coronavir* or corona virus* or HCoV* or ncov* or 2019 cov or covid or covid19 or sars-cov* or sarscov* or sars-coronavirus* or Severe Acute Respiratory Syndrome Coronavirus* or nCoV).mp.) and 20191101:20301231.(dc).

MEDLINE:

("severe acute respiratory syndrome coronavirus 2"[Supplementary Concept] OR "COVID-19" [Supplementary Concept] OR "coronavirus" OR "corona virus" OR "HCoV" OR "nCoV" OR "2019 CoV" OR "covid" OR "covid19" OR "Severe Acute Respiratory Syndrome Coronavirus 2" OR "SARS-CoV2" OR "SARS-CoV 2" OR "SARS Coronavirus 2") AND (2019/11/01:3000/12/31[PDAT])

**01.05.2021**

EMBASE:

(SARS coronavirus/ or middle east respiratory syndrome/ or severe acute respiratory syndrome/ or (coronavirus* or corona virus* or HCoV* or ncov* or covid or covid19 or sars-cov* or sarscov* or Sars-coronavirus* or Severe Acute Respiratory Syndrome Coronavirus*).mp.) and 20191201:20301231.(dc).

**29.04.2020**

MEDLINE:

("coronavirus"[MH] OR "coronavirus infections"[MH] OR "coronavirus"[TW] OR "corona virus"[TW] OR "HCoV"[TW] OR "nCov"[TW] OR "covid"[TW] OR "covid19"[TW] OR "Severe Acute Respiratory Syndrome Coronavirus 2"[TW] OR "SARS-CoV2"[TW] OR "SARS-CoV 2"[TW] OR "SARS Coronavirus 2"[TW] OR "MERS- CoV"[TW]) AND (2019/1/1:3000[PDAT])

**01.04.2020**

From 01.04.2020, we retrieve the [BioRxiv/MedRxiv dataset](https://connect.medrxiv.org/relate/content/181).

**26.03.2020**

MEDLINE:

("Wuhan coronavirus" [Supplementary Concept] OR "COVID-19" OR SARS-CoV-2 OR "2019 ncov"[tiab] OR (("novel coronavirus"[tiab] OR "new coronavirus"[tiab]) AND (wuhan[tiab] OR 2019[tiab])) OR 2019-nCoV[All Fields] OR (wuhan[tiab] AND coronavirus[tiab]))

EMBASE:

(nCoV or 2019-nCoV or ((new or novel or wuhan) adj3 coronavirus) or covid19 or covid-19 or SARS-CoV-2).mp.

BioRxiv/MedRxiv:

ncov or corona or wuhan or COVID or SARS-CoV-2

With the kind support of the [Public Health & Primary Care Library PHC](https://www.unibe.ch/university/services/university_library/faculty_libraries/medicine/public_health_amp_primary_care_library_phc/index_eng.html), and following guidance of the [Medical Library Association](https://www.mlanet.org/p/cm/ld/fid%3D1713)

**01.01.2020**

MEDLINE:

("Wuhan coronavirus" [Supplementary Concept] OR "COVID-19" OR "2019 ncov"[tiab] OR (("novel coronavirus"[tiab] OR "new coronavirus"[tiab]) AND (wuhan[tiab] OR 2019[tiab])) OR 2019-nCoV[All Fields] OR (wuhan[tiab] AND coronavirus[tiab])))))

EMBASE:

ncov OR (wuhan AND corona) OR COVID

BioRxiv/MedRxiv:

ncov or corona or wuhan or COVID

We retained publications that used the keywords listed below in the title or abstract.

"asymp*" OR "pre-symp*" OR "presymp*" OR "preclinical" OR "pre-clinical" OR "without symptoms" OR "no symptoms" OR "free of symptoms" OR "non-symp*" OR "nonsymp*" OR "symptom-free" OR "symptomfree"

***

## Flowchart
*In progress.*

***

## Risk of bias in studies included in review question 1 and review question 2.
*In progress.*

***

## Review question 1, subgroup analysis comparing studies of hospitalised patients with all other settings.
*Sub-group analysis to be decided*

***

## Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search.
![Figure 3. Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search](forest_meta_Q1_published.png)

***

## Assessment of credibility of mathematical modelling studies.
*In progress.*

***

## Types of study included in successive versions of the living systematic review, as of 10 June 2020.
*Settings to be reviewed. Some studies have been reclassified into different settings.*

***

## Location of studies contributing data to review questions 1 and 2.1.

```{r table1, ft.split=TRUE, tab.cap='Table 1. Location of studies contributing data to review questions 1', echo = FALSE}
table1_countries <- flextable(Q1_table_countries)

table1_countries %>% 
  set_header_labels(country = "Country",
                    total_SARS = "Total SARS-CoV-2, n",
                    total_asymp_SARS = "Total asymptomatic SARS-CoV-2, n",
                    n = "Total number of studies") %>%
  set_table_properties(layout = "autofit") %>%
  theme_vanilla()
```

*Table 2 in progress.*

### 2021-08-23 Manuscript_draft.Rmd
updated

---
title: "Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis"
author: "Diana Buitrago-Garcia, Aziz Mert Ipekci, Leonie Heron, Stefanie Hossmann, Hira Imeri, Georgia Salanti, Nicola Low"
date: "`r format(Sys.time(), '%d/%m/%y')`"
output: html_document
#always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#download packages
library(meta)
library(readxl)
library(tidyverse)
library(httr) # use to retrieve data from REDCap
library(kableExtra)
library(flextable)
library(dplyr)
library(RCurl)
library(tidyr)
library(ggplot2)
library(metafor)

##########################################
# table on characteristics of Q1 studies
##########################################

#prepare data for table 1: characteristics of studies included in q1

#download data
# get the data directly from redcap:
# report #155 is Q1:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='155',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response <- httr::POST(url, body = formData, encode = "form")
Q1_table <- httr::content(response)

#clean countries
Q1_table <- Q1_table %>%
  mutate(country = ifelse(country == 10, "Australia", country),
         country = ifelse(country == 11, "Austria", country),
         country = ifelse(country == 15, "Bahrain", country),
         country = ifelse(country == 19, "Belgium", country),
         country = ifelse(country == 28, "Brunei", country),
         country = ifelse(country == 34, "Canada", country),
         country = ifelse(country == 40, "China", country),
         country = ifelse(country == 41, "Colombia", country),
         country = ifelse(country == 51, "Denmark", country),
         country = ifelse(country == 62, "France", country),
         country = ifelse(country == 63, "French Guyana", country),
         country = ifelse(country == 67, "Germany", country),
         country = ifelse(country == 69, "Greece", country),
         country = ifelse(country == 78, "Iceland", country),
         country = ifelse(country == 79, "India", country),
         country = ifelse(country == 83, "Ireland", country),
         country = ifelse(country == 85, "Italy", country),
         country = ifelse(country == 87, "Japan", country),
         country = ifelse(country == 92, "Kuwait", country),
         country = ifelse(country == 105, "Malaysia", country),
         country = ifelse(country == 121, "Netherlands", country),
         country = ifelse(country == 128, "Norway", country),
         country = ifelse(country == 888, "Other", country),
         country = ifelse(country == 138, "Portugal", country),
         country = ifelse(country == 146, "Saudi Arabia", country),
         country = ifelse(country == 157, "South Korea", country),
         country = ifelse(country == 160, "Spain", country),
         country = ifelse(country == 174, "Turkey", country),
         country = ifelse(country == 176, "Uganda", country),
         country = ifelse(country == 180, "United Kingdom", country),
         country = ifelse(country == 181, "United States of America", country),
         country = ifelse(country == 185, "Vietnam", country))
#clean regions
Q1_table$region[Q1_table$region == "none" | Q1_table$region == "None"] <- NA
#create location variable
Q1_table$location <- Q1_table$country
Q1_table <- Q1_table %>%
  mutate(location = ifelse(!is.na(region), paste0(Q1_table$country, ", ", Q1_table$region), country))
#drop country and region variables
Q1_table$country <- NULL
Q1_table$region <- NULL

#author column
Q1_table$study <- paste0(Q1_table$author_1, " (", Q1_table$year, ")")
Q1_table$author_1 <- NULL
Q1_table$record_id <- NULL
Q1_table$year <- NULL

#clean settings
Q1_table <- Q1_table %>%
  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
         setting = ifelse(setting2 == 4, "Statistical model", setting),
         setting = ifelse(setting2 == 5, "Screening", setting),
         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
         setting = ifelse(setting2 == 9, "Screening: hospitalised patients", setting),
         setting = ifelse(setting2 == 10, "Screening: general population", setting),
         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
Q1_table$setting2 <- NULL

#clean case numbers
#total SARS-CoV-2 n
Q1_table$total_SARS_n <- Q1_table$q1_c1_total
Q1_table$total_SARS_n_c2 <- Q1_table$q1_c2_total #numbers for cluster 2 - must be arranged later
#asymp n
Q1_table$asymp_SARS_n <- Q1_table$q1_c1_event
Q1_table$asymp_SARS_n_c2 <- Q1_table$q1_c2_event #numbers for cluster 2 - must be arranged later
Q1_table$q1_c1_event <- NULL
Q1_table$q1_c2_event <- NULL
Q1_table$q1_c1_total <- NULL
Q1_table$q1_c2_total <- NULL
Q1_table$q1_nclus <- NULL
Q1_table$q1_c3_event <- NULL
Q1_table$q1_c3_total <- NULL
Q1_table$comment_q1 <- NULL

#clean sex category
Q1_table$sex <- "NR"
Q1_table$q1_female[Q1_table$q1_female == 9999] <- 0
Q1_table$q1_male[Q1_table$q1_male == 9999] <- 0
Q1_table <- Q1_table %>%
  mutate(sex = ifelse(q1_female == 0 & q1_male == 0, "NR", paste0(q1_female, " F, ", q1_male, " M")))
Q1_table$q1_male <- NULL
Q1_table$q1_female <- NULL

#clean age category

Q1_table$q1_age_median[Q1_table$q1_age_median == 9999] <- NA
Q1_table$q1_age_iqr[Q1_table$q1_age_iqr == 9999] <- NA
Q1_table$age <- as.character(Q1_table$q1_age_median)
Q1_table$age[is.na(Q1_table$age)] <- "NR"
Q1_table <- Q1_table %>%
  mutate(age = ifelse(!is.na(q1_age_iqr), 
                      paste0(q1_age_median, " IQR ", q1_age_iqr),
                      age))
Q1_table$q1_age_iqr <- NULL
Q1_table$q1_age_median <- NULL

#clean up follow up
Q1_table$follow_up <- NULL

Q1_table$fup___2[Q1_table$fup___2 == 1] <- 2
Q1_table$fup___3[Q1_table$fup___3 == 1] <- 3
Q1_table <- Q1_table %>%
  mutate(follow_up = ifelse(fup___1 != 0 & fup___2 != 0 & fup___3 != 0,
                            paste0(fup___1, ", ", fup___2, ", ", fup___3),
                            NA)) %>%
  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 0,
                            1,
                            follow_up)) %>%
  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 0,
                            2,
                            follow_up)) %>%
  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 3,
                            3,
                            follow_up)) %>%
  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 0,
                            "1, 2",
                            follow_up)) %>%
  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 3,
                            "1, 3",
                            follow_up)) %>%
  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 3,
                            "2, 3",
                            follow_up))
Q1_table$fup___1 <- NULL
Q1_table$fup___2 <- NULL
Q1_table$fup___3 <- NULL

names(Q1_table)
Q1_table$source <- NULL

#rearrange so that clusters and in one col
cluster2 <- Q1_table
cluster2 <- cluster2[!is.na(cluster2$total_SARS_n_c2), ]
cluster2$total_SARS_n <- cluster2$total_SARS_n_c2
cluster2$asymp_SARS_n <- cluster2$asymp_SARS_n_c2
cluster2$total_SARS_n_c2 <- NULL
cluster2$asymp_SARS_n_c2 <- NULL
cluster2$study <- paste0(cluster2$study, " [cluster 2]")
#add clusters to main table
Q1_table <- bind_rows(Q1_table, cluster2)
#drop extra cols
Q1_table$total_SARS_n_c2 <- NULL
Q1_table$asymp_SARS_n_c2 <- NULL

Q1_table <- Q1_table %>%
  arrange(setting)

##########################################
# Q1 forest plot
##########################################

asymptomaticQ1 <- httr::content(response)

settings=c("Contact investigation",
           "Contact investigation, aggregated",
           "Outbreak investigation",
           "Statistical model",
           "Screening",
           "Hospitalised adults",
           "Hospitalised children",
           "Hospitalised adults & children")

asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:8, labels=settings)
#combine contact investigation and contact investigation aggregated
asymptomaticQ1$setting2[asymptomaticQ1$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"

# minor cleaning
asymptomaticQ1[asymptomaticQ1==9999]=NA

asymptomaticQ1$setting=asymptomaticQ1$setting2

data_long1 <- gather(asymptomaticQ1, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
  mutate(id=1:nrow(.)) %>%
  select(record_id, author_1, setting, total, id, cluster)
data_long2 <-gather(asymptomaticQ1, cluster, events, c(q1_c1_event,q1_c2_event,q1_c3_event), factor_key=TRUE) %>% 
  mutate(id=1:nrow(.)) %>%
  select(events, id)

data_Q1 = merge(data_long1, data_long2, by="id")
data_Q1 = data_Q1[!is.na(data_Q1$total),]
data_Q1$cluster=factor(data_Q1$cluster,labels=c("1","2","3"),levels=c("q1_c1_total","q1_c2_total","q1_c3_total"))

data_Q1[data_Q1$record_id %in% asymptomaticQ1[is.na(asymptomaticQ1$q1_c2_event),]$record_id,]$cluster=NA

asymptomaticQ1=data_Q1

asymptomaticQ1$label=paste0("#", asymptomaticQ1$record_id, " ", asymptomaticQ1$author_1, " (2020)",ifelse(!is.na(asymptomaticQ1$cluster),paste0(" cluster:",asymptomaticQ1$cluster),"")) # [FU: ",asymptomaticQ1$fup_median,"]")

asymptomaticQ1$label=paste0("#", asymptomaticQ1$record_id, " ", asymptomaticQ1$author_1,ifelse(!is.na(asymptomaticQ1$cluster),paste0(" [cluster:",asymptomaticQ1$cluster,"]"),"")) # [FU: ",asymptomaticQ1$fup_median,"]")

#change clusters to descriptions
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:1]"] <- "#4479 Harada [Patients]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:2]"] <- "#4479 Harada [Healthcare workers]"
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor []" #clarify
#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor []"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:1]"] <- "#2892 Kennelly [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2802 Bender [cluster:1]"] <- "#2802 Bender [Hospital 1]"
asymptomaticQ1$label[asymptomaticQ1$label == "#2802 Bender [cluster:2]"] <- "#2802 Bender [Hospital 2]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:2]"] <- "#4968 van Buul [Healthcare workers]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:1]"] <- "#5273 Theuring [School students and staff]"
asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"

data=asymptomaticQ1[order(asymptomaticQ1$setting,1/(1/asymptomaticQ1$events+1/(asymptomaticQ1$total-asymptomaticQ1$events))),]

data[is.na(data$setting),]$record_id
data=data[!is.na(data$setting),]

asym_plot<-metaprop(events,total,data=data,sm = "PLOGIT", studlab=label, 
                    byvar=setting,# tau.common =TRUE,
                    prediction = TRUE,
                    control=list(stepadj=0.05, maxiter=10000))#, method ="INV") #, verbose=TRUE, digits=5, control=list(stepadj=0.5))

asym_plot

png(file = 'forest_meta_Q1.png',width=25,height=70, res=600, units="cm")

forest(asym_plot,  col.square=data$setting, sortvar = 1/seTE,
       #squaresize = 1/(1/data$events+1/(data$total-data$events)),
       #sortvar = 1/(1/events+1/(total-events)), 
       subgroup=TRUE, 
       just.studlab="left", colgap.studlab="2cm",
       #leftcols = c("label", "setting", "age", "design", "asym_denom"),
       #leftcols=c("studlab", "record_id", "event", "n"),
       xlab = "",just="left",comb.random=TRUE,test.subgroup.random=FALSE,
       comb.fixed=FALSE,test.subgroup.fixed=FALSE, predict=T)#, study.results=TRUE,test.subgroup=TRUE)
dev.off()

#sort by standard error
#read meta book and figure it out
#same as precision plot
pdf(file = 'forest_meta_Q1.pdf', width = 10, height = 30)

forest(asym_plot,  col.square=data$setting,sortvar = 1/(sqrt(seTE)),
       #squaresize = 1/(1/data$events+1/(data$total-data$events)),
       #sortvar = 1/(1/events+1/(total-events)), 
       subgroup=TRUE, 
       just.studlab="left", colgap.studlab="2cm",
       #leftcols = c("label", "setting", "age", "design", "asym_denom"),
       #leftcols=c("studlab", "record_id", "event", "n"),
       xlab = "",just="left",comb.random=TRUE,test.subgroup.random=FALSE,
       comb.fixed=FALSE,test.subgroup.fixed=FALSE, predict=T)#, study.results=TRUE,test.subgroup=TRUE)
dev.off()

##########################################
# Q2.1 forest plot
##########################################

# get the data directly from redcap: 
# report #172 is Q2.1 SAR:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData2_1 <- list("token"=token,
                    content='report',
                    format='csv',
                    report_id='172',
                    csvDelimiter='',
                    rawOrLabel='raw',
                    rawOrLabelHeaders='raw',
                    exportCheckboxLabel='false',
                    returnFormat='json'
)
response2_1 <- httr::POST(url, body = formData2_1, encode = "form")
asymptomaticQ2_1 <- httr::content(response2_1)

#clean data
asymptomaticQ2_1[asymptomaticQ2_1=="9999;9999"]=NA #indicate as missing
asymptomaticQ2_1[asymptomaticQ2_1=="9999"]=NA #indicate as missing
asymptomaticQ2_1=asymptomaticQ2_1%>% #separate symp SAR into 2 variables
  separate(q3_sar_s, c("Ec","Nc"), ";", remove=FALSE) 
asymptomaticQ2_1=asymptomaticQ2_1%>% #separate asymp SAR into 2 variables
  separate(q3_sar_a, c("Ee_a","Ne_a"), ";", remove=FALSE) 
asymptomaticQ2_1=asymptomaticQ2_1%>% #separate presymp SAR into 2 variables
  separate(q3_sar_p, c("Ee_p","Ne_p"), ";", remove=FALSE)

asymptomaticQ2_1=asymptomaticQ2_1 %>% #change values to numeric
  mutate(Ec=as.numeric(Ec),
         Nc=as.numeric(Nc),
         Ee_a=as.numeric(Ee_a),
         Ne_a=as.numeric(Ne_a),
         Ee_p=as.numeric(Ee_p),
         Ne_p=as.numeric(Ne_p))

#create new df with asymp/presymp as subgroups
q2_1_df_a <- asymptomaticQ2_1 %>%
  select("record_id", "author_1", "Ee_a", "Ne_a", "Ec", "Nc", "region", "year") %>%
  rename(Ee = Ee_a,
         Ne = Ne_a) %>%
  filter(!is.na(Ee)) %>%
  mutate(group = "Asymptomatic")
q2_1_df_p <- asymptomaticQ2_1 %>%
  select("record_id", "author_1", "Ee_p", "Ne_p", "Ec", "Nc", "region", "year") %>%
  rename(Ee = Ee_p,
         Ne = Ne_p) %>%
  filter(!is.na(Ee)) %>%
  mutate(group = "Presymptomatic")
#bind rows
q2_1_df <- bind_rows(q2_1_df_a, q2_1_df_p)

#metaanalysis for asymptomatic transmission

q2_1_asymp <- metabin(event.e = Ee,
                      n.e = Ne,
                      event.c = Ec,
                      n.c = Nc, 
                      data = q2_1_df,
                      studlab = author_1,
                      prediction = TRUE,
                      sm = "RR",
                      method = "MH",
                      MH.exact = TRUE, 
                      byvar = group)
q2_1_asymp

pdf(file = 'forest_meta_Q2_1.pdf', width = 8, height = 6)

forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE)

dev.off()

png(file = 'forest_meta_Q2_1.png', width=25,height=13, res=600, units="cm")

forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE)

dev.off()

##########################################
# supplementary information - by precision
##########################################

#metaanalysis for asymptomatic transmission

q2_1_asymp_precision <- metabin(event.e = Ee,
                                n.e = Ne,
                                event.c = Ec,
                                n.c = Nc, 
                                data = q2_1_df,
                                studlab = author_1,
                                sm = "RR",
                                byvar = group)

png(file = 'forest_meta_Q2_1_precision.png', width = 600, height = 480)

forest(q2_1_asymp_precision, sortvar = -seTE, overall = FALSE)

dev.off()

##########################################
# table on characteristics of Q2.1 studies
##########################################

#get data
Q2_1_table <- httr::content(response2_1)

#clean countries
Q2_1_table <- Q2_1_table %>%
  mutate(country = ifelse(country == 10, "Australia", country),
         country = ifelse(country == 11, "Austria", country),
         country = ifelse(country == 15, "Bahrain", country),
         country = ifelse(country == 19, "Belgium", country),
         country = ifelse(country == 28, "Brunei", country),
         country = ifelse(country == 34, "Canada", country),
         country = ifelse(country == 40, "China", country),
         country = ifelse(country == 41, "Colombia", country),
         country = ifelse(country == 51, "Denmark", country),
         country = ifelse(country == 62, "France", country),
         country = ifelse(country == 63, "French Guyana", country),
         country = ifelse(country == 67, "Germany", country),
         country = ifelse(country == 69, "Greece", country),
         country = ifelse(country == 78, "Iceland", country),
         country = ifelse(country == 79, "India", country),
         country = ifelse(country == 83, "Ireland", country),
         country = ifelse(country == 85, "Italy", country),
         country = ifelse(country == 87, "Japan", country),
         country = ifelse(country == 92, "Kuwait", country),
         country = ifelse(country == 105, "Malaysia", country),
         country = ifelse(country == 121, "Netherlands", country),
         country = ifelse(country == 128, "Norway", country),
         country = ifelse(country == 888, "Other", country),
         country = ifelse(country == 138, "Portugal", country),
         country = ifelse(country == 146, "Saudi Arabia", country),
         country = ifelse(country == 157, "South Korea", country),
         country = ifelse(country == 160, "Spain", country),
         country = ifelse(country == 174, "Turkey", country),
         country = ifelse(country == 176, "Uganda", country),
         country = ifelse(country == 180, "United Kingdom", country),
         country = ifelse(country == 181, "United States of America", country),
         country = ifelse(country == 185, "Vietnam", country))
#clean regions

Q2_1_table$region[Q2_1_table$region == "none" | Q2_1_table$region == "None."] <- NA
#create location variable
Q2_1_table$location <- Q2_1_table$country
Q2_1_table <- Q2_1_table %>%
  mutate(location = ifelse(!is.na(region), paste0(country, ", ", region), country))
#drop country and region variables
Q2_1_table$country <- NULL
Q2_1_table$region <- NULL

#author column
Q2_1_table$study <- paste0(Q2_1_table$author_1, " (", Q2_1_table$year, ")")
Q2_1_table$author_1 <- NULL
Q2_1_table$record_id <- NULL
Q2_1_table$year <- NULL

#clean settings
Q2_1_table$setting <- "Not available"
Q2_1_table <- Q2_1_table %>%
  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
         setting = ifelse(setting2 == 4, "Statistical model", setting),
         setting = ifelse(setting2 == 5, "Screening", setting),
         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
         setting = ifelse(setting2 == 9, "Screening: hospitalised patients", setting),
         setting = ifelse(setting2 == 10, "Screening: general population", setting),
         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
Q2_1_table$setting2 <- NULL

#reorder columns
Q2_1_table <- data.frame(Q2_1_table$study,
                         Q2_1_table$setting,
                         Q2_1_table$location)

names(Q2_1_table) <- c("study", "setting", "location")

###############################################################
# Question 2.2: results output ################################
# Proportion of transmission from asymp or pre-symp ###########
###############################################################

# get the data directly from REDCap: 
# report #157 is Q2.2:

url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData2_2 <- list("token"=token,
                    content='report',
                    format='csv',
                    report_id='157',
                    csvDelimiter='',
                    rawOrLabel='raw',
                    rawOrLabelHeaders='raw',
                    exportCheckboxLabel='false',
                    returnFormat='csv'
)
response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
asymptomaticQ2_2 <- httr::content(response2_2)

#clean data
asymptomaticQ2_2[asymptomaticQ2_2=="9999;9999"]=NA #indicate as missing
asymptomaticQ2_2[asymptomaticQ2_2 == "9999"] = NA #indicate as missing

#create a separate dataset for the records with >1 result
two_models <- asymptomaticQ2_2
#separate into 2 variables
two_models = two_models %>% 
  separate(q3_pp_m, c("q3_pp_m_1","q3_pp_m_2"), ";")
two_models = two_models %>% 
  separate(q3_pp_l, c("q3_pp_l_1","q3_pp_l_2"), ";") 
two_models = two_models %>%
  separate(q3_pp_u, c("q3_pp_u_1","q3_pp_u_2"), ";")
two_models = two_models %>% 
  separate(q3_setting, c("q3_setting_1","q3_setting_2"), ";")

two_models <- two_models %>% #change values to numeric
  mutate(q3_pp_m_1=as.numeric(q3_pp_m_1),
         q3_pp_m_2=as.numeric(q3_pp_m_2),
         q3_pp_l_1=as.numeric(q3_pp_l_1),
         q3_pp_l_2=as.numeric(q3_pp_l_2),
         q3_pp_u_1=as.numeric(q3_pp_u_1),
         q3_pp_u_2=as.numeric(q3_pp_u_2))

two_models <- two_models[!is.na(two_models$q3_pp_m_2),]

substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
}

L1 <- two_models %>%
  pivot_longer(cols = c(6:7),
               names_to = "model",
               values_to = "q3_pp_m") 
L1$label <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")
L2 <- two_models %>%
  pivot_longer(cols = c(8:9),
               names_to = "model",
               values_to = "q3_pp_l") %>%
  select("record_id", "model", "q3_pp_l", "author_1")
L2$label <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
L2 <- L2 %>% select("q3_pp_l", "label")
L3 <- two_models %>%
  pivot_longer(cols = c(10:11),
               names_to = "model",
               values_to = "q3_pp_u") %>%
  select("record_id", "model", "q3_pp_u", "author_1")
L3$label <- paste(L3$author_1, " [", substrRight(L3$model, 1), "]", sep = "")
L3 <- L3 %>% select("q3_pp_u", "label")
L4 <- two_models %>%
  pivot_longer(cols = c(13:14),
               names_to = "model",
               values_to = "setting") %>%
  select("record_id", "model", "setting", "author_1")
L4$label <- paste(L4$author_1, " [", substrRight(L4$model, 1), "]", sep = "")
L4 <- L4 %>% select("setting", "label")
#merge together
Lall <- merge(L2, L3, by = "label")   
Lall <- merge(Lall, L4, by = "label") 
Lall <- merge(Lall, L1, by = "label")
Lall <- Lall %>%
  select("record_id", "author_1", "q3_pa_m", "q3_pa_l", "q3_pa_u", 
         "q3_pp_m", "q3_pp_l", "q3_pp_u", "question_3_complete", "setting", 
         "label")

#clean original dataset
asymptomaticQ2_2$label <- asymptomaticQ2_2$author_1
asymptomaticQ2_2 <- asymptomaticQ2_2 %>%
  mutate(setting = q3_setting)
asymptomaticQ2_2$q3_setting <- NULL
asymptomaticQ2_2 <- as.data.frame(asymptomaticQ2_2)
attr(asymptomaticQ2_2, 'spec') <- NULL
str(asymptomaticQ2_2)
asymptomaticQ2_2$q3_pp_m <- as.numeric(asymptomaticQ2_2$q3_pp_m)
asymptomaticQ2_2$q3_pp_l <- as.numeric(asymptomaticQ2_2$q3_pp_l)
asymptomaticQ2_2$q3_pp_u <- as.numeric(asymptomaticQ2_2$q3_pp_u)

#add extra rows to original dataset
Q2_2 <- bind_rows(asymptomaticQ2_2, Lall)
#if q3_pp_m and q3_pa_m both NA then delete
Q2_2 <- Q2_2[!is.na(Q2_2$q3_pa_m) | !is.na(Q2_2$q3_pp_m),]

#create new variable for all estimates and indicate asymp/presymp with new variable
#fill Q2_2 first with estimates from q3_pp_m then q3_pa_m
Q2_2 <- Q2_2 %>%
  mutate(estimate = ifelse(!is.na(q3_pp_m),
                           q3_pp_m,
                           q3_pa_m),
         lower_bound = ifelse(!is.na(q3_pp_m),
                                 q3_pp_l,
                                 q3_pa_l),
         upper_bound = ifelse(!is.na(q3_pp_m),
                                 q3_pp_u,
                                 q3_pa_u),
         subgroup = ifelse(!is.na(q3_pp_m),
                           "presymp",
                           "asymp"))
#some records have presymp estimates in estimate now - must make new observation
both <- Q2_2 %>%
  filter(!is.na(Q2_2$q3_pa_m) & !is.na(Q2_2$q3_pp_m)) %>%
  mutate(estimate = q3_pa_m,
         lower_bound = q3_pa_l,
         upper_bound = q3_pa_u,
         subgroup = "asymp")
Q2_2 <- bind_rows(Q2_2, both)
#remove unnecessary cols
Q2_2 <- Q2_2 %>%
  select(c("record_id", "label", "setting", "estimate", "lower_bound", "upper_bound", "subgroup"))
#round numbers to 2 decimal points
Q2_2$estimate <- round(Q2_2$estimate, digits = 2)
Q2_2$lower_bound <- round(Q2_2$lower_bound, digits = 2)
Q2_2$upper_bound <- round(Q2_2$upper_bound, digits = 2)

###############################################################
# forest plot

#prepare data
Q2_2_df <- Q2_2
#create label for proportions
Q2_2_df$prop <- sprintf("%2.2f", Q2_2_df$estimate)
#create label for 95% CIs
Q2_2_df$CI_lower <- sprintf("%2.2f", Q2_2_df$lower_bound)
Q2_2_df$CI_upper <- sprintf("%2.2f", Q2_2_df$upper_bound)
Q2_2_df$CIs <- paste("[", Q2_2_df$CI_lower, #paste together 95% CIs
                     ";", Q2_2_df$CI_upper, "]", 
                     sep = "")
Q2_2_df <- Q2_2_df %>%
  mutate(CI = ifelse(is.na(Q2_2_df$CI_lower), NA, CIs))
Q2_2_df$CI[Q2_2_df$CI == "[NA;NA]"] <- NA
str(Q2_2_df)
#col to indicate headings/studies in plot
Q2_2_df$type <- 2
#new row for asymptomatic label in plot
Asymp_label <- data.frame(NA, "Asymptomatic transmission", NA, NA, NA, NA, NA, 
                          NA, NA, NA, NA, NA, 1)
names(Asymp_label) <- names(Q2_2_df)
#new row for asymptomatic label in plot
Presymp_label <- data.frame(NA, "Presymptomatic transmission", NA, NA, NA, NA, NA, 
                            NA, NA, NA, NA, NA, 1)
names(Presymp_label) <- names(Q2_2_df)
#add to exisiting dataframe
Q2_2_df <- rbind(Q2_2_df, Asymp_label, Presymp_label)
#font indicator
Q2_2_df$fontface = ifelse(Q2_2_df$type == 1, "italic","plain")
str(Q2_2_df$fontface)

#arrange studies by subgroup
asymp_n <- sum(Q2_2_df$subgroup == "asymp", #number of asymp studies
               na.rm = TRUE) 
presymp_n <- sum(Q2_2_df$subgroup == "presymp", #number of presymp studies
                 na.rm = TRUE) 
Q2_2_df$line[Q2_2_df$label == "Asymptomatic transmission"] <- 1
#new row for space in plot
space <- data.frame(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA)
names(space) <- names(Q2_2_df)
#add to exisiting dataframe
Q2_2_df <- rbind(Q2_2_df, space)
Q2_2_df$line[is.na(Q2_2_df$label)] <- 2 + asymp_n
Q2_2_df$line[Q2_2_df$label == "Presymptomatic transmission"] <- 3 + asymp_n
Q2_2_df_a <- Q2_2_df %>% #order the asymp studies
  filter(subgroup == "asymp") %>%
  mutate(line = 2:(asymp_n + 1))
Q2_2_df_p <- Q2_2_df %>% #order the presymp studies
  filter(subgroup == "presymp") %>%
  mutate(line = (asymp_n + 4):(presymp_n + asymp_n + 3))
Q2_2_df <- Q2_2_df[is.na(Q2_2_df$record_id),]
#join all rows again
Q2_2_df <- rbind(Q2_2_df, Q2_2_df_a, Q2_2_df_p)

#create forest plot
p <- ggplot() + 
  geom_point(data = Q2_2_df, #add estimates 
             aes(y = line, 
                 x = estimate),
             fill = "gray", 
             shape = 22, 
             color = "black",
             size = 4) +
  geom_errorbarh(data = Q2_2_df, #add error bars 
                 aes(y = line, 
                     xmin = lower_bound, 
                     xmax = upper_bound), 
                 height=0.3) +
  geom_text(aes(y = c(-1, -1, -1),  #add cols for study, estimates and CIs
                x = c(-0.2, 1.05, 1.12), 
                label=c("Study", "Prop.", "95% CI")), 
            hjust = 0, 
            fontface = "bold") +
  geom_text(data = Q2_2_df, #add estimate labels
            aes(y = line, 
                x = 1.05, 
                label = prop), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add CI labels
            aes(y = line,
                x = 1.12,
                label = CI), 
            hjust = 0) +
  geom_text(data = Q2_2_df, #add study labels
            aes(y= line, 
                x=-0.2, 
                label = label,
                hjust = 0,
                fontface = fontface)) +
  theme_void() + #remove background
  scale_y_reverse() +
  geom_segment(data = Q2_2_df, #add line below point estimates
               aes(y = max(line) + 1, x = 0, xend = 1, 
                   yend = max(line) + 1)) +
  geom_segment(data = Q2_2_df, #add dash for 0
               aes(y = max(line) + 1, yend = max(line) + 1.3, 
                   x = 0, xend = 0)) +
  geom_segment(data = Q2_2_df, #add dash for 0.25
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x = 0.25, xend = 0.25)) +
  geom_segment(data = Q2_2_df, #add dash for 0.5
               aes(y = max(line)+1, yend=max(line) + 1.3,
                   x=0.5, xend=0.5)) +
  geom_segment(data = Q2_2_df, #add dash for 0.75
               aes(y = max(line) + 1, yend = max(line) + 1.3,
                   x=0.75, xend = 0.75)) +
  geom_segment(data = Q2_2_df, #add dash for 1
               aes(y = max(line) + 1, 
                   yend = max(line) + 1.3,
                   x = 1, xend = 1)) +
  geom_text(aes(y = rep(max(Q2_2_df$line) + 2,5), #add numbers to line
                x = 0:4/4, 
                label = c(0.00,0.25,0.5,0.75,1.00))) +
  scale_x_continuous()

p

#create image file
png(file="forest_Q2_2.png", 
    res=300, 
    height=20, width=50, units="cm")
p
dev.off()

##########################################
# table on characteristics of Q2.2 studies
##########################################

#get data
Q2_2_table <- httr::content(response2_2)

#author column
Q2_2_table$study <- paste0(Q2_2_table$author_1, " (", Q2_2_table$year, ")")
Q2_2_table$author_1 <- NULL
Q2_2_table$record_id <- NULL
Q2_2_table$year <- NULL

#subset df
Q2_2_table <- Q2_2_table %>%
  select(study, q3_setting)

```

## Introduction

There is ongoing discussion about the level of asymptomatic severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) infection. The authors of a narrative review report a range of proportions of participants positive for SARS-CoV-2 but asymptomatic in different studies from 6 to 96% [1]. The discrepancy results, in part, from the interpretation of studies that report a proportion of asymptomatic people with SARS-CoV-2 detected at a single point. The studies cited include both people who will remain asymptomatic throughout and those, known as pre-symptomatic, who will develop symptoms of coronavirus disease 2019 (covid-19) if followed up [2]. The full spectrum and distribution of covid-19, from completely asymptomatic, to mild and non-specific symptoms, viral pneumonia, respiratory distress syndrome, and death are not yet known [3]. Without follow up, however, the proportions of asymptomatic and pre-symptomatic infections cannot be determined.

Accurate estimates of the proportions of true asymptomatic and pre-symptomatic infections are needed urgently because their contribution to overall SARS-CoV-2 transmission at the population level will determine the appropriate balance of control measures [3]. If the predominant route of transmission is from people who have symptoms, then strategies should focus on testing, followed by isolation of infected individuals and quarantine of their contacts. If, however, most transmission is from people without symptoms, social distancing measures that reduce contact with people who might be infectious, should be prioritised, enhanced by active case-finding through testing of asymptomatic people.

Something about vaccines and variants, which we can’t address

The objectives of this study were to address three questions: 1. Amongst people who become infected with SARS-CoV-2, what proportion does not experience symptoms at all during their infection? 2.1 what is the infectiousness of people with asymptomatic and presymptomatic, compared with symptomatic SARS-CoV-2 infection?. 3. What proportion of SARS-CoV-2 transmission is accounted for by people who are either asymptomatic throughout infection, or pre-symptomatic?

## Methods  
We conducted a living systematic review, a systematic review that provides an online summary of findings and is updated when relevant new evidence becomes available [4]. The review follows a published protocol (https://osf.io/9ewys/), which describes in detail the methods used to speed up review tasks [5] and to assess relevant evidence rapidly during a public health emergency [6]. Previous versions of the review have been published as preprints [7,8] or peer-reviewed. We report our findings according to the statement on preferred reporting items for systematic reviews and meta-analyses 2020 (S1 PRISMA Checklist) [9]. Ethics committee review was not required for this study. Box 1 shows our definitions of symptoms, asymptomatic infection and pre-symptomatic status. We use the term asymptomatic SARS-CoV-2 infection for people without symptoms of covid-19 who remain asymptomatic throughout the course of infection. We use the term pre-symptomatic for people who do not have symptoms of covid-19 when enrolled in a study, but who develop symptoms during adequate follow-up.

# Information sources and search

We conducted the first search on March 25, 2020 and updated it on April 20, and June 10, 2020, September 28, 2020, January 29, 2021, and weekly thereafter. We searched the covid-19 living evidence database [10], which is generated using automated workflow processes [5] to: i) provide daily updates of searches of four electronic databases: Medline Pubmed, Ovid Embase, bioRxiv and medRxiv, using medical subject headings and free text keywords for SARS-CoV-2 infection and covid-19; ii) de-duplicate the records; iii) tag records that are preprints; and iv) allow searches of titles and abstracts using Boolean operators. We used the search function to identify studies of asymptomatic or pre-symptomatic SARS-CoV-2 infection using a search string of medical subject headings and free text keywords (supporting information, S1 Text). We also examined articles suggested by experts and the reference lists of retrieved mathematical modelling studies and systematic reviews. Reports from this living rapid systematic review will be updated at three-monthly intervals, with continuously updated searches. 
# Eligibility criteria 
We included studies in any language of people with SARS-CoV-2 diagnosed by reverse transcriptase PCR (RT-PCR) that documented follow-up and symptom status at the beginning and end of follow-up, or investigated the contribution to SARS-CoV-2 transmission of asymptomatic or pre-symptomatic infection. We included contact tracing investigations, cohort studies, case-control studies and statistical and mathematical modelling studies. We excluded the following study types: case reports of a single patient and case series where participants were not enrolled consecutively. Where multiple records included data from the same study population, we linked the records and extracted data from the most complete report. 
Include a section here on changes to the protocol 
# Study selection and data extraction 
Reviewers worked in pairs to screen records using an application programming interface in the electronic data capture system (REDCap, Vanderbilt University, USA). One reviewer selected potentially eligible studies and a second reviewer verified all included and excluded studies. We reported the identification, exclusion and inclusion of studies in a flowchart (S1 Fig). The reviewers determined which of the three review questions each study addressed, using the definitions in Box 1. One reviewer extracted data using a pre-piloted extraction form in REDCap and a second reviewer verified the extracted data using the query system. A third reviewer adjudicated on disagreements that could not be resolved by discussion. We contacted study authors for clarification where the study description was insufficient to reach a decision on inclusion or if reported data in the manuscript were internally inconsistent. The extracted variables included, but were not limited to, study design, country and/or region, study setting, population, age, primary outcomes and length of follow-up. From empirical studies, we extracted raw numbers of individuals with any outcome and its relevant denominator. From statistical and mathematical modelling studies we extracted proportions and uncertainty intervals reported by the authors.

![Box 1. Definitions of symptoms and symptom status in a person with SARS-CoV-2 infections](Box1.png)

The primary outcomes for each review question were: 1. Proportion with asymptomatic SARS-CoV-2 infection who did not experience symptoms at all during follow-up;  2.1 the secondary attack rate from asymptomatic or pre-symptomatic index cases, compared with symptomatic cases. 2.2. Estimated proportion (with uncertainty interval) of SARS-CoV-2 transmission accounted for by people who are asymptomatic or pre-symptomatic.

# Risk of bias in included studies

Two authors independently assessed the risk of bias. A third reviewer resolved disagreements. We developed a tool with specific questions about selection and information biases [11]. The adapted tool included items about inclusion criteria, measurement of asymptomatic status, follow-up of course of disease, and statistical analysis. We added items about selection biases affecting the study population from a tool for the assessment of risk of bias in prevalence studies [12]. For mathematical modelling studies, we used a checklist for assessing relevance and credibility [13].

# Synthesis of the evidence

We used the metaprop and metabin functions from the meta package (version 4.11-0) [14] in R (version 3.5.1) to display the study findings in forest plots and synthesise their findings. The 95% confidence intervals (CI) for each study are estimated using the Clopper-Pearson method [15]. We examined heterogeneity visually in forest plots. We stratified studies according to the methods used to identify people with asymptomatic SARS-CoV-2 infection and the study setting. To synthesise proportions from comparable studies, in terms of design and population, we used stratified random effects meta-analysis. For the stratified and overall summary estimates we calculated prediction intervals, to represent the likely range of proportions that would be obtained in subsequent studies conducted in similar settings [16]. We calculated the secondary attack rate as the number of cases among contacts as a proportion of all close contacts ascertained. We did not account for potential clustering of contacts because the included studies did not report the size of clusters. We compared the secondary attack rate from asymptomatic or pre-symptomatic index cases with that from symptomatic cases. If there were no events in a group, we added 0.5 to each cell in the 2x2 table. We used random effects meta-analysis with the Mantel-Haenszel method to estimate a summary risk ratio (with 95% CI).

## Results 
The living evidence database contained a total of >200,000 records about SARS-CoV-2 or COVID-19 by 30 July 2021. The searches for studies about asymptomatic or pre-symptomatic SARS-CoV-2, on 25 March, 20 April and 10 June, resulted in 89, 230 and 688 records for screening (S1 Fig). In the first version of the review [7], 11 articles were eligible for inclusion [17-27], version 2 [8] identified another 26 eligible records [28-53], and version 3 identified another 61 eligible records [54-114]. After excluding  four articles for which more recent data became available in a subsequent version [25,29,30,35], the total number of articles included was 94 (S1 Table) [17-24,26-28,31-34,36-114]. The types of evidence changed across the three versions of the review (S1 Table). In the first version, six of 11 studies were contact investigations of single family clusters with a total of 39 people. In the next versions, study designs included larger investigations of contacts and outbreaks, screening of defined groups and studies of hospitalised adults and children. Across all three review versions, data from 79 empirical observational studies were collected in 19 countries or territories (Tables 1 and 2) and included 6832 people with SARS-CoV-2 infection. Forty seven of the studies, including 3802 infected people were done in China (S2 Table). At the time of their inclusion in the review, 23 of the included records were preprints; six of these had been published in peer-reviewed journals by 17 July 2020 [19,20,27,81,82,106].

# Proportion of people with asymptomatic SARS-CoV-2 infection

We included 79 studies that reported empirical data about 6616 people with SARS-CoV-2 infection (1287 defined as having asymptomatic infection) [17,18,21-23,26-28,31,32,34,36,39-45,47-50,52-54,56-62,64,66-68,70-77,79-90,92-112,114] and one statistical modelling study [24] (Table 1). The sex distribution of the people with asymptomatic infection was reported in 41/79 studies and the median age was reported in 35/79 studies (Table 1). The results of the studies were heterogeneous (S2 Fig). We defined seven strata, according to the method of selection of asymptomatic status and study settings. Study findings within some of these strata were more consistent (Fig 1). We considered the statistical modelling study of passengers on the Diamond Princess cruise ship passengers [24] separately, because of the different method of analysis and overlap with the study population reported by Tabata S, et al. [27].

```{r table1, ft.split=TRUE, tab.cap='Table 1. Characteristics of studies included for Q1', echo = FALSE}
table1 <- as_grouped_data(Q1_table, groups = "setting")

table1 %>% 
  as_flextable() %>% 
  set_header_labels(setting = "Setting",
                    location = "Country, region", 
                    study = "Study",
                    total_SARS_n = "Total SARS-CoV-2, n",
                    asymp_SARS_n = "Asymptomatic SARS-CoV-2, n",
                    sex = "Sex of asymptomatic people",         
                    age = "Age of asymptomatic people, years, median",            
                    follow_up = "Follow-up method") %>%
  set_table_properties(layout = "autofit") %>%
  footnote(i = 1, j = 7,
           value = as_paragraph("Follow-up according to protocol (1: 14 days after last possible exposure; 2: 7 days after diagnosis; 3: until negative RT-PCR result)."),
           ref_symbols = "a",
           part = "header") #add footnote
```

![Figure 1. Forest plot of proportion  of people with asymptomatic SARS-CoV-2 infection, stratified by setting and ordered by precision](forest_meta_Q1.png)

The main risks of bias across all categories of empirical studies were in the selection and enrolment of people with asymptomatic infection and mismeasurement of asymptomatic status because of absent or incomplete definitions (S3 Fig). Sources of bias specific to studies in particular settings are discussed with the relevant results.

```{r table2, ft.split=TRUE, tab.cap='Table 1. Characteristics of studies included for Q2.1', echo = FALSE}
#create table
Q2_1_table <- Q2_1_table %>%
  arrange(setting)

table2 <- as_grouped_data(Q2_1_table, groups = "setting")

table2 %>% 
  as_flextable() %>% 
  set_header_labels(setting = "Setting",
                    location = "Country, region", 
                    study = "Study") %>%
  set_table_properties(layout = "autofit") %>%
  theme_vanilla()

```

![Figure 2.1. Forest plot of secondary attack rate comparing infections in contacts of asymptomatic and presymptomatic index cases with infections in contacts of symptomatic cases, ordered by precision](forest_meta_Q2_1.png)
```{r table3, ft.split=TRUE, tab.cap='Table 1. Characteristics of studies included for Q2.2', echo = FALSE}
#create table
table2 <- flextable(Q2_2_table)

table2 %>% 
  set_header_labels(study = "Study",
                    q3_setting = "Setting") %>%
  set_table_properties(layout = "autofit") %>%
  theme_vanilla()

```

![Figure 4. Forest plot of proportion of SARS-CoV-2 infection resulting from asymptomatic or presymptomatic transmission](forest_Q2_2.png)

### 2021-08-23 ROB.R

@@ -1,0 +1,46 @@
+##################################################
+# Risk of bias visualisation                     #  
+##################################################
+rm(list=ls())
+
+#download package
+install.packages("devtools")
+devtools::install_github("mcguinlu/robvis")
+
+
+rob_data <- robvis::data_rob2
+rob_data$D6 <- rob_data$Overall
+rob_data$Overall <- NULL
+rob_data
+
+#summary table giving traffic lights for each domain in each study
+trafficlight_rob <- robvis::rob_traffic_light(data = rob_data,
+                                      tool = "Generic",
+                                      psize = 10,
+                                      overall = FALSE)
+
+trafficlight_rob +
+  ggplot2::labs(
+    caption = "  Domains:
+  D1: Representativeness of the sample (selection bias)
+  D2: Characteristics of non-respondents (selection bias)
+  D3: Symptom assessment (information bias)
+  D4: Recording of symptoms (information bias)
+  D5: Classification of asymptomatic status (misclassification bias)
+  D6: Selective reporting of symptoms status (attrition bias)
+                "
+  ) 
+
+
+#summary plot giving an overview of risk of bias from all studies
+
+names(rob_data) <- c("Representativeness of the sample (selection bias)",
+                     "D2: Characteristics of non-respondents (selection bias)",
+                     "D3: Symptom assessment (information bias)",
+                     "D4: Recording of symptoms (information bias)",
+                     "D5: Classification of asymptomatic status (misclassification bias)",
+                     "D6: Selective reporting of symptoms status (attrition bias)")
+summary_rob <- robvis::rob_summary(data = rob_data, tool = "ROB2")
+
+summary_rob
+###make changes to ggplot to relabel domains

### 2021-08-23 ROB_editing.R

@@ -1,0 +1,175 @@
+###code adapted from robvis package
+###https://github.com/mcguinlu/robvis/ 
+
+
+rob_traffic_light_edit <-
+  function(data,
+           tool,
+           colour = "cochrane",
+           psize = 10,
+           overall = TRUE,
+           ...) {
+    
+    check_tool(tool)
+    check_data(data)
+    colour <- weird_spelling(colour)
+    
+    check_colour(tool = tool, colour = colour)
+    
+    # Define colours
+    rob_colours <- get_colour(tool = tool, colour = colour)
+    
+    if (tool %in% c("Generic", "ROB1")) {
+      plot <- rob_traffic_light_custom(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = NULL,
+        ...
+      )
+    }
+    
+    # Add recommended saving height to the plot object
+    plot$rec_height <- get_height(
+      data = data,
+      tool = tool,
+      psize = psize,
+      type = "tf"
+    )
+    
+    # Add recommended saving width to the plot object
+    plot$rec_width <- get_width(data = data,
+                                psize = psize,
+                                type = "tf")
+    
+    plot$rob_type <- "traffic"
+    
+    return(plot)
+  }
+
+# ROB-1/Generic=================================================================
+
+rob_traffic_light_custom <- function(data,
+                                      tool,
+                                      rob_colours,
+                                      psize,
+                                      overall,
+                                      x_title = "Risk of bias domains",
+                                      y_title = "Study",
+                                      judgement_title = "Judgement",
+                                      judgement_labels = c("Critical",
+                                                           "High",
+                                                           "Unclear",
+                                                           "Low")) {
+  
+  rob1_warning(tool)
+  
+  max_domain_column <- dim(data)[2] - 1
+  
+  data.tmp <- data
+  
+  # Create caption vector, and add line breaks to maintain spacing
+  #captiondf <- data.frame(V1 = rep("", 8), stringsAsFactors = FALSE)
+  #captiondf$V1 <- c("D1: Representativeness of the sample (selection bias)\n",
+                    #"D2: Characteristics of non-respondents (selection bias)\n",
[…]

### 2021-08-23 SF_Q1_by_source.R

@@ -1,0 +1,123 @@
+###############################################################
+# Question 1: results output                         ##########
+# Proportion of asymptomatic cases                   ##########
+# Supplementary material: preprints removed          ##########
+###############################################################
+
+#load the libraries
+library(meta)
+library(readxl)
+library(tidyverse)
+library(httr) # use to retrieve data from REDCap
+library(kableExtra)
+library(flextable)
+library(dplyr)
+library(Rcpp)
+
+
+# Prepare the data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+asymptomaticQ1_pub <- httr::content(response)
+
+
+settings=c("Contact investigation",
+           "Contact investigation, aggregated",
+           "Outbreak investigation",
+           "Statistical model",
+           "Screening",
+           "Hospitalised adults",
+           "Hospitalised children",
+           "Hospitalised adults & children")
+
+
+asymptomaticQ1_pub$setting2<-factor(asymptomaticQ1_pub$setting2, levels=1:8, labels=settings)
+#combine contact investigation and contact investigation aggregated
+asymptomaticQ1_pub$setting2[asymptomaticQ1_pub$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"
+
+# minor cleaning
+asymptomaticQ1_pub[asymptomaticQ1_pub==9999]=NA
+
+asymptomaticQ1_pub$setting=asymptomaticQ1_pub$setting2
+
[…]

### 2021-08-23 SF_Q1_countries.R

@@ -1,0 +1,62 @@
+###############################################################
+# SF: Prepare countries in Q1, Q2.1, Q2.2            ##########
+###############################################################
+
+#load the libraries
+library(meta)
+library(readxl)
+library(tidyverse)
+library(httr) # use to retrieve data from REDCap
+
+# Prepare the data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+asymptomaticQ1 <- httr::content(response)
+
+#only keep required variables
+countries_q1 <- asymptomaticQ1 %>%
+  select(record_id, author_1, country, region) %>%
+  mutate(country = ifelse(country == 888, "Other", country),
+         country = ifelse(country == 40, "China", country),
+         country = ifelse(country == 87, "Japan", country),
+         country = ifelse(country == 62, "France", country),
+         country = ifelse(country == 85, "Italy", country),
+         country = ifelse(country == 67, "Germany", country),
+         country = ifelse(country == 157, "South Korea", country),
+         country = ifelse(country == 181, "United States of America", country),
+         country = ifelse(country == 28, "Brunei", country),
+         country = ifelse(country == 180, "United Kingdom", country),
+         country = ifelse(country == 185, "Vietnam", country),
+         country = ifelse(country == 138, "Portugal", country),
+         country = ifelse(country == 83, "Ireland", country),
+         country = ifelse(country == 92, "Kuwait", country),
+         country = ifelse(country == 160, "Other", country),
+         country = ifelse(country == 69, "Other", country),
+         country = ifelse(country == 170, "Other", country),
+         country = ifelse(country == 10, "Other", country),
+         country = ifelse(country == 34, "Other", country),
+         country = ifelse(country == 888, "Other", country),
+         country = ifelse(country == 888, "Other", country),
+         country = ifelse(country == 888, "Other", country),
+         country = ifelse(country == 888, "Other", country),
+         country = ifelse(country == 888, "Other", country),
+         country = ifelse(country == 888, "Other", country),
[…]

### 2021-08-23 SF_Q1_table_countries.R

@@ -1,0 +1,110 @@
+###############################################################
+# Question 1: results output                         ##########
+# Proportion of asymptomatic cases                   ##########
+###############################################################
+
+#load the libraries
+library(meta)
+library(readxl)
+library(tidyverse)
+library(httr) # use to retrieve data from REDCap
+library(kableExtra)
+library(flextable)
+library(dplyr)
+library(Rcpp)
+
+
+##########################################
+# table on characteristics of Q1 studies
+##########################################
+
+#download data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+Q1_table_countries <- httr::content(response)
+
+#clean countries
+Q1_table_countries <- Q1_table_countries %>%
+  mutate(country = ifelse(country == 10, "Australia", country),
+         country = ifelse(country == 11, "Austria", country),
+         country = ifelse(country == 15, "Bahrain", country),
+         country = ifelse(country == 19, "Belgium", country),
+         country = ifelse(country == 28, "Brunei", country),
+         country = ifelse(country == 34, "Canada", country),
+         country = ifelse(country == 40, "China", country),
+         country = ifelse(country == 41, "Colombia", country),
+         country = ifelse(country == 51, "Denmark", country),
+         country = ifelse(country == 62, "France", country),
+         country = ifelse(country == 63, "French Guyana", country),
+         country = ifelse(country == 67, "Germany", country),
+         country = ifelse(country == 69, "Greece", country),
+         country = ifelse(country == 78, "Iceland", country),
+         country = ifelse(country == 79, "India", country),
+         country = ifelse(country == 83, "Ireland", country),
+         country = ifelse(country == 85, "Italy", country),
[…]

### 2021-08-23 SF_Q1_by_precision.R
update supplementary files

@@ -1,0 +1,80 @@
+###############################################################
+# Supplementary material                        ##########
+# Q1 - studies ordered by precision                   ##########
+###############################################################
+
+
+#load the libraries
+library(meta)
+library(readxl)
+library(tidyverse)
+library(httr) # use to retrieve data from REDCap
+
+# Prepare the data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+asymptomaticQ1 <- httr::content(response)
+
+# minor cleaning
+asymptomaticQ1[asymptomaticQ1 == 9999] = NA
+
+asymptomaticQ1$setting = asymptomaticQ1$setting2
+
+
+data_long1 <- gather(asymptomaticQ1, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
+  mutate(id=1:nrow(.)) %>%
+  select(record_id, author_1, total, id, cluster)
+data_long2 <-gather(asymptomaticQ1, cluster, events, c(q1_c1_event,q1_c2_event,q1_c3_event), factor_key=TRUE) %>% 
+  mutate(id=1:nrow(.)) %>%
+  select(events, id)
+
+data_Q1 = merge(data_long1, data_long2, by="id")
+data_Q1 = data_Q1[!is.na(data_Q1$total),]
+data_Q1$cluster = factor(data_Q1$cluster, labels = c("1","2","3"), levels = c("q1_c1_total", "q1_c2_total", "q1_c3_total"))
+
+data_Q1[data_Q1$record_id %in% asymptomaticQ1[is.na(asymptomaticQ1$q1_c2_event),]$record_id,]$cluster=NA
+
+asymptomaticQ1 <- data_Q1
+
+asymptomaticQ1$label=paste0(asymptomaticQ1$author_1, " (2020)",
+                            ifelse(!is.na(asymptomaticQ1$cluster),
[…]

### 2021-08-23 SF_Q2.1_by_precision.R

@@ -1,0 +1,111 @@
+###############################################################
+# Question 2.1: results output ################################
+# Secondary attack rate from asymp or pre-symp cases ##########
+###############################################################
+
+
+#load libraries
+library(RCurl)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(meta)
+library(metafor)
+library(flextable)
+
+# get the data directly from redcap: 
+# report #172 is Q2.1 SAR:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData2_1 <- list("token"=token,
+                    content='report',
+                    format='csv',
+                    report_id='172',
+                    csvDelimiter='',
+                    rawOrLabel='raw',
+                    rawOrLabelHeaders='raw',
+                    exportCheckboxLabel='false',
+                    returnFormat='json'
+)
+response2_1 <- httr::POST(url, body = formData2_1, encode = "form")
+asymptomaticQ2_1 <- httr::content(response2_1)
+
+#clean data
+asymptomaticQ2_1[asymptomaticQ2_1=="9999;9999"]=NA #indicate as missing
+asymptomaticQ2_1[asymptomaticQ2_1=="9999"]=NA #indicate as missing
+asymptomaticQ2_1=asymptomaticQ2_1%>% #separate symp SAR into 2 variables
+  separate(q3_sar_s, c("Ec","Nc"), ";", remove=FALSE) 
+asymptomaticQ2_1=asymptomaticQ2_1%>% #separate asymp SAR into 2 variables
+  separate(q3_sar_a, c("Ee_a","Ne_a"), ";", remove=FALSE) 
+asymptomaticQ2_1=asymptomaticQ2_1%>% #separate presymp SAR into 2 variables
+  separate(q3_sar_p, c("Ee_p","Ne_p"), ";", remove=FALSE) 
+
+asymptomaticQ2_1=asymptomaticQ2_1 %>% #change values to numeric
+  mutate(Ec=as.numeric(Ec),
+         Nc=as.numeric(Nc),
+         Ee_a=as.numeric(Ee_a),
+         Ne_a=as.numeric(Ne_a),
+         Ee_p=as.numeric(Ee_p),
+         Ne_p=as.numeric(Ne_p))
+
+#create new df with asymp/presymp as subgroups
+q2_1_df_a <- asymptomaticQ2_1 %>%
[…]

### 2021-08-24 Manuscript_draft.Rmd
Added numbers to text (abstract and results) that will update automatically

@@
 
+q1_nstudies <- nrow(asym_plot$data) #total number of studies included in q1
+q1_nppl <- prettyNum(sum(asymptomaticQ1$total), big.mark = ",") #total number of people included in q1
+q1_nasymp <-  prettyNum(sum(asymptomaticQ1$events), big.mark = ",") #number of people asymptomatic included in q1
+
 ##########################################
@@
 dev.off()
+
+q2_1_nstudies <- nrow(q2_1_asymp$data) #total number of studies included in q1
 
@@
 
+q2_2_nstudies <- nrow(Q2_2_table) #total number of studies included in q1
+
 ```
+
+## ABSTRACT
+
+There is disagreement about the level of asymptomatic severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) infection.
+We conducted a living systematic review and meta-analysis to address three questions: 1.
+amongst people who become infected with SARS-CoV-2, what proportion does not experience symptoms at all during their infection?
+2.
+Amongst people with SARS-CoV-2 infection who are asymptomatic when diagnosed, what proportion will develop symptoms later?
+2.13.
+What is the infectiousness of asymptomatic and pre-symptomatic, compared with symptomatic, SARS-CoV-2 infection?
+2.2.
+What proportion of SARS-CoV-2 transmission is accounted for by people who are either asymptomatic throughout infection, or pre-symptomatic?
+We searched PubMed, Embase, bioRxiv and medRxiv using a database of SARS-CoV-2 literature that is updated daily, on 25 March 2020, 20 April 2020, and 10 June 2020, 28 Sept 2020, 29 Jan 2021 and weekly thereafter.
+Studies of people with SARS-CoV-2 diagnosed by reverse transcriptase PCR that documented follow-up and symptom status at the beginning and end of follow-up, or modelling studies were included.
+One reviewer extracted data and a second verified the extraction, with disagreement resolved by discussion or a third reviewer.
+Risk of bias in empirical studies was assessed with an adapted bespoke checklist for case series and the relevance and credibility of modelling studies were assessed using a published checklist.
+**We included a total of `r q1_nstudies` studies that reported empirical data about `r q1_nppl` people with SARS-CoV-2 infection (`r q1_nasymp` defined as having asymptomatic infection), `r q2_1_nstudies` studies for Q2.1, and `r q2_2_nstudies` studies for Q2.2.** The overall estimate of the proportion of people who become infected with SARS-CoV-2 and remain asymptomatic throughout infection was 20% (95% CI 17-25) with a prediction interval of 3-67% in 79 studies that addressed this review question.
+There was some evidence that biases in the selection of participants influence the estimate.
+In seven studies of defined populations screened for SARS-CoV-2 and then followed, 31% (95% CI 26-37%, prediction interval 24-38%) remained asymptomatic.
+The proportion of people that is pre-symptomatic could not be summarised, owing to heterogeneity.
+The secondary attack rate was lower in contacts of people with asymptomatic infection than those with symptomatic infection (relative risk 0.35, 95% CI 0.10-1.27).
+Modelling studies fit to data found a higher proportion of all SARS-CoV-2 infections resulting from transmission from pre-symptomatic individuals than from asymptomatic individuals.
+Limitations of the review include that most included studies were not designed to estimate the proportion of asymptomatic SARS-CoV-2 infections and were at risk of selection biases, we did not consider the possible impact of false negative RT-PCR results, which would underestimate the proportion of asymptomatic infections, and that the database does not include all sources.
+The findings of this living systematic review suggest that most people who become infected with SARS-CoV-2 will not remain asymptomatic throughout the course of the infection.
+The contribution of pre-symptomatic and asymptomatic infections to overall SARS-CoV-2 transmission means that combination prevention measures, with enhanced hand hygiene, masks, testing tracing and isolation strategies and social distancing, will continue to be needed.
 
@@
 
-We included 79 studies that reported empirical data about 6616 people with SARS-CoV-2 infection (1287 defined as having asymptomatic infection) [17,18,21-23,26-28,31,32,34,36,39-45,47-50,52-54,56-62,64,66-68,70-77,79-90,92-112,114] and one statistical modelling study [24] (Table 1).
-The sex distribution of the people with asymptomatic infection was reported in 41/79 studies and the median age was reported in 35/79 studies (Table 1).
+**We included `r q1_nstudies` studies that reported empirical data about `r q1_nppl` people with SARS-CoV-2 infection (`r q1_nasymp` defined as having asymptomatic infection) (Table 1).** The sex distribution of the people with asymptomatic infection was reported in 41/79 studies and the median age was reported in 35/79 studies (Table 1).
 The results of the studies were heterogeneous (S2 Fig).

### 2021-08-24 Methods and Results.Rmd
adding old version

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-output: pdf_document
+output: html_document
 ---
@@
 
+#create new df with asymp/presymp as subgroups
+q2_1_df_a <- asymptomaticQ2_1 %>%
+  select("record_id", "author_1", "Ee_a", "Ne_a", "Ec", "Nc", "region", "year") %>%
+  rename(Ee = Ee_a,
+         Ne = Ne_a) %>%
+  filter(!is.na(Ee)) %>%
+  mutate(group = "Asymptomatic")
+q2_1_df_p <- asymptomaticQ2_1 %>%
+  select("record_id", "author_1", "Ee_p", "Ne_p", "Ec", "Nc", "region", "year") %>%
+  rename(Ee = Ee_p,
+         Ne = Ne_p) %>%
+  filter(!is.na(Ee)) %>%
+  mutate(group = "Presymptomatic")
+#bind rows
+q2_1_df <- bind_rows(q2_1_df_a, q2_1_df_p)
+
 #metaanalysis for asymptomatic transmission
 
-q2_1_asymp <- metabin(event.e = Ee_a,
-                      n.e = Ne_a,
+q2_1_asymp <- metabin(event.e = Ee,
+                      n.e = Ne,
                       event.c = Ec,
                       n.c = Nc, 
-                      data = asymptomaticQ2_1[!is.na(asymptomaticQ2_1$Ee_a),],
+                      data = q2_1_df,
                       studlab = author_1,
@@
                       method = "MH",
-                      MH.exact = TRUE)
+                      MH.exact = TRUE, 
+                      byvar = group)
 q2_1_asymp
 
-png(file = 'forest_meta_Q2_1_asymp.png',width=750,height=250)
+pdf(file = 'forest_meta_Q2_1.pdf', width = 10, height = 6)
 
-forest(q2_1_asymp)
+forest(q2_1_asymp, overall = FALSE)
 
@@
 
-#metaanalysis for presymptomatic transmission
+##########################################
+# supplementary information - by precision
+##########################################
 
-q2_1_presymp <- metabin(event.e = Ee_p,
-                        n.e = Ne_p,
+#metaanalysis for asymptomatic transmission
+
+q2_1_asymp_precision <- metabin(event.e = Ee,
+                                n.e = Ne,
                                 event.c = Ec,
                                 n.c = Nc, 
-                        data = asymptomaticQ2_1[!is.na(asymptomaticQ2_1$Ee_p),],
+                                data = q2_1_df,
                                 studlab = author_1,
-                        prediction = TRUE,
                                 sm = "RR",
-                        method = "MH",
-                        MH.exact = TRUE)
+                                byvar = group)
 
-q2_1_presymp
+pdf(file = 'forest_meta_Q2_1_precision.pdf', width = 10, height = 6)
 
-png(file = 'forest_meta_Q2_1_presymp.png',width=750,height=190)
-
-forest(q2_1_presymp)
+forest(q2_1_asymp_precision, sortvar = -seTE, overall = FALSE)
 
@@
 
-![Figure 2. Forest plot of secondary attack rate comparing infections in contacts of asymptomatic index cases with infections in contacts of symptomatic cases](forest_meta_Q2_1_asymp.png)
-
-![Figure 3. Forest plot of secondary attack rate comparing infections in contacts of presymptomatic index cases with infections in contacts of symptomatic cases](forest_meta_Q2_1_presymp.png)
+![Figure 2. Forest plot of secondary attack rate comparing infections in contacts of asymptomatic and presymptomatic index cases with infections in contacts of symptomatic cases](forest_meta_Q2_1.pdf)
 

### 2021-10-05 Asymptomatic_LSR_Supplement.Rmd
Update
Update

@@
   arrange(desc(n))
+#create PRISMA 2020 flowchart
+
+#download packages
+library(devtools)
+library(dplyr)
+install_github("nealhaddaway/PRISMA2020")
+
+#create df from example csv file
+PRISMA <- read.csv("PRISMA.csv")
+
+#set the REDCap IDs
+#last REDCap ID in previous version
+last_ID_prev <- 1000
+#last REDCap ID in current version
+last_ID_current <- 5296
+#load all records in redcap
+
+# get the data directly from redcap:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='158',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response_all <- httr::POST(url, body = formData, encode = "form")
+all_records <- httr::content(response_all)
+
+#find number of studies identified in databases since previous update
+current_records <- all_records[last_ID_prev:last_ID_current, ]
+PRISMA$n[PRISMA$data == "database_results"] <- nrow(current_records[!is.na(current_records$record_id), ]) - 1 #1 was added manually 9484
+
+#find number included in review
+PRISMA$n[PRISMA$data == "new_studies"] <- nrow(current_records %>% filter(review == 1))
+
+#find number of duplicates removed before screening
+PRISMA$n[PRISMA$data == "duplicates"] <- nrow(current_records %>% filter(ex_reas == 14))
+#find number of records screening
+PRISMA$n[PRISMA$data == "records_screened"] <- nrow(current_records) - 
+  nrow(current_records %>% filter(ex_reas == 14))
+#add number of studies found via other methods 
+#1 study #9484 was added manually - it's the published v of a preprint
+#as a result, I need to minus 1 record from the database result
+PRISMA$n[PRISMA$box == "othstud"] <- 1
+
+#find number of records excluded from title and abstract
+PRISMA$n[PRISMA$data == "records_excluded"] <- nrow(current_records %>% filter(ex_reas == 1))
+check <- current_records %>% filter(ex_reas == 1)
+#current records left after title and abstract screening
+full_text_screen <- current_records %>% filter(ex_reas != 14 & ex_reas != 1)
+
+#find number of full texts retrieved
+PRISMA$n[PRISMA$data == "dbr_sought_reports"] <- nrow(current_records) - 
+  (nrow(current_records %>% filter(ex_reas == 14)) + 
+  nrow(current_records %>% filter(ex_reas == 1)))
+
+#find number of full texts screened
+PRISMA$n[PRISMA$data == "dbr_assessed"] <- nrow(current_records) - 
+  (nrow(current_records %>% filter(ex_reas == 14)) + 
+     nrow(current_records %>% filter(ex_reas == 1)))
+
+#find number included in previous version
+prev_records <- all_records[1:last_ID_prev, ]
+PRISMA$n[PRISMA$data == "previous_studies"] <- nrow(prev_records[prev_records$review == 1, ])
+
+#calculate total studies included
+PRISMA$n[PRISMA$data == "total_studies"] <- nrow(prev_records[prev_records$review == 1, ]) +
+  nrow(current_records[current_records$review == 1, ])
+
+# studies excluded
+excl_11 <-  nrow(current_records %>% filter(ex_reas == 11))
+excl_12 <-  nrow(current_records %>% filter(ex_reas == 12))
+excl_13 <-  nrow(current_records %>% filter(ex_reas == 13))
+excl_15 <-  nrow(current_records %>% filter(ex_reas == 15))
+excl_16 <-  nrow(current_records %>% filter(ex_reas == 16))
+excl_17 <-  nrow(current_records %>% filter(ex_reas == 17))
+excl_19 <-  nrow(current_records %>% filter(ex_reas == 19))
+excl_20 <-  nrow(current_records %>% filter(ex_reas == 20))
+excl_21 <-  nrow(current_records %>% filter(ex_reas == 21))
+excl_18 <-  nrow(current_records %>% filter(ex_reas == 18))
+
+excl_reasons <- paste0("Publication not on COVID-19, ", excl_11, 
+                       "; No original data, ", excl_12, 
+                       "; Data included in other publication, ", excl_13, 
+                       "; Insufficient extractable data, ", excl_15, 
+                       "; Study design inappropriate, ", excl_16, 
+                       "; No PCR/serological test, ", excl_17, 
+                       "; Math. model not in review scope, ", excl_19, 
+                       "; Inadequate follow-up time, ", excl_20, 
+                       "; Preprint of published article, ", excl_21, 
+                       "; Other, ", excl_18)
+excl_reasons
+PRISMA$n[PRISMA$data == "dbr_excluded"] <- excl_reasons
+
+#fix some text in the flowchart data
+PRISMA$boxtext[PRISMA$data == "identification"] <- "Identification"
+PRISMA$boxtext[PRISMA$box == "prevstud"] <- "Previous studies"
+
+#read data
+flowchart <- PRISMA2020::PRISMA_data(PRISMA)
+flowchart
+#generate flowchart
+PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
+flowchart_plot <- PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
+
+PRISMA2020::PRISMA_save(flowchart_plot, filename = "PRISMA2020_flowdiagram.png", filetype = "png", overwrite = TRUE)
 
@@
 
-## Flowchart
-*In progress.*
-
+## PRISMA 2020 Flowchart
+![Figure 3. PRISMA 2020 Flow Diagram](PRISMA2020_flowdiagram.png)
 ***
@@
 ## Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search.
-![Figure 3. Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search](forest_meta_Q1_published.png)
+![Figure 4. Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search](forest_meta_Q1_published.png)
 

### 2021-10-05 Manuscript_draft.Rmd
Update
Update

@@
          setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
-         setting = ifelse(setting2 == 9, "Screening: hospitalised patients", setting),
-         setting = ifelse(setting2 == 10, "Screening: general population", setting),
+         setting = ifelse(setting2 == 9, "Screening: institutional setting", setting),
+         setting = ifelse(setting2 == 10, "Screening: community setting", setting),
          setting = ifelse(setting2 == 11, "Screening: occupational", setting))
@@
            "Hospitalised children",
-           "Hospitalised adults & children")
+           "Hospitalised adults & children",
+           "Screening: institutional setting",
+           "Screening: community setting",
+           "Screening: occupational")
 
-asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:8, labels=settings)
+asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:11, labels=settings)
 #combine contact investigation and contact investigation aggregated
@@
 
-asymptomaticQ1$setting=asymptomaticQ1$setting2
+asymptomaticQ1$setting = asymptomaticQ1$setting2
 
@@
 asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#2751 van den Besselaar [cluster:1]"] <- "#2751 van den Besselaar [Healthcare workers]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#2751 van den Besselaar [cluster:2]"] <- "#2751 van den Besselaar [Residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor [Healthcare personnel]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor [Residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani [cluster:1]"] <- "#3719 Ladhani [Residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani [cluster:2]"] <- "#3719 Ladhani [Healthcare workers]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:1]"] <- "#5551 Vohra [Presurgical patients]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:2]"] <- "#5551 Vohra [Undergoing chemotherapy]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:1]"] <- "#6526 Garibaldi [Residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:2]"] <- "#6526 Garibaldi [Staff]"
 
@@
 data=data[!is.na(data$setting),]
+
+#cut data at end of jan 31
+data <- data[data$record_id <= 5296, ]
 
@@
 
-png(file = 'forest_meta_Q1.png',width=25,height=70, res=600, units="cm")
+png(file = 'forest_meta_Q1.png',width=25,height=80, res=600, units="cm")
 
@@
 
-![Box 1. Definitions of symptoms and symptom status in a person with SARS-CoV-2 infections](Box1.png)
-
 The primary outcomes for each review question were: 1.

### 2021-10-06 Manuscript_draft.Rmd
update
updated country codes, removed text from draft (not useful)

@@
 
-## ABSTRACT
+ **We included a total of `r q1_nstudies` studies that reported empirical data about `r q1_nppl` people with SARS-CoV-2 infection (`r q1_nasymp` defined as having asymptomatic infection), `r q2_1_nstudies` studies for Q2.1, and `r q2_2_nstudies` studies for Q2.2.**
 
-There is disagreement about the level of asymptomatic severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) infection.
-We conducted a living systematic review and meta-analysis to address three questions: 1.
-amongst people who become infected with SARS-CoV-2, what proportion does not experience symptoms at all during their infection?
-2.
-Amongst people with SARS-CoV-2 infection who are asymptomatic when diagnosed, what proportion will develop symptoms later?
-2.13.
-What is the infectiousness of asymptomatic and pre-symptomatic, compared with symptomatic, SARS-CoV-2 infection?
-2.2.
-What proportion of SARS-CoV-2 transmission is accounted for by people who are either asymptomatic throughout infection, or pre-symptomatic?
-We searched PubMed, Embase, bioRxiv and medRxiv using a database of SARS-CoV-2 literature that is updated daily, on 25 March 2020, 20 April 2020, and 10 June 2020, 28 Sept 2020, 29 Jan 2021 and weekly thereafter.
-Studies of people with SARS-CoV-2 diagnosed by reverse transcriptase PCR that documented follow-up and symptom status at the beginning and end of follow-up, or modelling studies were included.
-One reviewer extracted data and a second verified the extraction, with disagreement resolved by discussion or a third reviewer.
-Risk of bias in empirical studies was assessed with an adapted bespoke checklist for case series and the relevance and credibility of modelling studies were assessed using a published checklist.
-**We included a total of `r q1_nstudies` studies that reported empirical data about `r q1_nppl` people with SARS-CoV-2 infection (`r q1_nasymp` defined as having asymptomatic infection), `r q2_1_nstudies` studies for Q2.1, and `r q2_2_nstudies` studies for Q2.2.** The overall estimate of the proportion of people who become infected with SARS-CoV-2 and remain asymptomatic throughout infection was 20% (95% CI 17-25) with a prediction interval of 3-67% in 79 studies that addressed this review question.
-There was some evidence that biases in the selection of participants influence the estimate.
-In seven studies of defined populations screened for SARS-CoV-2 and then followed, 31% (95% CI 26-37%, prediction interval 24-38%) remained asymptomatic.
-The proportion of people that is pre-symptomatic could not be summarised, owing to heterogeneity.
-The secondary attack rate was lower in contacts of people with asymptomatic infection than those with symptomatic infection (relative risk 0.35, 95% CI 0.10-1.27).
-Modelling studies fit to data found a higher proportion of all SARS-CoV-2 infections resulting from transmission from pre-symptomatic individuals than from asymptomatic individuals.
-Limitations of the review include that most included studies were not designed to estimate the proportion of asymptomatic SARS-CoV-2 infections and were at risk of selection biases, we did not consider the possible impact of false negative RT-PCR results, which would underestimate the proportion of asymptomatic infections, and that the database does not include all sources.
-The findings of this living systematic review suggest that most people who become infected with SARS-CoV-2 will not remain asymptomatic throughout the course of the infection.
-The contribution of pre-symptomatic and asymptomatic infections to overall SARS-CoV-2 transmission means that combination prevention measures, with enhanced hand hygiene, masks, testing tracing and isolation strategies and social distancing, will continue to be needed.
-
-## Introduction
-
-There is ongoing discussion about the level of asymptomatic severe acute respiratory syndrome coronavirus 2 (SARS-CoV-2) infection.
-The authors of a narrative review report a range of proportions of participants positive for SARS-CoV-2 but asymptomatic in different studies from 6 to 96% [1].
-The discrepancy results, in part, from the interpretation of studies that report a proportion of asymptomatic people with SARS-CoV-2 detected at a single point.
-The studies cited include both people who will remain asymptomatic throughout and those, known as pre-symptomatic, who will develop symptoms of coronavirus disease 2019 (covid-19) if followed up [2].
-The full spectrum and distribution of covid-19, from completely asymptomatic, to mild and non-specific symptoms, viral pneumonia, respiratory distress syndrome, and death are not yet known [3].
-Without follow up, however, the proportions of asymptomatic and pre-symptomatic infections cannot be determined.
-
-Accurate estimates of the proportions of true asymptomatic and pre-symptomatic infections are needed urgently because their contribution to overall SARS-CoV-2 transmission at the population level will determine the appropriate balance of control measures [3].
-If the predominant route of transmission is from people who have symptoms, then strategies should focus on testing, followed by isolation of infected individuals and quarantine of their contacts.
-If, however, most transmission is from people without symptoms, social distancing measures that reduce contact with people who might be infectious, should be prioritised, enhanced by active case-finding through testing of asymptomatic people.
-
-Something about vaccines and variants, which we can’t address
-
-The objectives of this study were to address three questions: 1.
-Amongst people who become infected with SARS-CoV-2, what proportion does not experience symptoms at all during their infection?
-2.1 what is the infectiousness of people with asymptomatic and presymptomatic, compared with symptomatic SARS-CoV-2 infection?.
-3.
-What proportion of SARS-CoV-2 transmission is accounted for by people who are either asymptomatic throughout infection, or pre-symptomatic?
-
-## Methods  
-We conducted a living systematic review, a systematic review that provides an online summary of findings and is updated when relevant new evidence becomes available [4].
-The review follows a published protocol (https://osf.io/9ewys/), which describes in detail the methods used to speed up review tasks [5] and to assess relevant evidence rapidly during a public health emergency [6].
-Previous versions of the review have been published as preprints [7,8] or peer-reviewed.
-We report our findings according to the statement on preferred reporting items for systematic reviews and meta-analyses 2020 (S1 PRISMA Checklist) [9].
-Ethics committee review was not required for this study.
-Box 1 shows our definitions of symptoms, asymptomatic infection and pre-symptomatic status.
-We use the term asymptomatic SARS-CoV-2 infection for people without symptoms of covid-19 who remain asymptomatic throughout the course of infection.
-We use the term pre-symptomatic for people who do not have symptoms of covid-19 when enrolled in a study, but who develop symptoms during adequate follow-up.
-
-# Information sources and search
-
-We conducted the first search on March 25, 2020 and updated it on April 20, and June 10, 2020, September 28, 2020, January 29, 2021, and weekly thereafter.
-We searched the covid-19 living evidence database [10], which is generated using automated workflow processes [5] to: i) provide daily updates of searches of four electronic databases: Medline Pubmed, Ovid Embase, bioRxiv and medRxiv, using medical subject headings and free text keywords for SARS-CoV-2 infection and covid-19; ii) de-duplicate the records; iii) tag records that are preprints; and iv) allow searches of titles and abstracts using Boolean operators.
-We used the search function to identify studies of asymptomatic or pre-symptomatic SARS-CoV-2 infection using a search string of medical subject headings and free text keywords (supporting information, S1 Text).
-We also examined articles suggested by experts and the reference lists of retrieved mathematical modelling studies and systematic reviews.
-Reports from this living rapid systematic review will be updated at three-monthly intervals, with continuously updated searches.
-# Eligibility criteria 
-We included studies in any language of people with SARS-CoV-2 diagnosed by reverse transcriptase PCR (RT-PCR) that documented follow-up and symptom status at the beginning and end of follow-up, or investigated the contribution to SARS-CoV-2 transmission of asymptomatic or pre-symptomatic infection.
-We included contact tracing investigations, cohort studies, case-control studies and statistical and mathematical modelling studies.
-We excluded the following study types: case reports of a single patient and case series where participants were not enrolled consecutively.
-Where multiple records included data from the same study population, we linked the records and extracted data from the most complete report.
-Include a section here on changes to the protocol 
-# Study selection and data extraction 
-Reviewers worked in pairs to screen records using an application programming interface in the electronic data capture system (REDCap, Vanderbilt University, USA).
-One reviewer selected potentially eligible studies and a second reviewer verified all included and excluded studies.
-We reported the identification, exclusion and inclusion of studies in a flowchart (S1 Fig).
-The reviewers determined which of the three review questions each study addressed, using the definitions in Box 1.
-One reviewer extracted data using a pre-piloted extraction form in REDCap and a second reviewer verified the extracted data using the query system.
-A third reviewer adjudicated on disagreements that could not be resolved by discussion.
-We contacted study authors for clarification where the study description was insufficient to reach a decision on inclusion or if reported data in the manuscript were internally inconsistent.
-The extracted variables included, but were not limited to, study design, country and/or region, study setting, population, age, primary outcomes and length of follow-up.
-From empirical studies, we extracted raw numbers of individuals with any outcome and its relevant denominator.
-From statistical and mathematical modelling studies we extracted proportions and uncertainty intervals reported by the authors.
-
-The primary outcomes for each review question were: 1.
-Proportion with asymptomatic SARS-CoV-2 infection who did not experience symptoms at all during follow-up;  2.1 the secondary attack rate from asymptomatic or pre-symptomatic index cases, compared with symptomatic cases.
-2.2.
-Estimated proportion (with uncertainty interval) of SARS-CoV-2 transmission accounted for by people who are asymptomatic or pre-symptomatic.
-
-# Risk of bias in included studies
-
-Two authors independently assessed the risk of bias.
-A third reviewer resolved disagreements.
-We developed a tool with specific questions about selection and information biases [11].
-The adapted tool included items about inclusion criteria, measurement of asymptomatic status, follow-up of course of disease, and statistical analysis.
-We added items about selection biases affecting the study population from a tool for the assessment of risk of bias in prevalence studies [12].
-For mathematical modelling studies, we used a checklist for assessing relevance and credibility [13].
-
-# Synthesis of the evidence
-
-We used the metaprop and metabin functions from the meta package (version 4.11-0) [14] in R (version 3.5.1) to display the study findings in forest plots and synthesise their findings.
-The 95% confidence intervals (CI) for each study are estimated using the Clopper-Pearson method [15].
-We examined heterogeneity visually in forest plots.
-We stratified studies according to the methods used to identify people with asymptomatic SARS-CoV-2 infection and the study setting.
-To synthesise proportions from comparable studies, in terms of design and population, we used stratified random effects meta-analysis.
-For the stratified and overall summary estimates we calculated prediction intervals, to represent the likely range of proportions that would be obtained in subsequent studies conducted in similar settings [16].
-We calculated the secondary attack rate as the number of cases among contacts as a proportion of all close contacts ascertained.
-We did not account for potential clustering of contacts because the included studies did not report the size of clusters.
-We compared the secondary attack rate from asymptomatic or pre-symptomatic index cases with that from symptomatic cases.
-If there were no events in a group, we added 0.5 to each cell in the 2x2 table.
-We used random effects meta-analysis with the Mantel-Haenszel method to estimate a summary risk ratio (with 95% CI).
-
-## Results 
-The living evidence database contained a total of >200,000 records about SARS-CoV-2 or COVID-19 by 30 July 2021.
-The searches for studies about asymptomatic or pre-symptomatic SARS-CoV-2, on 25 March, 20 April and 10 June, resulted in 89, 230 and 688 records for screening (S1 Fig).
-In the first version of the review [7], 11 articles were eligible for inclusion [17-27], version 2 [8] identified another 26 eligible records [28-53], and version 3 identified another 61 eligible records [54-114].
-After excluding  four articles for which more recent data became available in a subsequent version [25,29,30,35], the total number of articles included was 94 (S1 Table) [17-24,26-28,31-34,36-114].
-The types of evidence changed across the three versions of the review (S1 Table).
-In the first version, six of 11 studies were contact investigations of single family clusters with a total of 39 people.
-In the next versions, study designs included larger investigations of contacts and outbreaks, screening of defined groups and studies of hospitalised adults and children.
-Across all three review versions, data from 79 empirical observational studies were collected in 19 countries or territories (Tables 1 and 2) and included 6832 people with SARS-CoV-2 infection.
-Forty seven of the studies, including 3802 infected people were done in China (S2 Table).
-At the time of their inclusion in the review, 23 of the included records were preprints; six of these had been published in peer-reviewed journals by 17 July 2020 [19,20,27,81,82,106].
-
-# Proportion of people with asymptomatic SARS-CoV-2 infection
-
-**We included `r q1_nstudies` studies that reported empirical data about `r q1_nppl` people with SARS-CoV-2 infection (`r q1_nasymp` defined as having asymptomatic infection) (Table 1).** The sex distribution of the people with asymptomatic infection was reported in 41/79 studies and the median age was reported in 35/79 studies (Table 1).
-The results of the studies were heterogeneous (S2 Fig).
-We defined seven strata, according to the method of selection of asymptomatic status and study settings.
-Study findings within some of these strata were more consistent (Fig 1).
-We considered the statistical modelling study of passengers on the Diamond Princess cruise ship passengers [24] separately, because of the different method of analysis and overlap with the study population reported by Tabata S, et al.
-[27].
+**We included `r q1_nstudies` studies that reported empirical data about `r q1_nppl` people with SARS-CoV-2 infection (`r q1_nasymp` defined as having asymptomatic infection) (Table 1).**
 

### 2021-10-07 Manuscript_draft.Rmd
Update Q1 table

@@
 output: html_document
+
 #always_allow_html: true
@@
 Q1_table <- httr::content(response)
+#cut data at end of jan 31
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+Q1_table <- Q1_table %>%
+  filter(record_id <= 5296 | record_id %in% published_preprints)
+Q1_table <- Q1_table %>%
+  select(-contains("rob")) %>%
+  select(-contains("risk_of_bias")) %>%
+  select(-journal)
 
@@
          country = ifelse(country == 19, "Belgium", country),
+         country = ifelse(country == 27, "Brazil", country),
          country = ifelse(country == 28, "Brunei", country),
@@
          country = ifelse(country == 121, "Netherlands", country),
+         country = ifelse(country == 130, "N", country),
+         country = ifelse(country == 28, "Brunei", country),
+         country = ifelse(country == 888, "Other", country),
          country = ifelse(country == 128, "Norway", country),
-         country = ifelse(country == 888, "Other", country),
          country = ifelse(country == 138, "Portugal", country),
@@
 Q1_table <- Q1_table %>%
-  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
-         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
+  mutate(setting = ifelse(setting2 == 1 | setting2 == 2, "Contact investigation", setting),
          setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
@@
 Q1_table$fup___3[Q1_table$fup___3 == 1] <- 3
+Q1_table$fup___4[Q1_table$fup___4 == 1] <- 4
 Q1_table <- Q1_table %>%
-  mutate(follow_up = ifelse(fup___1 != 0 & fup___2 != 0 & fup___3 != 0,
-                            paste0(fup___1, ", ", fup___2, ", ", fup___3),
+  mutate(follow_up = ifelse(fup___1 != 0 & fup___2 != 0 & fup___3 != 0 & fup___4 != 0,
+                            paste0(fup___1, ", ", fup___2, ", ", fup___3, ", ", fup___4),
                             NA)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 0,
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 0 & fup___4 == 0,
                             1,
                             follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 0,
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 0 & fup___4 == 0,
                             2,
                             follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 3,
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 3 & fup___4 == 0,
                             3,
                             follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 0,
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 0 & fup___4 == 4,
+                            4,
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 0 & fup___4 == 0,
                             "1, 2",
                             follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 3,
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 3 & fup___4 == 0,
                             "1, 3",
                             follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 3,
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 3 & fup___4 == 0,
                             "2, 3",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 0 & fup___4 == 4,
+                            "1, 4",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 0 & fup___4 == 4,
+                            "2, 4",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 3 & fup___4 == 4,
+                            "3, 4",
+                            follow_up)) %>%
+mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 0 & fup___4 == 4,
+                          "1, 2, 4",
+                          follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 3 & fup___4 == 0,
+                            "1, 2, 3",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 3 & fup___4 == 4,
+                            "1, 3, 4",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 3 & fup___4 == 4,
+                            "2, 3, 4",
                             follow_up))
-Q1_table$fup___1 <- NULL
-Q1_table$fup___2 <- NULL
-Q1_table$fup___3 <- NULL
+check <- Q1_table %>%
+  select(fup___1, fup___2, fup___3, fup___4, follow_up)
+Q1_table <- Q1_table %>%
+  select(-contains("fup"))
 
@@
   arrange(setting)
+
+Q1_table <- Q1_table[, c(1, 3, 2, 4, 5, 6, 7, 8)]
 
@@
 asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#2802 Bender [cluster:1]"] <- "#2802 Bender [Hospital 1]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#2802 Bender [cluster:2]"] <- "#2802 Bender [Hospital 2]"
 asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
@@
 #cut data at end of jan 31
-data <- data[data$record_id <= 5296, ]
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+data <- data %>%
+  filter(record_id <= 5296 | record_id %in% published_preprints)
 
@@
   footnote(i = 1, j = 7,
-           value = as_paragraph("Follow-up according to protocol (1: 14 days after last possible exposure; 2: 7 days after diagnosis; 3: until negative RT-PCR result)."),
+           value = as_paragraph("Follow-up according to protocol (1: 14 days after last possible exposure; 2: 7 days after diagnosis; 3: until negative RT-PCR result; 4:>7 days after diagnosis).
+NR = not reported."),
            ref_symbols = "a",
            part = "header") #add footnote
+
+#print(flextable, preview = "docx") #to print in word
+
 ```

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
copy rmd

--- 2021-10-05 Asymptomatic_LSR_Supplement.Rmd
@@
 
+library(dplyr)
 Q1_table_countries <- httr::content(response)
+
+#censor until 5296 (31 Jan) plus the published versions of preprints
+pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
+
+Q1_table_countries <- Q1_table_countries %>%
+  filter(record_id %in%  pub_preprints | record_id <= 5296)
 
@@
          country = ifelse(country == 128, "Norway", country),
+         country = ifelse(country == 130, "Pakistan", country),
          country = ifelse(country == 888, "Other", country),

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
HI

--- 2021-08-23 Asymptomatic_LSR_Supplement.Rmd
@@
   arrange(desc(n))
+#create PRISMA 2020 flowchart
+
+#download packages
+library(devtools)
+library(dplyr)
+#install_github("nealhaddaway/PRISMA2020")
+
+#create df from example csv file
+#PRISMA <- read.csv("PRISMA.csv")
+
+#set the REDCap IDs
+#last REDCap ID in previous version
+#last_ID_prev <- 1000
+#last REDCap ID in current version
+#last_ID_current <- 5296
+#load all records in redcap
+
+# get the data directly from redcap:
+# url <- "https://redcap.ispm.unibe.ch/api/"
+# token <- "F2725F15FE84D2832E2793BB23B0A62B"
+# formData <- list("token"=token,
+#                  content='report',
+#                  format='csv',
+#                  report_id='158',
+#                  csvDelimiter='',
+#                  rawOrLabel='raw',
+#                  rawOrLabelHeaders='raw',
+#                  exportCheckboxLabel='false',
+#                  returnFormat='csv'
+# )
+# response_all <- httr::POST(url, body = formData, encode = "form")
+# all_records <- httr::content(response_all)
+# 
+# #find number of studies identified in databases since previous update
+# current_records <- all_records[last_ID_prev:last_ID_current, ]
+# PRISMA$n[PRISMA$data == "database_results"] <- nrow(current_records[!is.na(current_records$record_id), ]) - 1 #1 was added manually 9484
+# 
+# #find number included in review
+# PRISMA$n[PRISMA$data == "new_studies"] <- nrow(current_records %>% filter(review == 1))
+# 
+# #find number of duplicates removed before screening
+# PRISMA$n[PRISMA$data == "duplicates"] <- nrow(current_records %>% filter(ex_reas == 14))
+# #find number of records screening
+# PRISMA$n[PRISMA$data == "records_screened"] <- nrow(current_records) - 
+#   nrow(current_records %>% filter(ex_reas == 14))
+# #add number of studies found via other methods 
+# #1 study #9484 was added manually - it's the published v of a preprint
+# #as a result, I need to minus 1 record from the database result
+# PRISMA$n[PRISMA$box == "othstud"] <- 1
+# 
+# #find number of records excluded from title and abstract
+# PRISMA$n[PRISMA$data == "records_excluded"] <- nrow(current_records %>% filter(ex_reas == 1))
+# check <- current_records %>% filter(ex_reas == 1)
+# #current records left after title and abstract screening
+# full_text_screen <- current_records %>% filter(ex_reas != 14 & ex_reas != 1)
+# 
+# #find number of full texts retrieved
+# PRISMA$n[PRISMA$data == "dbr_sought_reports"] <- nrow(current_records) - 
+#   (nrow(current_records %>% filter(ex_reas == 14)) + 
+#   nrow(current_records %>% filter(ex_reas == 1)))
+# 
+# #find number of full texts screened
+# PRISMA$n[PRISMA$data == "dbr_assessed"] <- nrow(current_records) - 
+#   (nrow(current_records %>% filter(ex_reas == 14)) + 
+#      nrow(current_records %>% filter(ex_reas == 1)))
+# 
+# #find number included in previous version
+# prev_records <- all_records[1:last_ID_prev, ]
+# PRISMA$n[PRISMA$data == "previous_studies"] <- nrow(prev_records[prev_records$review == 1, ])
+# 
+# #calculate total studies included
+# PRISMA$n[PRISMA$data == "total_studies"] <- nrow(prev_records[prev_records$review == 1, ]) +
+#   nrow(current_records[current_records$review == 1, ])
+# 
+# # studies excluded
+# excl_11 <-  nrow(current_records %>% filter(ex_reas == 11))
+# excl_12 <-  nrow(current_records %>% filter(ex_reas == 12))
+# excl_13 <-  nrow(current_records %>% filter(ex_reas == 13))
+# excl_15 <-  nrow(current_records %>% filter(ex_reas == 15))
+# excl_16 <-  nrow(current_records %>% filter(ex_reas == 16))
+# excl_17 <-  nrow(current_records %>% filter(ex_reas == 17))
+# excl_19 <-  nrow(current_records %>% filter(ex_reas == 19))
+# excl_20 <-  nrow(current_records %>% filter(ex_reas == 20))
+# excl_21 <-  nrow(current_records %>% filter(ex_reas == 21))
+# excl_18 <-  nrow(current_records %>% filter(ex_reas == 18))
+# 
+# excl_reasons <- paste0("Publication not on COVID-19, ", excl_11, 
+#                        "; No original data, ", excl_12, 
+#                        "; Data included in other publication, ", excl_13, 
+#                        "; Insufficient extractable data, ", excl_15, 
+#                        "; Study design inappropriate, ", excl_16, 
+#                        "; No PCR/serological test, ", excl_17, 
+#                        "; Math. model not in review scope, ", excl_19, 
+#                        "; Inadequate follow-up time, ", excl_20, 
+#                        "; Preprint of published article, ", excl_21, 
+#                        "; Other, ", excl_18)
+# excl_reasons
+# PRISMA$n[PRISMA$data == "dbr_excluded"] <- excl_reasons
+# 
+# #fix some text in the flowchart data
+# PRISMA$boxtext[PRISMA$data == "identification"] <- "Identification"
+# PRISMA$boxtext[PRISMA$box == "prevstud"] <- "Previous studies"
+# 
+#   
+# #read data
+# flowchart <- PRISMA2020::PRISMA_data(PRISMA)
+# flowchart
+# #generate flowchart
+# PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
+# flowchart_plot <- PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
+#                                
+# PRISMA2020::PRISMA_save(flowchart_plot, filename = "PRISMA2020_flowdiagram.png", filetype = "png", overwrite = TRUE)
+
+#######ROB Analysis HI##########
 
@@
 
-## Flowchart
+## PRISMA 2020 Flowchart
 *In progress.*
-
 ***

### 2021-10-08 robisfunctions.R
robis functions

@@ -1,0 +1,1248 @@
+rob_traffic_light <-
+  function(data,
+           tool,
+           colour = "cochrane",
+           psize = 10,
+           overall = TRUE,
+           ...) {
+    
+    check_tool(tool)
+    check_data(data)
+    colour <- weird_spelling(colour)
+    
+    check_colour(tool = tool, colour = colour)
+    
+    # Define colours
+    rob_colours <- get_colour(tool = tool, colour = colour)
+    
+    if (tool == "ROB2") {
+      plot <- rob_traffic_light_rob2(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool == "ROB2-Cluster") {
+      plot <- rob_traffic_light_rob2_cluster(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool == "ROBINS-I") {
+      plot <- rob_traffic_light_robinsi(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool == "QUADAS-2") {
+      plot <- rob_traffic_light_quadas2(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool == "QUIPS") {
+      plot <- rob_traffic_light_quips(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool %in% c("Generic", "ROB1")) {
+      plot <- rob_traffic_light_generic(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall,
+        ...
+      )
+    }
+    
+    # Add recommended saving height to the plot object
+    plot$rec_height <- get_height(
+      data = data,
+      tool = tool,
+      psize = psize,
+      type = "tf"
+    )
+    
+    # Add recommended saving width to the plot object
+    plot$rec_width <- get_width(data = data,
+                                psize = psize,
+                                type = "tf")
+    
+    plot$rob_type <- "traffic"
+    
+    return(plot)
+  }
+
+# ROB-2=========================================================================
+
+rob_traffic_light_rob2 <- function(data,
[…]

### 2021-10-08 Q1_summary_table.R
Q1_summary_table

@@ -1,0 +1,333 @@
+
+#download packages
+library(meta)
+library(readxl)
+library(tidyverse)
+library(httr) # use to retrieve data from REDCap
+library(kableExtra)
+library(flextable)
+library(dplyr)
+library(RCurl)
+library(tidyr)
+library(ggplot2)
+library(metafor)
+
+##########################################
+# table on characteristics of Q1 studies
+##########################################
+
+#prepare data for table 1: characteristics of studies included in q1
+
+#download data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+Q1_table <- httr::content(response)
+#cut data at end of jan 31
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+Q1_table <- Q1_table %>%
+  filter(record_id <= 5296 | record_id %in% published_preprints)
+Q1_table <- Q1_table %>%
+  select(-contains("rob")) %>%
+  select(-contains("risk_of_bias")) %>%
+  select(-journal)
+
+
+
+#clean countries
+Q1_table <- Q1_table %>%
+  mutate(country = ifelse(country == 10, "Australia", country),
+         country = ifelse(country == 11, "Austria", country),
+         country = ifelse(country == 15, "Bahrain", country),
+         country = ifelse(country == 19, "Belgium", country),
+         country = ifelse(country == 27, "Brazil", country),
+         country = ifelse(country == 28, "Brunei", country),
+         country = ifelse(country == 34, "Canada", country),
+         country = ifelse(country == 40, "China", country),
+         country = ifelse(country == 41, "Colombia", country),
+         country = ifelse(country == 51, "Denmark", country),
[…]

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd

@@
 
+library(dplyr)
+install.packages("ggpubr")
+library("ggpubr")
+
+#use the package as a new source. Some functions of the package are changed by HI
+source("robisfunctions.R")
+
+# get the data directly from redcap:
+urlrob <- "https://redcap.ispm.unibe.ch/api/"
+tokenrob <- "F2725F15FE84D2832E2793BB23B0A62B"
+formDatarob <- list("token"=tokenrob,
+                 content='report',
+                 format='csv',
+                 report_id='283',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response_rob <- httr::POST(urlrob, body = formDatarob, encode = "form")
+rob_records <- httr::content(response_rob)
+
+rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
+rob_records <- rob_records[1:166,]
+
+#added a new column HI
+df_rob <- rob_records %>%
+  select(record_id,author_1, authoryear,quest___1, q3_sar, setting2, 
+         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
+         risk_of_bias_update_3_complete)
+df_rob['setting'] <- NA
+
+df_rob <- df_rob %>%
+  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
+         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
+         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
+         setting = ifelse(setting2 == 4, "Statistical model", setting),
+         setting = ifelse(setting2 == 5, "Screening", setting),
+         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
+         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
+         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
+         setting = ifelse(setting2 == 9, "Screening: institutional setting", setting),
+         setting = ifelse(setting2 == 10, "Screening: community setting", setting),
+         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
+
+#Filtered by Q1
+q1_rob <- df_rob %>%
+  filter(!is.na(rob_1)) %>%
+  filter(record_id != 122) %>%
+  filter(quest___1 == 1)  %>%
+  select(authoryearId, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
+  rename(Study = authoryearId, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
+         D5 = rob_5, D6 = rob_6)
+
+q1_rob$D1 <- ifelse(q1_rob$D1 == 1, "High", ifelse(q1_rob$D1 == 2, "Unclear", "Low"))
+q1_rob$D2 <- ifelse(q1_rob$D2 == 1, "High", ifelse(q1_rob$D2 == 2, "Unclear", "Low"))
+q1_rob$D3 <- ifelse(q1_rob$D3 == 1, "High", ifelse(q1_rob$D3 == 2, "Unclear", "Low"))
+q1_rob$D4 <- ifelse(q1_rob$D4 == 1, "High", ifelse(q1_rob$D4 == 2, "Unclear", "Low"))
+q1_rob$D5 <- ifelse(q1_rob$D5 == 1, "High", ifelse(q1_rob$D5 == 2, "Unclear", "Low"))
+q1_rob$D6 <- ifelse(q1_rob$D6 == 1, "High", ifelse(q1_rob$D6 == 2, "Unclear", "Low"))
+
+####Plots filtered by settings#########
+
+#1. "Contact investigation"
+contactinvestigation <- q1_rob %>% 
+  filter(setting == "Contact investigation" | setting == "Contact investigation, aggregated") %>%
+  select(Study, D1, D2, D3, D4, D5, D6)
+
+contactinvestigation_rob_trafficlight <- rob_traffic_light(data = contactinvestigation,
+                                         tool = "Generic",
+                                         psize = 10,
+                                         overall = FALSE)
+
+p1 <- contactinvestigation_rob_trafficlight +
+  ggplot2::labs(
+    caption = " ") + 
+  ggplot2::ggtitle("Contact investigation") +
+  ggplot2::theme(legend.position = "none")
+
+# 3. "Outbreak investigation"
+outbreakinv <- q1_rob %>% 
+  filter(setting == "Outbreak investigation") %>%
+  select(Study, D1, D2, D3, D4, D5, D6)
+
+outbreakinv_rob_trafficlight <- rob_traffic_light(data = outbreakinv,
+                                                           tool = "Generic",
+                                                           psize = 10,
+                                                           overall = FALSE)
+
+p2 <- outbreakinv_rob_trafficlight +
+  ggplot2::labs(
+    caption = "  
+    Domains:
+  D1: Representativeness of the sample (selection bias)
+  D2: Characteristics of non-respondents (selection bias)
+  D3: Symptom assessment (information bias)
+  D4: Recording of symptoms (information bias)
+  D5: Classification of asymptomatic status (misclassification bias)
+  D6: Selective reporting of symptoms status (attrition bias)")
+
+p2 <- p2 + 
+  ggplot2::ggtitle("Outbreak investigation")
+
+p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)
+
 ```
@@
 *In progress.*
+```{r screenplot, echo=FALSE}
+p1
+```
 

### 2021-10-08 Asymptomatic_LSR_Supplement.Rmd
Update RMarkdowns

@@
 library(Rcpp)
+library(RCurl)
+library(tidyr)
+library(ggplot2)
+library(metafor)
+
+##########################################
+# table on characteristics of Q1 studies
+##########################################
+
+#prepare data for table 1: characteristics of studies included in q1
+
+#download data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+Q1_table <- httr::content(response)
+#cut data at end of jan 31
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+Q1_table <- Q1_table %>%
+  filter(record_id <= 5296 | record_id %in% published_preprints)
+Q1_table <- Q1_table %>%
+  select(-contains("rob")) %>%
+  select(-contains("risk_of_bias")) %>%
+  select(-journal)
+
+#clean countries
+Q1_table <- Q1_table %>%
+  mutate(country = ifelse(country == 10, "Australia", country),
+         country = ifelse(country == 11, "Austria", country),
+         country = ifelse(country == 15, "Bahrain", country),
+         country = ifelse(country == 19, "Belgium", country),
+         country = ifelse(country == 27, "Brazil", country),
+         country = ifelse(country == 28, "Brunei", country),
+         country = ifelse(country == 34, "Canada", country),
+         country = ifelse(country == 40, "China", country),
+         country = ifelse(country == 41, "Colombia", country),
+         country = ifelse(country == 51, "Denmark", country),
+         country = ifelse(country == 62, "France", country),
+         country = ifelse(country == 63, "French Guyana", country),
+         country = ifelse(country == 67, "Germany", country),
+         country = ifelse(country == 69, "Greece", country),
+         country = ifelse(country == 78, "Iceland", country),
+         country = ifelse(country == 79, "India", country),
+         country = ifelse(country == 83, "Ireland", country),
+         country = ifelse(country == 85, "Italy", country),
+         country = ifelse(country == 87, "Japan", country),
+         country = ifelse(country == 92, "Kuwait", country),
+         country = ifelse(country == 105, "Malaysia", country),
+         country = ifelse(country == 121, "Netherlands", country),
+         country = ifelse(country == 130, "N", country),
+         country = ifelse(country == 28, "Brunei", country),
+         country = ifelse(country == 888, "Other", country),
+         country = ifelse(country == 128, "Norway", country),
+         country = ifelse(country == 138, "Portugal", country),
+         country = ifelse(country == 146, "Saudi Arabia", country),
+         country = ifelse(country == 157, "South Korea", country),
+         country = ifelse(country == 160, "Spain", country),
+         country = ifelse(country == 174, "Turkey", country),
+         country = ifelse(country == 176, "Uganda", country),
+         country = ifelse(country == 180, "United Kingdom", country),
+         country = ifelse(country == 181, "United States of America", country),
+         country = ifelse(country == 185, "Vietnam", country))
+#clean regions
+Q1_table$region[Q1_table$region == "none" | Q1_table$region == "None"] <- NA
+#create location variable
+Q1_table$location <- Q1_table$country
+Q1_table <- Q1_table %>%
+  mutate(location = ifelse(!is.na(region), paste0(Q1_table$country, ", ", Q1_table$region), country))
+#drop country and region variables
+Q1_table$country <- NULL
+Q1_table$region <- NULL
+
+#author column
+Q1_table$study <- paste0(Q1_table$author_1, " (", Q1_table$year, ")")
+Q1_table$author_1 <- NULL
+Q1_table$record_id <- NULL
+Q1_table$year <- NULL
+
+#clean settings
+Q1_table <- Q1_table %>%
+  mutate(setting = ifelse(setting2 == 1 | setting2 == 2, "Contact investigation", setting),
+         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
+         setting = ifelse(setting2 == 4, "Statistical model", setting),
+         setting = ifelse(setting2 == 5, "Screening", setting),
+         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
+         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
+         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
+         setting = ifelse(setting2 == 9, "Screening: institutional setting", setting),
+         setting = ifelse(setting2 == 10, "Screening: community setting", setting),
+         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
+Q1_table$setting2 <- NULL
+
+#clean case numbers
+#total SARS-CoV-2 n
+Q1_table$total_SARS_n <- Q1_table$q1_c1_total
+Q1_table$total_SARS_n_c2 <- Q1_table$q1_c2_total #numbers for cluster 2 - must be arranged later
+#asymp n
+Q1_table$asymp_SARS_n <- Q1_table$q1_c1_event
+Q1_table$asymp_SARS_n_c2 <- Q1_table$q1_c2_event #numbers for cluster 2 - must be arranged later
+Q1_table$q1_c1_event <- NULL
+Q1_table$q1_c2_event <- NULL
+Q1_table$q1_c1_total <- NULL
+Q1_table$q1_c2_total <- NULL
+Q1_table$q1_nclus <- NULL
+Q1_table$q1_c3_event <- NULL
+Q1_table$q1_c3_total <- NULL
+Q1_table$comment_q1 <- NULL
+
+#clean sex category
+Q1_table$sex <- "NR"
+Q1_table$q1_female[Q1_table$q1_female == 9999] <- 0
+Q1_table$q1_male[Q1_table$q1_male == 9999] <- 0
+Q1_table <- Q1_table %>%
+  mutate(sex = ifelse(q1_female == 0 & q1_male == 0, "NR", paste0(q1_female, " F, ", q1_male, " M")))
+Q1_table$q1_male <- NULL
+Q1_table$q1_female <- NULL
+
+#clean age category
+
+Q1_table$q1_age_median[Q1_table$q1_age_median == 9999] <- NA
+Q1_table$q1_age_iqr[Q1_table$q1_age_iqr == 9999] <- NA
+Q1_table$age <- as.character(Q1_table$q1_age_median)
+Q1_table$age[is.na(Q1_table$age)] <- "NR"
+Q1_table <- Q1_table %>%
+  mutate(age = ifelse(!is.na(q1_age_iqr), 
+                      paste0(q1_age_median, " IQR ", q1_age_iqr),
+                      age))
+Q1_table$q1_age_iqr <- NULL
+Q1_table$q1_age_median <- NULL
+
+#clean up follow up
+Q1_table$follow_up <- NULL
+
+Q1_table$fup___2[Q1_table$fup___2 == 1] <- 2
+Q1_table$fup___3[Q1_table$fup___3 == 1] <- 3
+Q1_table$fup___4[Q1_table$fup___4 == 1] <- 4
+Q1_table <- Q1_table %>%
+  mutate(follow_up = ifelse(fup___1 != 0 & fup___2 != 0 & fup___3 != 0 & fup___4 != 0,
+                            paste0(fup___1, ", ", fup___2, ", ", fup___3, ", ", fup___4),
+                            NA)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 0 & fup___4 == 0,
+                            1,
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 0 & fup___4 == 0,
+                            2,
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 3 & fup___4 == 0,
+                            3,
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 0 & fup___4 == 4,
+                            4,
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 0 & fup___4 == 0,
+                            "1, 2",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 3 & fup___4 == 0,
+                            "1, 3",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 3 & fup___4 == 0,
+                            "2, 3",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 0 & fup___4 == 4,
+                            "1, 4",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 0 & fup___4 == 4,
+                            "2, 4",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 3 & fup___4 == 4,
+                            "3, 4",
+                            follow_up)) %>%
+mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 0 & fup___4 == 4,
+                          "1, 2, 4",
+                          follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 3 & fup___4 == 0,
+                            "1, 2, 3",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 3 & fup___4 == 4,
+                            "1, 3, 4",
+                            follow_up)) %>%
+  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 3 & fup___4 == 4,
+                            "2, 3, 4",
+                            follow_up))
+check <- Q1_table %>%
+  select(fup___1, fup___2, fup___3, fup___4, follow_up)
+Q1_table <- Q1_table %>%
+  select(-contains("fup"))
+
+names(Q1_table)
+Q1_table$source <- NULL
+
+#rearrange so that clusters and in one col
+cluster2 <- Q1_table
+cluster2 <- cluster2[!is.na(cluster2$total_SARS_n_c2), ]
+cluster2$total_SARS_n <- cluster2$total_SARS_n_c2
+cluster2$asymp_SARS_n <- cluster2$asymp_SARS_n_c2
+cluster2$total_SARS_n_c2 <- NULL
+cluster2$asymp_SARS_n_c2 <- NULL
+cluster2$study <- paste0(cluster2$study, " [cluster 2]")
+#add clusters to main table
+Q1_table <- bind_rows(Q1_table, cluster2)
+#drop extra cols
+Q1_table$total_SARS_n_c2 <- NULL
+Q1_table$asymp_SARS_n_c2 <- NULL
+
+Q1_table <- Q1_table %>%
+  arrange(setting)
+
+Q1_table <- Q1_table[, c(1, 3, 2, 4, 5, 6, 7, 8)]
 
@@
 
+## Full Characteristics of Q1 studies
+
+```{r table1, ft.split=TRUE, tab.cap='Table 1. Characteristics of studies included for Q1', echo = FALSE}
+table1 <- as_grouped_data(Q1_table, groups = "setting")
+
+table1 %>% 
+  as_flextable() %>% 
+  set_header_labels(setting = "Setting",
+                    location = "Country, region", 
+                    study = "Study",
+                    total_SARS_n = "Total SARS-CoV-2, n",
+                    asymp_SARS_n = "Asymptomatic SARS-CoV-2, n",
+                    sex = "Sex of asymptomatic people",         
+                    age = "Age of asymptomatic people, years, median",            
+                    follow_up = "Follow-up method") %>%
+  set_table_properties(layout = "autofit") %>%
+  footnote(i = 1, j = 7,
+           value = as_paragraph("Follow-up according to protocol (1: 14 days after last possible exposure; 2: 7 days after diagnosis; 3: until negative RT-PCR result; 4:>7 days after diagnosis).
+NR = not reported."),
+           ref_symbols = "a",
+           part = "header") #add footnote
+
+#print(flextable, preview = "docx") #to print in word
+
+```
+
 ## PRISMA 2020 Checklist
@@
 
-```{r table1, ft.split=TRUE, tab.cap='Table 1. Location of studies contributing data to review questions 1', echo = FALSE}
+```{r table1_countries, ft.split=TRUE, tab.cap='Table 1. Location of studies contributing data to review questions 1', echo = FALSE}
 table1_countries <- flextable(Q1_table_countries)

### 2021-10-08 Manuscript_draft.Rmd
Update RMarkdowns

@@
 
-##########################################
-# table on characteristics of Q1 studies
-##########################################
-
-#prepare data for table 1: characteristics of studies included in q1
-
 #download data
@@
 response <- httr::POST(url, body = formData, encode = "form")
-Q1_table <- httr::content(response)
-#cut data at end of jan 31
-published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
-Q1_table <- Q1_table %>%
-  filter(record_id <= 5296 | record_id %in% published_preprints)
-Q1_table <- Q1_table %>%
-  select(-contains("rob")) %>%
-  select(-contains("risk_of_bias")) %>%
-  select(-journal)
-
-#clean countries
-Q1_table <- Q1_table %>%
-  mutate(country = ifelse(country == 10, "Australia", country),
-         country = ifelse(country == 11, "Austria", country),
-         country = ifelse(country == 15, "Bahrain", country),
-         country = ifelse(country == 19, "Belgium", country),
-         country = ifelse(country == 27, "Brazil", country),
-         country = ifelse(country == 28, "Brunei", country),
-         country = ifelse(country == 34, "Canada", country),
-         country = ifelse(country == 40, "China", country),
-         country = ifelse(country == 41, "Colombia", country),
-         country = ifelse(country == 51, "Denmark", country),
-         country = ifelse(country == 62, "France", country),
-         country = ifelse(country == 63, "French Guyana", country),
-         country = ifelse(country == 67, "Germany", country),
-         country = ifelse(country == 69, "Greece", country),
-         country = ifelse(country == 78, "Iceland", country),
-         country = ifelse(country == 79, "India", country),
-         country = ifelse(country == 83, "Ireland", country),
-         country = ifelse(country == 85, "Italy", country),
-         country = ifelse(country == 87, "Japan", country),
-         country = ifelse(country == 92, "Kuwait", country),
-         country = ifelse(country == 105, "Malaysia", country),
-         country = ifelse(country == 121, "Netherlands", country),
-         country = ifelse(country == 130, "N", country),
-         country = ifelse(country == 28, "Brunei", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 128, "Norway", country),
-         country = ifelse(country == 138, "Portugal", country),
-         country = ifelse(country == 146, "Saudi Arabia", country),
-         country = ifelse(country == 157, "South Korea", country),
-         country = ifelse(country == 160, "Spain", country),
-         country = ifelse(country == 174, "Turkey", country),
-         country = ifelse(country == 176, "Uganda", country),
-         country = ifelse(country == 180, "United Kingdom", country),
-         country = ifelse(country == 181, "United States of America", country),
-         country = ifelse(country == 185, "Vietnam", country))
-#clean regions
-Q1_table$region[Q1_table$region == "none" | Q1_table$region == "None"] <- NA
-#create location variable
-Q1_table$location <- Q1_table$country
-Q1_table <- Q1_table %>%
-  mutate(location = ifelse(!is.na(region), paste0(Q1_table$country, ", ", Q1_table$region), country))
-#drop country and region variables
-Q1_table$country <- NULL
-Q1_table$region <- NULL
-
-#author column
-Q1_table$study <- paste0(Q1_table$author_1, " (", Q1_table$year, ")")
-Q1_table$author_1 <- NULL
-Q1_table$record_id <- NULL
-Q1_table$year <- NULL
-
-#clean settings
-Q1_table <- Q1_table %>%
-  mutate(setting = ifelse(setting2 == 1 | setting2 == 2, "Contact investigation", setting),
-         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
-         setting = ifelse(setting2 == 4, "Statistical model", setting),
-         setting = ifelse(setting2 == 5, "Screening", setting),
-         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
-         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
-         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
-         setting = ifelse(setting2 == 9, "Screening: institutional setting", setting),
-         setting = ifelse(setting2 == 10, "Screening: community setting", setting),
-         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
-Q1_table$setting2 <- NULL
-
-#clean case numbers
-#total SARS-CoV-2 n
-Q1_table$total_SARS_n <- Q1_table$q1_c1_total
-Q1_table$total_SARS_n_c2 <- Q1_table$q1_c2_total #numbers for cluster 2 - must be arranged later
-#asymp n
-Q1_table$asymp_SARS_n <- Q1_table$q1_c1_event
-Q1_table$asymp_SARS_n_c2 <- Q1_table$q1_c2_event #numbers for cluster 2 - must be arranged later
-Q1_table$q1_c1_event <- NULL
-Q1_table$q1_c2_event <- NULL
-Q1_table$q1_c1_total <- NULL
-Q1_table$q1_c2_total <- NULL
-Q1_table$q1_nclus <- NULL
-Q1_table$q1_c3_event <- NULL
-Q1_table$q1_c3_total <- NULL
-Q1_table$comment_q1 <- NULL
-
-#clean sex category
-Q1_table$sex <- "NR"
-Q1_table$q1_female[Q1_table$q1_female == 9999] <- 0
-Q1_table$q1_male[Q1_table$q1_male == 9999] <- 0
-Q1_table <- Q1_table %>%
-  mutate(sex = ifelse(q1_female == 0 & q1_male == 0, "NR", paste0(q1_female, " F, ", q1_male, " M")))
-Q1_table$q1_male <- NULL
-Q1_table$q1_female <- NULL
-
-#clean age category
-
-Q1_table$q1_age_median[Q1_table$q1_age_median == 9999] <- NA
-Q1_table$q1_age_iqr[Q1_table$q1_age_iqr == 9999] <- NA
-Q1_table$age <- as.character(Q1_table$q1_age_median)
-Q1_table$age[is.na(Q1_table$age)] <- "NR"
-Q1_table <- Q1_table %>%
-  mutate(age = ifelse(!is.na(q1_age_iqr), 
-                      paste0(q1_age_median, " IQR ", q1_age_iqr),
-                      age))
-Q1_table$q1_age_iqr <- NULL
-Q1_table$q1_age_median <- NULL
-
-#clean up follow up
-Q1_table$follow_up <- NULL
-
-Q1_table$fup___2[Q1_table$fup___2 == 1] <- 2
-Q1_table$fup___3[Q1_table$fup___3 == 1] <- 3
-Q1_table$fup___4[Q1_table$fup___4 == 1] <- 4
-Q1_table <- Q1_table %>%
-  mutate(follow_up = ifelse(fup___1 != 0 & fup___2 != 0 & fup___3 != 0 & fup___4 != 0,
-                            paste0(fup___1, ", ", fup___2, ", ", fup___3, ", ", fup___4),
-                            NA)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 0 & fup___4 == 0,
-                            1,
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 0 & fup___4 == 0,
-                            2,
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 3 & fup___4 == 0,
-                            3,
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 0 & fup___4 == 4,
-                            4,
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 0 & fup___4 == 0,
-                            "1, 2",
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 3 & fup___4 == 0,
-                            "1, 3",
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 3 & fup___4 == 0,
-                            "2, 3",
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 0 & fup___4 == 4,
-                            "1, 4",
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 0 & fup___4 == 4,
-                            "2, 4",
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 0 & fup___3 == 3 & fup___4 == 4,
-                            "3, 4",
-                            follow_up)) %>%
-mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 0 & fup___4 == 4,
-                          "1, 2, 4",
-                          follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 2 & fup___3 == 3 & fup___4 == 0,
-                            "1, 2, 3",
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 1 & fup___2 == 0 & fup___3 == 3 & fup___4 == 4,
-                            "1, 3, 4",
-                            follow_up)) %>%
-  mutate(follow_up = ifelse(fup___1 == 0 & fup___2 == 2 & fup___3 == 3 & fup___4 == 4,
-                            "2, 3, 4",
-                            follow_up))
-check <- Q1_table %>%
-  select(fup___1, fup___2, fup___3, fup___4, follow_up)
-Q1_table <- Q1_table %>%
-  select(-contains("fup"))
-
-names(Q1_table)
-Q1_table$source <- NULL
-
-#rearrange so that clusters and in one col
-cluster2 <- Q1_table
-cluster2 <- cluster2[!is.na(cluster2$total_SARS_n_c2), ]
-cluster2$total_SARS_n <- cluster2$total_SARS_n_c2
-cluster2$asymp_SARS_n <- cluster2$asymp_SARS_n_c2
-cluster2$total_SARS_n_c2 <- NULL
-cluster2$asymp_SARS_n_c2 <- NULL
-cluster2$study <- paste0(cluster2$study, " [cluster 2]")
-#add clusters to main table
-Q1_table <- bind_rows(Q1_table, cluster2)
-#drop extra cols
-Q1_table$total_SARS_n_c2 <- NULL
-Q1_table$asymp_SARS_n_c2 <- NULL
-
-Q1_table <- Q1_table %>%
-  arrange(setting)
-
-Q1_table <- Q1_table[, c(1, 3, 2, 4, 5, 6, 7, 8)]
 
@@
 
-```{r table1, ft.split=TRUE, tab.cap='Table 1. Characteristics of studies included for Q1', echo = FALSE}
-table1 <- as_grouped_data(Q1_table, groups = "setting")
-
-table1 %>% 
-  as_flextable() %>% 
-  set_header_labels(setting = "Setting",
-                    location = "Country, region", 
-                    study = "Study",
-                    total_SARS_n = "Total SARS-CoV-2, n",
-                    asymp_SARS_n = "Asymptomatic SARS-CoV-2, n",
-                    sex = "Sex of asymptomatic people",         
-                    age = "Age of asymptomatic people, years, median",            
-                    follow_up = "Follow-up method") %>%
-  set_table_properties(layout = "autofit") %>%
-  footnote(i = 1, j = 7,
-           value = as_paragraph("Follow-up according to protocol (1: 14 days after last possible exposure; 2: 7 days after diagnosis; 3: until negative RT-PCR result; 4:>7 days after diagnosis).
-NR = not reported."),
-           ref_symbols = "a",
-           part = "header") #add footnote
-
-#print(flextable, preview = "docx") #to print in word
-
-```
-
 ![Figure 1. Forest plot of proportion  of people with asymptomatic SARS-CoV-2 infection, stratified by setting and ordered by precision](forest_meta_Q1.png)

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
commit

@@
 library(dplyr)
-install.packages("ggpubr")
+#install.packages("ggpubr")
 library("ggpubr")
@@
   filter(quest___1 == 1)  %>%
-  select(authoryearId, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
-  rename(Study = authoryearId, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
+  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
+  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
          D5 = rob_5, D6 = rob_6)
@@
   ggplot2::ggtitle("Outbreak investigation")
+p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)
 
-p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)
+png("q1_1_new.png", height = 1500, width = 1100)
+p3
+dev.set(dev.next())
+dev.off()
 
@@
 ## Risk of bias in studies included in review question 1 and review question 2.
-*In progress.*
-```{r screenplot, echo=FALSE}
-p1
-```
+
+![ROB Q1_1](q1_1_new.png)
 

### 2021-10-08 ROB_new_081021.R
updated ROB script

@@ -1,0 +1,256 @@
+##################################################
+# Risk of bias visualisation                     #  
+##################################################
+rm(list=ls())
+
+#download package
+#install.packages("devtools")
+#devtools::install_github("mcguinlu/robvis")
+library(dplyr)
+install.packages("ggpubr")
+library("ggpubr")
+
+#use the package as a new source. Some functions of the package are changed by HI
+source("robisfunctions.R")
+
+# get the data directly from redcap:
+urlrob <- "https://redcap.ispm.unibe.ch/api/"
+tokenrob <- "F2725F15FE84D2832E2793BB23B0A62B"
+formDatarob <- list("token"=tokenrob,
+                    content='report',
+                    format='csv',
+                    report_id='283',
+                    csvDelimiter='',
+                    rawOrLabel='raw',
+                    rawOrLabelHeaders='raw',
+                    exportCheckboxLabel='false',
+                    returnFormat='csv'
+)
+response_rob <- httr::POST(urlrob, body = formDatarob, encode = "form")
+rob_records <- httr::content(response_rob)
+
+rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
+rob_records <- rob_records[rob_records$record_id < "5566", ]
+
+df_rob <- rob_records %>%
+  select(record_id,author_1, authoryear,quest___1, q3_sar, setting2, 
+         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
+         risk_of_bias_update_3_complete)
+df_rob['setting'] <- NA
+
+
+df_rob <- df_rob %>%
+  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
+         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
+         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
+         setting = ifelse(setting2 == 4, "Statistical model", setting),
+         setting = ifelse(setting2 == 5, "Screening", setting),
+         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
+         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
[…]

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update
Update Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd

@@
 rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
-rob_records <- rob_records[1:166,]
+rob_records <- rob_records[rob_records$record_id < "5566", ]
 
-#added a new column HI
+#prepare a dataset
 df_rob <- rob_records %>%
-  select(record_id,author_1, authoryear,quest___1, q3_sar, setting2, 
+  select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
          rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
@@
 
-#1. "Contact investigation"
+#1. "Contact investigation" and "Contact investigation, aggregated"
 contactinvestigation <- q1_rob %>% 
@@
 
-png("q1_1_new.png", height = 1500, width = 1100)
+dev.new()
+png("q1_1_new.png", width = 1000, height = 1500)
 p3
-dev.set(dev.next())
-dev.off()
+graphics.off()
 
@@
 ![ROB Q1_1](q1_1_new.png)
+![ROB Q1_1](q1_2_new.png)
+![ROB Q1_1](q2_new.png)
 

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
code added

@@
 
+# 9. "Screening: institutional setting"
+institutional <- q1_rob %>% 
+  filter(setting == "Screening: institutional setting") %>%
+  select(Study, D1, D2, D3, D4, D5, D6)
+#Records: 21 studies
+
+institutional_rob_trafficlight <- rob_traffic_light(data = institutional,
+                                                    tool = "Generic",
+                                                    psize = 10,
+                                                    overall = FALSE)
+p4 <- institutional_rob_trafficlight +
+  ggplot2::labs(
+    caption = " ") + 
+  ggplot2::ggtitle("Screening: institutional setting") +
+  ggplot2::theme(legend.position = "none")
+
+# 10. "Screening: community setting"
+communityset <- q1_rob %>% 
+  filter(setting == "Screening: community setting") %>%
+  select(Study, D1, D2, D3, D4, D5, D6)
+#Records: 17 studies
+
+communityset_rob_trafficlight <- rob_traffic_light(data = communityset,
+                                                   tool = "Generic",
+                                                   psize = 10,
+                                                   overall = FALSE)
+
+p5 <- communityset_rob_trafficlight +
+  ggplot2::labs(
+    caption = " ") + 
+  ggplot2::ggtitle("Screening: community setting") +
+  ggplot2::theme(legend.position = "none")
+
+# 11. "Screening: occupational"
+occupationalset <- q1_rob %>% 
+  filter(setting == "Screening: occupational") %>%
+  select(Study, D1, D2, D3, D4, D5, D6)
+#Records: 12 studies
+
+occupationalset_rob_trafficlight <- rob_traffic_light(data = occupationalset,
+                                                      tool = "Generic",
+                                                      psize = 10,
+                                                      overall = FALSE)
+
+p6 <- occupationalset_rob_trafficlight +
+  ggplot2::labs(
+    caption = "
+    Domains:
+  D1: Representativeness of the sample (selection bias)
+  D2: Characteristics of non-respondents (selection bias)
+  D3: Symptom assessment (information bias)
+  D4: Recording of symptoms (information bias)
+  D5: Classification of asymptomatic status (misclassification bias)
+  D6: Selective reporting of symptoms status (attrition bias)")
+
+p6 <- p6 + 
+  ggplot2::ggtitle("Screening: occupational")
+
+p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 1), ncol = 1, nrow = 3)
+
 ```

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
Update Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
DELETE

@@
                                                            overall = FALSE)
-
 p2 <- outbreakinv_rob_trafficlight +
   ggplot2::labs(
-    caption = "  
-    Domains:
-  D1: Representativeness of the sample (selection bias)
-  D2: Characteristics of non-respondents (selection bias)
-  D3: Symptom assessment (information bias)
-  D4: Recording of symptoms (information bias)
-  D5: Classification of asymptomatic status (misclassification bias)
-  D6: Selective reporting of symptoms status (attrition bias)")
+    caption = " ") + 
+  ggplot2::ggtitle("Outbreak investigation") +
+  ggplot2::theme(legend.position = "none")
 
-p2 <- p2 + 
-  ggplot2::ggtitle("Outbreak investigation")
 p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)
+
+p3 <- annotate_figure(p3, top = text_grob("Question 1", 
+                                      color = "black", face = "bold", size = 21))
 
@@
 p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 1), ncol = 1, nrow = 3)
+
+dev.new()
+png("q1_2_new.png", width = 1400, height = 2200)
+p7
+graphics.off()
 
@@
 ![ROB Q1_1](q1_2_new.png)
-![ROB Q1_1](q2_new.png)
 

### 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
Everything added

@@
 
+###ROB analysis for Q2.1
+q2_rob <- df_rob %>%
+  filter(!is.na(rob_1)) %>%
+  filter(record_id != 122) %>%
+  filter(q3_sar == 1)  %>%
+  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
+  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
+         D5 = rob_5, D6 = rob_6)
+
+q2_rob$D1 <- ifelse(q2_rob$D1 == 1, "High", ifelse(q2_rob$D1 == 2, "Unclear", "Low"))
+q2_rob$D2 <- ifelse(q2_rob$D2 == 1, "High", ifelse(q2_rob$D2 == 2, "Unclear", "Low"))
+q2_rob$D3 <- ifelse(q2_rob$D3 == 1, "High", ifelse(q2_rob$D3 == 2, "Unclear", "Low"))
+q2_rob$D4 <- ifelse(q2_rob$D4 == 1, "High", ifelse(q2_rob$D4 == 2, "Unclear", "Low"))
+q2_rob$D5 <- ifelse(q2_rob$D5 == 1, "High", ifelse(q2_rob$D5 == 2, "Unclear", "Low"))
+q2_rob$D6 <- ifelse(q2_rob$D6 == 1, "High", ifelse(q2_rob$D6 == 2, "Unclear", "Low"))
+
+q2_plot_ds <- q2_rob %>% 
+  select(Study, D1, D2, D3, D4, D5, D6)
+
+q2_rob_trafficlight <- rob_traffic_light(data = q2_plot_ds,
+                                                    tool = "Generic",
+                                                    psize = 10,
+                                                    overall = FALSE)
+
+p8 <- q2_rob_trafficlight +
+  ggplot2::labs(
+    caption = "
+    Domains:
+  D1: Representativeness of the sample (selection bias)
+  D2: Characteristics of non-respondents (selection bias)
+  D3: Symptom assessment (information bias)
+  D4: Recording of symptoms (information bias)
+  D5: Classification of asymptomatic status (misclassification bias)
+  D6: Selective reporting of symptoms status (attrition bias)")
+
+p8 <- p8 + 
+  ggplot2::ggtitle("Question 2.1") +
+  theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 16, face = "bold"))
+
+dev.new()
+png("q2_new.png", width = 1000, height = 300)
+p8
+graphics.off()
+
 ```
@@
 ![ROB Q1_1](q1_2_new.png)
+![ROB Q1_1](q2_new.png)
 

### 2021-10-18 Manuscript_draft.Rmd
Table Q2.2 updated

@@
   select(study, q3_setting)
-
+Q2_2_table$q3_setting <- gsub(";([[:alpha:]])", "; \\1", Q2_2_table$q3_setting)
+Q2_2_table$q3_setting <- gsub("/([[:alpha:]])", ", \\1", Q2_2_table$q3_setting)
 q2_2_nstudies <- nrow(Q2_2_table) #total number of studies included in q1

### 2021-10-18 Manuscript_draft.Rmd
update forest plot

--- 2021-10-08 Manuscript_draft.Rmd
@@
                 label = c(0.00,0.25,0.5,0.75,1.00))) +
-  scale_x_continuous()
+  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.25))
 
@@
     res=300, 
-    height=20, width=50, units="cm")
+    height=20, width=30, units="cm")
 p
@@
   select(study, q3_setting)
+Q2_2_table$q3_setting <- gsub(";([[:alpha:]])", "; \\1", Q2_2_table$q3_setting)
+Q2_2_table$q3_setting <- gsub("/([[:alpha:]])", ", \\1", Q2_2_table$q3_setting)
 

### 2021-10-18 Manuscript_draft.Rmd
update HI

--- 2021-10-08 Manuscript_draft.Rmd
@@
                 x = 0:4/4,
-                label = c(0.00,0.25,0.5,0.75,1.00))) +
-  scale_x_continuous()
+                label = c(0, 0.25, 0.5, 0.75, 1))) +
+  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.5))
 
@@
     res=300, 
-    height=20, width=50, units="cm")
+    height=35, width=42, units="cm")
 p
@@
 
+#some pre-processing HI
+Q2_2_table$q3_setting <- gsub(";([[:alpha:]])", "; \\1", Q2_2_table$q3_setting)
+Q2_2_table$q3_setting <- gsub("/([[:alpha:]])", ", \\1", Q2_2_table$q3_setting)
+Q2_2_table$q3_setting[15] <- gsub(",", ";",Q2_2_table$q3_setting[15])
 q2_2_nstudies <- nrow(Q2_2_table) #total number of studies included in q1

### 2021-10-19 Manuscript_draft.Rmd
update table1

@@
 table2 <- as_grouped_data(Q2_1_table, groups = "setting")
+table2 <- flextable(table2)
+table2 <- table2 %>%
+  set_header_labels(setting = "Setting",
+                    location = "Country, region", 
+                    study = "Study") %>%
+  set_table_properties(layout = "autofit") %>%
+  theme_vanilla()
+table2 <- width(table2, width = 10)
+table2
 
+Q2_1_table <- Q2_1_table %>%
+  arrange(setting)
+table2 <- as_grouped_data(Q2_1_table, groups = "setting")
 table2 %>%
@@
                     study = "Study") %>%
-  set_table_properties(layout = "autofit") %>%
+  set_table_properties(layout = "autofit") %>% fit_to_width(20) %>% 
   theme_vanilla()

### 2021-10-21 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update

@@
 rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
-rob_records <- rob_records[rob_records$record_id < "5566", ]
+#rob_records <- rob_records[rob_records$record_id < "5566", ]
+rob_records <- rob_records[rob_records$record_id < "5296", ]
 

### 2021-10-21 Manuscript_draft.Rmd
update

@@
 asymptomaticQ2_1[asymptomaticQ2_1=="9999"]=NA #indicate as missing
+
+#added for now
+asymptomaticQ2_1 <- asymptomaticQ2_1[asymptomaticQ2_1$record_id < "5296", ]
+
 asymptomaticQ2_1=asymptomaticQ2_1%>% #separate symp SAR into 2 variables
@@
 q2_1_df <- bind_rows(q2_1_df_a, q2_1_df_p)
+
+#Note: Chaw is missing
 

### 2021-10-22 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
ROB update

--- 2021-10-08 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
@@
 rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
-rob_records <- rob_records[rob_records$record_id < "5566", ]
+#rob_records <- rob_records[rob_records$record_id < "5566", ]
+rob_records <- rob_records[rob_records$record_id < 5296, ]
 
@@
     caption = "
-    Domains:
-  D1: Representativeness of the sample (selection bias)
-  D2: Characteristics of non-respondents (selection bias)
-  D3: Symptom assessment (information bias)
-  D4: Recording of symptoms (information bias)
-  D5: Classification of asymptomatic status (misclassification bias)
-  D6: Selective reporting of symptoms status (attrition bias)")
+    Domains
+
+    Selection Bias:
+  D1.1: Representativeness of the sample
+  D1.2: Characteristics of non-respondents
+    Information Bias:
+  D2.1: Symptom assessment
+  D2.1: Recording of symptoms
+    Misclassification bias:
+  D3: Classification of asymptomatic status
+    Attrition bias:
+  D4: Selective reporting of symptoms status")
 

### 2021-10-25 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update

@@
 png("q1_2_new.png", width = 1400, height = 2200)
-p7
+p75
 graphics.off()
@@
 q2_rob <- df_rob %>%
-  filter(!is.na(rob_1)) %>%
-  filter(record_id != 122) %>%
   filter(q3_sar == 1)  %>%

### 2021-10-25 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update
Changed records included in ROB plots
Cut off is 5296, plus preprints published afterwards

@@
 rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
-#rob_records <- rob_records[rob_records$record_id < "5566", ]
-rob_records <- rob_records[rob_records$record_id < 5296, ]
+
+#censor until 5296 (31 Jan) plus the published versions of preprints
+pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
+rob_records <- rob_records %>%
+  filter(record_id %in%  pub_preprints | record_id <= 5296)
 
@@
 png("q1_2_new.png", width = 1400, height = 2200)
-p75
+p7
 graphics.off()

### 2021-10-27 robisfunctions.R
Delete robisfunctions.R

@@ -1,1248 +1,0 @@
-rob_traffic_light <-
-  function(data,
-           tool,
-           colour = "cochrane",
-           psize = 10,
-           overall = TRUE,
-           ...) {
-    
-    check_tool(tool)
-    check_data(data)
-    colour <- weird_spelling(colour)
-    
-    check_colour(tool = tool, colour = colour)
-    
-    # Define colours
-    rob_colours <- get_colour(tool = tool, colour = colour)
-    
-    if (tool == "ROB2") {
-      plot <- rob_traffic_light_rob2(
-        data = data,
-        tool = tool,
-        rob_colours = rob_colours,
-        psize = psize,
-        overall = overall
-      )
-    }
-    
-    if (tool == "ROB2-Cluster") {
-      plot <- rob_traffic_light_rob2_cluster(
-        data = data,
-        tool = tool,
-        rob_colours = rob_colours,
-        psize = psize,
-        overall = overall
-      )
-    }
-    
-    if (tool == "ROBINS-I") {
-      plot <- rob_traffic_light_robinsi(
-        data = data,
-        tool = tool,
-        rob_colours = rob_colours,
-        psize = psize,
-        overall = overall
-      )
-    }
-    
-    if (tool == "QUADAS-2") {
-      plot <- rob_traffic_light_quadas2(
-        data = data,
-        tool = tool,
-        rob_colours = rob_colours,
-        psize = psize,
-        overall = overall
-      )
-    }
-    
-    if (tool == "QUIPS") {
-      plot <- rob_traffic_light_quips(
-        data = data,
-        tool = tool,
-        rob_colours = rob_colours,
-        psize = psize,
-        overall = overall
-      )
-    }
-    
-    if (tool %in% c("Generic", "ROB1")) {
-      plot <- rob_traffic_light_generic(
-        data = data,
-        tool = tool,
-        rob_colours = rob_colours,
-        psize = psize,
-        overall = overall,
-        ...
-      )
-    }
-    
-    # Add recommended saving height to the plot object
-    plot$rec_height <- get_height(
-      data = data,
-      tool = tool,
-      psize = psize,
-      type = "tf"
-    )
-    
-    # Add recommended saving width to the plot object
-    plot$rec_width <- get_width(data = data,
-                                psize = psize,
-                                type = "tf")
-    
-    plot$rob_type <- "traffic"
-    
-    return(plot)
-  }
-
-# ROB-2=========================================================================
-
-rob_traffic_light_rob2 <- function(data,
[…]

### 2021-10-27 robisfunctions.R
updated robisfunctions

@@ -1,0 +1,1249 @@
+rob_traffic_light <-
+  function(data,
+           tool,
+           colour = "cochrane",
+           psize = 10,
+           overall = TRUE,
+           ...) {
+    
+    check_tool(tool)
+    check_data(data)
+    colour <- weird_spelling(colour)
+    
+    check_colour(tool = tool, colour = colour)
+    
+    # Define colours
+    rob_colours <- get_colour(tool = tool, colour = colour)
+    
+    if (tool == "ROB2") {
+      plot <- rob_traffic_light_rob2(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool == "ROB2-Cluster") {
+      plot <- rob_traffic_light_rob2_cluster(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool == "ROBINS-I") {
+      plot <- rob_traffic_light_robinsi(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool == "QUADAS-2") {
+      plot <- rob_traffic_light_quadas2(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool == "QUIPS") {
+      plot <- rob_traffic_light_quips(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall
+      )
+    }
+    
+    if (tool %in% c("Generic", "ROB1")) {
+      plot <- rob_traffic_light_generic(
+        data = data,
+        tool = tool,
+        rob_colours = rob_colours,
+        psize = psize,
+        overall = overall,
+        ...
+      )
+    }
+    
+    # Add recommended saving height to the plot object
+    plot$rec_height <- get_height(
+      data = data,
+      tool = tool,
+      psize = psize,
+      type = "tf"
+    )
+    
+    # Add recommended saving width to the plot object
+    plot$rec_width <- get_width(data = data,
+                                psize = psize,
+                                type = "tf")
+    
+    plot$rob_type <- "traffic"
+    
+    return(plot)
+  }
+
+# ROB-2=========================================================================
+
+rob_traffic_light_rob2 <- function(data,
[…]

### 2021-10-27 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
Update Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
new run

@@
 #prepare a dataset
+# df_rob <- rob_records %>%
+#   select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
+#          rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
+#          risk_of_bias_update_3_complete)
+
 df_rob <- rob_records %>%
-  select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
+  select(record_id,author_1, quest___1, q3_sar, setting2, 
          rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
@@
   rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
-         D5 = rob_5, D6 = rob_6)
+         D5 = rob_5, `6` = rob_6)
 
@@
 q1_rob$D5 <- ifelse(q1_rob$D5 == 1, "High", ifelse(q1_rob$D5 == 2, "Unclear", "Low"))
-q1_rob$D6 <- ifelse(q1_rob$D6 == 1, "High", ifelse(q1_rob$D6 == 2, "Unclear", "Low"))
+q1_rob$`6` <- ifelse(q1_rob$`6` == 1, "High", ifelse(q1_rob$`6` == 2, "Unclear", "Low"))
 
@@
   filter(setting == "Contact investigation" | setting == "Contact investigation, aggregated") %>%
-  select(Study, D1, D2, D3, D4, D5, D6)
+  select(Study, D1, D2, D3, D4, D5, `6`)
 
@@
   filter(setting == "Outbreak investigation") %>%
-  select(Study, D1, D2, D3, D4, D5, D6)
+  select(Study, D1, D2, D3, D4, D5, `6`)
 
@@
   filter(setting == "Screening: institutional setting") %>%
-  select(Study, D1, D2, D3, D4, D5, D6)
+  select(Study, D1, D2, D3, D4, D5, `6`)
 #Records: 21 studies
@@
   filter(setting == "Screening: community setting") %>%
-  select(Study, D1, D2, D3, D4, D5, D6)
+  select(Study, D1, D2, D3, D4, D5, `6`)
 #Records: 17 studies
@@
   filter(setting == "Screening: occupational") %>%
-  select(Study, D1, D2, D3, D4, D5, D6)
+  select(Study, D1, D2, D3, D4, D5, `6`)
 #Records: 12 studies
@@
     Selection Bias:
-  D1.1: Representativeness of the sample
-  D1.2: Characteristics of non-respondents
+  1: Representativeness of the sample
+  2: Characteristics of non-respondents
     Information Bias:
-  D2.1: Symptom assessment
-  D2.1: Recording of symptoms
+  3: Symptom assessment
+  4: Recording of symptoms
     Misclassification bias:
-  D3: Classification of asymptomatic status
+  5: Classification of asymptomatic status
     Attrition bias:
-  D4: Selective reporting of symptoms status")
+  6: Selective reporting of symptoms status")
 
@@
 q2_rob$D5 <- ifelse(q2_rob$D5 == 1, "High", ifelse(q2_rob$D5 == 2, "Unclear", "Low"))
-q2_rob$D6 <- ifelse(q2_rob$D6 == 1, "High", ifelse(q2_rob$D6 == 2, "Unclear", "Low"))
+q2_rob$`6` <- ifelse(q2_rob$`6` == 1, "High", ifelse(q2_rob$`6` == 2, "Unclear", "Low"))
 
 q2_plot_ds <- q2_rob %>% 
-  select(Study, D1, D2, D3, D4, D5, D6)
+  select(Study, D1, D2, D3, D4, D5, `6`)
 
@@
 dev.new()
-png("q2_new.png", width = 1000, height = 300)
+png("q2_new.png", width = 1000, height = 350)
 p8

### 2021-10-27 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
new update

@@
 
-rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
+# rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
 
@@
   filter(quest___1 == 1)  %>%
-  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
-  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
+  select(author_1, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
+  rename(Study = author_1, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
          D5 = rob_5, `6` = rob_6)
@@
   filter(q3_sar == 1)  %>%
-  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
-  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
+  select(author_1, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
+  rename(Study = author_1, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
          D5 = rob_5, `6` = rob_6)

### 2021-10-27 robisfunctions.R
updated robis functions

@@ -592,7 +592,7 @@ rob_traffic_light_generic <- function(data,
   adjust_caption <- get_caption_adjustment(rob.tidy)
   
   # Set sizes
-  ssize <- psize - (psize / 4)
+  ssize <- psize - (psize / 2)
   
   # name the provided judgement labels with appropriate judgement levels to
   # enable this to be passed as a named character variable to the
@@ -626,8 +626,11 @@ rob_traffic_light_generic <- function(data,
       labels = judgement_labels
     ) +
     ggplot2::scale_shape_manual(values = c(
-      l = 43,
-      s = 45,
+      #l = 43,
+      #s = 45,
+      #h = 120
+      l = 83,
+      s = 85,
       h = 120
     ),
     labels = judgement_labels)
@@ -829,7 +832,7 @@ rob_summ_theme <- function(overall = TRUE, max_domain_column){
         fill = judgement,
         weight = Weights
       ),
-      width = 0.7,
+      width = 1,
       position = "fill",
       color = "black"
     ),
@@ -892,8 +895,8 @@ rob_tf_theme <-function(rob.tidy,
                           factor(domain, levels = domain_names),
                         switch = "y",
                         space = "free"),
-    ggplot2::geom_point(size = 4),
-    ggplot2::geom_point(size = 2,
+    ggplot2::geom_point(size = 6),
+    ggplot2::geom_point(size = 4,
                         colour = "black",
                         #colour = "white",
                         ggplot2::aes(shape = judgement)),
@@ -950,15 +953,15 @@ rob_tf_theme <-function(rob.tidy,
         t = -0.2, r = 0,
         b = adjust_caption, l = -10, unit = "cm"
       ),
-      strip.text.x = ggplot2::element_text(size = 10),
+      strip.text.x = ggplot2::element_text(size = 15),
       strip.text.y.left = ggplot2::element_text(
         angle = 0,
-        size = 10
-      ), legend.text = ggplot2::element_text(size = 9),
-      legend.title = ggplot2::element_text(size = 9),
+        size = 15
+      ), legend.text = ggplot2::element_text(size = 14),
+      legend.title = ggplot2::element_text(size = 14),
       strip.background = ggplot2::element_rect(fill = "#ffffff"),
       plot.caption = ggplot2::element_text(
-        size = 10,
+        size = 15,
         hjust = 0, vjust = 1
       )
     ),

### 2021-10-27 robisfunctions.R
run

@@ -592,7 +592,7 @@ rob_traffic_light_generic <- function(data,
   adjust_caption <- get_caption_adjustment(rob.tidy)
   
   # Set sizes
-  ssize <- psize - (psize / 2)
+  ssize <- psize - (psize / 4)
   
   # name the provided judgement labels with appropriate judgement levels to
   # enable this to be passed as a named character variable to the
@@ -626,11 +626,8 @@ rob_traffic_light_generic <- function(data,
       labels = judgement_labels
     ) +
     ggplot2::scale_shape_manual(values = c(
-      #l = 43,
-      #s = 45,
-      #h = 120
-      l = 83,
-      s = 85,
+      l = 43,
+      s = 45,
       h = 120
     ),
     labels = judgement_labels)
@@ -832,7 +829,7 @@ rob_summ_theme <- function(overall = TRUE, max_domain_column){
         fill = judgement,
         weight = Weights
       ),
-      width = 1,
+      width = 0.7,
       position = "fill",
       color = "black"
     ),
@@ -895,8 +892,8 @@ rob_tf_theme <-function(rob.tidy,
                           factor(domain, levels = domain_names),
                         switch = "y",
                         space = "free"),
-    ggplot2::geom_point(size = 6),
-    ggplot2::geom_point(size = 4,
+    ggplot2::geom_point(size = 4),
+    ggplot2::geom_point(size = 2,
                         colour = "black",
                         #colour = "white",
                         ggplot2::aes(shape = judgement)),
@@ -953,15 +950,15 @@ rob_tf_theme <-function(rob.tidy,
         t = -0.2, r = 0,
         b = adjust_caption, l = -10, unit = "cm"
       ),
-      strip.text.x = ggplot2::element_text(size = 15),
+      strip.text.x = ggplot2::element_text(size = 10),
       strip.text.y.left = ggplot2::element_text(
         angle = 0,
-        size = 15
-      ), legend.text = ggplot2::element_text(size = 14),
-      legend.title = ggplot2::element_text(size = 14),
+        size = 10
+      ), legend.text = ggplot2::element_text(size = 9),
+      legend.title = ggplot2::element_text(size = 9),
       strip.background = ggplot2::element_rect(fill = "#ffffff"),
       plot.caption = ggplot2::element_text(
-        size = 15,
+        size = 10,
         hjust = 0, vjust = 1
       )
     ),

### 2021-10-27 robisfunctions.R
update in robisfunctions

@@ -829,7 +829,7 @@ rob_summ_theme <- function(overall = TRUE, max_domain_column){
         fill = judgement,
         weight = Weights
       ),
-      width = 0.7,
+      width = 1,
       position = "fill",
       color = "black"
     ),
@@ -845,7 +845,7 @@ rob_summ_theme <- function(overall = TRUE, max_domain_column){
       axis.ticks.y = ggplot2::element_blank(),
       axis.line.x = ggplot2::element_line(
         colour = "black",
-        size = 0.5,
+        size = 1,
         linetype = "solid"
       ),
       legend.position = "bottom",
@@ -857,18 +857,18 @@ rob_summ_theme <- function(overall = TRUE, max_domain_column){
         colour = "black"
       ),
       legend.title = ggplot2::element_blank(),
-      legend.key.size = ggplot2::unit(0.75, "lines"),
-      legend.text = ggplot2::element_text(size = 6)
+      legend.key.size = ggplot2::unit(1, "lines"),
+      legend.text = ggplot2::element_text(size = 10)
     ),
     bold_overall = ggplot2::theme(axis.text.y = ggplot2::element_text(
-      size = 10,
+      size = 15,
       color = "black"
     ))
   )
   
   if (overall) {
     standard[["bold_overall"]] <-
-      ggplot2::theme(axis.text.y = ggtext::element_markdown(size = 10,
+      ggplot2::theme(axis.text.y = ggtext::element_markdown(size = 15,
                                                             color = "black",
                                                             face = c("bold", rep("plain",max_domain_column))))
   }
@@ -950,12 +950,12 @@ rob_tf_theme <-function(rob.tidy,
         t = -0.2, r = 0,
         b = adjust_caption, l = -10, unit = "cm"
       ),
-      strip.text.x = ggplot2::element_text(size = 10),
+      strip.text.x = ggplot2::element_text(size = 15),
       strip.text.y.left = ggplot2::element_text(
         angle = 0,
         size = 10
-      ), legend.text = ggplot2::element_text(size = 9),
-      legend.title = ggplot2::element_text(size = 9),
+      ), legend.text = ggplot2::element_text(size = 14),
+      legend.title = ggplot2::element_text(size = 14),
       strip.background = ggplot2::element_rect(fill = "#ffffff"),
       plot.caption = ggplot2::element_text(
         size = 10,

### 2021-10-27 robisfunctions.R
new update

@@ -845,7 +845,7 @@ rob_summ_theme <- function(overall = TRUE, max_domain_column){
       axis.ticks.y = ggplot2::element_blank(),
       axis.line.x = ggplot2::element_line(
         colour = "black",
-        size = 1,
+        size = 2,
         linetype = "solid"
       ),
       legend.position = "bottom",
@@ -858,7 +858,7 @@ rob_summ_theme <- function(overall = TRUE, max_domain_column){
       ),
       legend.title = ggplot2::element_blank(),
       legend.key.size = ggplot2::unit(1, "lines"),
-      legend.text = ggplot2::element_text(size = 10)
+      legend.text = ggplot2::element_text(size = 15)
     ),
     bold_overall = ggplot2::theme(axis.text.y = ggplot2::element_text(
       size = 15,
@@ -954,11 +954,11 @@ rob_tf_theme <-function(rob.tidy,
       strip.text.y.left = ggplot2::element_text(
         angle = 0,
         size = 10
-      ), legend.text = ggplot2::element_text(size = 14),
-      legend.title = ggplot2::element_text(size = 14),
+      ), legend.text = ggplot2::element_text(size = 15),
+      legend.title = ggplot2::element_text(size = 20),
       strip.background = ggplot2::element_rect(fill = "#ffffff"),
       plot.caption = ggplot2::element_text(
-        size = 10,
+        size = 15,
         hjust = 0, vjust = 1
       )
     ),

### 2021-10-27 Manuscript_draft.Rmd
update manuscript
Update Q2.1 forest plot

@@
 #added for now
-asymptomaticQ2_1 <- asymptomaticQ2_1[asymptomaticQ2_1$record_id < "5296", ]
+asymptomaticQ2_1 <- asymptomaticQ2_1[asymptomaticQ2_1$record_id < 5296, ]
 
@@
 
-#Note: Chaw is missing
+#cut data at end of jan 31
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+q2_1_df <- q2_1_df %>%
+  filter(record_id <= 5296 | record_id %in% published_preprints)
 
@@
                       MH.exact = TRUE, 
-                      byvar = group)
+                      byvar = group, 
+                      comb.random = TRUE,
+                      comb.fixed = FALSE)
 q2_1_asymp

### 2021-10-27 Manuscript_draft.Rmd
updated 2.1 plot

@@
 
-```{r setup, include=FALSE}
+```{r setup, include = FALSE}
 knitr::opts_chunk$set(echo = FALSE)
@@
                       comb.random = TRUE,
-                      comb.fixed = FALSE)
+                      comb.fixed = FALSE, 
+                      label.e = "",
+                      label.c = "Symptomatic")
 q2_1_asymp
@@
 
-forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE)
-
-dev.off()
-
-png(file = 'forest_meta_Q2_1.png', width=25,height=13, res=600, units="cm")
-
-forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE)
+forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE,
+       overall.hetstat = FALSE,
+       leftlabs = c(NA, "      E", "      N", "            E", "        N"))
 

### 2021-10-28 Manuscript_draft.Rmd
Update Q2.1 plot and removed Q2.1 table for now

@@
 
+pdf(file = 'forest_meta_Q2_1.pdf', width = 8, height = 6)
+
+forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE,
+       overall.hetstat = FALSE,
+       leftlabs = c(NA, "      E", "      N", "            E", "        N"))
+
 dev.off()
@@
 
-png(file = 'forest_meta_Q2_1_precision.png', width = 600, height = 480)
+png(file = 'forest_meta_Q2_1.png', width = 600, height = 300)
 
-forest(q2_1_asymp_precision, sortvar = -seTE, overall = FALSE)
+forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE,
+       overall.hetstat = FALSE,
+       leftlabs = c(NA, "      E", "      N", "            E", "        N"))
 
@@
 
+#table not necessary - all studies in q2.1 described in full table on q1, and numbers are in forest plot
+
 #get data
-Q2_1_table <- httr::content(response2_1)
+#Q2_1_table <- httr::content(response2_1)
 
 #clean countries
-Q2_1_table <- Q2_1_table %>%
-  mutate(country = ifelse(country == 10, "Australia", country),
-         country = ifelse(country == 11, "Austria", country),
-         country = ifelse(country == 15, "Bahrain", country),
-         country = ifelse(country == 19, "Belgium", country),
-         country = ifelse(country == 28, "Brunei", country),
-         country = ifelse(country == 34, "Canada", country),
-         country = ifelse(country == 40, "China", country),
-         country = ifelse(country == 41, "Colombia", country),
-         country = ifelse(country == 51, "Denmark", country),
-         country = ifelse(country == 62, "France", country),
-         country = ifelse(country == 63, "French Guyana", country),
-         country = ifelse(country == 67, "Germany", country),
-         country = ifelse(country == 69, "Greece", country),
-         country = ifelse(country == 78, "Iceland", country),
-         country = ifelse(country == 79, "India", country),
-         country = ifelse(country == 83, "Ireland", country),
-         country = ifelse(country == 85, "Italy", country),
-         country = ifelse(country == 87, "Japan", country),
-         country = ifelse(country == 92, "Kuwait", country),
-         country = ifelse(country == 105, "Malaysia", country),
-         country = ifelse(country == 121, "Netherlands", country),
-         country = ifelse(country == 128, "Norway", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 138, "Portugal", country),
-         country = ifelse(country == 146, "Saudi Arabia", country),
-         country = ifelse(country == 157, "South Korea", country),
-         country = ifelse(country == 160, "Spain", country),
-         country = ifelse(country == 174, "Turkey", country),
-         country = ifelse(country == 176, "Uganda", country),
-         country = ifelse(country == 180, "United Kingdom", country),
-         country = ifelse(country == 181, "United States of America", country),
-         country = ifelse(country == 185, "Vietnam", country))
+#Q2_1_table <- Q2_1_table %>%
+ # mutate(country = ifelse(country == 10, "Australia", country),
+  #       country = ifelse(country == 11, "Austria", country),
+  #       country = ifelse(country == 15, "Bahrain", country),
+  #       country = ifelse(country == 19, "Belgium", country),
+  #       country = ifelse(country == 28, "Brunei", country),
+  #       country = ifelse(country == 34, "Canada", country),
+  #       country = ifelse(country == 40, "China", country),
+  #       country = ifelse(country == 41, "Colombia", country),
+  #       country = ifelse(country == 51, "Denmark", country),
+  #       country = ifelse(country == 62, "France", country),
+  #       country = ifelse(country == 63, "French Guyana", country),
+  #       country = ifelse(country == 67, "Germany", country),
+  #       country = ifelse(country == 69, "Greece", country),
+  #       country = ifelse(country == 78, "Iceland", country),
+  #       country = ifelse(country == 79, "India", country),
+  #       country = ifelse(country == 83, "Ireland", country),
+  #       country = ifelse(country == 85, "Italy", country),
+  #       country = ifelse(country == 87, "Japan", country),
+  #       country = ifelse(country == 92, "Kuwait", country),
+  #       country = ifelse(country == 105, "Malaysia", country),
+  #       country = ifelse(country == 121, "Netherlands", country),
+  #       country = ifelse(country == 128, "Norway", country),
+  #       country = ifelse(country == 888, "Other", country),
+  #       country = ifelse(country == 138, "Portugal", country),
+  #       country = ifelse(country == 146, "Saudi Arabia", country),
+  #       country = ifelse(country == 157, "South Korea", country),
+  #       country = ifelse(country == 160, "Spain", country),
+  #       country = ifelse(country == 174, "Turkey", country),
+  #       country = ifelse(country == 176, "Uganda", country),
+  #       country = ifelse(country == 180, "United Kingdom", country),
+  #       country = ifelse(country == 181, "United States of America", country),
+  #       country = ifelse(country == 185, "Vietnam", country))
 #clean regions
 
-Q2_1_table$region[Q2_1_table$region == "none" | Q2_1_table$region == "None."] <- NA
+#Q2_1_table$region[Q2_1_table$region == "none" | Q2_1_table$region == "None."] <- NA
 #create location variable
-Q2_1_table$location <- Q2_1_table$country
-Q2_1_table <- Q2_1_table %>%
-  mutate(location = ifelse(!is.na(region), paste0(country, ", ", region), country))
+#Q2_1_table$location <- Q2_1_table$country
+#Q2_1_table <- Q2_1_table %>%
+#  mutate(location = ifelse(!is.na(region), paste0(country, ", ", region), country))
 #drop country and region variables
-Q2_1_table$country <- NULL
-Q2_1_table$region <- NULL
+#Q2_1_table$country <- NULL
+#Q2_1_table$region <- NULL
 
 #author column
-Q2_1_table$study <- paste0(Q2_1_table$author_1, " (", Q2_1_table$year, ")")
-Q2_1_table$author_1 <- NULL
-Q2_1_table$record_id <- NULL
-Q2_1_table$year <- NULL
+#Q2_1_table$study <- paste0(Q2_1_table$author_1, " (", Q2_1_table$year, ")")
+#Q2_1_table$author_1 <- NULL
+#Q2_1_table$record_id <- NULL
+#Q2_1_table$year <- NULL
 
 #clean settings
-Q2_1_table$setting <- "Not available"
-Q2_1_table <- Q2_1_table %>%
-  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
-         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
-         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
-         setting = ifelse(setting2 == 4, "Statistical model", setting),
-         setting = ifelse(setting2 == 5, "Screening", setting),
-         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
-         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
-         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
-         setting = ifelse(setting2 == 9, "Screening: hospitalised patients", setting),
-         setting = ifelse(setting2 == 10, "Screening: general population", setting),
-         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
-Q2_1_table$setting2 <- NULL
+#Q2_1_table$setting <- "Not available"
+#Q2_1_table <- Q2_1_table %>%
+ # mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
+#         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
+#         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
+#         setting = ifelse(setting2 == 4, "Statistical model", setting),
+#         setting = ifelse(setting2 == 5, "Screening", setting),
+#         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
+#         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
+#         setting = ifelse(setting2 == 8, "Hospitalised children and adults", setting),
+#         setting = ifelse(setting2 == 9, "Screening: hospitalised patients", setting),
+#         setting = ifelse(setting2 == 10, "Screening: general population", setting),
+#         setting = ifelse(setting2 == 11, "Screening: occupational", setting))
+#Q2_1_table$setting2 <- NULL
 
 #reorder columns
-Q2_1_table <- data.frame(Q2_1_table$study,
-                         Q2_1_table$setting,
-                         Q2_1_table$location)
+#Q2_1_table <- data.frame(Q2_1_table$study,
+ #                        Q2_1_table$setting,
+#                         Q2_1_table$location)
 
-names(Q2_1_table) <- c("study", "setting", "location")
+#names(Q2_1_table) <- c("study", "setting", "location")
 

### 2021-10-28 robisfunctions.R
Update robisfunctions.R

@@ -953,7 +953,7 @@ rob_tf_theme <-function(rob.tidy,
       strip.text.x = ggplot2::element_text(size = 15),
       strip.text.y.left = ggplot2::element_text(
         angle = 0,
-        size = 10
+        size = 15
       ), legend.text = ggplot2::element_text(size = 15),
       legend.title = ggplot2::element_text(size = 20),
       strip.background = ggplot2::element_rect(fill = "#ffffff"),

### 2021-10-28 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
new update
Update Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update

@@
 
-p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 1), ncol = 1, nrow = 3)
+p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 0.7), ncol = 1, nrow = 3)
 
 dev.new()
-png("q1_2_new.png", width = 1400, height = 2200)
+png("q1_2_new.png", width = 1000, height = 2500)
 p7
@@
   ggplot2::ggtitle("Question 2.1") +
-  theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 16, face = "bold"))
+  theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 20, face = "bold"))
 
 dev.new()
-png("q2_new.png", width = 1000, height = 350)
+png("q2_new.png", width = 1000, height = 500)
 p8

### 2021-10-28 Manuscript_draft.Rmd
manuscript commented

@@
 #create table
-Q2_1_table <- Q2_1_table %>%
-  arrange(setting)
-
-table2 <- as_grouped_data(Q2_1_table, groups = "setting")
-table2 <- flextable(table2)
-table2 <- table2 %>%
-  set_header_labels(setting = "Setting",
-                    location = "Country, region", 
-                    study = "Study") %>%
-  set_table_properties(layout = "autofit") %>%
-  theme_vanilla()
-table2 <- width(table2, width = 10)
-table2
-
-Q2_1_table <- Q2_1_table %>%
-  arrange(setting)
-table2 <- as_grouped_data(Q2_1_table, groups = "setting")
-table2 %>%
-  as_flextable() %>%
-  set_header_labels(setting = "Setting",
-                    location = "Country, region", 
-                    study = "Study") %>%
-  set_table_properties(layout = "autofit") %>% fit_to_width(20) %>% 
-  theme_vanilla()
+# Q2_1_table <- Q2_1_table %>%
+#   arrange(setting)
+# 
+# table2 <- as_grouped_data(Q2_1_table, groups = "setting")
+# table2 <- flextable(table2)
+# table2 <- table2 %>%
+#   set_header_labels(setting = "Setting",
+#                     location = "Country, region", 
+#                     study = "Study") %>%
+#   set_table_properties(layout = "autofit") %>%
+#   theme_vanilla()
+# table2 <- width(table2, width = 10)
+# table2
+# 
+# Q2_1_table <- Q2_1_table %>%
+#   arrange(setting)
+# table2 <- as_grouped_data(Q2_1_table, groups = "setting")
+# table2 %>%
+#   as_flextable() %>%
+#   set_header_labels(setting = "Setting",
+#                     location = "Country, region", 
+#                     study = "Study") %>%
+#   set_table_properties(layout = "autofit") %>% fit_to_width(20) %>% 
+#   theme_vanilla()
 

### 2021-10-28 Manuscript_draft.Rmd
Formatting Q1 plot

@@
 #change clusters to descriptions
-asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:1]"] <- "#4479 Harada [Patients]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada [cluster:2]"] <- "#4479 Harada [Healthcare workers]"
-#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor []" #clarify
-#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor []"
-asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:1]"] <- "#2892 Kennelly [Nursing home residents]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul [cluster:2]"] <- "#4968 van Buul [Healthcare workers]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:1]"] <- "#5273 Theuring [School students and staff]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#2751 van den Besselaar [cluster:1]"] <- "#2751 van den Besselaar [Healthcare workers]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#2751 van den Besselaar [cluster:2]"] <- "#2751 van den Besselaar [Residents]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor [Healthcare personnel]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor [Residents]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani [cluster:1]"] <- "#3719 Ladhani [Residents]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani [cluster:2]"] <- "#3719 Ladhani [Healthcare workers]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:1]"] <- "#5551 Vohra [Presurgical patients]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:2]"] <- "#5551 Vohra [Undergoing chemotherapy]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:1]"] <- "#6526 Garibaldi [Residents]"
-asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:2]"] <- "#6526 Garibaldi [Staff]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada S [cluster:1]"] <- "#4479 Harada S [Patients]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#4479 Harada S [cluster:2]"] <- "#4479 Harada S [Healthcare workers]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly SP [cluster:1]"] <- "#2892 Kennelly SP [Nursing home residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#2892 Kennelly SP [cluster:2]"] <- "#2892 Kennelly SP [Nursing home staff]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul LW [cluster:1]"] <- "#4968 van Buul LW [Nursing home residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#4968 van Buul LW [cluster:2]"] <- "#4968 van Buul LW [Healthcare workers]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#9442 Theuring S [cluster:1]"] <- "#9442 Theuring S [School students and staff]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#9442 Theuring S [cluster:2]"] <- "#9442 Theuring S [Household members]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#7465 van den Besselaar JH [cluster:1]"] <- "#7465 van den Besselaar JH [Healthcare workers]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#7465 van den Besselaar JH [cluster:2]"] <- "#7465 van den Besselaar JH [Residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor J [cluster:1]"] <- "#2826 Taylor J [Healthcare personnel]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor J [cluster:2]"] <- "#2826 Taylor J [Residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani SN [cluster:1]"] <- "#3719 Ladhani SN [Residents]"
+asymptomaticQ1$label[asymptomaticQ1$label == "#3719 Ladhani SN [cluster:2]"] <- "#3719 Ladhani SN [Healthcare workers]"
+#asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:1]"] <- "#5551 Vohra [Presurgical patients]"
+#asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:2]"] <- "#5551 Vohra [Undergoing chemotherapy]"
+#asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:1]"] <- "#6526 Garibaldi [Residents]"
+#asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:2]"] <- "#6526 Garibaldi [Staff]"
 
@@
 #same as precision plot
-pdf(file = 'forest_meta_Q1.pdf', width = 10, height = 30)
+pdf(file = 'forest_meta_Q1.pdf', width = 10, height = 28)
 

### 2021-10-28 Manuscript_draft.Rmd
png width changed
update

@@
 
-png(file = 'forest_meta_Q1.png',width=25,height=80, res=600, units="cm")
+png(file = 'forest_meta_Q1.png',width=28,height=70, res=600, units="cm")
 
@@
 two_models <- asymptomaticQ2_2
+two_models$author_1 <- gsub(",","",two_models$author_1)
 #separate into 2 variables

### 2021-10-28 Manuscript_draft.Rmd
updated codes for Q2.2 forest plot

@@
 
-pdf(file = 'forest_meta_Q2_1.pdf', width = 8, height = 6)
+pdf(file = 'forest_meta_Q2_1.pdf', width = 10, height = 6)
 
@@
                values_to = "q3_pp_m")
-L1$label <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")
+
+L1$label <- "Value"
+for (i in 1:nrow(L1)) {
+  if (L1$model[i] == "q3_pp_m_1") {
+  L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_1[i], "]", sep = "")
+  }else{
+    L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_2[i], "]", sep = "")
+  }
+
+}
+L1$label2 <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")
+
 L2 <- two_models %>%
@@
                values_to = "q3_pp_l") %>%
-  select("record_id", "model", "q3_pp_l", "author_1")
-L2$label <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
+  select("record_id", "model", "q3_pp_l", "author_1", "q3_setting_1", "q3_setting_2")
+
+L2$label2 <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
+L2$label <- "Value"
+for (i in 1:nrow(L2)) {
+  if (L2$model[i] == "q3_pp_l_1") {
+  L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_1[i], "]", sep = "")
+  }else{
+    L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_2[i], "]", sep = "")
+  }
+
+}
+
 L2 <- L2 %>% select("q3_pp_l", "label")
+
 L3 <- two_models %>%
@@
                values_to = "q3_pp_u") %>%
-  select("record_id", "model", "q3_pp_u", "author_1")
-L3$label <- paste(L3$author_1, " [", substrRight(L3$model, 1), "]", sep = "")
+  select("record_id", "model", "q3_pp_u", "author_1", "q3_setting_1", "q3_setting_2")
+
+L3$label <- "Value"
+i = 1
+for (i in 1:nrow(L3)) {
+  if (L3$model[i] == "q3_pp_u_1") {
+  L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_1[i], "]", sep = "")
+  }else{
+    L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_2[i], "]", sep = "")
+  }
+
+}
+
+L3$label2 <- paste(L3$author_1, " [", substrRight(L3$model, 1), "]", sep = "")
+
 L3 <- L3 %>% select("q3_pp_u", "label")
+
 L4 <- two_models %>%
@@
   select("record_id", "model", "setting", "author_1")
-L4$label <- paste(L4$author_1, " [", substrRight(L4$model, 1), "]", sep = "")
+L4$label2 <- paste(L4$author_1, " [", substrRight(L4$model, 1), "]", sep = "")
+L4$label <- paste(L4$author_1, " [", L4$setting, "]", sep = "")
+
 L4 <- L4 %>% select("setting", "label")
@@
 Asymp_label <- data.frame(NA, "Asymptomatic transmission", NA, NA, NA, NA, NA, 
-                          NA, NA, NA, NA, NA, 1)
+                          NA, NA, NA, NA, NA,1)
 names(Asymp_label) <- names(Q2_2_df)

### 2021-10-28 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

@@
 L2$label <- "Value"
+i = 1
 for (i in 1:nrow(L2)) {

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

--- 2021-10-28 Manuscript_draft.Rmd
@@
   if (L1$model[i] == "q3_pp_m_1") {
-  L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_1[i], "]", sep = "")
+    sett <- L1$q3_setting_1[i]
   }else{
-    L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_2[i], "]", sep = "")
+    sett <- L1$q3_setting_2[i]
   }
-
+    L1$label[i] <- paste(L1$author_1[i], " [", sett, "]", sep = "")
   }
@@
 L2$label <- "Value"
+i = 1
 for (i in 1:nrow(L2)) {
   if (L2$model[i] == "q3_pp_l_1") {
-  L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_1[i], "]", sep = "")
+    sett -> L2$q3_setting_1[i]
   }else{
-    L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_2[i], "]", sep = "")
+    sett -> L2$q3_setting_2[i]
   }
-
+  L2$label[i] <- paste(L2$author_1[i], " [", sett, "]", sep = "")
 }
@@
   if (L3$model[i] == "q3_pp_u_1") {
-  L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_1[i], "]", sep = "")
+    sett -> L3$q3_setting_1[i]
   }else{
-    L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_2[i], "]", sep = "")
+    sett -> L3$q3_setting_2[i]
   }
-
+  L3$label[i] <- paste(L3$author_1[i], " [", sett, "]", sep = "")
 }

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

@@
   if (L1$model[i] == "q3_pp_m_1") {
-    sett <- L1$q3_setting_1[i]
+  L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_1[i], "]", sep = "")
   }else{
-    sett <- L1$q3_setting_2[i]
+    L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_2[i], "]", sep = "")
   }
-    L1$label[i] <- paste(L1$author_1[i], " [", sett, "]", sep = "")
+
 }
+
 L1$label2 <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")
@@
   L2$label[i] <- paste(L2$author_1[i], " [", sett, "]", sep = "")
+}
+
+for (i in 1:nrow(L2)) {
+  if (L2$model[i] == "q3_pp_l_1") {
+  L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_1[i], "]", sep = "")
+  }else{
+    L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_2[i], "]", sep = "")
+  }
+
 }

### 2021-10-29 Q2_2_Figure4.R
Hira created a new plot

@@ -1,0 +1,142 @@
+
+## Q3 = Figure4 #####
+
+
+library(RCurl)
+result <- postForm(
+  uri='https://redcap.ispm.unibe.ch/api/',
+  token='F2725F15FE84D2832E2793BB23B0A62B',
+  content='report',
+  format='csv',
+  report_id='157',
+  rawOrLabel='label',
+  rawOrLabelHeaders='raw',
+  exportCheckboxLabel='false',
+  returnFormat='json'
+)
+tmp<-textConnection(result)
+asymptomaticQ3<-read.csv(tmp, stringsAsFactors = FALSE)
+
+
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData2_2 <- list("token"=token,
+                    content='report',
+                    format='csv',
+                    report_id='157',
+                    csvDelimiter='',
+                    rawOrLabel='raw',
+                    rawOrLabelHeaders='raw',
+                    exportCheckboxLabel='false',
+                    returnFormat='csv'
+)
+response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
+asymptomaticQ3 <- httr::content(response2_2)
+
+
+library(dplyr)
+
+asymptomaticQ3 = asymptomaticQ3 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
+asymptomaticQ3$q3_setting=ifelse(asymptomaticQ3$q3_setting=="",NA,asymptomaticQ3$q3_setting)
+
+s <- strsplit(asymptomaticQ3$q3_setting, split = ";")
+pp_m <- strsplit(asymptomaticQ3$q3_pp_m, split = ";")
+pp_l <- strsplit(asymptomaticQ3$q3_pp_l, split = ";")
+pp_u <- strsplit(asymptomaticQ3$q3_pp_u, split = ";")
+
+dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ3$author_1), sapply(pp_m, length)),
+                 Q3set=unlist(s),
+                 p = as.numeric(unlist(pp_m)), 
[…]

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

@@
   if (L3$model[i] == "q3_pp_u_1") {
-    sett -> L3$q3_setting_1[i]
+    L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_1[i], "]", sep = "")
   }else{
-    sett -> L3$q3_setting_2[i]
+    L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_2[i], "]", sep = "")
   }
-  L3$label[i] <- paste(L3$author_1[i], " [", sett, "]", sep = "")
+
 }

### 2021-10-29 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -1,21 +1,5 @@
 
-## Q3 = Figure4 #####
-
-
-library(RCurl)
-result <- postForm(
-  uri='https://redcap.ispm.unibe.ch/api/',
-  token='F2725F15FE84D2832E2793BB23B0A62B',
-  content='report',
-  format='csv',
-  report_id='157',
-  rawOrLabel='label',
-  rawOrLabelHeaders='raw',
-  exportCheckboxLabel='false',
-  returnFormat='json'
-)
-tmp<-textConnection(result)
-asymptomaticQ3<-read.csv(tmp, stringsAsFactors = FALSE)
+## Q2.2 = Figure4 #####
 
 
 url <- "https://redcap.ispm.unibe.ch/api/"

### 2021-10-29 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -15,20 +15,20 @@ formData2_2 <- list("token"=token,
                     returnFormat='csv'
 )
 response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
-asymptomaticQ3 <- httr::content(response2_2)
+asymptomaticQ2_2 <- httr::content(response2_2)
 
 
 library(dplyr)
 
-asymptomaticQ3 = asymptomaticQ3 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
-asymptomaticQ3$q3_setting=ifelse(asymptomaticQ3$q3_setting=="",NA,asymptomaticQ3$q3_setting)
+asymptomaticQ2_2 = asymptomaticQ2_2 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
+asymptomaticQ2_2$q3_setting=ifelse(asymptomaticQ2_2$q3_setting=="",NA,asymptomaticQ2_2$q3_setting)
 
-s <- strsplit(asymptomaticQ3$q3_setting, split = ";")
-pp_m <- strsplit(asymptomaticQ3$q3_pp_m, split = ";")
-pp_l <- strsplit(asymptomaticQ3$q3_pp_l, split = ";")
-pp_u <- strsplit(asymptomaticQ3$q3_pp_u, split = ";")
+s <- strsplit(asymptomaticQ2_2$q3_setting, split = ";")
+pp_m <- strsplit(asymptomaticQ2_2$q3_pp_m, split = ";")
+pp_l <- strsplit(asymptomaticQ2_2$q3_pp_l, split = ";")
+pp_u <- strsplit(asymptomaticQ2_2$q3_pp_u, split = ";")
 
-dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ3$author_1), sapply(pp_m, length)),
+dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ2_2$author_1), sapply(pp_m, length)),
                  Q3set=unlist(s),
                  p = as.numeric(unlist(pp_m)), 
                  l = as.numeric(unlist(pp_l)),
@@ -40,11 +40,11 @@ dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ3$author_1), sapply(pp_m, l
 dfQ3a[dfQ3a==9999]<-NA
 dfQ3a=dfQ3a[!is.na(dfQ3a$p),]
 
-dfQ3b=data.frame(label=paste0("   ",asymptomaticQ3$author_1),
[…]

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

--- 2021-10-29 Manuscript_draft.Rmd
@@
 
+############Old Codes###############
 #clean data
-asymptomaticQ2_2[asymptomaticQ2_2=="9999;9999"]=NA #indicate as missing
-asymptomaticQ2_2[asymptomaticQ2_2 == "9999"] = NA #indicate as missing
-
-#create a separate dataset for the records with >1 result
-two_models <- asymptomaticQ2_2
-two_models$author_1 <- gsub(",","",two_models$author_1)
-#separate into 2 variables
-two_models = two_models %>% 
-  separate(q3_pp_m, c("q3_pp_m_1","q3_pp_m_2"), ";")
-two_models = two_models %>% 
-  separate(q3_pp_l, c("q3_pp_l_1","q3_pp_l_2"), ";") 
-two_models = two_models %>%
-  separate(q3_pp_u, c("q3_pp_u_1","q3_pp_u_2"), ";")
-two_models = two_models %>% 
-  separate(q3_setting, c("q3_setting_1","q3_setting_2"), ";")
-
-two_models <- two_models %>% #change values to numeric
-  mutate(q3_pp_m_1=as.numeric(q3_pp_m_1),
-         q3_pp_m_2=as.numeric(q3_pp_m_2),
-         q3_pp_l_1=as.numeric(q3_pp_l_1),
-         q3_pp_l_2=as.numeric(q3_pp_l_2),
-         q3_pp_u_1=as.numeric(q3_pp_u_1),
-         q3_pp_u_2=as.numeric(q3_pp_u_2))
-
-two_models <- two_models[!is.na(two_models$q3_pp_m_2),]
-
-substrRight <- function(x, n){
-  substr(x, nchar(x)-n+1, nchar(x))
-}
-
-L1 <- two_models %>%
-  pivot_longer(cols = c(6:7),
-               names_to = "model",
-               values_to = "q3_pp_m")
-
-L1$label <- "Value"
-for (i in 1:nrow(L1)) {
-  if (L1$model[i] == "q3_pp_m_1") {
-    sett <- L1$q3_setting_1[i]
-  }else{
-    sett <- L1$q3_setting_2[i]
-  }
-    L1$label[i] <- paste(L1$author_1[i], " [", sett, "]", sep = "")
-  }
-L1$label2 <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")
-
-L2 <- two_models %>%
-  pivot_longer(cols = c(8:9),
-               names_to = "model",
-               values_to = "q3_pp_l") %>%
-  select("record_id", "model", "q3_pp_l", "author_1", "q3_setting_1", "q3_setting_2")
-
-L2$label2 <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
-L2$label <- "Value"
-i = 1
-for (i in 1:nrow(L2)) {
-  if (L2$model[i] == "q3_pp_l_1") {
-    sett -> L2$q3_setting_1[i]
-  }else{
-    sett -> L2$q3_setting_2[i]
-  }
-  L2$label[i] <- paste(L2$author_1[i], " [", sett, "]", sep = "")
-}
-
-L2 <- L2 %>% select("q3_pp_l", "label")
-
-L3 <- two_models %>%
-  pivot_longer(cols = c(10:11),
-               names_to = "model",
-               values_to = "q3_pp_u") %>%
-  select("record_id", "model", "q3_pp_u", "author_1", "q3_setting_1", "q3_setting_2")
-
-L3$label <- "Value"
-i = 1
-for (i in 1:nrow(L3)) {
-  if (L3$model[i] == "q3_pp_u_1") {
-    sett -> L3$q3_setting_1[i]
-  }else{
-    sett -> L3$q3_setting_2[i]
-  }
-  L3$label[i] <- paste(L3$author_1[i], " [", sett, "]", sep = "")
-}
-
-L3$label2 <- paste(L3$author_1, " [", substrRight(L3$model, 1), "]", sep = "")
-
-L3 <- L3 %>% select("q3_pp_u", "label")
-
-L4 <- two_models %>%
-  pivot_longer(cols = c(13:14),
-               names_to = "model",
-               values_to = "setting") %>%
-  select("record_id", "model", "setting", "author_1")
-L4$label2 <- paste(L4$author_1, " [", substrRight(L4$model, 1), "]", sep = "")
-L4$label <- paste(L4$author_1, " [", L4$setting, "]", sep = "")
-
-L4 <- L4 %>% select("setting", "label")
-#merge together
-Lall <- merge(L2, L3, by = "label")   
-Lall <- merge(Lall, L4, by = "label") 
-Lall <- merge(Lall, L1, by = "label")
-Lall <- Lall %>%
-  select("record_id", "author_1", "q3_pa_m", "q3_pa_l", "q3_pa_u", 
-         "q3_pp_m", "q3_pp_l", "q3_pp_u", "question_3_complete", "setting", 
-         "label")
-
-#clean original dataset
-asymptomaticQ2_2$label <- asymptomaticQ2_2$author_1
-asymptomaticQ2_2 <- asymptomaticQ2_2 %>%
-  mutate(setting = q3_setting)
-asymptomaticQ2_2$q3_setting <- NULL
-asymptomaticQ2_2 <- as.data.frame(asymptomaticQ2_2)
-attr(asymptomaticQ2_2, 'spec') <- NULL
-str(asymptomaticQ2_2)
-asymptomaticQ2_2$q3_pp_m <- as.numeric(asymptomaticQ2_2$q3_pp_m)
-asymptomaticQ2_2$q3_pp_l <- as.numeric(asymptomaticQ2_2$q3_pp_l)
-asymptomaticQ2_2$q3_pp_u <- as.numeric(asymptomaticQ2_2$q3_pp_u)
-
-#add extra rows to original dataset
-Q2_2 <- bind_rows(asymptomaticQ2_2, Lall)
-#if q3_pp_m and q3_pa_m both NA then delete
-Q2_2 <- Q2_2[!is.na(Q2_2$q3_pa_m) | !is.na(Q2_2$q3_pp_m),]
-
-#create new variable for all estimates and indicate asymp/presymp with new variable
-#fill Q2_2 first with estimates from q3_pp_m then q3_pa_m
-Q2_2 <- Q2_2 %>%
-  mutate(estimate = ifelse(!is.na(q3_pp_m),
-                           q3_pp_m,
-                           q3_pa_m),
-         lower_bound = ifelse(!is.na(q3_pp_m),
-                                 q3_pp_l,
-                                 q3_pa_l),
-         upper_bound = ifelse(!is.na(q3_pp_m),
-                                 q3_pp_u,
-                                 q3_pa_u),
-         subgroup = ifelse(!is.na(q3_pp_m),
-                           "presymp",
-                           "asymp"))
-#some records have presymp estimates in estimate now - must make new observation
-both <- Q2_2 %>%
-  filter(!is.na(Q2_2$q3_pa_m) & !is.na(Q2_2$q3_pp_m)) %>%
-  mutate(estimate = q3_pa_m,
-         lower_bound = q3_pa_l,
-         upper_bound = q3_pa_u,
-         subgroup = "asymp")
-Q2_2 <- bind_rows(Q2_2, both)
-#remove unnecessary cols
-Q2_2 <- Q2_2 %>%
-  select(c("record_id", "label", "setting", "estimate", "lower_bound", "upper_bound", "subgroup"))
-#round numbers to 2 decimal points
-Q2_2$estimate <- round(Q2_2$estimate, digits = 2)
-Q2_2$lower_bound <- round(Q2_2$lower_bound, digits = 2)
-Q2_2$upper_bound <- round(Q2_2$upper_bound, digits = 2)
-
-###############################################################
-# forest plot
-
-#prepare data
-Q2_2_df <- Q2_2
-#create label for proportions
-Q2_2_df$prop <- sprintf("%2.2f", Q2_2_df$estimate)
-#create label for 95% CIs
-Q2_2_df$CI_lower <- sprintf("%2.2f", Q2_2_df$lower_bound)
-Q2_2_df$CI_upper <- sprintf("%2.2f", Q2_2_df$upper_bound)
-Q2_2_df$CIs <- paste("[", Q2_2_df$CI_lower, #paste together 95% CIs
-                     ";", Q2_2_df$CI_upper, "]", 
-                     sep = "")
-Q2_2_df <- Q2_2_df %>%
-  mutate(CI = ifelse(is.na(Q2_2_df$CI_lower), NA, CIs))
-Q2_2_df$CI[Q2_2_df$CI == "[NA;NA]"] <- NA
-str(Q2_2_df)
-#col to indicate headings/studies in plot
-Q2_2_df$type <- 2
-#new row for asymptomatic label in plot
-Asymp_label <- data.frame(NA, "Asymptomatic transmission", NA, NA, NA, NA, NA, 
-                          NA, NA, NA, NA, NA,1)
-names(Asymp_label) <- names(Q2_2_df)
-#new row for asymptomatic label in plot
-Presymp_label <- data.frame(NA, "Presymptomatic transmission", NA, NA, NA, NA, NA, 
-                            NA, NA, NA, NA, NA, 1)
-names(Presymp_label) <- names(Q2_2_df)
-#add to exisiting dataframe
-Q2_2_df <- rbind(Q2_2_df, Asymp_label, Presymp_label)
-#font indicator
-Q2_2_df$fontface = ifelse(Q2_2_df$type == 1, "italic","plain")
-str(Q2_2_df$fontface)
-
-#arrange studies by subgroup
-asymp_n <- sum(Q2_2_df$subgroup == "asymp", #number of asymp studies
-               na.rm = TRUE) 
-presymp_n <- sum(Q2_2_df$subgroup == "presymp", #number of presymp studies
-                 na.rm = TRUE) 
-Q2_2_df$line[Q2_2_df$label == "Asymptomatic transmission"] <- 1
-#new row for space in plot
-space <- data.frame(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA)
-names(space) <- names(Q2_2_df)
-#add to exisiting dataframe
-Q2_2_df <- rbind(Q2_2_df, space)
-Q2_2_df$line[is.na(Q2_2_df$label)] <- 2 + asymp_n
-Q2_2_df$line[Q2_2_df$label == "Presymptomatic transmission"] <- 3 + asymp_n
-Q2_2_df_a <- Q2_2_df %>% #order the asymp studies
-  filter(subgroup == "asymp") %>%
-  mutate(line = 2:(asymp_n + 1))
-Q2_2_df_p <- Q2_2_df %>% #order the presymp studies
-  filter(subgroup == "presymp") %>%
-  mutate(line = (asymp_n + 4):(presymp_n + asymp_n + 3))
-Q2_2_df <- Q2_2_df[is.na(Q2_2_df$record_id),]
-#join all rows again
-Q2_2_df <- rbind(Q2_2_df, Q2_2_df_a, Q2_2_df_p)
-
-#create forest plot
-p <- ggplot() + 
-  geom_point(data = Q2_2_df, #add estimates 
-             aes(y = line, 
-                 x = estimate),
-             fill = "gray", 
-             shape = 22, 
-             color = "black",
-             size = 4) +
-  geom_errorbarh(data = Q2_2_df, #add error bars 
-                 aes(y = line, 
-                     xmin = lower_bound, 
-                     xmax = upper_bound), 
-                 height=0.3) +
-  geom_text(aes(y = c(-1, -1, -1),  #add cols for study, estimates and CIs
-                x = c(-0.2, 1.05, 1.12), 
-                label=c("Study", "Prop.", "95% CI")), 
-            hjust = 0, 
-            fontface = "bold") +
-  geom_text(data = Q2_2_df, #add estimate labels
-            aes(y = line, 
-                x = 1.05, 
-                label = prop), 
-            hjust = 0) +
-  geom_text(data = Q2_2_df, #add CI labels
-            aes(y = line,
-                x = 1.12,
-                label = CI), 
-            hjust = 0) +
-  geom_text(data = Q2_2_df, #add study labels
-            aes(y= line, 
-                x=-0.2, 
-                label = label,
-                hjust = 0,
-                fontface = fontface)) +
-  theme_void() + #remove background
-  scale_y_reverse() +
-  geom_segment(data = Q2_2_df, #add line below point estimates
-               aes(y = max(line) + 1, x = 0, xend = 1, 
-                   yend = max(line) + 1)) +
-  geom_segment(data = Q2_2_df, #add dash for 0
-               aes(y = max(line) + 1, yend = max(line) + 1.3, 
-                   x = 0, xend = 0)) +
-  geom_segment(data = Q2_2_df, #add dash for 0.25
-               aes(y = max(line) + 1, yend = max(line) + 1.3,
-                   x = 0.25, xend = 0.25)) +
-  geom_segment(data = Q2_2_df, #add dash for 0.5
-               aes(y = max(line)+1, yend=max(line) + 1.3,
-                   x=0.5, xend=0.5)) +
-  geom_segment(data = Q2_2_df, #add dash for 0.75
-               aes(y = max(line) + 1, yend = max(line) + 1.3,
-                   x=0.75, xend = 0.75)) +
-  geom_segment(data = Q2_2_df, #add dash for 1
-               aes(y = max(line) + 1, 
-                   yend = max(line) + 1.3,
-                   x = 1, xend = 1)) +
-  geom_text(aes(y = rep(max(Q2_2_df$line) + 2,5), #add numbers to line
-                x = 0:4/4,
-                label = c(0, 0.25, 0.5, 0.75, 1))) +
-  scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.5))
+# asymptomaticQ2_2[asymptomaticQ2_2=="9999;9999"]=NA #indicate as missing
+# asymptomaticQ2_2[asymptomaticQ2_2 == "9999"] = NA #indicate as missing
+# 
+# #create a separate dataset for the records with >1 result
+# two_models <- asymptomaticQ2_2
+# two_models$author_1 <- gsub(",","",two_models$author_1)
+# #separate into 2 variables
+# two_models = two_models %>% 
+#   separate(q3_pp_m, c("q3_pp_m_1","q3_pp_m_2"), ";")
+# two_models = two_models %>% 
+#   separate(q3_pp_l, c("q3_pp_l_1","q3_pp_l_2"), ";") 
+# two_models = two_models %>%
+#   separate(q3_pp_u, c("q3_pp_u_1","q3_pp_u_2"), ";")
+# two_models = two_models %>% 
+#   separate(q3_setting, c("q3_setting_1","q3_setting_2"), ";") 
+# 
+# two_models <- two_models %>% #change values to numeric
+#   mutate(q3_pp_m_1=as.numeric(q3_pp_m_1),
+#          q3_pp_m_2=as.numeric(q3_pp_m_2),
+#          q3_pp_l_1=as.numeric(q3_pp_l_1),
+#          q3_pp_l_2=as.numeric(q3_pp_l_2),
+#          q3_pp_u_1=as.numeric(q3_pp_u_1),
+#          q3_pp_u_2=as.numeric(q3_pp_u_2))
+# 
+# 
+# two_models <- two_models[!is.na(two_models$q3_pp_m_2),]
+# 
+# substrRight <- function(x, n){
+#   substr(x, nchar(x)-n+1, nchar(x))
+# }
+# 
+# L1 <- two_models %>%
+#   pivot_longer(cols = c(6:7),
+#                names_to = "model",
+#                values_to = "q3_pp_m") 
+# 
+# L1$label <- "Value"
+# for (i in 1:nrow(L1)) {
+#   if (L1$model[i] == "q3_pp_m_1") {
+#   L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_1[i], "]", sep = "")
+#   }else{
+#     L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_2[i], "]", sep = "")
+#   }
+#   
+# }
+# 
+# L1$label2 <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")
+# L2 <- two_models %>%
+#   pivot_longer(cols = c(8:9),
+#                names_to = "model",
+#                values_to = "q3_pp_l") %>%
+#   select("record_id", "model", "q3_pp_l", "author_1", "q3_setting_1", "q3_setting_2")
+# 
+# L2$label2 <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
+# L2$label <- "Value"
+# i = 1
+# for (i in 1:nrow(L2)) {
+#   if (L2$model[i] == "q3_pp_l_1") {
+#     sett -> L2$q3_setting_1[i]
+#   }else{
+#     sett -> L2$q3_setting_2[i]
+#   }
+#   L2$label[i] <- paste(L2$author_1[i], " [", sett, "]", sep = "")
+# }
+# 
+# i=1
+# for (i in 1:nrow(L2)) {
+#   if (L2$model[i] == "q3_pp_l_1") {
+#     L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_1[i], "]", sep = "")
+#   }else{
+#     L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_2[i], "]", sep = "")
+#   }
+#   
+# }
+# 
+# L2 <- L2 %>% select("q3_pp_l", "label")
+# L3 <- two_models %>%
+#   pivot_longer(cols = c(10:11),
+#                names_to = "model",
+#                values_to = "q3_pp_u") %>%
+#   select("record_id", "model", "q3_pp_u", "author_1", "q3_setting_1", "q3_setting_2")
+# 
+# L3$label <- "Value"
+# i = 1
+# for (i in 1:nrow(L3)) {
+#   if (L3$model[i] == "q3_pp_u_1") {
+#     L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_1[i], "]", sep = "")
+#   }else{
+#     L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_2[i], "]", sep = "")
+#   }
+#   
+# }
+# 
+# L3$label2 <- paste(L3$author_1, " [", substrRight(L3$model, 1), "]", sep = "")
+# 
+# L3 <- L3 %>% select("q3_pp_u", "label")
+# L4 <- two_models %>%
+#   pivot_longer(cols = c(13:14),
+#                names_to = "model",
+#                values_to = "setting") %>%
+#   select("record_id", "model", "setting", "author_1")
+# L4$label2 <- paste(L4$author_1, " [", substrRight(L4$model, 1), "]", sep = "")
+# L4$label <- paste(L4$author_1, " [", L4$setting, "]", sep = "")
+# 
+# L4 <- L4 %>% select("setting", "label")
+# #merge together
+# Lall <- merge(L2, L3, by = "label")   
+# Lall <- merge(Lall, L4, by = "label") 
+# Lall <- merge(Lall, L1, by = "label")
+# Lall <- Lall %>%
+#   select("record_id", "author_1", "q3_pa_m", "q3_pa_l", "q3_pa_u", 
+#          "q3_pp_m", "q3_pp_l", "q3_pp_u", "question_3_complete", "setting", 
+#          "label")
+# 
+# #clean original dataset
+# asymptomaticQ2_2$label <- asymptomaticQ2_2$author_1
+# asymptomaticQ2_2 <- asymptomaticQ2_2 %>%
+#   mutate(setting = q3_setting)
+# asymptomaticQ2_2$q3_setting <- NULL
+# asymptomaticQ2_2 <- as.data.frame(asymptomaticQ2_2)
+# attr(asymptomaticQ2_2, 'spec') <- NULL
+# str(asymptomaticQ2_2)
+# asymptomaticQ2_2$q3_pp_m <- as.numeric(asymptomaticQ2_2$q3_pp_m)
+# asymptomaticQ2_2$q3_pp_l <- as.numeric(asymptomaticQ2_2$q3_pp_l)
+# asymptomaticQ2_2$q3_pp_u <- as.numeric(asymptomaticQ2_2$q3_pp_u)
+# 
+# #add extra rows to original dataset
+# Q2_2 <- bind_rows(asymptomaticQ2_2, Lall)
+# #if q3_pp_m and q3_pa_m both NA then delete
+# Q2_2 <- Q2_2[!is.na(Q2_2$q3_pa_m) | !is.na(Q2_2$q3_pp_m),]
+# 
+# #create new variable for all estimates and indicate asymp/presymp with new variable
+# #fill Q2_2 first with estimates from q3_pp_m then q3_pa_m
+# Q2_2 <- Q2_2 %>%
+#   mutate(estimate = ifelse(!is.na(q3_pp_m),
+#                            q3_pp_m,
+#                            q3_pa_m),
+#          lower_bound = ifelse(!is.na(q3_pp_m),
+#                                  q3_pp_l,
+#                                  q3_pa_l),
+#          upper_bound = ifelse(!is.na(q3_pp_m),
+#                                  q3_pp_u,
+#                                  q3_pa_u),
+#          subgroup = ifelse(!is.na(q3_pp_m),
+#                            "presymp",
+#                            "asymp"))
+# #some records have presymp estimates in estimate now - must make new observation
+# both <- Q2_2 %>%
+#   filter(!is.na(Q2_2$q3_pa_m) & !is.na(Q2_2$q3_pp_m)) %>%
+#   mutate(estimate = q3_pa_m,
+#          lower_bound = q3_pa_l,
+#          upper_bound = q3_pa_u,
+#          subgroup = "asymp")
+# Q2_2 <- bind_rows(Q2_2, both)
+# #remove unnecessary cols
+# Q2_2 <- Q2_2 %>%
+#   select(c("record_id", "label", "setting", "estimate", "lower_bound", "upper_bound", "subgroup"))
+# #round numbers to 2 decimal points
+# Q2_2$estimate <- round(Q2_2$estimate, digits = 2)
+# Q2_2$lower_bound <- round(Q2_2$lower_bound, digits = 2)
+# Q2_2$upper_bound <- round(Q2_2$upper_bound, digits = 2)
+# 
+# ###############################################################
+# # forest plot
+# 
+# 
+# #prepare data
+# Q2_2_df <- Q2_2
+# #create label for proportions
+# Q2_2_df$prop <- sprintf("%2.2f", Q2_2_df$estimate)
+# #create label for 95% CIs
+# Q2_2_df$CI_lower <- sprintf("%2.2f", Q2_2_df$lower_bound)
+# Q2_2_df$CI_upper <- sprintf("%2.2f", Q2_2_df$upper_bound)
+# Q2_2_df$CIs <- paste("[", Q2_2_df$CI_lower, #paste together 95% CIs
+#                      ";", Q2_2_df$CI_upper, "]", 
+#                      sep = "")
+# Q2_2_df <- Q2_2_df %>%
+#   mutate(CI = ifelse(is.na(Q2_2_df$CI_lower), NA, CIs))
+# Q2_2_df$CI[Q2_2_df$CI == "[NA;NA]"] <- NA
+# str(Q2_2_df)
+# #col to indicate headings/studies in plot
+# Q2_2_df$type <- 2
+# #new row for asymptomatic label in plot
+# Asymp_label <- data.frame(NA, "Asymptomatic transmission", NA, NA, NA, NA, NA, 
+#                           NA, NA, NA, NA, NA,1)
+# names(Asymp_label) <- names(Q2_2_df)
+# #new row for asymptomatic label in plot
+# Presymp_label <- data.frame(NA, "Presymptomatic transmission", NA, NA, NA, NA, NA, 
+#                             NA, NA, NA, NA, NA, 1)
+# names(Presymp_label) <- names(Q2_2_df)
+# #add to exisiting dataframe
+# Q2_2_df <- rbind(Q2_2_df, Asymp_label, Presymp_label)
+# #font indicator
+# Q2_2_df$fontface = ifelse(Q2_2_df$type == 1, "italic","plain")
+# str(Q2_2_df$fontface)
+# 
+# #arrange studies by subgroup
+# asymp_n <- sum(Q2_2_df$subgroup == "asymp", #number of asymp studies
+#                na.rm = TRUE) 
+# presymp_n <- sum(Q2_2_df$subgroup == "presymp", #number of presymp studies
+#                  na.rm = TRUE) 
+# Q2_2_df$line[Q2_2_df$label == "Asymptomatic transmission"] <- 1
+# #new row for space in plot
+# space <- data.frame(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA)
+# names(space) <- names(Q2_2_df)
+# #add to exisiting dataframe
+# Q2_2_df <- rbind(Q2_2_df, space)
+# Q2_2_df$line[is.na(Q2_2_df$label)] <- 2 + asymp_n
+# Q2_2_df$line[Q2_2_df$label == "Presymptomatic transmission"] <- 3 + asymp_n
+# Q2_2_df_a <- Q2_2_df %>% #order the asymp studies
+#   filter(subgroup == "asymp") %>%
+#   mutate(line = 2:(asymp_n + 1))
+# Q2_2_df_p <- Q2_2_df %>% #order the presymp studies
+#   filter(subgroup == "presymp") %>%
+#   mutate(line = (asymp_n + 4):(presymp_n + asymp_n + 3))
+# Q2_2_df <- Q2_2_df[is.na(Q2_2_df$record_id),]
+# #join all rows again
+# Q2_2_df <- rbind(Q2_2_df, Q2_2_df_a, Q2_2_df_p)
+# 
+# #create forest plot
+# p <- ggplot() + 
+#   geom_point(data = Q2_2_df, #add estimates 
+#              aes(y = line, 
+#                  x = estimate),
+#              fill = "gray", 
+#              shape = 22, 
+#              color = "black",
+#              size = 4) +
+#   geom_errorbarh(data = Q2_2_df, #add error bars 
+#                  aes(y = line, 
+#                      xmin = lower_bound, 
+#                      xmax = upper_bound), 
+#                  height=0.3) +
+#   geom_text(aes(y = c(-1, -1, -1),  #add cols for study, estimates and CIs
+#                 x = c(-0.2, 1.05, 1.12), 
+#                 label=c("Study", "Prop.", "95% CI")), 
+#             hjust = 0, 
+#             fontface = "bold") +
+#   geom_text(data = Q2_2_df, #add estimate labels
+#             aes(y = line, 
+#                 x = 1.05, 
+#                 label = prop), 
+#             hjust = 0) +
+#   geom_text(data = Q2_2_df, #add CI labels
+#             aes(y = line,
+#                 x = 1.12,
+#                 label = CI), 
+#             hjust = 0) +
+#   geom_text(data = Q2_2_df, #add study labels
+#             aes(y= line, 
+#                 x=-0.2, 
+#                 label = label,
+#                 hjust = 0,
+#                 fontface = fontface)) +
+#   theme_void() + #remove background
+#   scale_y_reverse() +
+#   geom_segment(data = Q2_2_df, #add line below point estimates
+#                aes(y = max(line) + 1, x = 0, xend = 1, 
+#                    yend = max(line) + 1)) +
+#   geom_segment(data = Q2_2_df, #add dash for 0
+#                aes(y = max(line) + 1, yend = max(line) + 1.3, 
+#                    x = 0, xend = 0)) +
+#   geom_segment(data = Q2_2_df, #add dash for 0.25
+#                aes(y = max(line) + 1, yend = max(line) + 1.3,
+#                    x = 0.25, xend = 0.25)) +
+#   geom_segment(data = Q2_2_df, #add dash for 0.5
+#                aes(y = max(line)+1, yend=max(line) + 1.3,
+#                    x=0.5, xend=0.5)) +
+#   geom_segment(data = Q2_2_df, #add dash for 0.75
+#                aes(y = max(line) + 1, yend = max(line) + 1.3,
+#                    x=0.75, xend = 0.75)) +
+#   geom_segment(data = Q2_2_df, #add dash for 1
+#                aes(y = max(line) + 1, 
+#                    yend = max(line) + 1.3,
+#                    x = 1, xend = 1)) +
+#   geom_text(aes(y = rep(max(Q2_2_df$line) + 2,5), #add numbers to line
+#                 x = 0:4/4,
+#                 label = c(0, 0.25, 0.5, 0.75, 1))) +
+#   scale_x_continuous(breaks = seq(from = 0, to = 1, by = 0.5))
 

### 2021-10-29 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -119,8 +119,8 @@ p=ggplot()+
   theme(legend.position = "none")
 p
 
-#png(file="forest_ggplotQ3_20200714.png", res=300, height=9, width=25, units="cm")
-pdf(file="Figure4.pdf", height=12/2, width=25/3)
+png(file="forest_ggplotQ3_20200714.png", res=300, height=17, width=20, units="cm")
+#pdf(file="Figure4.pdf", height=12/2, width=25/3)
 p
 dev.off()
 

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

@@
 
+asymptomaticQ2_2 = asymptomaticQ2_2 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
+asymptomaticQ2_2$q3_setting=ifelse(asymptomaticQ2_2$q3_setting=="",NA,asymptomaticQ2_2$q3_setting)
+
+s <- strsplit(asymptomaticQ2_2$q3_setting, split = ";")
+pp_m <- strsplit(asymptomaticQ2_2$q3_pp_m, split = ";")
+pp_l <- strsplit(asymptomaticQ2_2$q3_pp_l, split = ";")
+pp_u <- strsplit(asymptomaticQ2_2$q3_pp_u, split = ";")
+
+dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ2_2$author_1), sapply(pp_m, length)),
+                 Q3set=unlist(s),
+                 p = as.numeric(unlist(pp_m)), 
+                 l = as.numeric(unlist(pp_l)),
+                 h = as.numeric(unlist(pp_u)),
+                 setting="Pre-symptomatic",stringsAsFactors = FALSE)
+
+dfQ3a[dfQ3a==9999]<-NA
+dfQ3a=dfQ3a[!is.na(dfQ3a$p),]
+
+dfQ3b=data.frame(label=paste0("   ",asymptomaticQ2_2$author_1),
+                 Q3set=NA,
+                 p = asymptomaticQ2_2$q3_pa_m, 
+                 l = asymptomaticQ2_2$q3_pa_l,
+                 h = asymptomaticQ2_2$q3_pa_u,
+                 setting="Asymptomatic",stringsAsFactors = FALSE)
+
+dfQ3b[dfQ3b==9999]<-NA
+dfQ3b=dfQ3b[!is.na(dfQ3b$p),]
+
+dfQ3=rbind.data.frame(dfQ3b,dfQ3a, stringsAsFactors = FALSE)
+
+dfQ3$line=1:nrow(dfQ3)
+dfQ3$type=rep(2,nrow(dfQ3))
+
+insertRow <- function(existingDF, newrow, r) {
+  existingDF[seq(r+1,nrow(existingDF)+1),] <- existingDF[seq(r,nrow(existingDF)),]
+  existingDF[r,] <- newrow
+  existingDF
+}
+
+dfQ3=insertRow(dfQ3,c("Asymptomatic transmission",NA,NA,NA,NA,NA,1,1),1)
+
+dfQ3=insertRow(dfQ3,c("Pre-symptomatic transmission",NA,NA,NA,NA,NA,1,1),nrow(dfQ3b)+2)
+dfQ3=insertRow(dfQ3,c(rep(NA,7),1),nrow(dfQ3b)+2)
+dfQ3$line=1:nrow(dfQ3)
+
+dfQ3$p=as.numeric(dfQ3$p)
+dfQ3$l=as.numeric(dfQ3$l)
+dfQ3$h=as.numeric(dfQ3$h)
+
+# dfQ3c<-read.csv(file="Q3.csv", stringsAsFactors = FALSE)
+# dfQ3$p=dfQ3$p/100
+# dfQ3$l=dfQ3$l/100
+# dfQ3$h=dfQ3$h/100
+
+dataG=dfQ3
+
+dig=2
+r<-function(x){format(round(as.numeric(x),2),dig=2)}
+
+dataG$label=ifelse(dataG$type==2,
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+dataG$fontface=ifelse(dataG$type==1, "italic","plain")
+
+dataG$label_studyCI=ifelse(!is.na(dataG$h), paste0("[",r(dataG$l),";",r(dataG$h),"]"),NA)
+dataG$label_study=ifelse(!is.na(dataG$p),r(dataG$p),NA)
+
+p=ggplot()+ 
+  geom_point(data=dataG,aes(y=dataG$line, x=dataG$p),fill="gray", shape=22, color="black",size=4)+
+  geom_errorbarh(data=dataG,aes(y=dataG$line, xmin=dataG$l, xmax=dataG$h), height=0.3)+
+
+  geom_text(aes(y=c(-1,-1,-1), x=c(-2,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+
+
+  geom_text(data=dataG,aes(y=dataG$line, x=1.25, label=label_study), hjust = 0)+
+  geom_text(data=dataG,aes(y=dataG$line, x=1.75, label=label_studyCI), hjust = 0)+
+
+  geom_text(data=dataG,aes(y=dataG$line, x=-2, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
+  #geom_rect(data=dataG,aes(xmin=dataG$Pl,xmax=dataG$Ph,ymin=dataG$line-0.1,ymax=dataG$line+0.1),color="black", fill="red")+
+  theme_void() + 
+  scale_y_reverse()+
+  geom_segment(aes(y=max(dataG$line)+1, x=0, xend=1, yend=max(dataG$line)+1))+
+  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0,xend=0))+
+  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.25,xend=0.25))+
+  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.5,xend=0.5))+
+  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=0.75,xend=0.75))+
+  geom_segment(aes(y=max(dataG$line)+1,yend=max(dataG$line)+1.3,x=1,xend=1))+
+  geom_text(aes(y=rep(max(dataG$line)+2,5),x=0:4/4, label=c(0.00,0.25,0.5,0.75,1.00)))+
+  #geom_segment(data=dataG,aes(x=vlineloc, xend=vlineloc, y=0, yend=max(dataG$line)+1), linetype=3)+
+
+  xlim(c(-2,2.5))+
+  theme(legend.position = "none")
+
+p
+
+#create image file
+png(file="forest_Q2_2.png", 
+    res=300, 
+    height=35, width=42, units="cm")
+p
+dev.off()
+
 ############Old Codes###############
@@
 
-p
-
-#create image file
-png(file="forest_Q2_2.png", 
-    res=300, 
-    height=35, width=42, units="cm")
-p
-dev.off()
-
 ##########################################

### 2021-10-29 Manuscript_draft.Rmd
new run

@@
 
+#create image file
+
 p
 
-#create image file
-png(file="forest_Q2_2.png", 
-    res=300, 
-    height=35, width=42, units="cm")
+png(file="forest_Q2_2.png", res=300, height=17, width=20, units="cm")
+#pdf(file="Figure4.pdf", height=12/2, width=25/3)
 p
 dev.off()
+
+# png(file="forest_Q2_2.png", 
+#     res=300, 
+#     height=35, width=42, units="cm")
+# p
+# dev.off()
 

### 2021-10-29 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -84,7 +84,22 @@ dig=2
 r<-function(x){format(round(as.numeric(x),2),dig=2)}
 
 
-dataG$label=ifelse(dataG$type==2,
+# dataG$label=ifelse(dataG$type==2,
+#                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+dataG$label=ifelse(dataG$label=="   Ganyani T",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+dataG$label=ifelse(dataG$label=="   Peak CM",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+dataG$label=ifelse(dataG$label=="   Tindale LC",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+dataG$label=ifelse(dataG$label=="   Zhang W",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+
+dataG$label=ifelse(dataG$label=="   Casey M",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 
 dataG$fontface=ifelse(dataG$type==1, "italic","plain")

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

@@
 
-dataG$label=ifelse(dataG$type==2,
+# dataG$label=ifelse(dataG$type==2,
+#                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+dataG$label=ifelse(dataG$label=="   Ganyani T",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+dataG$label=ifelse(dataG$label=="   Peak CM",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+dataG$label=ifelse(dataG$label=="   Tindale LC",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+dataG$label=ifelse(dataG$label=="   Zhang W",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+dataG$label=ifelse(dataG$label=="   Casey M",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)

### 2021-10-29 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -97,8 +97,6 @@ dataG$label=ifelse(dataG$label=="   Tindale LC",
 
 dataG$label=ifelse(dataG$label=="   Zhang W",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
-
-
 dataG$label=ifelse(dataG$label=="   Casey M",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 

### 2021-11-02 Q2_2.R
Q2.2 plot for paper

@@ -1,15 +1,21 @@
+
+#download packages
+library(meta)
+library(readxl)
+library(tidyverse)
+library(httr) # use to retrieve data from REDCap
+library(kableExtra)
+library(flextable)
+library(dplyr)
+library(RCurl)
+library(tidyr)
+library(ggplot2)
+library(metafor)
+
 ###############################################################
 # Question 2.2: results output ################################
 # Proportion of transmission from asymp or pre-symp ###########
 ###############################################################
-
-rm(list = ls())
-
-library(RCurl)
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-
 
 # get the data directly from REDCap: 
 # report #157 is Q2.2:
@@ -29,246 +35,133 @@ formData2_2 <- list("token"=token,
 response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
 asymptomaticQ2_2 <- httr::content(response2_2)
 
-#clean data
-asymptomaticQ2_2[asymptomaticQ2_2=="9999;9999"]=NA #indicate as missing
-asymptomaticQ2_2[asymptomaticQ2_2 == "9999"] = NA #indicate as missing
 
-#create a separate dataset for the records with >1 result
-two_models <- asymptomaticQ2_2
-#separate into 2 variables
-two_models = two_models %>% 
-  separate(q3_pp_m, c("q3_pp_m_1","q3_pp_m_2"), ";")
-two_models = two_models %>% 
-  separate(q3_pp_l, c("q3_pp_l_1","q3_pp_l_2"), ";") 
-two_models = two_models %>%
-  separate(q3_pp_u, c("q3_pp_u_1","q3_pp_u_2"), ";")
-two_models = two_models %>% 
-  separate(q3_setting, c("q3_setting_1","q3_setting_2"), ";") 
+asymptomaticQ2_2 = asymptomaticQ2_2 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
+asymptomaticQ2_2$q3_setting=ifelse(asymptomaticQ2_2$q3_setting=="",NA,asymptomaticQ2_2$q3_setting)
 
-two_models <- two_models %>% #change values to numeric
-  mutate(q3_pp_m_1=as.numeric(q3_pp_m_1),
[…]

### 2021-11-03 Q2_2.R
manuscript figs

@@ -11,6 +11,9 @@ library(RCurl)
 library(tidyr)
 library(ggplot2)
 library(metafor)
+library(extrafont)
+loadfonts(device = "win")
+
 
 ###############################################################
 # Question 2.2: results output ################################
@@ -161,7 +164,7 @@ dev.off()
 
 
 tiff(filename = "Q2_2.tiff",
-     width = 2200, height = 2600,
+     width = 1700, height = 1900,
      res = 300)
 p
 dev.off()

### 2021-11-03 LSR-Progress-Report.Rmd
rerun

---
title: "LSR Progress Report"
author: "L Heron"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE, error = TRUE}

library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(kableExtra)

###########################################
#verification set up code
###########################################

url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='159',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)

response <- httr::POST(url, body = formData, encode = "form")
result <- httr::content(response)

ref_asymp2 = result %>% 
  mutate(status2=ifelse((is.na(screen1_veri) & screening_api_complete==1), "Ready to be assigned for verification", NA),
         status2=ifelse((!is.na(screen1_veri) & screening_api_complete==1), "Assigned for verification", status2),
         status2=ifelse((!is.na(screen1_veri) & screening_api_complete==0), "Verified: resolution needed", status2),
         status2=ifelse((!is.na(screen1_veri) & screening_api_complete==2), "Verified: Done", status2))

ref_asymp2 <- ref_asymp2[1874:length(ref_asymp2$record_id),]

tmpveri=ref_asymp2 %>%
  group_by(screen1_veri, status2) %>%
  summarize(n=n())

tmpveri = tmpveri[!is.na(tmpveri$status2), ]

# current number of verified records
verified <- sum(tmpveri[tmpveri$status2=="Verified: Done",]$n)
#total assigned for verification
assigned_veri <- sum(tmpveri[tmpveri$status2=="Assigned for verification",]$n)
#waiting to be assigned
unassigned_veri <- sum(tmpveri[tmpveri$status2=="Ready to be assigned for verification",]$n)
#resolution needed
resolve <- sum(tmpveri[tmpveri$status2=="Verified: resolution needed",]$n)

tmpveri[tmpveri$status2=="Assigned for verification",]
sum(tmpveri[tmpveri$status2=="Assigned for verification",]$n)
tmpveri[tmpveri$status2=="Verified: resolution needed",]
sum(tmpveri[tmpveri$status2=="Ready to be assigned for verification",]$n)
#total needing resolution:
sum(tmpveri[tmpveri$status2=="Verified: resolution needed",]$n)

###########################################
#verification plot
###########################################

veriplot<-ggplot(tmpveri,aes(screen1_veri, n, fill=status2))+
  geom_bar(stat="identity")+
  coord_flip()  +
  scale_fill_manual(values=c("tomato1", "forestgreen", "deepskyblue1", "orchid4")) + 
  xlab("Reviewers") + 
  ylab("Number of records")

###########################################
#screening set up code
###########################################

formData2 <- list("token"=token,
                  content='report',
                  format='csv',
                  report_id='159',
                  csvDelimiter='',
                  rawOrLabel='raw',
                  rawOrLabelHeaders='raw',
                  exportCheckboxLabel='false',
                  returnFormat='csv'
)

response2 <- httr::POST(url, body = formData2, encode = "form")
result2 <- httr::content(response2)

ref_asymp = result2 %>% 
  mutate(status=ifelse((!is.na(screen1_assigned) & !is.na(comment)),"Screening complete",NA),
         status=ifelse((!is.na(screen1_assigned) & is.na(comment)),"Assigned & incomplete",status),
         status=ifelse(is.na(screen1_assigned),"Unassigned",status))
ref_asymp <- ref_asymp[1874:length(ref_asymp$record_id),]

tmp2=ref_asymp %>%
  group_by(screen1_assigned, status) %>%
  summarize(n=n())

#screening plot 
screenplot <- ggplot(tmp2,aes(screen1_assigned, n, fill=status))+
  geom_bar(stat="identity")+ 
  coord_flip() + xlab("Reviewers") + ylab("Number of records")

#assigned and still to screen
assigned_screen <- sum(tmp2[tmp2$status=="Assigned & incomplete",]$n)

#screened up to now
screen_complete <- (sum(tmp2[tmp2$status=="Screening complete",]$n))

#total screened and need to be screened
totaltoscreen <- (sum(tmp2[tmp2$status=="Assigned & incomplete",]$n)+sum(tmp2[tmp2$status=="Screening complete",]$n))+sum(tmp2[tmp2$status=="Unassigned",]$n)
# percentage
fraction <- screen_complete/totaltoscreen
percent <- paste(round(100*fraction), "%", sep="")

###########################################
#overall progress set up code
###########################################

url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='159',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)

response <- httr::POST(url, body = formData, encode = "form")
result <- httr::content(response)

ref_asymp <- result %>% filter(screen1_assigned!="MC_X")

ref_asymp1 = ref_asymp %>%
  mutate(status=ifelse(screen1_assigned=="","New records",NA),
         status=ifelse((screen1_assigned!="" & comment==""),"Assigned",status),
         status=ifelse(((screen1_veri=="" | screen1_veri!="") & screening_api_complete==1), "Screened but not verified", status),
         status=ifelse((screen1_veri!="" & review ==1 & screening_api_complete==2), "Included",status),
         status=ifelse((screen1_veri!="" & review ==2 & screening_api_complete==2), "Excluded", status))

ref_asymp1$status[is.na(ref_asymp1$status)] <- "Help needed"
ref_asymp1 = filter(ref_asymp1, !(status %in% "Help needed"))
tmp0=ref_asymp1 %>% group_by(status) %>%
  summarize(n=n())
pre=tmp0[tmp0$status=="Screened but not verified",]$n

ref_asymp1$status[ref_asymp1$status == "Assigned" | ref_asymp1$status == "Screened but not verified"] <- "Records in screening"
ref_asymp1$status <- factor(ref_asymp1$status, levels = c("Included","Excluded","Records in screening","New records"))

p1<-ggplot(ref_asymp1,aes(x=1,fill=factor(ref_asymp1$status)))+
  geom_bar()+
  coord_flip()+
  scale_fill_manual(name="",breaks=c("New records", "Records in screening","Excluded","Included"),values=c("orange","yellow2","steelblue3","green3"))+
  ylab("Number of citations")+
  guides(fill=guide_legend(ncol=2,nrow=2,byrow=TRUE)) +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        #panel.border = element_blank(),
        #panel.grid.major = element_blank(),
        #panel.grid.minor = element_blank(),
        legend.position = "bottom",legend.spacing.x = unit(0.5,"cm"),
        plot.margin = margin(5,.5,2,.4, "cm"))

tmp1=ref_asymp1 %>% group_by(status) %>%
  summarize(n=n())

#Assigned and incomplete:
#pub=tmp1[tmp1$status=="Assigned",]$n
include=tmp1[tmp1$status=="Included",]$n[1]
exclude=tmp1[tmp1$status=="Excluded",]$n[1]
#veri=include+exclude
screened=pre+include+exclude
screeninprogress=tmp1[tmp1$status=="Records in screening",]$n[1]

text=paste0("From June 10th until ", format(Sys.Date(),"%d.%m.%Y"), ",\nthe search strategy has\nretrieved ",length(ref_asymp$record_id)," results.\n\n* ",
            screeninprogress, " records in screening\n* ", exclude," excluded\n* ",
            include, " included")

#total complete and still to be screened
total <- sum(tmp1[tmp1$status=="Included",]$n)+sum(tmp1[tmp1$status=="Excluded",]$n)+sum(tmp1[tmp1$status=="Records in screening",]$n)
#number included
included <-sum(tmp1[tmp1$status=="Included",]$n)
#number excluded
excluded <- sum(tmp1[tmp1$status=="Excluded",]$n)
#number still in the screening process
screening <- total - (included + excluded)
#number yet to be assigned
unassigned <- sum(tmp2[tmp2$status=="Unassigned",]$n)

###progress table###

#The last record we will consider including in the latest update is record #5296 
#(cut off being 31st Jan (date records entered COAP database))
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(kableExtra)

url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData2 <- list("token"=token,
                  content='report',
                  format='csv',
                  report_id='159',
                  csvDelimiter='',
                  rawOrLabel='raw',
                  rawOrLabelHeaders='raw',
                  exportCheckboxLabel='false',
                  returnFormat='csv'
)
response2 <- httr::POST(url, body = formData2, encode = "form")
result2 <- httr::content(response2)

ref_asymp = result2 %>% 
  mutate(status=ifelse((!is.na(screen1_assigned) & !is.na(comment)),"Screening complete",NA),
         status=ifelse((!is.na(screen1_assigned) & is.na(comment)),"Assigned & incomplete",status),
         status=ifelse(is.na(screen1_assigned),"Unassigned",status))
ref_asymp <- ref_asymp[1874:length(ref_asymp$record_id),]
#31 Jan is #5296, 28 Feb is 5856, 31 Mar is 6535, 30 Apr is 7176, 31 May is 7713, 30 Jun is 8332, 31 Jul is 8959
ref_asymp_latest <- ref_asymp %>%
  filter(record_id < 7025) #filter to last record that would be included
until_Jan31 <- ref_asymp %>%
  filter(record_id <= 5296) #filter to last record that would be included
until_Feb28 <- ref_asymp %>%
  filter(record_id <= 5856) #filter to last record that would be included
until_Mar31 <- ref_asymp %>%
  filter(record_id <= 6535) #filter to last record that would be included
until_Apr30 <- ref_asymp %>%
  filter(record_id <= 7176) #filter to last record that would be included
until_May31 <- ref_asymp %>%
  filter(record_id <= 7713) #filter to last record that would be included
until_Jun30 <- ref_asymp %>%
  filter(record_id <= 8332) #filter to last record that would be included
until_Jul31 <- ref_asymp %>%
  filter(record_id <= 8959) #filter to last record that would be included
until_Aug31 <- ref_asymp %>%
  filter(record_id <= 9483) #filter to last record that would be included
until_Sep30 <- ref_asymp %>%
  filter(record_id <= 10074) #filter to last record that would be included
until_Oct05 <- ref_asymp %>%
  filter(record_id <= 10154) #filter to last record that would be included

#create df
progress <- data.frame(search_date = c("Jan 31", "Feb 28", "31 Mar", "30 Apr", "31 May", "30 Jun", "31 Jul", "31 Aug", "30 Sep", "5 Oct"),
                       redcap_id = c(5296, 5856, 6535, 7176, 7713, 8332, 8959, 9483, 10074, 10154),
                       included = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA),
                       screening = c(nrow(until_Jan31[until_Jan31$status == "Assigned & incomplete",]), 
                                     nrow(until_Feb28[until_Feb28$status == "Assigned & incomplete",]),
                                     nrow(until_Mar31[until_Mar31$status == "Assigned & incomplete",]),
                                     nrow(until_Apr30[until_Apr30$status == "Assigned & incomplete",]),
                                     nrow(until_May31[until_May31$status == "Assigned & incomplete",]),
                                     nrow(until_Jun30[until_Jun30$status == "Assigned & incomplete",]),
                                     nrow(until_Jul31[until_Jul31$status == "Assigned & incomplete",]),
                                     nrow(until_Aug31[until_Aug31$status == "Assigned & incomplete",]),
                                     nrow(until_Sep30[until_Sep30$status == "Assigned & incomplete",]),
                                     nrow(until_Oct05[until_Oct05$status == "Assigned & incomplete",])), 
                       verification = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA),
                       disagreements = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA),
                       data_extraction = c(NA, NA, NA, NA, NA, NA, NA, NA, NA, NA))

#until_Jan31 <- ref_asymp %>%
# filter(record_id <= 5296) #filter to last record that would be included
#until_Feb28 <- ref_asymp %>%
#  filter(record_id <= 5856) #filter to last record that would be included
#until_Mar31 <- ref_asymp %>%
#  filter(record_id <= 6535) #filter to last record that would be included
#until_Apr30 <- ref_asymp %>%
#  filter(record_id <= 7176) #filter to last record that would be included
#until_May31 <- ref_asymp %>%
#  filter(record_id <= 7713) #filter to last record that would be included
#until_Jun30 <- ref_asymp %>%
#  filter(record_id <= 8332) #filter to last record that would be included
#until_Jul31 <- ref_asymp %>%
#  filter(record_id <= 8959)

until_Jan31 <- until_Jan31 %>% group_by(screen1_assigned, status) %>% summarize(n=n())  
until_Feb28 <- until_Feb28 %>% group_by(screen1_assigned, status) %>% summarize(n=n())  
until_Mar31 <- until_Mar31 %>% group_by(screen1_assigned, status) %>% summarize(n=n())  
until_Apr30 <- until_Apr30 %>% group_by(screen1_assigned, status) %>% summarize(n=n())  
until_May31 <- until_May31 %>% group_by(screen1_assigned, status) %>% summarize(n=n())  
until_Jun30 <- until_Jun30 %>% group_by(screen1_assigned, status) %>% summarize(n=n())  
until_Jul31 <- until_Jul31 %>% group_by(screen1_assigned, status) %>% summarize(n=n())
until_Aug31 <- until_Aug31 %>% group_by(screen1_assigned, status) %>% summarize(n=n())
until_Sep30 <- until_Sep30 %>% group_by(screen1_assigned, status) %>% summarize(n=n())
until_Oct05 <- until_Oct05 %>% group_by(screen1_assigned, status) %>% summarize(n=n())

#verification status

ref_asymp2 = result2 %>% 
  mutate(status2=ifelse((is.na(screen1_veri) & screening_api_complete==1), "Ready to be assigned for verification", NA),
         status2=ifelse((!is.na(screen1_veri) & screening_api_complete==1), "Assigned for verification", status2),
         status2=ifelse((!is.na(screen1_veri) & screening_api_complete==0), "Verified: resolution needed", status2),
         status2=ifelse((!is.na(screen1_veri) & screening_api_complete==2), "Verified: Done", status2))
ref_asymp2 <- ref_asymp2[1874:length(ref_asymp2$record_id),]

until_Jan31_veri <- ref_asymp2 %>%
  filter(record_id <= 5296) #filter to last record that would be included
until_Feb28_veri <- ref_asymp2 %>%
  filter(record_id <= 5856) #filter to last record that would be included
until_Mar31_veri <- ref_asymp2 %>%
  filter(record_id <= 6535) #filter to last record that would be included
until_Apr30_veri <- ref_asymp2 %>%
  filter(record_id <= 7176) #filter to last record that would be included
until_May31_veri <- ref_asymp2 %>%
  filter(record_id <= 7713) #filter to last record that would be included
until_Jun30_veri <- ref_asymp2 %>%
  filter(record_id <= 8332) #filter to last record that would be included
until_Jul31_veri <- ref_asymp2 %>%
  filter(record_id <= 8959)
until_Aug31_veri <- ref_asymp2 %>%
  filter(record_id <= 9483)
until_Sep30_veri <- ref_asymp2 %>%
  filter(record_id <= 10074)
until_Oct05_veri <- ref_asymp2 %>%
  filter(record_id <= 10154)

veri_jan31 <- nrow(until_Jan31_veri[until_Jan31_veri$status2 == "Ready to be assigned for verification" | 
                                    until_Jan31_veri$status2 == "Assigned for verification",])
veri_feb28 <- nrow(until_Feb28_veri[until_Feb28_veri$status2 == "Ready to be assigned for verification" | 
                                      until_Feb28_veri$status2 == "Assigned for verification",])
veri_mar30 <- nrow(until_Mar31_veri[until_Mar31_veri$status2 == "Ready to be assigned for verification" | 
                                      until_Mar31_veri$status2 == "Assigned for verification",])
veri_apr30 <- nrow(until_Apr30_veri[until_Apr30_veri$status2 == "Ready to be assigned for verification" | 
                                      until_Apr30_veri$status2 == "Assigned for verification",])
veri_may30 <- nrow(until_May31_veri[until_May31_veri$status2 == "Ready to be assigned for verification" | 
                                      until_May31_veri$status2 == "Assigned for verification",])
veri_jun30 <- nrow(until_Jun30_veri[until_Jun30_veri$status2 == "Ready to be assigned for verification" | 
                                      until_Jun30_veri$status2 == "Assigned for verification",])
veri_jul31 <- nrow(until_Jul31_veri[until_Jul31_veri$status2 == "Ready to be assigned for verification" | 
                                      until_Jul31_veri$status2 == "Assigned for verification",])
veri_aug31 <- nrow(until_Aug31_veri[until_Aug31_veri$status2 == "Ready to be assigned for verification" | 
                                      until_Aug31_veri$status2 == "Assigned for verification",])
veri_sep30 <- nrow(until_Sep30_veri[until_Sep30_veri$status2 == "Ready to be assigned for verification" | 
                                      until_Sep30_veri$status2 == "Assigned for verification",])
veri_oct05 <- nrow(until_Oct05_veri[until_Oct05_veri$status2 == "Ready to be assigned for verification" | 
                                      until_Oct05_veri$status2 == "Assigned for verification",])

progress$verification = c(veri_jan31, veri_feb28, veri_mar30, veri_apr30, veri_may30, veri_jun30, veri_jul31, veri_aug31, veri_sep30, veri_oct05)

progress$disagreements = c(nrow(until_Jan31_veri[until_Jan31_veri$status2 == "Verified: resolution needed",]), 
                           nrow(until_Feb28_veri[until_Feb28_veri$status2 == "Verified: resolution needed",]),
                           nrow(until_Mar31_veri[until_Mar31_veri$status2 == "Verified: resolution needed",]),
                           nrow(until_Apr30_veri[until_Apr30_veri$status2 == "Verified: resolution needed",]),
                           nrow(until_May31_veri[until_May31_veri$status2 == "Verified: resolution needed",]),
                           nrow(until_Jun30_veri[until_Jun30_veri$status2 == "Verified: resolution needed",]),
                           nrow(until_Jul31_veri[until_Jul31_veri$status2 == "Verified: resolution needed",]),
                           nrow(until_Aug31_veri[until_Aug31_veri$status2 == "Verified: resolution needed",]),
                           nrow(until_Sep30_veri[until_Sep30_veri$status2 == "Verified: resolution needed",]),
                           nrow(until_Oct05_veri[until_Oct05_veri$status2 == "Verified: resolution needed",]))

url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData2 <- list("token"=token,
                  content='report',
                  format='csv',
                  report_id='163',
                  csvDelimiter='',
                  rawOrLabel='raw',
                  rawOrLabelHeaders='raw',
                  exportCheckboxLabel='false',
                  returnFormat='csv'
)
response3 <- httr::POST(url, body = formData2, encode = "form")
included <- httr::content(response3)
nrow(included)

progress$included <- c(nrow(filter(included, record_id <= 5296)),
                       nrow(filter(included, record_id <= 5856)),
                       nrow(filter(included, record_id <= 6535)),
                       nrow(filter(included, record_id <= 7176)),
                       nrow(filter(included, record_id <= 7713)),
                       nrow(filter(included, record_id <= 8332)),
                       nrow(filter(included, record_id <= 8959)),
                       nrow(filter(included, record_id <= 9483)),
                       nrow(filter(included, record_id <= 10074)),
                       nrow(filter(included, record_id <= 10154)))

ext_jan <- sum(nrow(filter(included, record_id <= 5296 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 5296 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 5296 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_feb <- sum(nrow(filter(included, record_id <= 5856 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 5856 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 5856 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_mar <- sum(nrow(filter(included, record_id <= 6535 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 6535 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 6535 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_apr <- sum(nrow(filter(included, record_id <= 7176 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 7176 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 7176 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_may <- sum(nrow(filter(included, record_id <= 7713 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 7713 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 7713 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_jun <- sum(nrow(filter(included, record_id <= 8332 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 8332 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 8332 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_jul <- sum(nrow(filter(included, record_id <= 8959 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 8959 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 8959 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_aug <- sum(nrow(filter(included, record_id <= 9483 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 9483 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 9483 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_sep <- sum(nrow(filter(included, record_id <= 10074 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 10074 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 10074 & (quest___5 == 1 & question_3_complete != 2)))) 
ext_oct <- sum(nrow(filter(included, record_id <= 10154 & (quest___1 == 1 & question_1_complete != 2))),
               nrow(filter(included, record_id <= 10154 & (quest___2 == 1 & question_2_complete != 2))),
               nrow(filter(included, record_id <= 10154 & (quest___5 == 1 & question_3_complete != 2))))

progress$data_extraction <- c(ext_jan, ext_feb, ext_mar, ext_apr, ext_may, ext_jun, ext_jul, ext_aug, ext_sep, ext_oct)

```

## Screening progress

Since June 2020 we have screened **`r screen_complete`** records out of a total **`r totaltoscreen`** records identified in our search (**`r percent`**).

There are **`r unassigned`** records that have not yet been assigned for screening.

The following reviewer(s) have been assigned a total of **`r assigned_screen`** records:

```{r screen_table, echo=FALSE}
tmp2 %>%
  arrange(status) %>%
  kbl() %>%
  kable_material(c("striped", "hover"))
```

```{r screenplot, echo=FALSE}
screenplot
```

## Verification progress

We have verified **`r verified`** records in total.

**`r unassigned_veri`** records are waiting to be assigned for verification.

**`r resolve`** disagreements need to be resolved.

The following reviewer(s) have been assigned a total of **`r assigned_veri`** records:

```{r veri_table, echo=FALSE}
tmpveri %>%
  arrange(status2) %>%
  kbl() %>%
  kable_material(c("striped", "hover"))
```

```{r veriplot, echo=FALSE}
veriplot
```

## Overall progress with review

The following table gives an overview of our progress with each month's search results.

The numbers for screening, verification, disagreements, and data extraction indicate the records remaining.

Please note that as records in each stage are complete, more records will move to the next stage, i.e., once a disagreement is resolved, a record will be ready for extraction.

```{r progress_table, echo=FALSE}
progress %>%
  kbl() %>%
  kable_material(c("striped", "hover"))
```

### 2021-11-03 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -100,6 +100,9 @@ dataG$label=ifelse(dataG$label=="   Zhang W",
 dataG$label=ifelse(dataG$label=="   Casey M",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 
+dataG$label=ifelse(dataG$label== "   Moghadas SM",
+                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
 dataG$fontface=ifelse(dataG$type==1, "italic","plain")
 
 dataG$label_studyCI=ifelse(!is.na(dataG$h), paste0("[",r(dataG$l),";",r(dataG$h),"]"),NA)

### 2021-11-04 Q1_table_characteristics_full.Rmd
S1 table

--- 2021-10-08 Asymptomatic_LSR_Supplement.Rmd
@@
 ---
-title: "Supporting Information"
-author: "Diana Buitrago-Garcia, Aziz Mert Ipekci, Leonie Heron, Stefanie Hossmann, Hira Imeri, Georgia Salanti, Nicola Low"
-date: "`r format(Sys.time(), '%d/%m/%y')`"
+title: "Q1 table"
+author: "L Heron"
+date: "10/29/2021"
 output: 
-  html_document:
-  toc: true
-  toc_float: true
-  theme: united
-  highlight: tango
-  #always_allow_html: true
+  word_document:
+  always_allow_html: true
 ---
@@
 #author column
-Q1_table$study <- paste0(Q1_table$author_1, " (", Q1_table$year, ")")
+Q1_table$study <- Q1_table$author_1
 Q1_table$author_1 <- NULL
 Q1_table$record_id <- NULL
-Q1_table$year <- NULL
 
@@
 Q1_table$q1_age_median <- NULL
+#remove age range variables 
+Q1_table <- Q1_table %>%
+  select(-contains("agerange"))
 
@@
 
-Q1_table <- Q1_table[, c(1, 3, 2, 4, 5, 6, 7, 8)]
-
-# Prepare the data
-# get the data directly from redcap:
-# report #155 is Q1:
-url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
-formData <- list("token"=token,
-                 content='report',
-                 format='csv',
-                 report_id='155',
-                 csvDelimiter='',
-                 rawOrLabel='raw',
-                 rawOrLabelHeaders='raw',
-                 exportCheckboxLabel='false',
-                 returnFormat='csv'
-)
-response <- httr::POST(url, body = formData, encode = "form")
-asymptomaticQ1_pub <- httr::content(response)
-
-settings=c("Contact investigation",
-           "Contact investigation, aggregated",
-           "Outbreak investigation",
-           "Statistical model",
-           "Screening",
-           "Hospitalised adults",
-           "Hospitalised children",
-           "Hospitalised adults & children")
-
-asymptomaticQ1_pub$setting2<-factor(asymptomaticQ1_pub$setting2, levels=1:8, labels=settings)
-#combine contact investigation and contact investigation aggregated
-asymptomaticQ1_pub$setting2[asymptomaticQ1_pub$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"
-
-# minor cleaning
-asymptomaticQ1_pub[asymptomaticQ1_pub==9999]=NA
-
-asymptomaticQ1_pub$setting=asymptomaticQ1_pub$setting2
-
-#remove preprints at time of search
-asymptomaticQ1_pub <- asymptomaticQ1_pub %>%
-  filter(source != 1 & source != 2)
-
-data_long1_pub <- gather(asymptomaticQ1_pub, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
-  mutate(id=1:nrow(.)) %>%
-  select(record_id, author_1, setting, total, id, cluster)
-data_long2_pub <-gather(asymptomaticQ1_pub, cluster, events, c(q1_c1_event,q1_c2_event,q1_c3_event), factor_key=TRUE) %>% 
-  mutate(id=1:nrow(.)) %>%
-  select(events, id)
-
-data_Q1_pub = merge(data_long1_pub, data_long2_pub, by="id")
-data_Q1_pub = data_Q1_pub[!is.na(data_Q1_pub$total),]
-data_Q1_pub$cluster=factor(data_Q1_pub$cluster,labels=c("1","2","3"),levels=c("q1_c1_total","q1_c2_total","q1_c3_total"))
-
-data_Q1_pub[data_Q1_pub$record_id %in% asymptomaticQ1_pub[is.na(asymptomaticQ1_pub$q1_c2_event),]$record_id,]$cluster=NA
-
-asymptomaticQ1_pub=data_Q1_pub
-
-asymptomaticQ1_pub$label=paste0("#", asymptomaticQ1_pub$record_id, " ", asymptomaticQ1_pub$author_1, " (2020)",ifelse(!is.na(asymptomaticQ1_pub$cluster),paste0(" cluster:",asymptomaticQ1_pub$cluster),"")) # [FU: ",asymptomaticQ1$fup_median,"]")
-
-asymptomaticQ1_pub$label=paste0("#", asymptomaticQ1_pub$record_id, " ", asymptomaticQ1_pub$author_1,ifelse(!is.na(asymptomaticQ1_pub$cluster),paste0(" [cluster:",asymptomaticQ1_pub$cluster,"]"),"")) # [FU: ",asymptomaticQ1$fup_median,"]")
-
-#change clusters to descriptions
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4479 Harada [cluster:1]"] <- "#4479 Harada [Patients]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4479 Harada [cluster:2]"] <- "#4479 Harada [Healthcare workers]"
-#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor []" #clarify
-#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor []"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2892 Kennelly [cluster:1]"] <- "#2892 Kennelly [Nursing home residents]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2802 Bender [cluster:1]"] <- "#2802 Bender [Hospital 1]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2802 Bender [cluster:2]"] <- "#2802 Bender [Hospital 2]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4968 van Buul [cluster:2]"] <- "#4968 van Buul [Healthcare workers]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#5273 Theuring [cluster:1]"] <- "#5273 Theuring [School students and staff]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"
-
-data_pub=asymptomaticQ1_pub[order(asymptomaticQ1_pub$setting,1/(1/asymptomaticQ1_pub$events+1/(asymptomaticQ1_pub$total-asymptomaticQ1_pub$events))),]
-
-data_pub[is.na(data_pub$setting),]$record_id
-data_pub=data_pub[!is.na(data_pub$setting),]
-
-asym_plot<-metaprop(events,total,data=data_pub,sm = "PLOGIT", studlab=label, 
-                    byvar=setting,# tau.common =TRUE,
-                    prediction = TRUE,
-                    control=list(stepadj=0.05, maxiter=10000))#, method ="INV") #, verbose=TRUE, digits=5, control=list(stepadj=0.5))
-
-asym_plot
-
-png(file = 'forest_meta_Q1_published.png',width = 30,height = 60, res=600, units="cm")
-
-forest(asym_plot,  col.square=data_pub$setting, sortvar = 1/seTE,
-       #squaresize = 1/(1/data$events+1/(data$total-data$events)),
-       #sortvar = 1/(1/events+1/(total-events)), 
-       subgroup=TRUE, 
-       just.studlab="left", colgap.studlab="2cm",
-       #leftcols = c("label", "setting", "age", "design", "asym_denom"),
-       #leftcols=c("studlab", "record_id", "event", "n"),
-       xlab = "",just="left",comb.random=TRUE,test.subgroup.random=FALSE,
-       comb.fixed=FALSE,test.subgroup.fixed=FALSE, predict=T)#, study.results=TRUE,test.subgroup=TRUE)
-dev.off()
-
-###############################################################
-# Countries included in Q1                           ##########
-###############################################################
-
-library(dplyr)
-Q1_table_countries <- httr::content(response)
-
-#censor until 5296 (31 Jan) plus the published versions of preprints
-pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
-
-Q1_table_countries <- Q1_table_countries %>%
-  filter(record_id %in%  pub_preprints | record_id <= 5296)
-
-#clean countries
-Q1_table_countries <- Q1_table_countries %>%
-  mutate(country = ifelse(country == 10, "Australia", country),
-         country = ifelse(country == 11, "Austria", country),
-         country = ifelse(country == 15, "Bahrain", country),
-         country = ifelse(country == 19, "Belgium", country),
-         country = ifelse(country == 27, "Brazil", country),
-         country = ifelse(country == 28, "Brunei", country),
-         country = ifelse(country == 34, "Canada", country),
-         country = ifelse(country == 40, "China", country),
-         country = ifelse(country == 41, "Colombia", country),
-         country = ifelse(country == 51, "Denmark", country),
-         country = ifelse(country == 62, "France", country),
-         country = ifelse(country == 63, "French Guyana", country),
-         country = ifelse(country == 67, "Germany", country),
-         country = ifelse(country == 69, "Greece", country),
-         country = ifelse(country == 78, "Iceland", country),
-         country = ifelse(country == 79, "India", country),
-         country = ifelse(country == 83, "Ireland", country),
-         country = ifelse(country == 85, "Italy", country),
-         country = ifelse(country == 87, "Japan", country),
-         country = ifelse(country == 92, "Kuwait", country),
-         country = ifelse(country == 105, "Malaysia", country),
-         country = ifelse(country == 121, "Netherlands", country),
-         country = ifelse(country == 128, "Norway", country),
-         country = ifelse(country == 130, "Pakistan", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 138, "Portugal", country),
-         country = ifelse(country == 146, "Saudi Arabia", country),
-         country = ifelse(country == 157, "South Korea", country),
-         country = ifelse(country == 160, "Spain", country),
-         country = ifelse(country == 174, "Turkey", country),
-         country = ifelse(country == 176, "Uganda", country),
-         country = ifelse(country == 180, "United Kingdom", country),
-         country = ifelse(country == 181, "United States of America", country),
-         country = ifelse(country == 185, "Vietnam", country))
-
-#clean case numbers
-#total SARS-CoV-2 n
-Q1_table_countries$q1_c1_total[is.na(Q1_table_countries$q1_c1_total)] <- 0
-Q1_table_countries$q1_c2_total[is.na(Q1_table_countries$q1_c2_total)] <- 0
-Q1_table_countries$q1_c1_event[is.na(Q1_table_countries$q1_c1_event)] <- 0
-Q1_table_countries$q1_c2_event[is.na(Q1_table_countries$q1_c2_event)] <- 0
-
-Q1_table_countries$total_SARS_n <- Q1_table_countries$q1_c1_total + Q1_table_countries$q1_c2_total
-Q1_table_countries$asymp_SARS_n <- Q1_table_countries$q1_c1_event + Q1_table_countries$q1_c2_event
-
-#remove unnecessary cols
-Q1_table_countries <- Q1_table_countries %>%
-  select(country, total_SARS_n, asymp_SARS_n)
-
-#group by countries to calculate n, total cases, total asymp cases
-Q1_table_countries <- Q1_table_countries %>%
-  group_by(country) %>%
-  summarise(total_SARS = sum(total_SARS_n),
-            total_asymp_SARS = sum(asymp_SARS_n),
-            n = n())
-
-#arrange by number of studies
-Q1_table_countries <- Q1_table_countries %>%
-  arrange(desc(n))
-#create PRISMA 2020 flowchart
-
-#download packages
-library(devtools)
-library(dplyr)
-install_github("nealhaddaway/PRISMA2020")
-
-#create df from example csv file
-PRISMA <- read.csv("PRISMA.csv")
-
-#set the REDCap IDs
-#last REDCap ID in previous version
-last_ID_prev <- 1000
-#last REDCap ID in current version
-last_ID_current <- 5296
-#load all records in redcap
-
-# get the data directly from redcap:
-url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
-formData <- list("token"=token,
-                 content='report',
-                 format='csv',
-                 report_id='158',
-                 csvDelimiter='',
-                 rawOrLabel='raw',
-                 rawOrLabelHeaders='raw',
-                 exportCheckboxLabel='false',
-                 returnFormat='csv'
-)
-response_all <- httr::POST(url, body = formData, encode = "form")
-all_records <- httr::content(response_all)
-
-#find number of studies identified in databases since previous update
-current_records <- all_records[last_ID_prev:last_ID_current, ]
-PRISMA$n[PRISMA$data == "database_results"] <- nrow(current_records[!is.na(current_records$record_id), ]) - 1 #1 was added manually 9484
-
-#find number included in review
-PRISMA$n[PRISMA$data == "new_studies"] <- nrow(current_records %>% filter(review == 1))
-
-#find number of duplicates removed before screening
-PRISMA$n[PRISMA$data == "duplicates"] <- nrow(current_records %>% filter(ex_reas == 14))
-#find number of records screening
-PRISMA$n[PRISMA$data == "records_screened"] <- nrow(current_records) - 
-  nrow(current_records %>% filter(ex_reas == 14))
-#add number of studies found via other methods 
-#1 study #9484 was added manually - it's the published v of a preprint
-#as a result, I need to minus 1 record from the database result
-PRISMA$n[PRISMA$box == "othstud"] <- 1
-
-#find number of records excluded from title and abstract
-PRISMA$n[PRISMA$data == "records_excluded"] <- nrow(current_records %>% filter(ex_reas == 1))
-check <- current_records %>% filter(ex_reas == 1)
-#current records left after title and abstract screening
-full_text_screen <- current_records %>% filter(ex_reas != 14 & ex_reas != 1)
-
-#find number of full texts retrieved
-PRISMA$n[PRISMA$data == "dbr_sought_reports"] <- nrow(current_records) - 
-  (nrow(current_records %>% filter(ex_reas == 14)) + 
-  nrow(current_records %>% filter(ex_reas == 1)))
-
-#find number of full texts screened
-PRISMA$n[PRISMA$data == "dbr_assessed"] <- nrow(current_records) - 
-  (nrow(current_records %>% filter(ex_reas == 14)) + 
-     nrow(current_records %>% filter(ex_reas == 1)))
-
-#find number included in previous version
-prev_records <- all_records[1:last_ID_prev, ]
-PRISMA$n[PRISMA$data == "previous_studies"] <- nrow(prev_records[prev_records$review == 1, ])
-
-#calculate total studies included
-PRISMA$n[PRISMA$data == "total_studies"] <- nrow(prev_records[prev_records$review == 1, ]) +
-  nrow(current_records[current_records$review == 1, ])
-
-# studies excluded
-excl_11 <-  nrow(current_records %>% filter(ex_reas == 11))
-excl_12 <-  nrow(current_records %>% filter(ex_reas == 12))
-excl_13 <-  nrow(current_records %>% filter(ex_reas == 13))
-excl_15 <-  nrow(current_records %>% filter(ex_reas == 15))
-excl_16 <-  nrow(current_records %>% filter(ex_reas == 16))
-excl_17 <-  nrow(current_records %>% filter(ex_reas == 17))
-excl_19 <-  nrow(current_records %>% filter(ex_reas == 19))
-excl_20 <-  nrow(current_records %>% filter(ex_reas == 20))
-excl_21 <-  nrow(current_records %>% filter(ex_reas == 21))
-excl_18 <-  nrow(current_records %>% filter(ex_reas == 18))
-
-excl_reasons <- paste0("Publication not on COVID-19, ", excl_11, 
-                       "; No original data, ", excl_12, 
-                       "; Data included in other publication, ", excl_13, 
-                       "; Insufficient extractable data, ", excl_15, 
-                       "; Study design inappropriate, ", excl_16, 
-                       "; No PCR/serological test, ", excl_17, 
-                       "; Math. model not in review scope, ", excl_19, 
-                       "; Inadequate follow-up time, ", excl_20, 
-                       "; Preprint of published article, ", excl_21, 
-                       "; Other, ", excl_18)
-excl_reasons
-PRISMA$n[PRISMA$data == "dbr_excluded"] <- excl_reasons
-
-#fix some text in the flowchart data
-PRISMA$boxtext[PRISMA$data == "identification"] <- "Identification"
-PRISMA$boxtext[PRISMA$box == "prevstud"] <- "Previous studies"
-
-#read data
-flowchart <- PRISMA2020::PRISMA_data(PRISMA)
-flowchart
-#generate flowchart
-PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
-flowchart_plot <- PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
-
-PRISMA2020::PRISMA_save(flowchart_plot, filename = "PRISMA2020_flowdiagram.png", filetype = "png", overwrite = TRUE)
-
+Q1_table <- Q1_table[, c(1, 4, 2, 3, 5, 6, 7, 8)]
 ```
@@
   set_header_labels(setting = "Setting",
-                    location = "Country, region", 
+                    location = "Location", 
+                    year = "Year"
                     study = "Study",
@@
 ```
-
-## PRISMA 2020 Checklist
-*Shiny app can be used to complete checklist here:* <https://prisma.shinyapps.io/checklist/>
-
-***
-
-## Search strings
-
-From: Living Evidence on COVID-19 (<https://ispmbern.github.io/covid-19/living-review/collectingdata.html>, accessed 31.01.2021)
-
-We retrieve data from [EMBASE](http://www.embase.com/) via OVID, [MEDLINE](https://www.ncbi.nlm.nih.gov/pubmed/) via PubMed, BioRxiv and MedRxiv.
-
-**Search terms**
-
-When searches are updated, references that are identified that were not in the database before, are inserted by date (**date_entrez**) they were indexed in remote database, the date they are inserted in OUR database is formatted as the ‘**strategydate**’ (raw data is available [here](https://github.com/leonieheron/LSRworkflow>)).
-
-**30.10.2020**
-
-EMBASE:
-
-(exp SARS-related coronavirus/ or severe acute respiratory syndrome/ or coronavirus disease 2019/ or (coronavir* or corona virus* or HCoV* or ncov* or 2019 cov or covid or covid19 or sars-cov* or sarscov* or sars-coronavirus* or Severe Acute Respiratory Syndrome Coronavirus* or nCoV).mp.) and 20191101:20301231.(dc).
-
-MEDLINE:
-
-("severe acute respiratory syndrome coronavirus 2"[Supplementary Concept] OR "COVID-19" [Supplementary Concept] OR "coronavirus" OR "corona virus" OR "HCoV" OR "nCoV" OR "2019 CoV" OR "covid" OR "covid19" OR "Severe Acute Respiratory Syndrome Coronavirus 2" OR "SARS-CoV2" OR "SARS-CoV 2" OR "SARS Coronavirus 2") AND (2019/11/01:3000/12/31[PDAT])
-
-**01.05.2021**
-
-EMBASE:
-
-(SARS coronavirus/ or middle east respiratory syndrome/ or severe acute respiratory syndrome/ or (coronavirus* or corona virus* or HCoV* or ncov* or covid or covid19 or sars-cov* or sarscov* or Sars-coronavirus* or Severe Acute Respiratory Syndrome Coronavirus*).mp.) and 20191201:20301231.(dc).
-
-**29.04.2020**
-
-MEDLINE:
-
-("coronavirus"[MH] OR "coronavirus infections"[MH] OR "coronavirus"[TW] OR "corona virus"[TW] OR "HCoV"[TW] OR "nCov"[TW] OR "covid"[TW] OR "covid19"[TW] OR "Severe Acute Respiratory Syndrome Coronavirus 2"[TW] OR "SARS-CoV2"[TW] OR "SARS-CoV 2"[TW] OR "SARS Coronavirus 2"[TW] OR "MERS- CoV"[TW]) AND (2019/1/1:3000[PDAT])
-
-**01.04.2020**
-
-From 01.04.2020, we retrieve the [BioRxiv/MedRxiv dataset](https://connect.medrxiv.org/relate/content/181).
-
-**26.03.2020**
-
-MEDLINE:
-
-("Wuhan coronavirus" [Supplementary Concept] OR "COVID-19" OR SARS-CoV-2 OR "2019 ncov"[tiab] OR (("novel coronavirus"[tiab] OR "new coronavirus"[tiab]) AND (wuhan[tiab] OR 2019[tiab])) OR 2019-nCoV[All Fields] OR (wuhan[tiab] AND coronavirus[tiab]))
-
-EMBASE:
-
-(nCoV or 2019-nCoV or ((new or novel or wuhan) adj3 coronavirus) or covid19 or covid-19 or SARS-CoV-2).mp.
-
-BioRxiv/MedRxiv:
-
-ncov or corona or wuhan or COVID or SARS-CoV-2
-
-With the kind support of the [Public Health & Primary Care Library PHC](https://www.unibe.ch/university/services/university_library/faculty_libraries/medicine/public_health_amp_primary_care_library_phc/index_eng.html), and following guidance of the [Medical Library Association](https://www.mlanet.org/p/cm/ld/fid%3D1713)
-
-**01.01.2020**
-
-MEDLINE:
-
-("Wuhan coronavirus" [Supplementary Concept] OR "COVID-19" OR "2019 ncov"[tiab] OR (("novel coronavirus"[tiab] OR "new coronavirus"[tiab]) AND (wuhan[tiab] OR 2019[tiab])) OR 2019-nCoV[All Fields] OR (wuhan[tiab] AND coronavirus[tiab])))))
-
-EMBASE:
-
-ncov OR (wuhan AND corona) OR COVID
-
-BioRxiv/MedRxiv:
-
-ncov or corona or wuhan or COVID
-
-We retained publications that used the keywords listed below in the title or abstract.
-
-"asymp*" OR "pre-symp*" OR "presymp*" OR "preclinical" OR "pre-clinical" OR "without symptoms" OR "no symptoms" OR "free of symptoms" OR "non-symp*" OR "nonsymp*" OR "symptom-free" OR "symptomfree"
-
-***
-
-## PRISMA 2020 Flowchart
-![Figure 3. PRISMA 2020 Flow Diagram](PRISMA2020_flowdiagram.png)
-***
-
-## Risk of bias in studies included in review question 1 and review question 2.
-*In progress.*
-
-***
-
-## Review question 1, subgroup analysis comparing studies of hospitalised patients with all other settings.
-*Sub-group analysis to be decided*
-
-***
-
-## Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search.
-![Figure 4. Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search](forest_meta_Q1_published.png)
-
-***
-
-## Assessment of credibility of mathematical modelling studies.
-*In progress.*
-
-***
-
-## Types of study included in successive versions of the living systematic review, as of 10 June 2020.
-*Settings to be reviewed. Some studies have been reclassified into different settings.*
-
-***
-
-## Location of studies contributing data to review questions 1 and 2.1.
-
-```{r table1_countries, ft.split=TRUE, tab.cap='Table 1. Location of studies contributing data to review questions 1', echo = FALSE}
-table1_countries <- flextable(Q1_table_countries)
-
-table1_countries %>% 
-  set_header_labels(country = "Country",
-                    total_SARS = "Total SARS-CoV-2, n",
-                    total_asymp_SARS = "Total asymptomatic SARS-CoV-2, n",
-                    n = "Total number of studies") %>%
-  set_table_properties(layout = "autofit") %>%
-  theme_vanilla()
-```
-
-*Table 2 in progress.*

### 2021-11-04 Q1_table_characteristics_full.Rmd
S1 TABLE

@@
 #author column
-Q1_table$study <- Q1_table$author_1
+Q1_table$study <- paste(Q1_table$author_1, ", ", Q1_table$year, sep="")
 Q1_table$author_1 <- NULL
+Q1_table$year <- NULL
 Q1_table$record_id <- NULL
@@
 
-Q1_table <- Q1_table[, c(1, 4, 2, 3, 5, 6, 7, 8)]
+Q1_table <- Q1_table[, c(1, 3, 2, 4, 5, 6, 7, 8)]
+
 ```
@@
                     location = "Location", 
-                    year = "Year"
                     study = "Study",

### 2021-11-04 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -17,6 +17,9 @@ formData2_2 <- list("token"=token,
 response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
 asymptomaticQ2_2 <- httr::content(response2_2)
 
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+asymptomaticQ2_2 <- asymptomaticQ2_2 %>%
+  filter(record_id <= 5296 | record_id %in% published_preprints)
 
 library(dplyr)
 
@@ -41,14 +44,28 @@ dfQ3a[dfQ3a==9999]<-NA
 dfQ3a=dfQ3a[!is.na(dfQ3a$p),]
 
 dfQ3b=data.frame(label=paste0("   ",asymptomaticQ2_2$author_1),
-                 Q3set=NA,
+                 Q3set=asymptomaticQ2_2$q3_setting,
                  p = asymptomaticQ2_2$q3_pa_m, 
                  l = asymptomaticQ2_2$q3_pa_l,
                  h = asymptomaticQ2_2$q3_pa_u,
                  setting="Asymptomatic",stringsAsFactors = FALSE)
 
+
 dfQ3b[dfQ3b==9999]<-NA
 dfQ3b=dfQ3b[!is.na(dfQ3b$p),]
+#dfQ3b[5,3:5] <- gsub("%", "",dfQ3b[5,3:5])
+dfQ3b <- rbind(dfQ3b,dfQ3b[2,]) 
+
+dfQ3b[2,] <- gsub(";.*","",dfQ3b[2,])
+dfQ3b[4,] <- gsub(".*;","",dfQ3b[4,])
+dfQ3b[dfQ3b==9999]<-NA
+dfQ3b[dfQ3b=="NA"]<-NA
+dfQ3b$Q3set[3] <-NA
+
+dfQ3b$label=ifelse(dfQ3b$label=="   Moghadas SM",
+                   paste0(dfQ3b$label, " ", ifelse(!is.na(dfQ3b$Q3set),paste0("[",dfQ3b$Q3set,"]"),"")),dfQ3b$label)
+
+dfQ3b$Q3set <- NA
 
 dfQ3=rbind.data.frame(dfQ3b,dfQ3a, stringsAsFactors = FALSE)
 
@@ -108,6 +125,7 @@ dataG$fontface=ifelse(dataG$type==1, "italic","plain")
[…]

### 2021-11-04 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

@@
 dfQ3b=data.frame(label=paste0("   ",asymptomaticQ2_2$author_1),
-                 Q3set=NA,
+                 Q3set=asymptomaticQ2_2$q3_setting,
                  p = asymptomaticQ2_2$q3_pa_m, 
@@
 dfQ3b=dfQ3b[!is.na(dfQ3b$p),]
+#dfQ3b[5,3:5] <- gsub("%", "",dfQ3b[5,3:5])
+dfQ3b <- rbind(dfQ3b,dfQ3b[2,])
+
+dfQ3b[2,] <- gsub(";.*","",dfQ3b[2,])
+dfQ3b[4,] <- gsub(".*;","",dfQ3b[4,])
+dfQ3b[dfQ3b==9999]<-NA
+dfQ3b[dfQ3b=="NA"]<-NA
+dfQ3b$Q3set[3] <-NA
+
+dfQ3b$label=ifelse(dfQ3b$label=="   Moghadas SM",
+                   paste0(dfQ3b$label, " ", ifelse(!is.na(dfQ3b$Q3set),paste0("[",dfQ3b$Q3set,"]"),"")),dfQ3b$label)
+
+dfQ3b$Q3set <- NA
 

### 2021-11-04 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -130,13 +130,13 @@ p=ggplot()+
   geom_point(data=dataG,aes(y=dataG$line, x=dataG$p),fill="gray", shape=22, color="black",size=4)+
   geom_errorbarh(data=dataG,aes(y=dataG$line, xmin=dataG$l, xmax=dataG$h), height=0.3)+
   
-  geom_text(aes(y=c(-1,-1,-1), x=c(-2,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+
+  geom_text(aes(y=c(-1,-1,-1), x=c(-1.3,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+
   
   geom_text(data=dataG,aes(y=dataG$line, x=1.25, label=label_study), hjust = 0)+
   geom_text(data=dataG,aes(y=dataG$line, x=1.75, label=label_studyCI), hjust = 0)+
   
   
-  geom_text(data=dataG,aes(y=dataG$line, x=-2, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
+  geom_text(data=dataG,aes(y=dataG$line, x=-1.3, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
   #geom_rect(data=dataG,aes(xmin=dataG$Pl,xmax=dataG$Ph,ymin=dataG$line-0.1,ymax=dataG$line+0.1),color="black", fill="red")+
   theme_void() + 
   scale_y_reverse()+

### 2021-11-04 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

@@
 
-  geom_text(aes(y=c(-1,-1,-1), x=c(-2,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+
+  geom_text(aes(y=c(-1,-1,-1), x=c(-1.3,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+
 
@@
 
-  geom_text(data=dataG,aes(y=dataG$line, x=-2, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
+  geom_text(data=dataG,aes(y=dataG$line, x=-1.3, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
   #geom_rect(data=dataG,aes(xmin=dataG$Pl,xmax=dataG$Ph,ymin=dataG$line-0.1,ymax=dataG$line+0.1),color="black", fill="red")+

### 2021-11-04 Q1_table_characteristics_full.Rmd
update s1 table

@@
 
+#swap order, 3 and 4
+fup4 <- Q1_table$fup___3
+fup3 <- Q1_table$fup___4
+Q1_table$fup___3 <- fup3
+Q1_table$fup___4 <- fup4
+
 Q1_table$fup___2[Q1_table$fup___2 == 1] <- 2
@@
 
+#change clusters to descriptions
+Q1_table$study[Q1_table$study == "Harada S, 2020"] <- "Harada S, 2020 [Patients]"
+Q1_table$study[Q1_table$study == "Harada S, 2020 [cluster 2]"] <- "Harada S, 2020 [Healthcare workers]"
+Q1_table$study[Q1_table$study == "Kennelly SP, 2020"] <- "Kennelly SP, 2020 [Nursing home residents]"
+Q1_table$study[Q1_table$study == "Kennelly SP, 2020 [cluster 2]"] <- "Kennelly SP, 2020 [Nursing home staff]"
+Q1_table$study[Q1_table$study == "van Buul LW, 2020"] <- "van Buul LW, 2020 [Nursing home residents]"
+Q1_table$study[Q1_table$study == "van Buul LW, 2020 [cluster 2]"] <- "van Buul LW, 2020 [Healthcare workers]"
+Q1_table$study[Q1_table$study == "Theuring S, 2021"] <- "Theuring S, 2021 [School students and staff]"
+Q1_table$study[Q1_table$study == "Theuring S, 2021 [cluster 2]"] <- "Theuring S, 2021 [Household members]"
+Q1_table$study[Q1_table$study == "van den Besselaar JH, 2021"] <- "van den Besselaar JH, 2021 [Healthcare workers]"
+Q1_table$study[Q1_table$study == "van den Besselaar JH, 2021 [cluster 2]"] <- "van den Besselaar JH, 2021 [Residents]"
+Q1_table$study[Q1_table$study == "Taylor J, 2020"] <- "Taylor J, 2020 [Healthcare personnel]"
+Q1_table$study[Q1_table$study == "Taylor J, 2020 [cluster 2]"] <- "Taylor J, 2020 [Residents]"
+Q1_table$study[Q1_table$study == "Ladhani SN, 2020"] <- "Ladhani SN, 2020 [Residents]"
+Q1_table$study[Q1_table$study == "Ladhani SN, 2020 [cluster 2]"] <- "Ladhani SN, 2020 [Healthcare workers]"
+#asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:1]"] <- "#5551 Vohra [Presurgical patients]"
+#asymptomaticQ1$label[asymptomaticQ1$label == "#5551 Vohra [cluster:2]"] <- "#5551 Vohra [Undergoing chemotherapy]"
+#asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:1]"] <- "#6526 Garibaldi [Residents]"
+#asymptomaticQ1$label[asymptomaticQ1$label == "#6526 Garibaldi [cluster:2]"] <- "#6526 Garibaldi [Staff]"
+
 Q1_table <- Q1_table[, c(1, 3, 2, 4, 5, 6, 7, 8)]

### 2021-11-04 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update
rerun

@@
 dev.new()
-png("q1_1_new.png", width = 1000, height = 1500)
+pdf("q1_1_new.pdf", width = 1000, height = 1500)
 p3
@@
 
-p7 <- ggarrange(p4,p5,p6, heights = c(1.1, 1, 0.7), ncol = 1, nrow = 3)
+p7 <- ggarrange(p4,p5,p6, heights = c(1, 0.8, 0.8), ncol = 1, nrow = 3)
 
@@
 
-![ROB Q1_1](q1_1_new.png)
+![ROB Q1_1](q1_1_new.pdf)
 ![ROB Q1_1](q1_2_new.png)

### 2021-11-05 Manuscript_draft.Rmd

--- 2021-11-04 Manuscript_draft.Rmd
@@
 
-  geom_text(aes(y=c(-1,-1,-1), x=c(-2,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+
+  geom_text(aes(y=c(-1,-1,-1), x=c(-1.5,1.25,1.75), label=c("Study","Prop.","95% CI")), hjust = 0, fontface = "bold")+
 
@@
 
-  geom_text(data=dataG,aes(y=dataG$line, x=-2, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
+  geom_text(data=dataG,aes(y=dataG$line, x=-1.5, label=dataG$label), hjust = 0, fontface=dataG$fontface)+
   #geom_rect(data=dataG,aes(xmin=dataG$Pl,xmax=dataG$Ph,ymin=dataG$line-0.1,ymax=dataG$line+0.1),color="black", fill="red")+
@@
 Q2_2_table$q3_setting <- gsub("/([[:alpha:]])", ", \\1", Q2_2_table$q3_setting)
-Q2_2_table$q3_setting[15] <- gsub(",", ";",Q2_2_table$q3_setting[15])
+#Q2_2_table$q3_setting[15] <- gsub(",", ";",Q2_2_table$q3_setting[15])
 q2_2_nstudies <- nrow(Q2_2_table) #total number of studies included in q1

### 2021-12-10 Q1.R
Update Q1.R

@@ -118,9 +118,19 @@ data[is.na(data$setting),]$record_id
 data=data[!is.na(data$setting),]
 
 #cut data at end of jan 31
+
+#published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+# data <- data %>%
+#   filter(record_id <= 5296 | record_id %in% published_preprints)
+
+#10.12.21 - updated HI
 published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+#include additional study identified from ref list
+additional <- 11099
 data <- data %>%
-  filter(record_id <= 5296 | record_id %in% published_preprints)
+  filter(record_id <= 5296 |
+           record_id %in% published_preprints |
+           record_id %in% additional)
 
 
 asym_plot<-metaprop(events,total,data=data,sm = "PLOGIT", studlab=label, 

### 2021-12-10 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
update

@@
 #censor until 5296 (31 Jan) plus the published versions of preprints
-pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
+# pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
+# rob_records <- rob_records %>%
+#   filter(record_id %in%  pub_preprints | record_id <= 5296)
+
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+#include additional study identified from ref list
+additional <- 11099
 rob_records <- rob_records %>%
-  filter(record_id %in%  pub_preprints | record_id <= 5296)
+  filter(record_id <= 5296 |
+           record_id %in% published_preprints |
+           record_id %in% additional)
 

### 2021-12-10 ROB_new_HI_101221.R
Create ROB_new_HI_101221.R

@@ -1,0 +1,248 @@
+library(dplyr)
+#install.packages("ggpubr")
+library("ggpubr")
+
+#use the package as a new source. Some functions of the package are changed by HI
+source("robisfunctions.R")
+
+# get the data directly from redcap:
+urlrob <- "https://redcap.ispm.unibe.ch/api/"
+tokenrob <- "F2725F15FE84D2832E2793BB23B0A62B"
+formDatarob <- list("token"=tokenrob,
+                    content='report',
+                    format='csv',
+                    report_id='283',
+                    csvDelimiter='',
+                    rawOrLabel='raw',
+                    rawOrLabelHeaders='raw',
+                    exportCheckboxLabel='false',
+                    returnFormat='csv'
+)
+response_rob <- httr::POST(urlrob, body = formDatarob, encode = "form")
+rob_records <- httr::content(response_rob)
+
+# rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
+
+#censor until 5296 (31 Jan) plus the published versions of preprints
+# pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
+# rob_records <- rob_records %>%
+#   filter(record_id %in%  pub_preprints | record_id <= 5296)
+
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+#include additional study identified from ref list
+additional <- 11099
+rob_records <- rob_records %>%
+  filter(record_id <= 5296 |
+           record_id %in% published_preprints |
+           record_id %in% additional)
+
+
+
+#prepare a dataset
+# df_rob <- rob_records %>%
+#   select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
+#          rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
+#          risk_of_bias_update_3_complete)
+
+df_rob <- rob_records %>%
+  select(record_id,author_1, quest___1, q3_sar, setting2, 
+         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
+         risk_of_bias_update_3_complete)
+df_rob['setting'] <- NA
+
+
+df_rob <- df_rob %>%
+  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
[…]

### 2021-12-10 ROB_new_HI_101221.R
Update ROB_new_HI_101221.R

@@ -98,6 +98,15 @@ p1 <- contactinvestigation_rob_trafficlight +
   ggplot2::ggtitle("Contact investigation") +
   ggplot2::theme(legend.position = "none")
 
+# p1 <- annotate_figure(p1, top = text_grob("Question 1", 
+#                                           color = "black", face = "bold", size = 21))
+dev.new()
+tiff("test.tiff", width = 600, height = 400)
+#pdf("q1_1_new.pdf", width = 1000, height = 1500)
+p1
+graphics.off()
+
+
 
 # 3. "Outbreak investigation"
 outbreakinv <- q1_rob %>% 
@@ -114,15 +123,12 @@ p2 <- outbreakinv_rob_trafficlight +
   ggplot2::ggtitle("Outbreak investigation") +
   ggplot2::theme(legend.position = "none")
 
-p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)
-
-p3 <- annotate_figure(p3, top = text_grob("Question 1", 
-                                          color = "black", face = "bold", size = 21))
+#p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)
 
 
 dev.new()
-pdf("q1_1_new.pdf", width = 1000, height = 1500)
-p3
+tiff("test2.tiff", width = 600, height = 900)
+p2
 graphics.off()
 
 
@@ -142,6 +148,13 @@ p4 <- institutional_rob_trafficlight +
   ggplot2::ggtitle("Screening: institutional setting") +
   ggplot2::theme(legend.position = "none")
 
+dev.new()
+tiff("test3.tiff", width = 600, height = 710)
+p4
+graphics.off()
+
+
+
 # 10. "Screening: community setting"
 communityset <- q1_rob %>% 
   filter(setting == "Screening: community setting") %>%
@@ -158,6 +171,11 @@ p5 <- communityset_rob_trafficlight +
     caption = " ") + 
   ggplot2::ggtitle("Screening: community setting") +
   ggplot2::theme(legend.position = "none")
+
+dev.new()
+tiff("test4.tiff", width = 600, height = 520)
+p5
+graphics.off()
 
 
 # 11. "Screening: occupational"
@@ -192,12 +210,13 @@ p6 <- p6 +
[…]

### 2021-12-13 ROB_analysis_1312_HI.Rmd
Create ROB_analysis_1312_HI.Rmd

--- 2021-12-10 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
@@
 ---
-title: "Supporting Information"
-author: "Diana Buitrago-Garcia, Aziz Mert Ipekci, Leonie Heron, Stefanie Hossmann, Hira Imeri, Georgia Salanti, Nicola Low"
-date: "`r format(Sys.time(), '%d/%m/%y')`"
-output: 
-  html_document:
-  toc: true
-  toc_float: true
-  theme: united
-  highlight: tango
-  #always_allow_html: true
+title: "ROB analysis"
+author: "H Imeri"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output: word_document
+
 ---
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE,}
 knitr::opts_chunk$set(echo = TRUE)
-
-###############################################################
-# Supplementary material                        ##########
-###############################################################
-
-###############################################################
-# Question 1: results output                         ##########
-# Proportion of asymptomatic cases                   ##########
-# Supplementary material: preprints removed          ##########
-###############################################################
-
-#load the libraries
-library(meta)
-library(readxl)
-library(tidyverse)
-library(httr) # use to retrieve data from REDCap
-library(kableExtra)
-library(flextable)
-library(dplyr)
-library(Rcpp)
-
-# Prepare the data
-# get the data directly from redcap:
-# report #155 is Q1:
-url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
-formData <- list("token"=token,
-                 content='report',
-                 format='csv',
-                 report_id='155',
-                 csvDelimiter='',
-                 rawOrLabel='raw',
-                 rawOrLabelHeaders='raw',
-                 exportCheckboxLabel='false',
-                 returnFormat='csv'
-)
-response <- httr::POST(url, body = formData, encode = "form")
-asymptomaticQ1_pub <- httr::content(response)
-
-settings=c("Contact investigation",
-           "Contact investigation, aggregated",
-           "Outbreak investigation",
-           "Statistical model",
-           "Screening",
-           "Hospitalised adults",
-           "Hospitalised children",
-           "Hospitalised adults & children")
-
-asymptomaticQ1_pub$setting2<-factor(asymptomaticQ1_pub$setting2, levels=1:8, labels=settings)
-#combine contact investigation and contact investigation aggregated
-asymptomaticQ1_pub$setting2[asymptomaticQ1_pub$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"
-
-# minor cleaning
-asymptomaticQ1_pub[asymptomaticQ1_pub==9999]=NA
-
-asymptomaticQ1_pub$setting=asymptomaticQ1_pub$setting2
-
-#remove preprints at time of search
-asymptomaticQ1_pub <- asymptomaticQ1_pub %>%
-  filter(source != 1 & source != 2)
-
-data_long1_pub <- gather(asymptomaticQ1_pub, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
-  mutate(id=1:nrow(.)) %>%
-  select(record_id, author_1, setting, total, id, cluster)
-data_long2_pub <-gather(asymptomaticQ1_pub, cluster, events, c(q1_c1_event,q1_c2_event,q1_c3_event), factor_key=TRUE) %>% 
-  mutate(id=1:nrow(.)) %>%
-  select(events, id)
-
-data_Q1_pub = merge(data_long1_pub, data_long2_pub, by="id")
-data_Q1_pub = data_Q1_pub[!is.na(data_Q1_pub$total),]
-data_Q1_pub$cluster=factor(data_Q1_pub$cluster,labels=c("1","2","3"),levels=c("q1_c1_total","q1_c2_total","q1_c3_total"))
-
-data_Q1_pub[data_Q1_pub$record_id %in% asymptomaticQ1_pub[is.na(asymptomaticQ1_pub$q1_c2_event),]$record_id,]$cluster=NA
-
-asymptomaticQ1_pub=data_Q1_pub
-
-asymptomaticQ1_pub$label=paste0("#", asymptomaticQ1_pub$record_id, " ", asymptomaticQ1_pub$author_1, " (2020)",ifelse(!is.na(asymptomaticQ1_pub$cluster),paste0(" cluster:",asymptomaticQ1_pub$cluster),"")) # [FU: ",asymptomaticQ1$fup_median,"]")
-
-asymptomaticQ1_pub$label=paste0("#", asymptomaticQ1_pub$record_id, " ", asymptomaticQ1_pub$author_1,ifelse(!is.na(asymptomaticQ1_pub$cluster),paste0(" [cluster:",asymptomaticQ1_pub$cluster,"]"),"")) # [FU: ",asymptomaticQ1$fup_median,"]")
-
-#change clusters to descriptions
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4479 Harada [cluster:1]"] <- "#4479 Harada [Patients]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4479 Harada [cluster:2]"] <- "#4479 Harada [Healthcare workers]"
-#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:1]"] <- "#2826 Taylor []" #clarify
-#asymptomaticQ1$label[asymptomaticQ1$label == "#2826 Taylor [cluster:2]"] <- "#2826 Taylor []"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2892 Kennelly [cluster:1]"] <- "#2892 Kennelly [Nursing home residents]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2892 Kennelly [cluster:2]"] <- "#2892 Kennelly [Nursing home staff]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2802 Bender [cluster:1]"] <- "#2802 Bender [Hospital 1]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#2802 Bender [cluster:2]"] <- "#2802 Bender [Hospital 2]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4968 van Buul [cluster:1]"] <- "#4968 van Buul [Nursing home residents]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#4968 van Buul [cluster:2]"] <- "#4968 van Buul [Healthcare workers]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#5273 Theuring [cluster:1]"] <- "#5273 Theuring [School students and staff]"
-asymptomaticQ1_pub$label[asymptomaticQ1_pub$label == "#5273 Theuring [cluster:2]"] <- "#5273 Theuring [Household members]"
-
-data_pub=asymptomaticQ1_pub[order(asymptomaticQ1_pub$setting,1/(1/asymptomaticQ1_pub$events+1/(asymptomaticQ1_pub$total-asymptomaticQ1_pub$events))),]
-
-data_pub[is.na(data_pub$setting),]$record_id
-data_pub=data_pub[!is.na(data_pub$setting),]
-
-asym_plot<-metaprop(events,total,data=data_pub,sm = "PLOGIT", studlab=label, 
-                    byvar=setting,# tau.common =TRUE,
-                    prediction = TRUE,
-                    control=list(stepadj=0.05, maxiter=10000))#, method ="INV") #, verbose=TRUE, digits=5, control=list(stepadj=0.5))
-
-asym_plot
-
-png(file = 'forest_meta_Q1_published.png',width = 30,height = 60, res=600, units="cm")
-
-forest(asym_plot,  col.square=data_pub$setting, sortvar = 1/seTE,
-       #squaresize = 1/(1/data$events+1/(data$total-data$events)),
-       #sortvar = 1/(1/events+1/(total-events)), 
-       subgroup=TRUE, 
-       just.studlab="left", colgap.studlab="2cm",
-       #leftcols = c("label", "setting", "age", "design", "asym_denom"),
-       #leftcols=c("studlab", "record_id", "event", "n"),
-       xlab = "",just="left",comb.random=TRUE,test.subgroup.random=FALSE,
-       comb.fixed=FALSE,test.subgroup.fixed=FALSE, predict=T)#, study.results=TRUE,test.subgroup=TRUE)
-dev.off()
-
-###############################################################
-# Countries included in Q1                           ##########
-###############################################################
-
-library(dplyr)
-Q1_table_countries <- httr::content(response)
-
-#censor until 5296 (31 Jan) plus the published versions of preprints
-pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
-
-Q1_table_countries <- Q1_table_countries %>%
-  filter(record_id %in%  pub_preprints | record_id <= 5296)
-
-#clean countries
-Q1_table_countries <- Q1_table_countries %>%
-  mutate(country = ifelse(country == 10, "Australia", country),
-         country = ifelse(country == 11, "Austria", country),
-         country = ifelse(country == 15, "Bahrain", country),
-         country = ifelse(country == 19, "Belgium", country),
-         country = ifelse(country == 27, "Brazil", country),
-         country = ifelse(country == 28, "Brunei", country),
-         country = ifelse(country == 34, "Canada", country),
-         country = ifelse(country == 40, "China", country),
-         country = ifelse(country == 41, "Colombia", country),
-         country = ifelse(country == 51, "Denmark", country),
-         country = ifelse(country == 62, "France", country),
-         country = ifelse(country == 63, "French Guyana", country),
-         country = ifelse(country == 67, "Germany", country),
-         country = ifelse(country == 69, "Greece", country),
-         country = ifelse(country == 78, "Iceland", country),
-         country = ifelse(country == 79, "India", country),
-         country = ifelse(country == 83, "Ireland", country),
-         country = ifelse(country == 85, "Italy", country),
-         country = ifelse(country == 87, "Japan", country),
-         country = ifelse(country == 92, "Kuwait", country),
-         country = ifelse(country == 105, "Malaysia", country),
-         country = ifelse(country == 121, "Netherlands", country),
-         country = ifelse(country == 128, "Norway", country),
-         country = ifelse(country == 130, "Pakistan", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 138, "Portugal", country),
-         country = ifelse(country == 146, "Saudi Arabia", country),
-         country = ifelse(country == 157, "South Korea", country),
-         country = ifelse(country == 160, "Spain", country),
-         country = ifelse(country == 174, "Turkey", country),
-         country = ifelse(country == 176, "Uganda", country),
-         country = ifelse(country == 180, "United Kingdom", country),
-         country = ifelse(country == 181, "United States of America", country),
-         country = ifelse(country == 185, "Vietnam", country))
-
-#clean case numbers
-#total SARS-CoV-2 n
-Q1_table_countries$q1_c1_total[is.na(Q1_table_countries$q1_c1_total)] <- 0
-Q1_table_countries$q1_c2_total[is.na(Q1_table_countries$q1_c2_total)] <- 0
-Q1_table_countries$q1_c1_event[is.na(Q1_table_countries$q1_c1_event)] <- 0
-Q1_table_countries$q1_c2_event[is.na(Q1_table_countries$q1_c2_event)] <- 0
-
-Q1_table_countries$total_SARS_n <- Q1_table_countries$q1_c1_total + Q1_table_countries$q1_c2_total
-Q1_table_countries$asymp_SARS_n <- Q1_table_countries$q1_c1_event + Q1_table_countries$q1_c2_event
-
-#remove unnecessary cols
-Q1_table_countries <- Q1_table_countries %>%
-  select(country, total_SARS_n, asymp_SARS_n)
-
-#group by countries to calculate n, total cases, total asymp cases
-Q1_table_countries <- Q1_table_countries %>%
-  group_by(country) %>%
-  summarise(total_SARS = sum(total_SARS_n),
-            total_asymp_SARS = sum(asymp_SARS_n),
-            n = n())
-
-#arrange by number of studies
-Q1_table_countries <- Q1_table_countries %>%
-  arrange(desc(n))
-#create PRISMA 2020 flowchart
-
-#download packages
-library(devtools)
-library(dplyr)
-#install_github("nealhaddaway/PRISMA2020")
-
-#create df from example csv file
-#PRISMA <- read.csv("PRISMA.csv")
-
-#set the REDCap IDs
-#last REDCap ID in previous version
-#last_ID_prev <- 1000
-#last REDCap ID in current version
-#last_ID_current <- 5296
-#load all records in redcap
-
-# get the data directly from redcap:
-# url <- "https://redcap.ispm.unibe.ch/api/"
-# token <- "F2725F15FE84D2832E2793BB23B0A62B"
-# formData <- list("token"=token,
-#                  content='report',
-#                  format='csv',
-#                  report_id='158',
-#                  csvDelimiter='',
-#                  rawOrLabel='raw',
-#                  rawOrLabelHeaders='raw',
-#                  exportCheckboxLabel='false',
-#                  returnFormat='csv'
-# )
-# response_all <- httr::POST(url, body = formData, encode = "form")
-# all_records <- httr::content(response_all)
-# 
-# #find number of studies identified in databases since previous update
-# current_records <- all_records[last_ID_prev:last_ID_current, ]
-# PRISMA$n[PRISMA$data == "database_results"] <- nrow(current_records[!is.na(current_records$record_id), ]) - 1 #1 was added manually 9484
-# 
-# #find number included in review
-# PRISMA$n[PRISMA$data == "new_studies"] <- nrow(current_records %>% filter(review == 1))
-# 
-# #find number of duplicates removed before screening
-# PRISMA$n[PRISMA$data == "duplicates"] <- nrow(current_records %>% filter(ex_reas == 14))
-# #find number of records screening
-# PRISMA$n[PRISMA$data == "records_screened"] <- nrow(current_records) - 
-#   nrow(current_records %>% filter(ex_reas == 14))
-# #add number of studies found via other methods 
-# #1 study #9484 was added manually - it's the published v of a preprint
-# #as a result, I need to minus 1 record from the database result
-# PRISMA$n[PRISMA$box == "othstud"] <- 1
-# 
-# #find number of records excluded from title and abstract
-# PRISMA$n[PRISMA$data == "records_excluded"] <- nrow(current_records %>% filter(ex_reas == 1))
-# check <- current_records %>% filter(ex_reas == 1)
-# #current records left after title and abstract screening
-# full_text_screen <- current_records %>% filter(ex_reas != 14 & ex_reas != 1)
-# 
-# #find number of full texts retrieved
-# PRISMA$n[PRISMA$data == "dbr_sought_reports"] <- nrow(current_records) - 
-#   (nrow(current_records %>% filter(ex_reas == 14)) + 
-#   nrow(current_records %>% filter(ex_reas == 1)))
-# 
-# #find number of full texts screened
-# PRISMA$n[PRISMA$data == "dbr_assessed"] <- nrow(current_records) - 
-#   (nrow(current_records %>% filter(ex_reas == 14)) + 
-#      nrow(current_records %>% filter(ex_reas == 1)))
-# 
-# #find number included in previous version
-# prev_records <- all_records[1:last_ID_prev, ]
-# PRISMA$n[PRISMA$data == "previous_studies"] <- nrow(prev_records[prev_records$review == 1, ])
-# 
-# #calculate total studies included
-# PRISMA$n[PRISMA$data == "total_studies"] <- nrow(prev_records[prev_records$review == 1, ]) +
-#   nrow(current_records[current_records$review == 1, ])
-# 
-# # studies excluded
-# excl_11 <-  nrow(current_records %>% filter(ex_reas == 11))
-# excl_12 <-  nrow(current_records %>% filter(ex_reas == 12))
-# excl_13 <-  nrow(current_records %>% filter(ex_reas == 13))
-# excl_15 <-  nrow(current_records %>% filter(ex_reas == 15))
-# excl_16 <-  nrow(current_records %>% filter(ex_reas == 16))
-# excl_17 <-  nrow(current_records %>% filter(ex_reas == 17))
-# excl_19 <-  nrow(current_records %>% filter(ex_reas == 19))
-# excl_20 <-  nrow(current_records %>% filter(ex_reas == 20))
-# excl_21 <-  nrow(current_records %>% filter(ex_reas == 21))
-# excl_18 <-  nrow(current_records %>% filter(ex_reas == 18))
-# 
-# excl_reasons <- paste0("Publication not on COVID-19, ", excl_11, 
-#                        "; No original data, ", excl_12, 
-#                        "; Data included in other publication, ", excl_13, 
-#                        "; Insufficient extractable data, ", excl_15, 
-#                        "; Study design inappropriate, ", excl_16, 
-#                        "; No PCR/serological test, ", excl_17, 
-#                        "; Math. model not in review scope, ", excl_19, 
-#                        "; Inadequate follow-up time, ", excl_20, 
-#                        "; Preprint of published article, ", excl_21, 
-#                        "; Other, ", excl_18)
-# excl_reasons
-# PRISMA$n[PRISMA$data == "dbr_excluded"] <- excl_reasons
-# 
-# #fix some text in the flowchart data
-# PRISMA$boxtext[PRISMA$data == "identification"] <- "Identification"
-# PRISMA$boxtext[PRISMA$box == "prevstud"] <- "Previous studies"
-# 
-#   
-# #read data
-# flowchart <- PRISMA2020::PRISMA_data(PRISMA)
-# flowchart
-# #generate flowchart
-# PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
-# flowchart_plot <- PRISMA2020::PRISMA_flowdiagram(data = flowchart, other = FALSE)
-#                                
-# PRISMA2020::PRISMA_save(flowchart_plot, filename = "PRISMA2020_flowdiagram.png", filetype = "png", overwrite = TRUE)
-
-#######ROB Analysis HI##########
 
@@
 #censor until 5296 (31 Jan) plus the published versions of preprints
+
 # pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
@@
 
+dev.new()
+tiff("test1.tiff", width = 17.78, height = 12.80, units = "cm", res = 600)
+#pdf("q1_1_new.pdf", width = 1000, height = 1500)
+p1
+graphics.off()
+
 # 3. "Outbreak investigation"
@@
 
-p3 <- ggarrange(p1,p2,heights = c(1, 1.7), ncol = 1, nrow = 2)
+dev.new()
+tiff("test2.tiff", width = 24, height = 26.35, units = "cm", res = 600)
+p2
+graphics.off()
 
-p3 <- annotate_figure(p3, top = text_grob("Question 1", 
-                                      color = "black", face = "bold", size = 21))
+# 10. "Screening: community setting"
+communityset <- q1_rob %>% 
+  filter(setting == "Screening: community setting") %>%
+  select(Study, D1, D2, D3, D4, D5, `6`)
+#Records: 17 studies
+
+communityset_rob_trafficlight <- rob_traffic_light(data = communityset,
+                                                   tool = "Generic",
+                                                   psize = 10,
+                                                   overall = FALSE)
+
+p3 <- communityset_rob_trafficlight +
+  ggplot2::labs(
+    caption = " ") + 
+  ggplot2::ggtitle("Screening: community setting") +
+  ggplot2::theme(legend.position = "none")
 
 dev.new()
-pdf("q1_1_new.pdf", width = 1000, height = 1500)
+#tiff("test3.tiff", width = 900, height = 520)
+tiff("test3.tiff", width = 17.78, height = 17.78, units = "cm", res = 600)
 p3
@@
 
-# 10. "Screening: community setting"
-communityset <- q1_rob %>% 
-  filter(setting == "Screening: community setting") %>%
-  select(Study, D1, D2, D3, D4, D5, `6`)
-#Records: 17 studies
-
-communityset_rob_trafficlight <- rob_traffic_light(data = communityset,
-                                                   tool = "Generic",
-                                                   psize = 10,
-                                                   overall = FALSE)
-
-p5 <- communityset_rob_trafficlight +
-  ggplot2::labs(
-    caption = " ") + 
-  ggplot2::ggtitle("Screening: community setting") +
-  ggplot2::theme(legend.position = "none")
+dev.new()
+#tiff("test3.tiff", width = 900, height = 710)
+tiff("test4.tiff", width = 17.78, height = 23, units = "cm", res = 600)
+p4
+graphics.off()
 
@@
 
-p6 <- occupationalset_rob_trafficlight +
+p5 <- occupationalset_rob_trafficlight +
   ggplot2::labs(
@@
 
-p6 <- p6 + 
+p5 <- p5 + 
   ggplot2::ggtitle("Screening: occupational")
 
-p7 <- ggarrange(p4,p5,p6, heights = c(1, 0.8, 0.8), ncol = 1, nrow = 3)
+#p7 <- ggarrange(p4,p5,p6, heights = c(1, 0.8, 0.8), ncol = 1, nrow = 3)
 
 dev.new()
-png("q1_2_new.png", width = 1000, height = 2500)
-p7
+tiff("test5.tiff", width = 17.78, height = 23, units = "cm", res = 600)
+#tiff("test5.tiff", width = 900, height = 620)
+p5
 graphics.off()
@@
 
-p8 <- q2_rob_trafficlight +
+p6 <- q2_rob_trafficlight +
   ggplot2::labs(
@@
 
-p8 <- p8 + 
-  ggplot2::ggtitle("Question 2.1") +
-  theme(plot.title = element_text(hjust = 0.5)) + theme(plot.title = element_text(size = 20, face = "bold"))
-
 dev.new()
-png("q2_new.png", width = 1000, height = 500)
-p8
+tiff("test6.tiff", width = 17.78, height = 15, units = "cm", res = 600)
+p6
 graphics.off()
@@
 
-## PRISMA 2020 Checklist
-*Shiny app can be used to complete checklist here:* <https://prisma.shinyapps.io/checklist/>
+**Question 1**
 
-***
-
-## Search strings
-
-From: Living Evidence on COVID-19 (<https://ispmbern.github.io/covid-19/living-review/collectingdata.html>, accessed 31.01.2021)
-
-We retrieve data from [EMBASE](http://www.embase.com/) via OVID, [MEDLINE](https://www.ncbi.nlm.nih.gov/pubmed/) via PubMed, BioRxiv and MedRxiv.
-
-**Search terms**
-
-When searches are updated, references that are identified that were not in the database before, are inserted by date (**date_entrez**) they were indexed in remote database, the date they are inserted in OUR database is formatted as the ‘**strategydate**’ (raw data is available [here](https://github.com/leonieheron/LSRworkflow>)).
-
-**30.10.2020**
-
-EMBASE:
-
-(exp SARS-related coronavirus/ or severe acute respiratory syndrome/ or coronavirus disease 2019/ or (coronavir* or corona virus* or HCoV* or ncov* or 2019 cov or covid or covid19 or sars-cov* or sarscov* or sars-coronavirus* or Severe Acute Respiratory Syndrome Coronavirus* or nCoV).mp.) and 20191101:20301231.(dc).
-
-MEDLINE:
-
-("severe acute respiratory syndrome coronavirus 2"[Supplementary Concept] OR "COVID-19" [Supplementary Concept] OR "coronavirus" OR "corona virus" OR "HCoV" OR "nCoV" OR "2019 CoV" OR "covid" OR "covid19" OR "Severe Acute Respiratory Syndrome Coronavirus 2" OR "SARS-CoV2" OR "SARS-CoV 2" OR "SARS Coronavirus 2") AND (2019/11/01:3000/12/31[PDAT])
-
-**01.05.2021**
-
-EMBASE:
-
-(SARS coronavirus/ or middle east respiratory syndrome/ or severe acute respiratory syndrome/ or (coronavirus* or corona virus* or HCoV* or ncov* or covid or covid19 or sars-cov* or sarscov* or Sars-coronavirus* or Severe Acute Respiratory Syndrome Coronavirus*).mp.) and 20191201:20301231.(dc).
-
-**29.04.2020**
-
-MEDLINE:
-
-("coronavirus"[MH] OR "coronavirus infections"[MH] OR "coronavirus"[TW] OR "corona virus"[TW] OR "HCoV"[TW] OR "nCov"[TW] OR "covid"[TW] OR "covid19"[TW] OR "Severe Acute Respiratory Syndrome Coronavirus 2"[TW] OR "SARS-CoV2"[TW] OR "SARS-CoV 2"[TW] OR "SARS Coronavirus 2"[TW] OR "MERS- CoV"[TW]) AND (2019/1/1:3000[PDAT])
-
-**01.04.2020**
-
-From 01.04.2020, we retrieve the [BioRxiv/MedRxiv dataset](https://connect.medrxiv.org/relate/content/181).
-
-**26.03.2020**
-
-MEDLINE:
-
-("Wuhan coronavirus" [Supplementary Concept] OR "COVID-19" OR SARS-CoV-2 OR "2019 ncov"[tiab] OR (("novel coronavirus"[tiab] OR "new coronavirus"[tiab]) AND (wuhan[tiab] OR 2019[tiab])) OR 2019-nCoV[All Fields] OR (wuhan[tiab] AND coronavirus[tiab]))
-
-EMBASE:
-
-(nCoV or 2019-nCoV or ((new or novel or wuhan) adj3 coronavirus) or covid19 or covid-19 or SARS-CoV-2).mp.
-
-BioRxiv/MedRxiv:
-
-ncov or corona or wuhan or COVID or SARS-CoV-2
-
-With the kind support of the [Public Health & Primary Care Library PHC](https://www.unibe.ch/university/services/university_library/faculty_libraries/medicine/public_health_amp_primary_care_library_phc/index_eng.html), and following guidance of the [Medical Library Association](https://www.mlanet.org/p/cm/ld/fid%3D1713)
-
-**01.01.2020**
-
-MEDLINE:
-
-("Wuhan coronavirus" [Supplementary Concept] OR "COVID-19" OR "2019 ncov"[tiab] OR (("novel coronavirus"[tiab] OR "new coronavirus"[tiab]) AND (wuhan[tiab] OR 2019[tiab])) OR 2019-nCoV[All Fields] OR (wuhan[tiab] AND coronavirus[tiab])))))
-
-EMBASE:
-
-ncov OR (wuhan AND corona) OR COVID
-
-BioRxiv/MedRxiv:
-
-ncov or corona or wuhan or COVID
-
-We retained publications that used the keywords listed below in the title or abstract.
-
-"asymp*" OR "pre-symp*" OR "presymp*" OR "preclinical" OR "pre-clinical" OR "without symptoms" OR "no symptoms" OR "free of symptoms" OR "non-symp*" OR "nonsymp*" OR "symptom-free" OR "symptomfree"
-
-***
-
-## PRISMA 2020 Flowchart
-*In progress.*
-***
-
-## Risk of bias in studies included in review question 1 and review question 2.
-
-![ROB Q1_1](q1_1_new.pdf)
-![ROB Q1_1](q1_2_new.png)
-![ROB Q1_1](q2_new.png)
-
-***
-
-## Review question 1, subgroup analysis comparing studies of hospitalised patients with all other settings.
-*Sub-group analysis to be decided*
-
-***
-
-## Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search.
-![Figure 4. Review question 1, sensitivity analysis, omitting studies that were preprints at the time of literature search](forest_meta_Q1_published.png)
-
-***
-
-## Assessment of credibility of mathematical modelling studies.
-*In progress.*
-
-***
-
-## Types of study included in successive versions of the living systematic review, as of 10 June 2020.
-*Settings to be reviewed. Some studies have been reclassified into different settings.*
-
-***
-
-## Location of studies contributing data to review questions 1 and 2.1.
-
-```{r table1, ft.split=TRUE, tab.cap='Table 1. Location of studies contributing data to review questions 1', echo = FALSE}
-table1_countries <- flextable(Q1_table_countries)
-
-table1_countries %>% 
-  set_header_labels(country = "Country",
-                    total_SARS = "Total SARS-CoV-2, n",
-                    total_asymp_SARS = "Total asymptomatic SARS-CoV-2, n",
-                    n = "Total number of studies") %>%
-  set_table_properties(layout = "autofit") %>%
-  theme_vanilla()
+```{r, echo = FALSE}
+# All defaults 
+#please change the path
+knitr::include_graphics("C:/Users/hi19u875/Desktop/Asymptomatic_Review_DataIntoRedcap_Everyweeksearch/test1.tiff")
 ```
 
-*Table 2 in progress.*
+```{r, echo = FALSE}
+# All defaults
+knitr::include_graphics("C:/Users/hi19u875/Desktop/Asymptomatic_Review_DataIntoRedcap_Everyweeksearch/test2.tiff")
+```
+
+```{r, echo = FALSE}
+# All defaults
+knitr::include_graphics("C:/Users/hi19u875/Desktop/Asymptomatic_Review_DataIntoRedcap_Everyweeksearch/test3.tiff")
+```
+
+```{r, echo = FALSE}
+# All defaults
+knitr::include_graphics("C:/Users/hi19u875/Desktop/Asymptomatic_Review_DataIntoRedcap_Everyweeksearch/test4.tiff")
+```
+
+```{r, echo = FALSE}
+# All defaults
+knitr::include_graphics("C:/Users/hi19u875/Desktop/Asymptomatic_Review_DataIntoRedcap_Everyweeksearch/test5.tiff")
+```
+
+**Question 2**
+
+```{r, echo = FALSE}
+# All defaults
+knitr::include_graphics("C:/Users/hi19u875/Desktop/Asymptomatic_Review_DataIntoRedcap_Everyweeksearch/test6.tiff")
+```

### 2021-12-13 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
Update with 11099

--- 2021-11-04 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
@@
 #download packages
-library(devtools)
 library(dplyr)
@@
 
-#censor until 5296 (31 Jan) plus the published versions of preprints
-pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
-rob_records <- rob_records %>%
-  filter(record_id %in%  pub_preprints | record_id <= 5296)
+#cut data at end of jan 31
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+#include additional study identified from ref list
+additional <- 11099
+data <- data %>%
+  filter(record_id <= 5296 |
+           record_id %in% published_preprints |
+           record_id %in% additional)
 

### 2021-12-13 Q1.R

@@ -352,11 +352,13 @@ asym_plot_rob_5 <- metaprop(events, total, data = data_rob_5,
                             sm = "PLOGIT", studlab=label, 
                             byvar=setting,# tau.common =TRUE,
                             prediction = TRUE,
+                            print.byvar = FALSE,
+                            comb.random = TRUE, comb.fixed = FALSE,
                             control=list(stepadj=0.05, maxiter=10000))#, method ="INV") #, verbose=TRUE, digits=5, control=list(stepadj=0.5))
 asym_plot_rob_5
 
-tiff(filename = "Q1_rob_5.tiff",
-     width = 3000, height = 1500,
+tiff(filename = "Q1_rob_alllowROB.tiff",
+     width = 2400, height = 1400,
      res = 300)
 forest(asym_plot_rob_5, #sortvar = n, #sorted by study precision
        subgroup=TRUE,
@@ -364,13 +366,14 @@ forest(asym_plot_rob_5, #sortvar = n, #sorted by study precision
        just="left", colgap.studlab="1cm",
        predict=T, comb.random = TRUE, comb.fixed = FALSE,
        print.byvar = FALSE, overall = FALSE,
+       overall.hetstat = FALSE,
        test.subgroup.random=FALSE, test.subgroup.fixed=FALSE)
 dev.off() 
 
 #6. without studies with sample size <10
 
 #prepare data
-data_sample_size_10 <- data_rob %>%
+data_sample_size_10 <- data %>%
   filter(total >= 10) %>%
   select(1:8)
 #conduct meta-analysis
@@ -379,6 +382,7 @@ asym_plot_sample_size_10 <- metaprop(events, total, data = data_sample_size_10,
                             sm = "PLOGIT", studlab=label, 
                             byvar=setting,# tau.common =TRUE,
                             prediction = TRUE,
+                            print.byvar = FALSE,
                             control=list(stepadj=0.05, maxiter=10000))#, method ="INV") #, verbose=TRUE, digits=5, control=list(stepadj=0.5))
 asym_plot_sample_size_10
 
@@ -390,9 +394,71 @@ forest(asym_plot_sample_size_10, #sortvar = n, #sorted by study precision
        col.square = "darkblue",
        just="left", colgap.studlab="1cm",
        predict=T, comb.random = TRUE, comb.fixed = FALSE,
-       print.byvar = FALSE, overall = FALSE,
[…]

### 2021-12-13 Q1_summary_table.R

@@ -37,8 +37,12 @@ response <- httr::POST(url, body = formData, encode = "form")
 Q1_table <- httr::content(response)
 #cut data at end of jan 31
 published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+#include additional study identified from ref list
+additional <- 11099
 Q1_table <- Q1_table %>%
-  filter(record_id <= 5296 | record_id %in% published_preprints)
+  filter(record_id <= 5296 | 
+           record_id %in% published_preprints | 
+           record_id %in% additional)
 Q1_table <- Q1_table %>%
   select(-contains("rob")) %>%
   select(-contains("risk_of_bias")) %>%
@@ -51,6 +55,7 @@ Q1_table <- Q1_table %>%
   mutate(country = ifelse(country == 10, "Australia", country),
          country = ifelse(country == 11, "Austria", country),
          country = ifelse(country == 15, "Bahrain", country),
+         country = ifelse(country == 16, "Bangladesh", country),                          
          country = ifelse(country == 19, "Belgium", country),
          country = ifelse(country == 27, "Brazil", country),
          country = ifelse(country == 28, "Brunei", country),
@@ -238,7 +243,7 @@ total_n <- Q1_table_studies %>%
 #calculate sex, total infections, asymp infections 
 
 sum_q1 <- Q1_table %>%
-  select(-age, -follow_up, -country) %>%
+  select(-age, -country) %>%
   group_by(setting) %>%
   summarise(female = sum(q1_female, na.rm = TRUE), 
             male = sum(q1_male, na.rm = TRUE), 

### 2021-12-20 ROB_new_HI_101221.R
Update ROB_new_HI_101221.R

@@ -1,5 +1,5 @@
-library(dplyr)
-#install.packages("ggpubr")
+##install all needed packages
+library("dplyr")
 library("ggpubr")
 
 #use the package as a new source. Some functions of the package are changed by HI

### 2021-12-20 ROB.R
delete unneeded scripts

@@ -1,46 +1,0 @@
-##################################################
-# Risk of bias visualisation                     #  
-##################################################
-rm(list=ls())
-
-#download package
-install.packages("devtools")
-devtools::install_github("mcguinlu/robvis")
-
-
-rob_data <- robvis::data_rob2
-rob_data$D6 <- rob_data$Overall
-rob_data$Overall <- NULL
-rob_data
-
-#summary table giving traffic lights for each domain in each study
-trafficlight_rob <- robvis::rob_traffic_light(data = rob_data,
-                                      tool = "Generic",
-                                      psize = 10,
-                                      overall = FALSE)
-
-trafficlight_rob +
-  ggplot2::labs(
-    caption = "  Domains:
-  D1: Representativeness of the sample (selection bias)
-  D2: Characteristics of non-respondents (selection bias)
-  D3: Symptom assessment (information bias)
-  D4: Recording of symptoms (information bias)
-  D5: Classification of asymptomatic status (misclassification bias)
-  D6: Selective reporting of symptoms status (attrition bias)
-                "
-  ) 
-
-
-#summary plot giving an overview of risk of bias from all studies
-
-names(rob_data) <- c("Representativeness of the sample (selection bias)",
-                     "D2: Characteristics of non-respondents (selection bias)",
-                     "D3: Symptom assessment (information bias)",
-                     "D4: Recording of symptoms (information bias)",
-                     "D5: Classification of asymptomatic status (misclassification bias)",
-                     "D6: Selective reporting of symptoms status (attrition bias)")
-summary_rob <- robvis::rob_summary(data = rob_data, tool = "ROB2")
-
-summary_rob
-###make changes to ggplot to relabel domains

### 2021-12-20 ROB_editing.R

@@ -1,175 +1,0 @@
-###code adapted from robvis package
-###https://github.com/mcguinlu/robvis/ 
-
-
-rob_traffic_light_edit <-
-  function(data,
-           tool,
-           colour = "cochrane",
-           psize = 10,
-           overall = TRUE,
-           ...) {
-    
-    check_tool(tool)
-    check_data(data)
-    colour <- weird_spelling(colour)
-    
-    check_colour(tool = tool, colour = colour)
-    
-    # Define colours
-    rob_colours <- get_colour(tool = tool, colour = colour)
-    
-    if (tool %in% c("Generic", "ROB1")) {
-      plot <- rob_traffic_light_custom(
-        data = data,
-        tool = tool,
-        rob_colours = rob_colours,
-        psize = psize,
-        overall = NULL,
-        ...
-      )
-    }
-    
-    # Add recommended saving height to the plot object
-    plot$rec_height <- get_height(
-      data = data,
-      tool = tool,
-      psize = psize,
-      type = "tf"
-    )
-    
-    # Add recommended saving width to the plot object
-    plot$rec_width <- get_width(data = data,
-                                psize = psize,
-                                type = "tf")
-    
-    plot$rob_type <- "traffic"
-    
-    return(plot)
-  }
-
-# ROB-1/Generic=================================================================
-
-rob_traffic_light_custom <- function(data,
-                                      tool,
-                                      rob_colours,
-                                      psize,
-                                      overall,
-                                      x_title = "Risk of bias domains",
-                                      y_title = "Study",
-                                      judgement_title = "Judgement",
-                                      judgement_labels = c("Critical",
-                                                           "High",
-                                                           "Unclear",
-                                                           "Low")) {
-  
-  rob1_warning(tool)
-  
-  max_domain_column <- dim(data)[2] - 1
-  
-  data.tmp <- data
-  
-  # Create caption vector, and add line breaks to maintain spacing
-  #captiondf <- data.frame(V1 = rep("", 8), stringsAsFactors = FALSE)
-  #captiondf$V1 <- c("D1: Representativeness of the sample (selection bias)\n",
-                    #"D2: Characteristics of non-respondents (selection bias)\n",
[…]

### 2021-12-20 SF_Q1_by_precision.R
remove APIs

@@ -14,7 +14,8 @@ library(httr) # use to retrieve data from REDCap
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',
@@ -59,13 +60,10 @@ asymptomaticQ1$label=paste0(asymptomaticQ1$author_1,
                                    paste0(" [cluster:",asymptomaticQ1$cluster,
                                           "]"),"")) # [FU: ",asymptomaticQ1$fup_median,"]")
 
-#data <- asymptomaticQ1[order(asymptomaticQ1$setting,1/(1/asymptomaticQ1$events+1/(asymptomaticQ1$total-asymptomaticQ1$events))),]
-
 asym_plot_by_precision <- metaprop(events, total, data = asymptomaticQ1, sm = "PLOGIT", 
                                    studlab = label)
 pdf(file = 'forest_meta_Q1_precision.pdf', width = 10, height = 27) 
 
-#forest(asym_plot_by_precision, sortvar = -seTE)
 forest(asym_plot_by_precision, sortvar = (1/(sqrt(seTE))))
 
 

### 2021-12-20 SF_Q1_by_source.R
delete API

@@ -19,7 +19,8 @@ library(Rcpp)
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',

### 2021-12-20 SF_Q1_countries.R
delete APIs

@@ -12,7 +12,8 @@ library(httr) # use to retrieve data from REDCap
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',

### 2021-12-20 SF_Q1_table_countries.R
delete APIs

@@ -22,7 +22,8 @@ library(Rcpp)
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',

### 2021-12-20 SF_Q2.1_by_precision.R
delete APIs

@@ -16,7 +16,8 @@ library(flextable)
 # get the data directly from redcap: 
 # report #172 is Q2.1 SAR:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData2_1 <- list("token"=token,
                     content='report',
                     format='csv',

### 2021-12-20 AsymptomaticAnalysis_Q2_2_Hira.R
Update AsymptomaticAnalysis_Q2_2_Hira.R

@@ -9,7 +9,8 @@ library(ggplot2)
 # report #157 is Q2.2:
 
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData2_2 <- list("token"=token,
                     content='report',
                     format='csv',
@@ -31,13 +32,6 @@ asymptomaticQ3$q3_setting=ifelse(asymptomaticQ3$q3_setting=="",NA,asymptomaticQ3
 
 asymptomaticQ3 <- asymptomaticQ3[-9,]
 
-#Michel`s codes` - doesn`t work now`
-# s <- strsplit(asymptomaticQ3$q3_setting, split = ";")
-# pp_m <- strsplit(asymptomaticQ3$q3_pp_m, split = ";")
-# pp_l <- strsplit(asymptomaticQ3$q3_pp_l, split = ";")
-# pp_u <- strsplit(asymptomaticQ3$q3_pp_u, split = ";")
-
-#New codes Hira - 06.04.21
 s <- gsub(";"," ",asymptomaticQ3$q3_setting)
 pp_m <- gsub(";"," ",asymptomaticQ3$q3_pp_m)
 pp_l <- gsub(";"," ",asymptomaticQ3$q3_pp_l)
@@ -45,15 +39,6 @@ pp_u <- gsub(";"," ",asymptomaticQ3$q3_pp_u)
 
 
 
-#Michel`s codes` - doesn`t work now`
-# dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ3$author_1), sapply(pp_m, length)),
-#                  Q3set=unlist(s),
-#                  p = as.numeric(unlist(pp_m)), 
-#                  l = as.numeric(unlist(pp_l)),
-#                  h = as.numeric(unlist(pp_u)),
-#                  setting="Pre-symptomatic",stringsAsFactors = FALSE)
-
-#New codes Hira - 06.04.21
 dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ3$author_1), sapply(pp_m, length)),
                  Q3set=s,
                  p = as.numeric(pp_m),
[…]

### 2021-12-20 Q2_2_Figure4.R
delete

@@ -89,19 +89,12 @@ dfQ3$p=as.numeric(dfQ3$p)
 dfQ3$l=as.numeric(dfQ3$l)
 dfQ3$h=as.numeric(dfQ3$h)
 
-# dfQ3c<-read.csv(file="Q3.csv", stringsAsFactors = FALSE)
-# dfQ3$p=dfQ3$p/100
-# dfQ3$l=dfQ3$l/100
-# dfQ3$h=dfQ3$h/100
 
 dataG=dfQ3
 
 dig=2
 r<-function(x){format(round(as.numeric(x),2),dig=2)}
 
-
-# dataG$label=ifelse(dataG$type==2,
-#                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 
 dataG$label=ifelse(dataG$label=="   Ganyani T",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)

### 2021-12-20 Q1_summary_table.R
delete APIs

@@ -22,7 +22,8 @@ library(metafor)
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',

### 2021-12-20 MC analysis v3.R
Delete MC analysis v3.R

@@ -1,70 +1,0 @@
-dataG=df_Q3SAR
-dig=2
-r<-function(x){format(round(as.numeric(x),2),dig=2)}
-r2<-function(x){format(round(as.numeric(x),4),dig=2)}
-dataG$label=ifelse(dataG$type==2,paste0("   ",dataG$label),dataG$label)
-dataG$fontface=ifelse(dataG$type==1, "italic","plain")
-dataG$fontface=ifelse(dataG$type==3, "bold",dataG$fontface)
-dataG$label_studyCI=ifelse(!is.na(dataG$h), paste0("[",r(dataG$l),";",r2(dataG$h),"]"),NA)
-#dataG$label_studyCI=ifelse(!is.na(dataG$Pl), paste0("[",r(dataG$Pl),";",r(dataG$Ph),"]"),dataG$label_studyCI)
-#dataG$label_studyCI=ifelse(!is.na(dataG$Rl), paste0("[",r(dataG$Rl),";",r(dataG$Rh),"]"),dataG$label_studyCI)
-dataG$label_study=ifelse(!is.na(dataG$p),r(dataG$p),NA)
-dataG$label_studyC=ifelse(!is.na(dataG$nc),paste0(dataG$event.c,"/",dataG$nc),NA)
-dataG$label_studyE=ifelse(!is.na(dataG$ne),paste0(dataG$event.e,"/",dataG$ne),NA)
-
-breaks=c(0.01,0.1,1,10)
-
-
-dataG = dataG %>% mutate(Rp=ifelse(type==3, p, NA),
-                         Rl=ifelse(type==3, l, NA),
-                         Rh=ifelse(type==3, h, NA),
-                         p=ifelse(type!=3, p, NA),
-                         l=ifelse(type!=3, l, NA),
-                         h=ifelse(type!=3, h, NA))
-
-tmp=dataG[!is.na(dataG$Rl),]
-
-p=ggplot()+ 
-  geom_point(data=dataG,aes(y=dataG$line, x=log(dataG$p)),fill="gray", shape=22, color="black",size=4)+
-  geom_errorbarh(data=dataG,aes(y=dataG$line, xmin=log(dataG$l), xmax=log(dataG$h)), height=0.3)+
-  
-  
[…]

### 2021-12-20 Q1.R
Update Q1.R

@@ -17,7 +17,8 @@ library(metafor)
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',
@@ -142,11 +143,6 @@ dev.off()
 
 #cut data at end of jan 31
 
-#published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
-# data <- data %>%
-#   filter(record_id <= 5296 | record_id %in% published_preprints)
-
-#10.12.21 - updated HI
 published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
 #include additional study identified from ref list
 additional <- 11099
@@ -233,13 +229,16 @@ forest(asym_plot_select_bias, sortvar = 1/seTE, #sorted by study precision
        test.subgroup.random=TRUE, test.subgroup.fixed=FALSE)
 dev.off() 
 
-#subgroup analyses by ROB assessments
+######################################
+#subgroup analyses by ROB assessments#
+######################################
 
 #download rob data
 
 # get the data directly from redcap:
 urlrob <- "https://redcap.ispm.unibe.ch/api/"
-tokenrob <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formDatarob <- list("token"=tokenrob,
                     content='report',
                     format='csv',
@@ -263,12 +262,13 @@ names(data_rob)
 
 #1. selection bias - only analyse those with low ROB for representativeness
 #and characteristics of non-respondents
+
 #prepare data
 data_rob_1 <- data_rob %>%
   filter(rob_1 == 3 & rob_2 == 3) %>%
   select(1:8)
-#conduct meta-analysis
 
+#conduct meta-analysis
 asym_plot_rob_1<-metaprop(events,total,data=data_rob_1,sm = "PLOGIT", 
                           studlab=label, byvar=setting, prediction = TRUE, 
                           print.byvar = FALSE, comb.fixed = FALSE,
@@ -290,12 +290,13 @@ dev.off()
 
[…]

### 2021-12-20 ROB_new_081021.R
Delete ROB_new_081021.R

@@ -1,256 +1,0 @@
-##################################################
-# Risk of bias visualisation                     #  
-##################################################
-rm(list=ls())
-
-#download package
-#install.packages("devtools")
-#devtools::install_github("mcguinlu/robvis")
-library(dplyr)
-install.packages("ggpubr")
-library("ggpubr")
-
-#use the package as a new source. Some functions of the package are changed by HI
-source("robisfunctions.R")
-
-# get the data directly from redcap:
-urlrob <- "https://redcap.ispm.unibe.ch/api/"
-tokenrob <- "F2725F15FE84D2832E2793BB23B0A62B"
-formDatarob <- list("token"=tokenrob,
-                    content='report',
-                    format='csv',
-                    report_id='283',
-                    csvDelimiter='',
-                    rawOrLabel='raw',
-                    rawOrLabelHeaders='raw',
-                    exportCheckboxLabel='false',
-                    returnFormat='csv'
-)
-response_rob <- httr::POST(urlrob, body = formDatarob, encode = "form")
-rob_records <- httr::content(response_rob)
-
-rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
-rob_records <- rob_records[rob_records$record_id < "5566", ]
-
-df_rob <- rob_records %>%
-  select(record_id,author_1, authoryear,quest___1, q3_sar, setting2, 
-         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
-         risk_of_bias_update_3_complete)
-df_rob['setting'] <- NA
-
-
-df_rob <- df_rob %>%
-  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
-         setting = ifelse(setting2 == 2, "Contact investigation, aggregated", setting),
-         setting = ifelse(setting2 == 3, "Outbreak investigation", setting),
-         setting = ifelse(setting2 == 4, "Statistical model", setting),
-         setting = ifelse(setting2 == 5, "Screening", setting),
-         setting = ifelse(setting2 == 6, "Hospitalised adults", setting),
-         setting = ifelse(setting2 == 7, "Hospitalised children", setting),
[…]

### 2021-12-20 ROB_analysis.R
Create ROB_analysis.R

@@ -1,0 +1,269 @@
+##install all needed packages
+library("dplyr")
+library("ggpubr")
+
+#use the package as a new source. Some functions of the package are changed by HI
+source("robisfunctions.R")
+
+# get the data directly from redcap:
+urlrob <- "https://redcap.ispm.unibe.ch/api/"
+#APIs token is not sharable
+token <- "##################################"
+formDatarob <- list("token"=tokenrob,
+                    content='report',
+                    format='csv',
+                    report_id='283',
+                    csvDelimiter='',
+                    rawOrLabel='raw',
+                    rawOrLabelHeaders='raw',
+                    exportCheckboxLabel='false',
+                    returnFormat='csv'
+)
+response_rob <- httr::POST(urlrob, body = formDatarob, encode = "form")
+rob_records <- httr::content(response_rob)
+
+# rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
+
+#censor until 5296 (31 Jan) plus the published versions of preprints
+# pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
+# rob_records <- rob_records %>%
+#   filter(record_id %in%  pub_preprints | record_id <= 5296)
+
+published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+#include additional study identified from ref list
+additional <- 11099
+rob_records <- rob_records %>%
+  filter(record_id <= 5296 |
+           record_id %in% published_preprints |
+           record_id %in% additional)
+
+
+
+#prepare a dataset
+# df_rob <- rob_records %>%
+#   select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
+#          rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
+#          risk_of_bias_update_3_complete)
+
+df_rob <- rob_records %>%
+  select(record_id,author_1, quest___1, q3_sar, setting2, 
+         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
+         risk_of_bias_update_3_complete)
+df_rob['setting'] <- NA
+
+
+df_rob <- df_rob %>%
[…]

### 2021-12-20 Q2_1.R
delete API

@@ -19,7 +19,8 @@ library(metafor)
 # get the data directly from redcap: 
 # report #172 is Q2.1 SAR:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData2_1 <- list("token"=token,
                     content='report',
                     format='csv',

### 2021-12-20 ROB_new_HI_101221.R

@@ -1,268 +1,0 @@
-##install all needed packages
-library("dplyr")
-library("ggpubr")
-
-#use the package as a new source. Some functions of the package are changed by HI
-source("robisfunctions.R")
-
-# get the data directly from redcap:
-urlrob <- "https://redcap.ispm.unibe.ch/api/"
-tokenrob <- "F2725F15FE84D2832E2793BB23B0A62B"
-formDatarob <- list("token"=tokenrob,
-                    content='report',
-                    format='csv',
-                    report_id='283',
-                    csvDelimiter='',
-                    rawOrLabel='raw',
-                    rawOrLabelHeaders='raw',
-                    exportCheckboxLabel='false',
-                    returnFormat='csv'
-)
-response_rob <- httr::POST(urlrob, body = formDatarob, encode = "form")
-rob_records <- httr::content(response_rob)
-
-# rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")
-
-#censor until 5296 (31 Jan) plus the published versions of preprints
-# pub_preprints <- c(5565, 6219, 6685, 7030, 7465, 8249, 9442, 9484) #published version of preprints before 31 Jan
-# rob_records <- rob_records %>%
-#   filter(record_id %in%  pub_preprints | record_id <= 5296)
-
-published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
-#include additional study identified from ref list
-additional <- 11099
-rob_records <- rob_records %>%
-  filter(record_id <= 5296 |
-           record_id %in% published_preprints |
-           record_id %in% additional)
-
-
-
-#prepare a dataset
-# df_rob <- rob_records %>%
-#   select(record_id,author_1, authoryear, quest___1, q3_sar, setting2, 
-#          rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
-#          risk_of_bias_update_3_complete)
-
-df_rob <- rob_records %>%
-  select(record_id,author_1, quest___1, q3_sar, setting2, 
-         rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, 
-         risk_of_bias_update_3_complete)
-df_rob['setting'] <- NA
-
-
-df_rob <- df_rob %>%
-  mutate(setting = ifelse(setting2 == 1, "Contact investigation", setting),
[…]

### 2021-12-20 Q2_2.R
Update Q2_2.R

@@ -92,19 +92,13 @@ dfQ3$p=as.numeric(dfQ3$p)
 dfQ3$l=as.numeric(dfQ3$l)
 dfQ3$h=as.numeric(dfQ3$h)
 
-# dfQ3c<-read.csv(file="Q3.csv", stringsAsFactors = FALSE)
-# dfQ3$p=dfQ3$p/100
-# dfQ3$l=dfQ3$l/100
-# dfQ3$h=dfQ3$h/100
+
 
 dataG=dfQ3
 
 dig=2
 r<-function(x){format(round(as.numeric(x),2),dig=2)}
 
-
-# dataG$label=ifelse(dataG$type==2,
-#                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 
 
 dataG$label=ifelse(dataG$label=="   Ganyani T",

### 2021-12-20 Q2_2.R
delete API

@@ -24,7 +24,8 @@ loadfonts(device = "win")
 # report #157 is Q2.2:
 
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+#APIs token is not sharable
+token <- "##################################"
 formData2_2 <- list("token"=token,
                     content='report',
                     format='csv',

### 2021-12-22 Q2_2_Figure4.R
Update Q2_2_Figure4.R

@@ -1,3 +1,9 @@
+rm(list = ls())
+
+library(RCurl)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
 
 ## Q2.2 = Figure4 #####
 
@@ -89,12 +95,19 @@ dfQ3$p=as.numeric(dfQ3$p)
 dfQ3$l=as.numeric(dfQ3$l)
 dfQ3$h=as.numeric(dfQ3$h)
 
+# dfQ3c<-read.csv(file="Q3.csv", stringsAsFactors = FALSE)
+# dfQ3$p=dfQ3$p/100
+# dfQ3$l=dfQ3$l/100
+# dfQ3$h=dfQ3$h/100
 
 dataG=dfQ3
 
 dig=2
 r<-function(x){format(round(as.numeric(x),2),dig=2)}
 
+
+# dataG$label=ifelse(dataG$type==2,
+#                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 
 dataG$label=ifelse(dataG$label=="   Ganyani T",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
@@ -106,8 +119,10 @@ dataG$label=ifelse(dataG$label=="   Tindale LC",
 
 dataG$label=ifelse(dataG$label=="   Zhang W",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
-dataG$label=ifelse(dataG$label=="   Casey M",
-                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
+
+#Removed on Wednesday (22.12.21)
+#dataG$label=ifelse(dataG$label=="   Casey M",
+#                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 
 dataG$label=ifelse(dataG$label== "   Moghadas SM",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
@@ -129,7 +144,6 @@ p=ggplot()+
   
   
[…]

### 2021-12-22 Q2_2.R
Update Q2_2.R

@@ -1,3 +1,4 @@
+rm(list = ls())
 
 #download packages
 library(meta)
@@ -111,9 +112,6 @@ dataG$label=ifelse(dataG$label=="   Tindale LC",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 
 dataG$label=ifelse(dataG$label=="   Zhang W",
-                   paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
-
-dataG$label=ifelse(dataG$label=="   Casey M",
                    paste0(dataG$label, " ", ifelse(!is.na(dataG$Q3set),paste0("[",dataG$Q3set,"]"),"")),dataG$label)
 
 

### 2021-12-22 AsymptomaticAnalysis_Q2_2_old.R
delete not needed

@@ -1,131 +1,0 @@
-rm(list = ls())
-
-library(RCurl)
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-
-# get the data directly from REDCap: 
-# report #157 is Q2.2:
-
-url <- "https://redcap.ispm.unibe.ch/api/"
-#APIs token is not sharable
-token <- "##################################"
-formData2_2 <- list("token"=token,
-                    content='report',
-                    format='csv',
-                    report_id='157',
-                    csvDelimiter='',
-                    rawOrLabel='raw',
-                    rawOrLabelHeaders='raw',
-                    exportCheckboxLabel='false',
-                    returnFormat='csv'
-)
-response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
-asymptomaticQ2_2 <- httr::content(response2_2)
-
-
-library(dplyr)
-
-asymptomaticQ3 = asymptomaticQ2_2 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
-asymptomaticQ3$q3_setting=ifelse(asymptomaticQ3$q3_setting=="",NA,asymptomaticQ3$q3_setting)
-
-asymptomaticQ3 <- asymptomaticQ3[-9,]
-
-s <- gsub(";"," ",asymptomaticQ3$q3_setting)
-pp_m <- gsub(";"," ",asymptomaticQ3$q3_pp_m)
-pp_l <- gsub(";"," ",asymptomaticQ3$q3_pp_l)
-pp_u <- gsub(";"," ",asymptomaticQ3$q3_pp_u)
-
-
-
-dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ3$author_1), sapply(pp_m, length)),
-                 Q3set=s,
-                 p = as.numeric(pp_m),
-                 l = as.numeric(pp_l),
-                 h = as.numeric(pp_u),
-                 setting="Pre-symptomatic",stringsAsFactors = FALSE)
-
-dfQ3a[dfQ3a==9999]<-NA
-dfQ3a=dfQ3a[!is.na(dfQ3a$p),]
-
[…]

### 2021-12-22 Q2_2_Figure4.R

@@ -1,169 +1,0 @@
-rm(list = ls())
-
-library(RCurl)
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-
-## Q2.2 = Figure4 #####
-
-url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
-formData2_2 <- list("token"=token,
-                    content='report',
-                    format='csv',
-                    report_id='157',
-                    csvDelimiter='',
-                    rawOrLabel='raw',
-                    rawOrLabelHeaders='raw',
-                    exportCheckboxLabel='false',
-                    returnFormat='csv'
-)
-response2_2 <- httr::POST(url, body = formData2_2, encode = "form")
-asymptomaticQ2_2 <- httr::content(response2_2)
-
-published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
-asymptomaticQ2_2 <- asymptomaticQ2_2 %>%
-  filter(record_id <= 5296 | record_id %in% published_preprints)
-
-library(dplyr)
-
-asymptomaticQ2_2 = asymptomaticQ2_2 %>% filter(!(q3_pp_m=="" & is.na(q3_pa_m)))
-asymptomaticQ2_2$q3_setting=ifelse(asymptomaticQ2_2$q3_setting=="",NA,asymptomaticQ2_2$q3_setting)
-
-s <- strsplit(asymptomaticQ2_2$q3_setting, split = ";")
-pp_m <- strsplit(asymptomaticQ2_2$q3_pp_m, split = ";")
-pp_l <- strsplit(asymptomaticQ2_2$q3_pp_l, split = ";")
-pp_u <- strsplit(asymptomaticQ2_2$q3_pp_u, split = ";")
-
-dfQ3a=data.frame(label=rep(paste0("   ",asymptomaticQ2_2$author_1), sapply(pp_m, length)),
-                 Q3set=unlist(s),
-                 p = as.numeric(unlist(pp_m)), 
-                 l = as.numeric(unlist(pp_l)),
[…]

### 2021-12-22 Manuscript_draft_RmarkdownExample.Rmd
update

--- 2021-11-05 Manuscript_draft.Rmd
@@
 title: "Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis"
-author: "Diana Buitrago-Garcia, Aziz Mert Ipekci, Leonie Heron, Stefanie Hossmann, Hira Imeri, Georgia Salanti, Nicola Low"
+author: "Diana Buitrago-Garcia, Aziz Mert Ipekci, Leonie Heron, Hira Imeri, Georgia Salanti, Nicola Low, ..."
 date: "`r format(Sys.time(), '%d/%m/%y')`"

### 2021-12-22 RshinyApp-Screening/config.R
Add  screening app

@@ -1,0 +1,26 @@
+
+
+################ set user data here: ###############
+
+# example project
+#API<- '4E0DB920DE37B84B5B905773scdfjkl' # not valid API key
+#user<- 'MC' # for example KM
+#reportid = '150' #screening report
+
+# live project
+reportid='152'
+API='#################################'
+
+####################################################
+
+
+row_limit = 30
+
+log_dir_veri = "logs_veri"
+temp_dir_veri = "temp_veri"
+
+log_dir_screen = "logs_screen"
+temp_dir_screen = "temp_screen"
+
+
+logins=read.csv(file="logins.csv", stringsAsFactors = FALSE)

### 2021-12-22 RshinyApp-Screening/server.R

@@ -1,0 +1,167 @@
+
+source("config.R")
+source("shared.R")
+
+decisions<-c("No: No reason needed" = 1,
+             "No: Publication not on COVID-19" = 11,
+             "No: No original data" = 12,
+             "No: Data included in other publication" = 13,
+             "No: Duplicate" = 14,
+             "No: Insufficient extractable data" = 15,
+             "No: Study design inappropriate" = 16,
+             "No: Infections not diagnosed with a molecular test" = 17,
+             "No: Aim of mathematical model not in review scope"=19,
+             "No: Inadequate or undocumented follow-up time"=20,
+             "No: Other" = 18)
+
+postdata<-function(id, decision,helpme,user,design_groupscreen,comment){ # this function handles the reason (decision) and posts this to the appropriate id, with the appropriate logic.
+  if(helpme==1){
+    data_redcap<-paste0('record_id,help,screen1_assigned,comment,screening_api_complete\n',id,',',helpme,',',user,',\"',comment,'\",1')
+  }else{
+    if(decision==99){  # include decision:
+      data_redcap<-paste0('record_id,review,help,screen1_assigned,design_groupscreen,comment,screening_api_complete\n', id,',1,',helpme,',',design_groupscreen,',',user,',\"',comment,'\",1')
+    } else{ # exclude decisions:
+      data_redcap<-paste0('record_id,review,ex_reas,help,screen1_assigned,design_groupscreen,comment,screening_api_complete\n', id,',2,',decision,',',helpme,',',design_groupscreen,',',user,',\"',comment,'\",1')
+    }
+    
+  }
+  postRedcap(data_redcap)
+}
+
+
+server <- function(input, output, session) {
+  logname<-paste0(log_dir_screen,  "/", format(Sys.time(), "%Y%m%d_%H%M%S_"), ".csv")
+  
+  # retrieve screening data
+  result <- postForm(
+    uri='https://redcap.ispm.unibe.ch/api/',
+    token=API, # API of project, MC
+    content='report',
+    format='csv',
+    report_id=reportid, #  from config
+    rawOrLabel='raw',
+    rawOrLabelHeaders='raw',
+    exportCheckboxLabel='false',
+    returnFormat='csv'
+  )
+  
+  # write temp file with retrieved data, timestamped
+  filename<-paste0(temp_dir_screen, "/", format(Sys.time(), "%Y%m%d_%H%M%S_"), "data_set.csv")
+  
+  
[…]

### 2021-12-22 RshinyApp-Screening/shared.R

@@ -1,0 +1,62 @@
+# decisions
+decisions<-c("No: No reason needed" = 1,
+             "No: Publication not on COVID-19" = 11,
+             "No: No original data" = 12,
+             "No: Data included in other publication" = 13,
+             "No: Duplicate" = 14,
+             "No: Insufficient extractable data" = 15,
+             "No: Study design inappropriate" = 16,
+             "No: Infections not diagnosed with a molecular test" = 17,
+             "No: Aim of mathematical model not in review scope"=19,
+             "No: Inadequate or undocumented follow-up time"=20,
+             "No: Other" = 18)
+
+postRedcap = function(data) {
+  cat(data)
+  result<-postForm(
+    uri='https://redcap.ispm.unibe.ch/api/',
+    token=API,
+    content='record',
+    format='csv',
+    type='flat',
+    overwriteBehavior='overwrite',
+    forceAutoNumber='false',
+    data=data,
+    returnContent='ids',
+    returnFormat='csv'
+  )
+  return(result) # returns id if succesful
+}
+
+highlightWords = function(text)
+{
+  # highlight words with high relevance, use regex to not completly mess up text
+  text = gsub('(?i)[.?: ](review|reviews)[ ,]', '<mark style="background-color:#ffee6f">\\1</mark>',    text, perl = T)
+  text = gsub('(?i)[.?: ](here)[ ,]', '<mark style="background-color:#ffee6f">\\1</mark>',              text, perl = T)
+  text = gsub('(?i)[.?: ](we)[ ,]', '<mark style="background-color:#ffee6f">\\1</mark>',                text, perl = T)
+  text = gsub('(?i)[.?: ](mouse|mice)[ ,]', '<mark style="background-color:#ffee6f">\\1</mark>',        text, perl = T)
+  text = gsub('(?i)[.?: ](asymp|pre\\-symp|presymp|preclinical|pre\\-clinical|without symptoms|no symptoms|free of symptoms|non\\-symp|nonsymp|symptom\\-free|symptomfree)', '<mark style="background-color:#90EE90">\\1</mark>',        text, perl = T)
+  text
+}  
+
+# logging function
+logfun = function(a, response, redcapdb, logname, addtext = "" )
+{
+  tryCatch(
+    {
+      response_id = as.numeric(gsub("[^\\d]+", "", response, perl=TRUE))
+    
+      
+      if(response_id == redcapdb$id[a]){
+        
[…]

### 2021-12-22 RshinyApp-Screening/ui.R

@@ -1,0 +1,20 @@
+
+library(RCurl)
+library(shiny)
+
+
+source("config.R")
+source("shared.R")
+
+ui <- fluidPage(
+  tags$head(tags$style(HTML(" body { margin:0.4%; "))),
+  titlePanel(HTML("COVID screening: Asymptomatics"), windowTitle="COVID SCREENING APP"),
+  fluidRow(shinyjs::useShinyjs(),
+    textOutput("server_response", inline = T),
+    textOutput("login_response", inline = T), br(),
+    selectInput('in1', 'Select user:', c(Choose='', logins$users), selectize=FALSE),
+    passwordInput('passw', 'Code', value = ""),
+    actionButton("add", "Show data!"),
+    br()
+  )
+)

### 2021-12-22 RshinyApp-Verification/config.R
add verification app

@@ -1,0 +1,27 @@
+# file to store configuration 
+
+
+################ set user data here: ###############
+
+# example project
+#API<- '4E0DB920DE37B84B5B905773scdfjkl' # not valid API key
+#user<- 'MC' # for example KM
+#reportid = '150' #screening report
+
+# live project
+reportid='152'
+API='#################################'
+
+####################################################
+
+
+row_limit = 30
+
+log_dir_veri = "logs_veri"
+temp_dir_veri = "temp_veri"
+
+log_dir_screen = "logs_screen"
+temp_dir_screen = "temp_screen"
+
+
+logins=read.csv(file="logins.csv", stringsAsFactors = FALSE)

### 2021-12-22 RshinyApp-Verification/server.R

@@ -1,0 +1,145 @@
+
+source("config.R")
+source("shared.R")
+
+
+postdata<-function(id,agreed,design_group,commentText,user){ # this function handles the reason (decision) and posts this to the appropriate id, with the appropriate logic.
+  if(agreed==1){
+    data_redcap<-paste0('record_id,design_group,screening_api_complete\n',id,',',design_group,',2')
+  }else{
+    data_redcap<-paste0('record_id,design_group,veri_comment,screening_api_complete\n', id,',',design_group,',',paste0("\"",user,": ",commentText,"\""),',0')
+  }
+  postRedcap(data_redcap)
+}
+
+
+server <- function(input, output, session) {
+  logname<-paste0(log_dir_screen,  "/", format(Sys.time(), "%Y%m%d_%H%M%S_"), ".csv")
+  
+  # put inside server so its unique per user
+  result <- postForm(
+    uri='https://redcap.ispm.unibe.ch/api/',
+    token=API, # API of copy project, MC
+    content='report',
+    format='csv',
+    report_id=reportid, #  3395 = report number verification
+    rawOrLabel='label',
+    rawOrLabelHeaders='raw',
+    exportCheckboxLabel='false',
+    returnFormat='csv'
+  )
+  
+  # write temp file with retrieved data, timestamped
+  filename<-paste0(temp_dir_screen, "/", format(Sys.time(), "%Y%m%d_%H%M%S_"), "data_set.csv")
+  
+  
+  con <- file(filename, open = "wt", encoding = "UTF-8") # encoding does not properly translate ('portuguese' characters not correct)
+  writeLines(result, con = con)
+  close(con)
+  
+  redcapdb<- read.csv(filename,header=TRUE, stringsAsFactors=FALSE)
+  #redcapdb<-head(redcapdb, row_limit) #limit number of displayed rows
+  
+  redcapdb$id=redcapdb$record_id
+  rvals = reactiveValues()
+  
+  observeEvent(rvals, {
+    output$server_response = renderText(paste0("last response: ", rvals$last))  
+  })
+  
+  observeEvent(input$add, {
+
+    user=input$in1
+    passw=input$passw
+    
+    if(user!=""){
+    
+      login=ifelse(passw==logins[logins$users==user,]$pw,TRUE,FALSE)
+      login2=logins[logins$users==user,]$names
+      output$login_response=renderText(paste0("User selected:", logins[logins$users==user,]$names, " login success:",login))
+      if(login){
[…]

### 2021-12-22 RshinyApp-Verification/ui.R

@@ -1,0 +1,22 @@
+
+
+library(RCurl)
+library(shiny)
+
+
+source("config.R")
+source("shared.R")
+
+ui <- fluidPage(
+  tags$head(tags$style(HTML(" body { margin:0.4%; "))),
+  titlePanel(HTML("COVID verification"), windowTitle="COVID VERIFICATION APP"),
+  fluidRow(shinyjs::useShinyjs(),
+    #h4(paste("user selection:",user)),
+    textOutput("server_response", inline = T),
+    textOutput("login_response", inline = T), br(),
+    selectInput('in1', 'Select user:', c(Choose='', logins$users), selectize=FALSE),
+    passwordInput('passw', 'Code', value = ""),
+    actionButton("add", "Show data!"),
+    br()
+  )
+)

### 2021-12-22 RshinyApp-Extraction/config.R
add Data Extraction app

@@ -1,0 +1,23 @@
+
+# file to store configuration 
+
+
+################ set user data here: ###############
+
+
+# live project
+reportid='309'
+#can`t share API`
+API='#####################################'
+
+####################################################
+
+
+row_limit = 1
+
+
+log_dir_rob = "logs_rob"
+temp_dir_rob = "temp_rob"
+
+
+logins=read.csv(file="logins.csv", stringsAsFactors = FALSE)

### 2021-12-22 RshinyApp-Extraction/server.R

@@ -1,0 +1,440 @@
+######Hira Imeri   ROB application: Reviewer 2####
+
+library(shiny)
+library(RCurl)
+library(shinyjs)
+
+source("config.R")
+source("shared.R")
+
+
+
+
+postnew <- function(id, user, studyaim,studydesign,otherstudydesign,diagnosis,settings,othersetting,settingsother,countries,regions,ibcheck1,ibcheck2,ibcheck3,ibcheck4,questionf,questions,fccomment,selectn,q1event,q1total,q2event,q2total,followup,q1female,q1male,q1median,q1iqr,q1comment,omitstudyq1,summaryres,asar,asarrisk,asarrisklc,asarriskuc,asarods,asarodslc,asarodsuc,psar,psarrisk,psarrisklc,psarriskuc,psarods,psarodslc,psarodsuc,mildsar,modsar,sevsar,anysar,q3region,prosympmed,prosympmedlc,prosympmeduc,prosarrriskmed,prosarrisklowc,prosarriskupc,prosarcomment,agecheck1,agecheck2,agecheck3,agecheck4,agecheck5){
+  data_redcap <- paste0('record_id, ext_gen, aim, design, oth_spec, gen_diag, setting, oth_spec_3, setting2, country, region,fup___1,fup___2,fup___3,fup___4,quest___1,quest___5,comments_gen,q1_nclus,q1_c1_event,q1_c1_total,q1_c2_event,q1_c2_total,q1_fu_descrip,q1_female,q1_male,q1_age_median,q1_age_iqr,comment_q1,q3_sar,q3_sum,q3_sar_a,q3_sae_a_rr,q3_sae_a_rr_lci,q3_sae_a_rr_uci,q3_sae_a_or,q3_sae_a_or_lci,q3_sae_a_or_uci,q3_sar_p,q3_sar_rr,q3_sar_rr_lci,q3_sar_rr_uci,q3_sar_or,q3_sar_or_lci,q3_sar_or_uci,q3_sar_m1,q3_sar_m2,q3_sar_c,q3_sar_s,q3_setting,q3_pa_m,q3_pa_l,q3_pa_u,q3_pp_m,q3_pp_l,q3_pp_u,q3_comments,agerange___1,agerange___2,agerange___3,agerange___4,agerange___5\n',
[…]

### 2021-12-22 RshinyApp-Extraction/ui.R

@@ -1,0 +1,22 @@
+# Extraction Application
+
+library(RCurl)
+library(shiny)
+
+
+source("config.R")
+source("shared.R")
+
+ui <- fluidPage(
+  tags$head(tags$style(HTML(" body { margin:0.4%; "))),
+  titlePanel(HTML("COVID general information: Asymptomatics"), windowTitle="COVID EXTRACTION APP"),
+  fluidRow(shinyjs::useShinyjs(),
+           #h4(paste("user selection:",user)),
+           textOutput("server_response", inline = T),
+           textOutput("login_response", inline = T), br(),
+           selectInput('in1', 'Select user:', c(Choose='', logins$users), selectize=FALSE),
+           passwordInput('passw', 'Code', value = ""),
+           actionButton("add", "Show data!"),
+           br()
+  )
+)

### 2021-12-22 ROB_analysis.R
Update ROB_analysis.R

@@ -2,7 +2,7 @@
 library("dplyr")
 library("ggpubr")
 
-#use the package as a new source. Some functions of the package are changed by HI
+#use the robvis package as a new source. Some functions of the package are changed according to our review
 source("robisfunctions.R")
 
 # get the data directly from redcap:

### 2021-12-22 RshinyApp-RiskOfBias-SecondReviewer/config.R
add ROB app second reviewer

@@ -1,0 +1,21 @@
+
+# file to store configuration 
+
+
+################ set user data here: ###############
+
+
+# live project
+reportid='283'
+#API can`t be shared
+API='#################################'
+
+
+row_limit = 1
+
+
+log_dir_rob = "logs_rob"
+temp_dir_rob = "temp_rob"
+
+
+logins=read.csv(file="logins.csv", stringsAsFactors = FALSE)

### 2021-12-22 RshinyApp-RiskOfBias-SecondReviewer/server.R

@@ -1,0 +1,464 @@
+######ROB application: Reviewer 2####
+
+library(shiny)
+library(RCurl)
+library(shinyjs)
+
+source("config.R")
+source("shared.R")
+
+#1. sb - selection bias 2. rr - responnse rate 
+#3. sbrr - selection bias & response rate 4. ib - information bias
+#5. si - selective or incomplete 6. final comments - fc
+
+
+postnew <- function(id, user, sbreport,sbselect,sbcomments,rrselect1,rrselect2,rrcomment1,rrcomment2,rrcomment3,rrcomment4,sbrrselect,sbrrcomment,ibcomment,ibselect,ibcomment2,ibselect2,ibcomment3,ibcheck1,ibcheck2,ibcheck3,ibcheck4,ibcheck5,ibcomment4,ibselect3,ibcomment5,siselect1,siselect2,sicomment,fcselect,fccomment,robcluster,sbreportc2,sbselectc2,rrselect1c2,rrselect2c2,rrcomment1c2,rrcomment2c2,rrcomment3c2,sbrrselectc2,ibselectc2,ibselect2c2,ibcheck1c2,ibcheck2c2,ibcheck3c2,ibcheck4c2,ibcheck5c2,ibcheck6c2,ibselect3c2,siselect1c2,siselect2c2,fcselectc2){
[…]

### 2021-12-22 RshinyApp-RiskOfBias-SecondReviewer/shared.R

@@ -1,0 +1,41 @@
+
+
+postRedcap = function(data) {
+  cat(data)
+  result<-postForm(
+    uri='https://redcap.ispm.unibe.ch/api/',
+    token=API,
+    content='record',
+    format='csv',
+    type='flat',
+    overwriteBehavior='overwrite',
+    forceAutoNumber='false',
+    data=data,
+    returnContent='ids',
+    returnFormat='csv'
+  )
+  return(result) # returns id if succesful
+}
+
+
+# logging function
+logfun = function(a, response, redcapdb, logname, addtext = "" )
+{
+  tryCatch(
+    {
+      response_id = as.numeric(gsub("[^\\d]+", "", response, perl=TRUE))
+    
+      
+      if(response_id == redcapdb$id[a]){
+        
+        write.table(data.frame(redcapdb$id[a], "success", response, addtext) , logname, sep = ",", col.names = F,row.names = F, append = T)
+      }
+      else        {
+        write.table(data.frame(redcapdb$id[a], "possible failure", response, addtext) , logname, sep = ",", col.names = F, row.names = F, append = T)
+      }
+    }, error=function(cond) {write.table(data.frame(redcapdb$id[a], "possible failure", response) , logname, sep = ",", col.names = F, row.names = F, append = T)}
+    , warning = function (cond) {write.table(data.frame(redcapdb$id[a], "possible failure", response) , logname, sep = ",", col.names = F, row.names = F, append = T)})
+}
+
+
+

### 2021-12-22 RshinyApp-RiskOfBias-SecondReviewer/ui.R

@@ -1,0 +1,20 @@
+
+library(RCurl)
+library(shiny)
+
+source("config.R")
+source("shared.R")
+
+ui <- fluidPage(
+  tags$head(tags$style(HTML(" body { margin:0.4%; "))),
+  titlePanel(HTML("COVID ROB: Asymptomatics (Reviewer 2)"), windowTitle="COVID ROB APP"),
+  fluidRow(shinyjs::useShinyjs(),
+           #h4(paste("user selection:",user)),
+           textOutput("server_response", inline = T),
+           textOutput("login_response", inline = T), br(),
+           selectInput('in1', 'Select user:', c(Choose='', logins$users), selectize=FALSE),
+           passwordInput('passw', 'Code', value = ""),
+           actionButton("add", "Show data!"),
+           br()
+  )
+)

### 2021-12-22 RshinyApp-RiskOfBias-FirstReviewer/config.R
add ROB app first reviewer

@@ -1,0 +1,21 @@
+
+# file to store configuration 
+
+
+################ set user data here: ###############
+
+
+# live project
+reportid='283'
+API='################################'
+
+
+
+row_limit = 1
+
+
+log_dir_rob = "logs_rob"
+temp_dir_rob = "temp_rob"
+
+
+logins=read.csv(file="logins.csv", stringsAsFactors = FALSE)

### 2021-12-22 RshinyApp-RiskOfBias-FirstReviewer/server.R

@@ -1,0 +1,449 @@
+######ROB application: Reviewer 1####
+
+library(shiny)
+library(RCurl)
+library(shinyjs)
+
+source("config.R")
+source("shared.R")
+
+#1. sb - selection bias 2. rr - responnse rate 
+#3. sbrr - selection bias & response rate 4. ib - information bias
+#5. si - selective or incomplete 6. final comments - fc
+
+
+postnew <- function(id, user, sbreport,sbselect,sbcomments,rrselect1,rrselect2,rrcomment1,rrcomment2,rrcomment3,rrcomment4,sbrrselect,sbrrcomment,ibcomment,ibselect,ibcomment2,ibselect2,ibcomment3,ibcheck1,ibcheck2,ibcheck3,ibcheck4,ibcheck5,ibcomment4,ibselect3,ibcomment5,siselect1,siselect2,sicomment,fcselect,fccomment,robcluster,sbreportc2,sbselectc2,rrselect1c2,rrselect2c2,rrcomment1c2,rrcomment2c2,rrcomment3c2,sbrrselectc2,ibselectc2,ibselect2c2,ibcheck1c2,ibcheck2c2,ibcheck3c2,ibcheck4c2,ibcheck5c2,ibcheck6c2,ibselect3c2,siselect1c2,siselect2c2,fcselectc2){
[…]

### 2021-12-22 RshinyApp-RiskOfBias-FirstReviewer/ui.R

@@ -1,0 +1,23 @@
+
+
+library(RCurl)
+library(shiny)
+
+
+
+source("config.R")
+source("shared.R")
+
+ui <- fluidPage(
+  tags$head(tags$style(HTML(" body { margin:0.4%; "))),
+  titlePanel(HTML("COVID ROB: Asymptomatics (Reviewer 1)"), windowTitle="COVID ROB APP"),
+  fluidRow(shinyjs::useShinyjs(),
+           #h4(paste("user selection:",user)),
+           textOutput("server_response", inline = T),
+           textOutput("login_response", inline = T), br(),
+           selectInput('in1', 'Select user:', c(Choose='', logins$users), selectize=FALSE),
+           passwordInput('passw', 'Code', value = ""),
+           actionButton("add", "Show data!"),
+           br()
+  )
+)

### 2021-12-23 Q1.R
update scripts

@@ -17,8 +17,7 @@ library(metafor)
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-#APIs token is not sharable
-token <- "##################################"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
 formData <- list("token"=token,
                  content='report',
                  format='csv',
@@ -130,9 +129,9 @@ asym_plot<-metaprop(events,total,data=data,sm = "PLOGIT", studlab=label,
 asym_plot
 
 tiff(filename = "Q1_update5.tiff",
-     width = 4000, height = 11000,
+     width = 4000, height = 12000,
      res = 400)
-forest(asym_plot, sortvar = 1/seTE, #sorted by study precision
+forest(asym_plot, sortvar = total, #sorted by study precision
        #subgroup=TRUE,
        col.square = "darkblue",
        just="left", colgap.studlab="1cm",
@@ -143,11 +142,15 @@ dev.off()
 
 #cut data at end of jan 31
 
+#published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+# data <- data %>%
+#   filter(record_id <= 5296 | record_id %in% published_preprints)
+
+#10.12.21 - updated HI
 published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
 #include additional study identified from ref list
 additional <- 11099
 data <- data %>%
-#<<<<<<< HEAD
   filter(record_id <= 5296 | 
            record_id %in% published_preprints | 
            record_id %in% additional)
@@ -165,6 +168,7 @@ asym_plot<-metaprop(events,total,data=data,sm = "PLOGIT", studlab=label,
                     prediction = TRUE,
                     print.byvar = FALSE,
                     comb.fixed = FALSE,
+                    overall.hetstat = FALSE,
                     control=list(stepadj=0.05, maxiter=10000))#, method ="INV") #, verbose=TRUE, digits=5, control=list(stepadj=0.5))
 
 asym_plot
@@ -172,10 +176,21 @@ asym_plot
 tiff(filename = "Q1.tiff",
      width = 4000, height = 9500,
      res = 400)
-forest(asym_plot, sortvar = 1/seTE, #sorted by study precision
+forest(asym_plot, sortvar = total, #sorted by study precision
        #subgroup=TRUE,
        col.square = "darkblue",
[…]

### 2021-12-23 Q1_stratified_all_settings.R

@@ -1,0 +1,166 @@
+
+#download packages
+library(meta)
+library(readxl)
+library(tidyverse)
+library(httr) # use to retrieve data from REDCap
+library(kableExtra)
+library(flextable)
+library(dplyr)
+library(RCurl)
+library(tidyr)
+library(ggplot2)
+library(metafor)
+
+
+#download data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+
+##########################################
+# Q1 forest plot
+##########################################
+
+asymptomaticQ1 <- httr::content(response)
+
+
+settings=c("Contact investigation",
+           "Contact investigation, aggregated",
+           "Outbreak investigation",
+           "Statistical model",
+           "Screening",
+           "Hospitalised adults",
+           "Hospitalised children",
+           "Hospitalised adults & children",
+           "Screening: institutional setting",
+           "Screening: community setting",
+           "Screening: occupational")
+
+
+asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:11, labels=settings)
+#combine contact investigation and contact investigation aggregated
+asymptomaticQ1$setting2[asymptomaticQ1$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"
+
+# minor cleaning
+asymptomaticQ1[asymptomaticQ1==9999]=NA
+
+
+asymptomaticQ1$setting = asymptomaticQ1$setting2
+
+
+
+
+data_long1 <- gather(asymptomaticQ1, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
[…]

### 2021-12-23 S3_countries.Rmd
rename files

---
title: "S4_countries"
author: "L Heron"
date: "11/5/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

###############################################################
# Question 1: results output                         ##########
# Proportion of asymptomatic cases                   ##########
###############################################################

#load the libraries
library(meta)
library(readxl)
library(tidyverse)
library(httr) # use to retrieve data from REDCap
library(kableExtra)
library(flextable)
library(dplyr)
library(Rcpp)

##########################################
# table on characteristics of Q1 studies
##########################################

#download data
# get the data directly from redcap:
# report #155 is Q1:
url <- "https://redcap.ispm.unibe.ch/api/"
token <- "F2725F15FE84D2832E2793BB23B0A62B"
formData <- list("token"=token,
                 content='report',
                 format='csv',
                 report_id='155',
                 csvDelimiter='',
                 rawOrLabel='raw',
                 rawOrLabelHeaders='raw',
                 exportCheckboxLabel='false',
                 returnFormat='csv'
)
response <- httr::POST(url, body = formData, encode = "form")
Q1_table_countries <- httr::content(response)

#clean countries
Q1_table_countries <- Q1_table_countries %>%
  mutate(country = ifelse(country == 10, "Australia", country),
         country = ifelse(country == 11, "Austria", country),
         country = ifelse(country == 15, "Bahrain", country),
         country = ifelse(country == 19, "Belgium", country),
         country = ifelse(country == 28, "Brunei", country),
         country = ifelse(country == 34, "Canada", country),
         country = ifelse(country == 40, "China", country),
         country = ifelse(country == 41, "Colombia", country),
         country = ifelse(country == 51, "Denmark", country),
         country = ifelse(country == 62, "France", country),
         country = ifelse(country == 63, "French Guyana", country),
         country = ifelse(country == 67, "Germany", country),
         country = ifelse(country == 69, "Greece", country),
         country = ifelse(country == 78, "Iceland", country),
         country = ifelse(country == 79, "India", country),
         country = ifelse(country == 83, "Ireland", country),
         country = ifelse(country == 85, "Italy", country),
         country = ifelse(country == 87, "Japan", country),
         country = ifelse(country == 92, "Kuwait", country),
         country = ifelse(country == 105, "Malaysia", country),
         country = ifelse(country == 121, "Netherlands", country),
         country = ifelse(country == 128, "Norway", country),
         country = ifelse(country == 888, "Other", country),
         country = ifelse(country == 138, "Portugal", country),
         country = ifelse(country == 146, "Saudi Arabia", country),
         country = ifelse(country == 157, "South Korea", country),
         country = ifelse(country == 160, "Spain", country),
         country = ifelse(country == 174, "Turkey", country),
         country = ifelse(country == 176, "Uganda", country),
         country = ifelse(country == 180, "United Kingdom", country),
         country = ifelse(country == 181, "United States of America", country),
         country = ifelse(country == 185, "Vietnam", country))

#clean case numbers
#total SARS-CoV-2 n
Q1_table_countries$q1_c1_total[is.na(Q1_table_countries$q1_c1_total)] <- 0
Q1_table_countries$q1_c2_total[is.na(Q1_table_countries$q1_c2_total)] <- 0
Q1_table_countries$q1_c1_event[is.na(Q1_table_countries$q1_c1_event)] <- 0
Q1_table_countries$q1_c2_event[is.na(Q1_table_countries$q1_c2_event)] <- 0

Q1_table_countries$total_SARS_n <- Q1_table_countries$q1_c1_total + Q1_table_countries$q1_c2_total
Q1_table_countries$asymp_SARS_n <- Q1_table_countries$q1_c1_event + Q1_table_countries$q1_c2_event

#remove unnecessary cols
Q1_table_countries <- Q1_table_countries %>%
  select(country, total_SARS_n, asymp_SARS_n)

#group by countries to calculate n, total cases, total asymp cases
Q1_table_countries <- Q1_table_countries %>%
  group_by(country) %>%
  summarise(total_SARS = sum(total_SARS_n),
            total_asymp_SARS = sum(asymp_SARS_n),
            n = n())

#arrange by number of studies
Q1_table_countries <- Q1_table_countries %>%
  arrange(desc(n))

table1_countries <- flextable(Q1_table_countries)

table1_countries %>% 
  set_header_labels(country = "Country",
                    total_SARS = "Total SARS-CoV-2, n",
                    total_asymp_SARS = "Total asymptomatic SARS-CoV-2, n",
                    n = "Total number of studies") %>%
  set_table_properties(layout = "autofit") %>%
  theme_vanilla()

```

## Location of studies contributing data to review questions 1 and 2.1.

```{r table1, ft.split=TRUE, tab.cap='Table 1. Location of studies contributing data to review questions 1', echo = FALSE}
table1_countries <- flextable(Q1_table_countries)

table1_countries %>% 
  set_header_labels(country = "Country",
                    total_SARS = "Total SARS-CoV-2, n",
                    total_asymp_SARS = "Total asymptomatic SARS-CoV-2, n",
                    n = "Total number of studies") %>%
  set_table_properties(layout = "autofit") %>%
  theme_vanilla()
```

### 2021-12-23 Q1.R
Update Q1.R

@@ -135,7 +135,7 @@ forest(asym_plot, sortvar = total, #sorted by study precision
        #subgroup=TRUE,
        col.square = "darkblue",
        just="left", colgap.studlab="1cm",
-       predict=T, comb.random = TRUE, comb.fixed = FALSE,
+       predict=T, comb.random = FALSE, comb.fixed = FALSE,
        print.byvar = FALSE, overall = FALSE)
 dev.off() 
 
@@ -180,7 +180,7 @@ forest(asym_plot, sortvar = total, #sorted by study precision
        #subgroup=TRUE,
        col.square = "darkblue",
        just="left", colgap.studlab="1cm",
-       predict=T, comb.random = TRUE, comb.fixed = FALSE,
+       predict=T, comb.random = FALSE, comb.fixed = FALSE,
        overall.hetstat = FALSE,
        print.byvar = FALSE, overall = FALSE)
 dev.off() 

### 2021-12-23 Q1.R
Update Q1.R

@@ -176,6 +176,7 @@ asym_plot
 tiff(filename = "Q1.tiff",
      width = 4000, height = 9500,
      res = 400)
+#without pooled estimate
 forest(asym_plot, sortvar = total, #sorted by study precision
        #subgroup=TRUE,
        col.square = "darkblue",
@@ -184,6 +185,17 @@ forest(asym_plot, sortvar = total, #sorted by study precision
        overall.hetstat = FALSE,
        print.byvar = FALSE, overall = FALSE)
 dev.off() 
+
+# #with pooled estimate
+
+# forest(asym_plot, sortvar = total, #sorted by study precision
+#        #subgroup=TRUE,
+#        col.square = "darkblue",
+#        just="left", colgap.studlab="1cm",
+#        predict=T, comb.random = TRUE, comb.fixed = FALSE,
+#        overall.hetstat = FALSE,
+#        print.byvar = FALSE, overall = FALSE)
+
 
 pdf("Q1.pdf", width = 10, height = 24)
 forest(asym_plot, sortvar = total, #sorted by study precision

### 2021-12-23 Q2_1.R
Update Q2_1.R

@@ -96,7 +96,7 @@ q2_1_asymp <- metabin(event.e = Ee,
                       hakn = TRUE,
                       MH.exact = TRUE, 
                       byvar = group,
-                      comb.random = TRUE,
+                      comb.random = FALSE, #TRUE,
                       comb.fixed = FALSE, 
                       label.e = "",
                       label.c = "Symp.  ")

### 2021-12-23 Q2_1.R
update

@@ -96,7 +96,7 @@ q2_1_asymp <- metabin(event.e = Ee,
                       hakn = TRUE,
                       MH.exact = TRUE, 
                       byvar = group,
-                      comb.random = FALSE, #TRUE,
+                      comb.random = TRUE,
                       comb.fixed = FALSE, 
                       label.e = "",
                       label.c = "Symp.  ")

### 2021-12-23 Q2_1.R
Add files via upload

@@ -19,8 +19,7 @@ library(metafor)
 # get the data directly from redcap: 
 # report #172 is Q2.1 SAR:
 url <- "https://redcap.ispm.unibe.ch/api/"
-#APIs token is not sharable
-token <- "##################################"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
 formData2_1 <- list("token"=token,
                     content='report',
                     format='csv',
@@ -48,6 +47,8 @@ asymptomaticQ2_1=asymptomaticQ2_1%>% #separate asymp SAR into 2 variables
 asymptomaticQ2_1=asymptomaticQ2_1%>% #separate presymp SAR into 2 variables
   separate(q3_sar_p, c("Ee_p","Ne_p"), ";", remove=FALSE) 
 
+
+
 asymptomaticQ2_1=asymptomaticQ2_1 %>% #change values to numeric
   mutate(Ec=as.numeric(Ec),
          Nc=as.numeric(Nc),
@@ -72,15 +73,57 @@ q2_1_df_p <- asymptomaticQ2_1 %>%
 #bind rows
 q2_1_df <- bind_rows(q2_1_df_a, q2_1_df_p)
 
-#cut data at end of jan 31
-published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
-q2_1_df <- q2_1_df %>%
-  filter(record_id <= 5296 | record_id %in% published_preprints)
+#rename groups
+q2_1_df$group[q2_1_df$group == "Presymptomatic"] <- "Presymptomatic vs. Symptomatic"
+q2_1_df$group[q2_1_df$group == "Asymptomatic"] <- "Asymptomatic vs. Symptomatic"
+q2_1_df$group[q2_1_df$record_id == 821] <- "Asymptomatic vs. Presymptomatic"
+
+
 
 #add columns for forest plot
 q2_1_df$col_1 <- paste0(q2_1_df$Ee, "/", q2_1_df$Ne, sep = "")
 
 q2_1_df$col_2 <- paste0(q2_1_df$Ec, "/", q2_1_df$Nc, sep = "")
+
+
+#run meta analysis for all available studies
+#metaanalysis for asymptomatic transmission
+
+q2_1_asymp <- metabin(event.e = Ee,
+                      n.e = Ne,
+                      event.c = Ec,
+                      n.c = Nc, 
+                      data = q2_1_df,
+                      studlab = author_1,
+                      prediction = TRUE,
+                      sm = "RR",
+                      method = "MH",
[…]

### 2021-12-23 Q2_1.R
Update Q2_1.R

@@ -101,7 +101,7 @@ q2_1_asymp <- metabin(event.e = Ee,
                       hakn = TRUE,
                       MH.exact = TRUE, 
                       byvar = group,
-                      comb.random = TRUE,
+                      comb.random = FALSE, #with pooled estimate set it to TRUE,
                       comb.fixed = FALSE,
                       print.byvar = FALSE,
                       label.e = "",
@@ -139,7 +139,7 @@ q2_1_asymp <- metabin(event.e = Ee,
                       hakn = TRUE,
                       MH.exact = TRUE, 
                       byvar = group,
-                      comb.random = TRUE,
+                      comb.random = FALSE, #with pooled estimate set it to TRUE,
                       print.byvar = FALSE,
                       comb.fixed = FALSE, 
                       label.e = "",

### 2021-12-23 Q1.R
Update Q1.R

@@ -135,18 +135,27 @@ forest(asym_plot, sortvar = total, #sorted by study precision
        #subgroup=TRUE,
        col.square = "darkblue",
        just="left", colgap.studlab="1cm",
-       predict=T, comb.random = FALSE, comb.fixed = FALSE,
+       predict=T, comb.random = TRUE, comb.fixed = FALSE,
        print.byvar = FALSE, overall = FALSE)
 dev.off() 
 
 
+#without pooled estimates
+
+# tiff(filename = "Q1_update5.tiff",
+#      width = 4000, height = 12000,
+#      res = 400)
+# forest(asym_plot, sortvar = total, #sorted by study precision
+#        #subgroup=TRUE,
+#        col.square = "darkblue",
+#        just="left", colgap.studlab="1cm",
+#        predict=T, comb.random = TRUE, comb.fixed = FALSE,
+#        print.byvar = FALSE, overall = FALSE)
+# dev.off()
+
 #cut data at end of jan 31
 
-#published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
-# data <- data %>%
-#   filter(record_id <= 5296 | record_id %in% published_preprints)
-
-#10.12.21 - updated HI
+#10.12.21
 published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
 #include additional study identified from ref list
 additional <- 11099

### 2021-12-23 Q1.R
new ROB figures

@@ -140,22 +140,13 @@ forest(asym_plot, sortvar = total, #sorted by study precision
 dev.off() 
 
 
-#without pooled estimates
-
-# tiff(filename = "Q1_update5.tiff",
-#      width = 4000, height = 12000,
-#      res = 400)
-# forest(asym_plot, sortvar = total, #sorted by study precision
-#        #subgroup=TRUE,
-#        col.square = "darkblue",
-#        just="left", colgap.studlab="1cm",
-#        predict=T, comb.random = TRUE, comb.fixed = FALSE,
-#        print.byvar = FALSE, overall = FALSE)
-# dev.off()
-
 #cut data at end of jan 31
 
-#10.12.21
+#published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
+# data <- data %>%
+#   filter(record_id <= 5296 | record_id %in% published_preprints)
+
+#10.12.21 - updated HI
 published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
 #include additional study identified from ref list
 additional <- 11099
@@ -185,26 +176,14 @@ asym_plot
 tiff(filename = "Q1.tiff",
      width = 4000, height = 9500,
      res = 400)
-#without pooled estimate
 forest(asym_plot, sortvar = total, #sorted by study precision
        #subgroup=TRUE,
        col.square = "darkblue",
        just="left", colgap.studlab="1cm",
-       predict=T, comb.random = FALSE, comb.fixed = FALSE,
+       predict=T, comb.random = TRUE, comb.fixed = FALSE,
        overall.hetstat = FALSE,
        print.byvar = FALSE, overall = FALSE)
 dev.off() 
-
-# #with pooled estimate
-
-# forest(asym_plot, sortvar = total, #sorted by study precision
-#        #subgroup=TRUE,
-#        col.square = "darkblue",
-#        just="left", colgap.studlab="1cm",
-#        predict=T, comb.random = TRUE, comb.fixed = FALSE,
-#        overall.hetstat = FALSE,
-#        print.byvar = FALSE, overall = FALSE)
-
 
 pdf("Q1.pdf", width = 10, height = 24)
 forest(asym_plot, sortvar = total, #sorted by study precision

### 2021-12-23 Q1.R
New ROB figures

@@ -215,14 +215,42 @@ forest(asym_plot, sortvar = total, #sorted by study precision
        just="left", colgap.studlab="1cm",
        predict=TRUE, comb.random = TRUE, comb.fixed = FALSE)
 dev.off() 
+pdf("Q1_notstratified.pdf", width = 10, height = 23)
+forest(asym_plot, sortvar = total, #sorted by study precision
+       col.square = "darkblue",
+       overall.hetstat = FALSE,
+       just="left", colgap.studlab="1cm",
+       predict=TRUE, comb.random = TRUE, comb.fixed = FALSE)
+dev.off() 
 
 #####
-#subgroup analysis
+#subgroup analysis for rob
+
+
+#download data
+# get the data directly from redcap:
+# report #155 is Q1:
+url <- "https://redcap.ispm.unibe.ch/api/"
+token <- "F2725F15FE84D2832E2793BB23B0A62B"
+formData <- list("token"=token,
+                 content='report',
+                 format='csv',
+                 report_id='155',
+                 csvDelimiter='',
+                 rawOrLabel='raw',
+                 rawOrLabelHeaders='raw',
+                 exportCheckboxLabel='false',
+                 returnFormat='csv'
+)
+response <- httr::POST(url, body = formData, encode = "form")
+
 #studies removed at high risk of selection bias
 #studies 443, 597, 1960, 2802, 2907, 3921, 5068, 5238, 170, 2987, 5086, 1225, 4880
 high_risk_select_bias <-c(443, 597, 1960, 2802, 2907, 3921, 5068, 5238, 170, 2987, 5086, 1225, 4880)
 data_selectionbias <- data %>%
   filter(!record_id %in% high_risk_select_bias)
+data_selectionbias <- data %>%
+  
 
 #run metaprop and forest plot
 
@@ -248,6 +276,18 @@ forest(asym_plot_select_bias, sortvar = total, #sorted by study precision
        test.subgroup.random=TRUE, test.subgroup.fixed=FALSE)
 dev.off() 
 
+pdf(filename = "Q1_select_bias.tiff")
+forest(asym_plot_select_bias, sortvar = total, #sorted by study precision
+       subgroup=TRUE,
+       col.square = "darkblue",
+       overall.hetstat = FALSE,
+       just="left", colgap.studlab="1cm",
+       predict=T, comb.random = TRUE, comb.fixed = FALSE,
[…]

### 2021-12-23 Q1.R
Update Q1.R

@@ -17,7 +17,7 @@ library(metafor)
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+token <- "################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',
@@ -51,6 +51,7 @@ settings=c("Contact investigation",
 
 
 asymptomaticQ1$setting2<-factor(asymptomaticQ1$setting2, levels=1:11, labels=settings)
+
 #combine contact investigation and contact investigation aggregated
 asymptomaticQ1$setting2[asymptomaticQ1$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"
 
@@ -139,14 +140,23 @@ forest(asym_plot, sortvar = total, #sorted by study precision
        print.byvar = FALSE, overall = FALSE)
 dev.off() 
 
+##=======without pooled estimates
+
+# tiff(filename = "Q1_update5.tiff",
+#      width = 4000, height = 12000,
+#      res = 400)
+# forest(asym_plot, sortvar = total, #sorted by study precision
+#        #subgroup=TRUE,
+#        col.square = "darkblue",
+#        just="left", colgap.studlab="1cm",
+#        predict=T, comb.random = FALSE, comb.fixed = FALSE,
+#        print.byvar = FALSE, overall = FALSE)
+# dev.off() 
+
+
 
 #cut data at end of jan 31
 
-#published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
-# data <- data %>%
-#   filter(record_id <= 5296 | record_id %in% published_preprints)
-
-#10.12.21 - updated HI
 published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
 #include additional study identified from ref list
 additional <- 11099
@@ -185,6 +195,20 @@ forest(asym_plot, sortvar = total, #sorted by study precision
        print.byvar = FALSE, overall = FALSE)
 dev.off() 
 
+##=======without pooled estimates
+# tiff(filename = "Q1.tiff",
+#      width = 4000, height = 9500,
+#      res = 400)
+# forest(asym_plot, sortvar = total, #sorted by study precision
+#        #subgroup=TRUE,
+#        col.square = "darkblue",
[…]

### 2021-12-23 Q1.R
Update Q1.R

@@ -264,7 +264,7 @@ dev.off()
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+token <- "################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',
@@ -327,7 +327,7 @@ dev.off()
 
 # get the data directly from redcap:
 urlrob <- "https://redcap.ispm.unibe.ch/api/"
-tokenrob <- "F2725F15FE84D2832E2793BB23B0A62B"
+tokenrob <- "################################"
 formDatarob <- list("token"=tokenrob,
                     content='report',
                     format='csv',
@@ -645,7 +645,7 @@ Q1_data_region <- Q1_data %>%
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+token <- "################################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',

### 2021-12-23 Q2_1.R
Update Q2_1.R

@@ -19,7 +19,7 @@ library(metafor)
 # get the data directly from redcap: 
 # report #172 is Q2.1 SAR:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+token <- "####################################"
 formData2_1 <- list("token"=token,
                     content='report',
                     format='csv',

### 2021-12-23 Q2_1.R
Update Q2_1.R

@@ -101,7 +101,7 @@ q2_1_asymp <- metabin(event.e = Ee,
                       hakn = TRUE,
                       MH.exact = TRUE, 
                       byvar = group,
-                      comb.random = FALSE, #with pooled estimate set it to TRUE,
+                      comb.random = TRUE, #with pooled estimate set it to FALSE,
                       comb.fixed = FALSE,
                       print.byvar = FALSE,
                       label.e = "",
@@ -139,7 +139,7 @@ q2_1_asymp <- metabin(event.e = Ee,
                       hakn = TRUE,
                       MH.exact = TRUE, 
                       byvar = group,
-                      comb.random = FALSE, #with pooled estimate set it to TRUE,
+                      comb.random = TRUE, #without pooled estimate set it to FALSE,
                       print.byvar = FALSE,
                       comb.fixed = FALSE, 
                       label.e = "",
@@ -148,7 +148,7 @@ q2_1_asymp
 
 
 tiff(filename = "Q2_1.tiff",
-     width = 2450, height = 1600,
+     width = 2450, height = 1800,
      res = 300)
 forest(q2_1_asymp, sortvar = (1/(sqrt(seTE))), overall = FALSE,
        overall.hetstat = FALSE,

### 2021-12-23 SF_Q1_by_precision.R
delete unnecessary files

@@ -1,78 +1,0 @@
-###############################################################
-# Supplementary material                        ##########
-# Q1 - studies ordered by precision                   ##########
-###############################################################
-
-
-#load the libraries
-library(meta)
-library(readxl)
-library(tidyverse)
-library(httr) # use to retrieve data from REDCap
-
-# Prepare the data
-# get the data directly from redcap:
-# report #155 is Q1:
-url <- "https://redcap.ispm.unibe.ch/api/"
-#APIs token is not sharable
-token <- "##################################"
-formData <- list("token"=token,
-                 content='report',
-                 format='csv',
-                 report_id='155',
-                 csvDelimiter='',
-                 rawOrLabel='raw',
-                 rawOrLabelHeaders='raw',
-                 exportCheckboxLabel='false',
-                 returnFormat='csv'
-)
-response <- httr::POST(url, body = formData, encode = "form")
-asymptomaticQ1 <- httr::content(response)
-
-# minor cleaning
-asymptomaticQ1[asymptomaticQ1 == 9999] = NA
-
-asymptomaticQ1$setting = asymptomaticQ1$setting2
-
-
-data_long1 <- gather(asymptomaticQ1, cluster, total, c(q1_c1_total,q1_c2_total,q1_c3_total), factor_key=TRUE) %>% 
-  mutate(id=1:nrow(.)) %>%
-  select(record_id, author_1, total, id, cluster)
-data_long2 <-gather(asymptomaticQ1, cluster, events, c(q1_c1_event,q1_c2_event,q1_c3_event), factor_key=TRUE) %>% 
-  mutate(id=1:nrow(.)) %>%
-  select(events, id)
-
-data_Q1 = merge(data_long1, data_long2, by="id")
-data_Q1 = data_Q1[!is.na(data_Q1$total),]
-data_Q1$cluster = factor(data_Q1$cluster, labels = c("1","2","3"), levels = c("q1_c1_total", "q1_c2_total", "q1_c3_total"))
-
-data_Q1[data_Q1$record_id %in% asymptomaticQ1[is.na(asymptomaticQ1$q1_c2_event),]$record_id,]$cluster=NA
-
-asymptomaticQ1 <- data_Q1
-
-asymptomaticQ1$label=paste0(asymptomaticQ1$author_1, " (2020)",
-                            ifelse(!is.na(asymptomaticQ1$cluster),
[…]

### 2021-12-23 SF_Q1_by_source.R

@@ -1,124 +1,0 @@
-###############################################################
-# Question 1: results output                         ##########
-# Proportion of asymptomatic cases                   ##########
-# Supplementary material: preprints removed          ##########
-###############################################################
-
-#load the libraries
-library(meta)
-library(readxl)
-library(tidyverse)
-library(httr) # use to retrieve data from REDCap
-library(kableExtra)
-library(flextable)
-library(dplyr)
-library(Rcpp)
-
-
-# Prepare the data
-# get the data directly from redcap:
-# report #155 is Q1:
-url <- "https://redcap.ispm.unibe.ch/api/"
-#APIs token is not sharable
-token <- "##################################"
-formData <- list("token"=token,
-                 content='report',
-                 format='csv',
-                 report_id='155',
-                 csvDelimiter='',
-                 rawOrLabel='raw',
-                 rawOrLabelHeaders='raw',
-                 exportCheckboxLabel='false',
-                 returnFormat='csv'
-)
-response <- httr::POST(url, body = formData, encode = "form")
-asymptomaticQ1_pub <- httr::content(response)
-
-
-settings=c("Contact investigation",
-           "Contact investigation, aggregated",
-           "Outbreak investigation",
-           "Statistical model",
-           "Screening",
-           "Hospitalised adults",
-           "Hospitalised children",
-           "Hospitalised adults & children")
-
-
-asymptomaticQ1_pub$setting2<-factor(asymptomaticQ1_pub$setting2, levels=1:8, labels=settings)
-#combine contact investigation and contact investigation aggregated
-asymptomaticQ1_pub$setting2[asymptomaticQ1_pub$setting2 == "Contact investigation, aggregated"] <- "Contact investigation"
-
-# minor cleaning
-asymptomaticQ1_pub[asymptomaticQ1_pub==9999]=NA
-
[…]

### 2021-12-23 SF_Q1_countries.R

@@ -1,63 +1,0 @@
-###############################################################
-# SF: Prepare countries in Q1, Q2.1, Q2.2            ##########
-###############################################################
-
-#load the libraries
-library(meta)
-library(readxl)
-library(tidyverse)
-library(httr) # use to retrieve data from REDCap
-
-# Prepare the data
-# get the data directly from redcap:
-# report #155 is Q1:
-url <- "https://redcap.ispm.unibe.ch/api/"
-#APIs token is not sharable
-token <- "##################################"
-formData <- list("token"=token,
-                 content='report',
-                 format='csv',
-                 report_id='155',
-                 csvDelimiter='',
-                 rawOrLabel='raw',
-                 rawOrLabelHeaders='raw',
-                 exportCheckboxLabel='false',
-                 returnFormat='csv'
-)
-response <- httr::POST(url, body = formData, encode = "form")
-asymptomaticQ1 <- httr::content(response)
-
-#only keep required variables
-countries_q1 <- asymptomaticQ1 %>%
-  select(record_id, author_1, country, region) %>%
-  mutate(country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 40, "China", country),
-         country = ifelse(country == 87, "Japan", country),
-         country = ifelse(country == 62, "France", country),
-         country = ifelse(country == 85, "Italy", country),
-         country = ifelse(country == 67, "Germany", country),
-         country = ifelse(country == 157, "South Korea", country),
-         country = ifelse(country == 181, "United States of America", country),
-         country = ifelse(country == 28, "Brunei", country),
-         country = ifelse(country == 180, "United Kingdom", country),
-         country = ifelse(country == 185, "Vietnam", country),
-         country = ifelse(country == 138, "Portugal", country),
-         country = ifelse(country == 83, "Ireland", country),
-         country = ifelse(country == 92, "Kuwait", country),
-         country = ifelse(country == 160, "Other", country),
-         country = ifelse(country == 69, "Other", country),
-         country = ifelse(country == 170, "Other", country),
-         country = ifelse(country == 10, "Other", country),
-         country = ifelse(country == 34, "Other", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 888, "Other", country),
-         country = ifelse(country == 888, "Other", country),
[…]

### 2021-12-23 SF_Q1_table_countries.R

@@ -1,111 +1,0 @@
-###############################################################
-# Question 1: results output                         ##########
-# Proportion of asymptomatic cases                   ##########
-###############################################################
-
-#load the libraries
-library(meta)
-library(readxl)
-library(tidyverse)
-library(httr) # use to retrieve data from REDCap
-library(kableExtra)
-library(flextable)
-library(dplyr)
-library(Rcpp)
-
-
-##########################################
-# table on characteristics of Q1 studies
-##########################################
-
-#download data
-# get the data directly from redcap:
-# report #155 is Q1:
-url <- "https://redcap.ispm.unibe.ch/api/"
-#APIs token is not sharable
-token <- "##################################"
-formData <- list("token"=token,
-                 content='report',
-                 format='csv',
-                 report_id='155',
-                 csvDelimiter='',
-                 rawOrLabel='raw',
-                 rawOrLabelHeaders='raw',
-                 exportCheckboxLabel='false',
-                 returnFormat='csv'
-)
-response <- httr::POST(url, body = formData, encode = "form")
-Q1_table_countries <- httr::content(response)
-
-#clean countries
-Q1_table_countries <- Q1_table_countries %>%
-  mutate(country = ifelse(country == 10, "Australia", country),
-         country = ifelse(country == 11, "Austria", country),
-         country = ifelse(country == 15, "Bahrain", country),
-         country = ifelse(country == 19, "Belgium", country),
-         country = ifelse(country == 28, "Brunei", country),
-         country = ifelse(country == 34, "Canada", country),
-         country = ifelse(country == 40, "China", country),
-         country = ifelse(country == 41, "Colombia", country),
-         country = ifelse(country == 51, "Denmark", country),
-         country = ifelse(country == 62, "France", country),
-         country = ifelse(country == 63, "French Guyana", country),
-         country = ifelse(country == 67, "Germany", country),
-         country = ifelse(country == 69, "Greece", country),
-         country = ifelse(country == 78, "Iceland", country),
-         country = ifelse(country == 79, "India", country),
-         country = ifelse(country == 83, "Ireland", country),
-         country = ifelse(country == 85, "Italy", country),
[…]

### 2021-12-23 SF_Q2.1_by_precision.R

@@ -1,112 +1,0 @@
-###############################################################
-# Question 2.1: results output ################################
-# Secondary attack rate from asymp or pre-symp cases ##########
-###############################################################
-
-
-#load libraries
-library(RCurl)
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(meta)
-library(metafor)
-library(flextable)
-
-# get the data directly from redcap: 
-# report #172 is Q2.1 SAR:
-url <- "https://redcap.ispm.unibe.ch/api/"
-#APIs token is not sharable
-token <- "##################################"
-formData2_1 <- list("token"=token,
-                    content='report',
-                    format='csv',
-                    report_id='172',
-                    csvDelimiter='',
-                    rawOrLabel='raw',
-                    rawOrLabelHeaders='raw',
-                    exportCheckboxLabel='false',
-                    returnFormat='json'
-)
-response2_1 <- httr::POST(url, body = formData2_1, encode = "form")
-asymptomaticQ2_1 <- httr::content(response2_1)
-
-#clean data
-asymptomaticQ2_1[asymptomaticQ2_1=="9999;9999"]=NA #indicate as missing
-asymptomaticQ2_1[asymptomaticQ2_1=="9999"]=NA #indicate as missing
-asymptomaticQ2_1=asymptomaticQ2_1%>% #separate symp SAR into 2 variables
-  separate(q3_sar_s, c("Ec","Nc"), ";", remove=FALSE) 
-asymptomaticQ2_1=asymptomaticQ2_1%>% #separate asymp SAR into 2 variables
-  separate(q3_sar_a, c("Ee_a","Ne_a"), ";", remove=FALSE) 
-asymptomaticQ2_1=asymptomaticQ2_1%>% #separate presymp SAR into 2 variables
-  separate(q3_sar_p, c("Ee_p","Ne_p"), ";", remove=FALSE) 
-
-asymptomaticQ2_1=asymptomaticQ2_1 %>% #change values to numeric
-  mutate(Ec=as.numeric(Ec),
-         Nc=as.numeric(Nc),
-         Ee_a=as.numeric(Ee_a),
-         Ne_a=as.numeric(Ne_a),
-         Ee_p=as.numeric(Ee_p),
-         Ne_p=as.numeric(Ne_p))
-
-#create new df with asymp/presymp as subgroups
-q2_1_df_a <- asymptomaticQ2_1 %>%
-  select("record_id", "author_1", "Ee_a", "Ne_a", "Ec", "Nc", "region", "year") %>%
[…]

### 2021-12-23 Q1_stratified_all_settings.R
Update Q1_stratified_all_settings.R

@@ -17,7 +17,7 @@ library(metafor)
 # get the data directly from redcap:
 # report #155 is Q1:
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+token <- "###############################"
 formData <- list("token"=token,
                  content='report',
                  format='csv',
@@ -131,7 +131,7 @@ forest(asym_plot, sortvar = 1/seTE, #sorted by study precision
        print.byvar = FALSE, overall = FALSE)
 dev.off() 
 
-#10.12.21 - updated HI
+
 published_preprints <-c(5565,6219, 6685, 7030, 7465, 8249, 9442, 9484)
 #include additional study identified from ref list
 additional <- 11099

### 2021-12-23 Q1_table_characteristics_full.Rmd
hide APIs

@@
 url <- "https://redcap.ispm.unibe.ch/api/"
-token <- "F2725F15FE84D2832E2793BB23B0A62B"
+token <- "################################"
 formData <- list("token"=token,
